### 2015-08-15 Docs/Paper/LaTex/template.tex
Added Latex Article

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

\begin{document}
\title{Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems}

\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galvao\and Lucas Cordeiro}

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
\maketitle

\begin{abstract}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing. The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker. Each instance checks for a different optimum value until the optimization problem is satisfied. The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. We compare the experimental results of our proposed approach with Integer Linear Programming and the Genetic Algorithm.
\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
\end{abstract}

\section{Introduction}
Nowadays, with the strong development of embedded systems, the design phase plays an important role. At early stages, the design is split into separated flows: hardware and software. Consequently, the partitioning decision process, which deals with the decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology. If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affects the overall development process, the quality and the lifecycle of the final system. Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in [1] and [2].
In any HW and SW design of complex systems, more time is spent on verification than on construction [3]. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification [4]. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.
In [5] and [6] was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems. The present work extends those studies since there is a substantial improvement in terms of the genetic algorithm and the SMT-based verification method, which has been extended with a multi-core architecture. Multi-core processors have been used in all segments of industry to implement high-performance computing [7]. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution. However, most verification algorithms still disregard the limitations of the CMOS technology, which limits the increase of the chip’s frequency after it reaches 4 GHz.
Here, we exploit the availability of multi-core processors. In particular, a multi-core SMT-based BMC method is applied to the HW-SW partitioning and then is compared to the results with classical integer linear programming (ILP) and genetic algorithm (GA) using a multi-core tool as well. To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
This paper is organized as follows: Section II gives a background on optimization, model checking, and multi-core support with Open MultiProcessing. Section III describes informal and formal mathematical modeling. Section IV describes briefly the binary integer programming and GA algorithms. The SMT-based BMC method is presented in Section V. Section VI presents the experimental evaluation. Section VII discusses related work. Section VIII presents the conclusion and future work.

\section{BACKGROUND}
\subsection{Optimization}
Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9]. In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].
There is no single method available for solving all optimization problems efficiently [9]. The most known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq. (1) shows a typical linear programming problem, where  and  are vectors or matrixes that describe the constraints.

\subsection{Optimization with Vz}
\subsection{Bounded Model Checking with ESBMC}
\subsection{Multi-core ESBMC with OpenMP}
\subsection{Multi-core ESBMC with OpenMP using Binary Search}

\section{Mathematical modeling}
The mathematical modeling was taken from [1], [2].
\subsection{Informal Model (or Assumptions)}
\subsection{Formal Model}

\section{Partitioning problem using ILP-based,Genetic Algorithms}
\label{ILPGA}
The ILP and GA were taken from [5] and [6]. Both use slack variables in order to be possible to represent the constraints and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to function ga of MATLAB [18]: the population size was set from 300 to 500, the Elite count changed from 2 (default value) to 50, and the number of Generations changed from 100* NumberOfVariables (default) to 75.

\section{Analysis of the partitioning problem using ESBMC}
\section{Analysis of the partitioning problem using vZ}
\section{Experimental Evaluation}
\section{Related Work}
\section{Conclusions}
\section{References}

\end{document}

% end of file template.tex

### 2015-08-15 Docs/Paper/LaTex/template.tex
fix eq VI Section

@@
 %
+
+\usepackage{booktabs}
+\usepackage{amsmath}
+\usepackage[utf8]{inputenc} 
 \usepackage{graphicx}
+\usepackage{listings}
+\usepackage{color}
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\lstset{frame=tb,
+  language=c,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{black},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
 %
@@
 \title{Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems}
-
-\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galvao\and Lucas Cordeiro}
-
-\institute{F. Author \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           S. Author \at
-              second address
-}
-
-\date{Received: date / Accepted: date}
+\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Lucas Cordeiro}
+\institute{Electronic and Information Research Center\\Federal University of Amazonas, Brazil}
 \maketitle
@@
 Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in [1] and [2].
+
 In any HW and SW design of complex systems, more time is spent on verification than on construction [3].
@@
 The system models are accompanied by algorithms that systematically explore all the states of the system model.
+
 In [5] and [6] was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
@@
 However, most verification algorithms still disregard the limitations of the CMOS technology, which limits the increase of the chip’s frequency after it reaches 4 GHz.
+
 Here, we exploit the availability of multi-core processors.
@@
 As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
+
 This paper is organized as follows: Section II gives a background on optimization, model checking, and multi-core support with Open MultiProcessing.
@@
 Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].
+
 There is no single method available for solving all optimization problems efficiently [9].
@@
 Eq.
-(1) shows a typical linear programming problem, where  and  are vectors or matrixes that describe the constraints.
+(1) shows a typical linear programming problem, where  and  are vectors or matrixes that describe the constraints
+\begin{equation}
+  minf^t x \: such that  = 
+  \begin{cases}
+    A.x \leq b, \\ 
+    Aeq.x = beq, \\ 
+    x \geq 0.
+  \end{cases}
+\end{equation}
+
+In some cases, the time to find a solution using ILP is impractical.
+Even with the use of powerful computers, a problem can take hours running before an optimal solution is reached.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA [9].
+The only drawback is that the found solution may not be the global minimum or maximum.
 
 \subsection{Optimization with Vz}
+Um solucionador SMT e uma ferramenta com finalidade de verificar a satisfabilidade de formulas baseada em um conjunto de regras SMT.
+Z3 e um solucionador SMT da Microsoft Research, disponibilizado livremente para a comunidade que integra suporte para uma variedade de teorias.
+Z3 tras consigo um solucionador DPLL juntamente de uma máquina de correspondencia para quantificadores.
+Z3 e implementado em C++.
+
+vZ e uma das ferramentas implementadas no solucionador Z3, a funcao base desta ferramenta e otimizar objetivos dentro do contexto logico das restricoes, este se destaca pelas funcoes que dao a possibilidade de formular criterios de otimizacao.
+vZ inclui uma versao incremental de MaxRes para MaxSAT e um Simplex para solucionar numeros sem padrao definido, em seu nucleo MaxSat e responsavel pelas restricoes enquanto OptSMT tem como funcao otimizar objetivos de aritmetica linear.
+Dentre todos os avancos do Z3 usando vZ destaca-se as funcoes: maximize, minimize and assert-soft.
+\begin{itemize}
+\item{\textbf{maximize(T)}
+esta instrucao diz ao solucionador que a variavel T devera ser maximizada, e possível maximizar valores reais, inteiros e vetores de bit.}
+\item{\textbf{minimize(T)}
+esta instrucao diz ao solucionador que a variavel T devera ser minimizada, os tipos aceitos pelo minimize e similar ao maximize.}
+\item{\textbf{Assert-Soft F :weight n}
+a instrucao Assert-soft e uma restricao sobre F, e possível adicionar um peso n, o padrão e 1.} 
+\end{itemize}
+
+Vamos otimizar (K+W), com restrições em (K \textless 2) e (W-K \textless 1), o resultado da otimização descrita no código abaixo é 2, o modelo gerado pelo vZ mostra que K = 1 e W =1.
+
+\begin{lstlisting}
+1. (declare-const K Int) 
+2. (declare-const W Int)
+3. (assert (< K 2)) 
+4. (assert (< (- W K) 1))
+5. (maximize (+ K W)) 
+6. (check-sat)
+\end{lstlisting}
+
+De acordo com [34] a arquitetura do vZ pode ser descrita na imagem XXX, inicialmente as formulas e os objetivos SMT sao reescritos para variaveis do tipo 0-1, posteriormente os objetivos sao convertidos para problemas MaxSAT, se houver muitos objetivos vZ invoca MaxSAT ou OptSMT.
+Para restricoes sob valores reais usando “Box”, vZ combina todas a aritmetica linear e faz chamada para OptSMT.
+Quando usamos “soft constrains” no modo “lexicographic” vZ invoca MaxSAT.
+
+\begin{figure}[ht]
+	\centering
+  \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
+	\caption{vZ Architecture}
+	\label{fig2}
+\end{figure}
+
+Z3 is available for platforms like C, C ++, Java, .NET and Python, it is possible to download the Z3 with vZ in http://z3.codeplex.com.
+API in python was used to formulate the optimization problem on the vZ tool.
+The pseudo code below describes the steps to achieve desired results.
+
 \subsection{Bounded Model Checking with ESBMC}
@@
 \subsection{Multi-core ESBMC with OpenMP using Binary Search}
+The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
+
+Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.
+\begin{figure}[ht]
+	\centering
+  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
+	\caption{gestaucht}
+	\label{fig2}
+\end{figure}
+So the first approach was to remove the Idle time from the parallel loops by creating workers inside the threads to always execute the next step until a violation is find.
+At first though it seemed to be a great improvement but as ESBMC executes almost the same time the steps, there was almost no optimization.
+
+The most optimized approach used was to use a parallelized binary search to reduce the complexity of the tasks.
+So was made a controller to return the best step to execute in order to reduce the domain as maximum as possible.
+This is done by dividing the domain in chunks and than returning the middle of the biggest chunk existent, and creating two new chunks.
+\begin{figure}[ht]
+	\centering
+  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
+	\caption{gestaucht}
+	\label{fig2}
+\end{figure}
+
+To exemplify, given a problem of domain 1 to 20, first we create an initial chunk  1 – 20.
+When the next available core asks for a step to execute, the controller gets the biggest chunk which in this case is 1 – 20, divide it by 2, creates two new chunks and return the middle of the original chunk.
+So it would be 2 new chunks 1 – 9 and 11 – 20, and the returned step will be 10.
+Additional checks are needed to avoid the creation of empty or invalid chunks.
+\begin{figure}[ht]
+	\centering
+  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
+	\caption{gestaucht}
+	\label{fig2}
+\end{figure}
+
+Additionally, since there will be a gap between the steps, produced by the customized binary search algorithm, it is possible that a lot of steps will not be needed to execute.
+For instance, on the example above, if a step 10 return false, it is obvious that every step after 10 will also be a violation.
+On the other hand, if the same step was successful, we can assume that every step before 10 will also be a valid.
+
+That said, was implemented in the controller a method to discard unnecessary steps by removing or shrinking existing chunks.
+It made a very big impact in the calculation time.
+However a step can be running and not be needed anymore, in this case the binary algorithm kills the forked  process and starts a new one.
+\begin{lstlisting}
+01. GetNextStep(){
+02.  int largestChunk = -1;
+03.  chunk largest;
+04.  for each(chunk in chunks){
+05.     if(chunk.right - chunk.left > largestChunk){
+06.           largestChunk = chunk.right - chunk.left;
+07.           largest = chunk;
+08.     }
+09.   }	
+10.   chunks.remove(largest);	
+11.   int median = largest.left + floor((largest.right - largest.left) / 2)
+12.   if(median > 0){
+13.      if(largest.right - largest.left > 1)
+14.         chunks.add(new chunk(largest.left, median - 1));	
+15.      if(largest.right != largest.left)
+16.         chunks.add(new chunk(median + 1, largest.right);
+17.    }
+18.   return median;
+19. }
+\end{lstlisting}
+ The execution is made by executing the procedure described pseudocode before and then starting the process of the ESBMC to execute the returned step.
+While the step is being executed the algorithm query the controller to check if this step is still needed. If not, the ESBMC instance is killed and the worker is free to start another step.
+
+\begin{lstlisting}
+01. step = controller.GetNextStep();
+02. int pid = ExecuteStep(step);
+03. while(isRunning(pid)){
+04.   if(!controller.isNeeded(step))
+05.    kill(pid);
+06. }     
+\end{lstlisting}
 
@@
 \subsection{Informal Model (or Assumptions)}
+The informal model can be described by five characteristics.
+First, there is only one software context, i.e., there is just one general-purpose processor, and there is only one hardware context.
+The components of the system must be mapped to either one of these two contexts.
+Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, and energy consumption.
+Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
+Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
+The consequence of these assumptions is that scheduling does not need to be addressed in this work.
+Hardware components do not need scheduling, because the running time is assumed to be zero.
+Because there is only one processor, software components do not need to be scheduled as well.
+Therefore, the focus is only on the partitioning problem.
+That configuration describes a first-generation co-design, where the focus is on bipartitioning [17].
+
 \subsection{Formal Model}
+...
 
@@
 \section{Analysis of the partitioning problem using vZ}
+O pseudocódigo abaixo mostra as condições aplicadas em ILP, GA e ESBMC convertida para a ferramenta vZ descrita em [34] e [35].
+
+Um contexto do vZ é criado, este recebe as restrições e devolve um modelo caso exista uma solução para o conjunto de restrições.
+Posteriormente são declarados a quantidade de nós, quantidade de arestas, o valor de , o custo de hardware, custo de software, custo de comunicação, e a matriz de incidência E.
+
+As declarações aritméticas descritas nas linhas 10, 11,12 e 13 do pseudocódigo é uma transcrição da formula $ S(1-x) + C|Ex| \leq S{0} $ descrita na seção III.B, é referente ao custo de software (SF).
+Observe que na linha 11 uma variável temporária chamada TMP é criada para representar $C|Ex|$  , é aplicado então um produto entre o valor absoluto de TMP com o valor do vetor C declarado na linha 07, logo, gera-se o resultado para o custo de comunicação (CMC).
+Na linha 13, a declaração Fobj (Função objetivo) é um produto entre o custo de hardware com um vector que contém valores 0 ou 1.
+Fobj deve ser minimizado para alcançarmos a melhor solução para o hardware.
+
+Duas restrições são impostas, a primeira refere-se à soma entre custo de software com o custo de comunicação, a resultante da soma deve ser menor do que , a segunda restrição diz ao vZ que ele deverá minimizar Fobj.
+O modelo então é checado, uma vez que há uma solução que obedeça às restrições, o valor da função objetiva é impressa.
+
+\begin{lstlisting}
+01.#Init Values
+02.  Create vZ context 
+03.  Create binary vector (x)
+04.  Declare number of nodes, edges and S0
+05.  Declare hardware cost of each node as array (h) 
+06.  Declare software cost of each node as array (s)
+07.  Declare communication cost of each edge (c)
+08.  Declare transposed incidence matrix graph G (E)
+09.#Arithmetic
+10.  SF receive s(1-x)
+11.  TMP vector receive E|x| 
+12.  CMC receive c*|EX|
+13.  Fobj receive  x[i] * h[i]
+14.#Asserts
+15.  Add restrictions (SF + CMC <= S0)
+16.  Add restrictions to minimize Fobj
+17.  Check Model
+18.  Print Result
+\end{lstlisting}
+
 \section{Experimental Evaluation}
+
 \section{Related Work}
+Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution [2], to use heuristics to speed up performance time [1], and hybrid ones [22].
+
+In the first group, the exact solution to the HW-SW partitioning problem is found.
+The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithm.
+The difference is based only in terms of the technique chosen to solve the problem.
+Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution.
+The difference between this kind of solutions and SMT-based verification is based on two facts: ESBMC is guaranteed to find the exact solution, but the heuristics are faster when the complexity is greater.
+
+Finally, there are approaches that mixes heuristics with exact solution tools.
+The idea is to use a heuristic to speed up some phase of an exact solution tool.
+It worth mentioning that the final solution is not necessarily an optimal global solution.
+Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.
+
+In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages (e.g., C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+In [16] it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and [14] uses the ESBMC model checker for embedded ANSI-C software.
+In [5] and [6] it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification [29], and modifications of internal search engines to support parallelism [30], but there is still the need for initiatives related to parallel SMT solvers [31].
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories [32].
 \section{Conclusions}
+Concerning the comparative tests, with the four techniques presented in this paper to solve HW-SW partitioning, it was evident that none of them is indicated to partition problems with more than 400 nodes.
+The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
+If we consider less than 400 nodes, then it is possible to use ILP as the best solution provider.
+If the problem to be solved has 150 nodes or less, then ESBMC represents a feasible alternative.
+GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
+This error may be reduced by changing some parameters.
+
+If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
+However, ESBMC has a BSD-style license and can be downloaded and used for free.
+Concerning the two versions of ESBMC, it is possible to conclude that Multi-core ESBMC had better performance results than pure ESBMC.
+Thus, considering that nowadays the processors have more and more cores, when modeling the problem, it is possible to consider multi-core ESBMC as an alternative to solve the partitioning problem.
+Future work can be done to decrease the processing time of ESBMC (solver included).
+
+Finally, there is an issue about 150 nodes problem, since it seems to be the limit of ESBMC.
+It really depends on the modeling granularity of the problem.
+Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW.
+This may lead to thousands of nodes or even more.
+Others defend coarse-grained models, where decisions are made for bigger components, thus even complex systems may consist of just some dozens of nodes to partition.
+In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space.
+In future work, we will exploit other search strategies in the multi-core ESBMC approach and address specifically more complex types of architectures in the HW-SW partitioning problem, including more than one CPU.
 \section{References}

### 2015-08-15 Docs/Paper/LaTex/template.tex
Section 2.3 Added

@@
 \subsection{Bounded Model Checking with ESBMC}
+
+Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior [3],[4].
+These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
+However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components [10].
+Much research has been devoted to mitigate this problem.
+
+Among the recent techniques, there is one that combines model checking with satisﬁability solving.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in [10].
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
+
+The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less [10].
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in [11], [12], and [13].
+
+According to [14] and [15], SMT-based model checking can be used to verify the single- and multi-threaded software.
+In [16], ESBMC can also be used to model check C++ software based on SMT solvers.
+In [5] and [6] it was shown that it is possible to use ESBMC, as an optimization tool.
+There are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
+The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition or code violation (minimum hardware cost).
+Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
+
 \subsection{Multi-core ESBMC with OpenMP}

### 2015-08-16 Docs/Paper/LaTex/template.tex
Complete conversion

@@
 \usepackage{booktabs}
-\usepackage{amsmath}
+\usepackage{tabu,xcolor,colortbl}
+\usepackage{rotating}
+\usepackage{amsmath,array}    
 \usepackage[utf8]{inputenc} 
-\usepackage{graphicx}
-\usepackage{listings}
+\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
+\usepackage{graphicx} %Imagens
+\usepackage{listings} % Codes
+\usepackage{tabularx} % in the preamble
+\usepackage{mathtools} % Serve para as equacoes
+
+\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
+
 \usepackage{color}
@@
 \definecolor{mauve}{rgb}{0.58,0,0.82}
+\definecolor{Gray}{gray}{0.93}
+\definecolor{DarkGray}{gray}{0.70}
+
 \lstset{frame=tb,
@@
 Quando usamos “soft constrains” no modo “lexicographic” vZ invoca MaxSAT.
-
 \begin{figure}[ht]
@@
 \subsection{Bounded Model Checking with ESBMC}
-
-Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior [3],[4].
+Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior [3], [4].
 These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
@@
 In [5] and [6] it was shown that it is possible to use ESBMC, as an optimization tool.
+
 There are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
@@
 \subsection{Multi-core ESBMC with OpenMP}
+Nowadays, although the CPU used to perform tests usually has a modern multi-core architecture, with the ability to run several threads on different processing cores, ESBMC verification runs are still performed only in a single-core.
+For instance, if the processor has 8 processing cores available, only one is used for the verification and the others remain idle.
+There is a significant unused hardware resource during this process.
+
+Fig.1 shows the ESBMC architecture, which consists of the C/C++ parser, GOTO Program, GOTO Symex, and SMT solver [16].
+In particular, ESBMC compiles the C/C++ code into equivalent GOTO-programs (i.e., control-flow graphs) using a gcc-compliant style.
+The GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($ C $) and properties ($ P $); finally it generates two sets of equations (i.e.,\:$ C \land \neg P $ ) which are checked by an SMT solver.
+
+The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
+Currently, the SMT solvers supported by ESBMC are: Z3 [24], Boolector [25], MathSAT [26], CVC4 [27], and Yices [28].
+Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
+\begin{figure}[ht]
+	\centering
+  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
+	\caption{gestaucht}
+\end{figure}
+
+To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library [23] is used in this present work as a front-end for ESBMC.
+
+OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications.
+The API provides a directive-based programming approach to write parallel versions of C/C++ programs [33].
+In OpenMP, the implementation is based on the fork-join model.
+The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
+After the parallel region finishes (i.e., the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode [7].
+Fig.
+2 shows our approach called “Multi-core ESBMC”.
+\begin{figure}[ht]
+	\centering
+  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
+	\caption{gestaucht}
+\end{figure}
+
+Multi-core ESBMC obtains the problem specification represented by a C program, which is violated when the correct optimum value () parameter is reached; Multi-core ESBMC starts a parallel region with  different instances of ESBMC, based on the number of available processing cores.
+All these ESBMC instances run independently of each other, as shown in Fig.
+2; note that there is no shared-memory (or message-passing) mechanism among the threads.
+In particular, different threads are managed by the OpenMP API, which is responsible for the thread lifecycle: start, running, and dead states, using different  values as condition.
+After executing  instances, if there is no code violation, then multi-core ESBMC starts  new instances again.
+During the parallel region execution, if a violation is found in any running thread, then it presents the counterexample with the violation condition and the verification time.
+If all threads of the batch processing are terminated, then multi-core ESBMC finishes its execution.
+
 \subsection{Multi-core ESBMC with OpenMP using Binary Search}
@@
 \subsection{Formal Model}
-...
+The inputs of the problem are: A directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
+The vertices $ V = \{V_1,V_2,\dotso,V_n\} $ represent the nodes that are the components of the system that will be partitioned.
+The edges $ E $ represent communication between the components.
+Additionally, each node  $ V_i $ has a cost $ h(V_i) $ (or $ h_i $ of hardware (if implemented in hardware) and a cost $ s(s_i) $ (or $ s_i $ of software (if implemented in software).
+Finally, $ c(V_i,V_j) $ represents the communication cost between $ V_i $ and $ V_j $ if they are implemented in different contexts (hardware or software).
+
+Based on [1],  is called a hardware-software partition if it is a bipartition of $ V:P = (V_h, V_s) $ , where $ V_h \cup V_s = V $  and $ V_h \cap V_s = 0$  .
+The crossing $ E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h \;or\; v_i \in V_h, v_j \in V_s $ edges are .
+The hardware cost of $ P $  is given by Eq.
+(2), and the software cost of $ P $ (i.e., software cost of the nodes and the communication cost) is given by Eq.
+(3):
+
+\begin{align}
+\ H_p &= \Sigma (v_i \;\in\; _Vh) H_i\\
+  S_p &= \Sigma (v_i \;\in\; _Vs) S_i + \Sigma (_(v_i,v_j) \in\; _Ep)\; C(V_i, V_j)
+\end{align}
+
+Three different optimization and decision problems can be defined.
+In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $ P $ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal (system with hard real-time constraints).
+So, based on Eq.
+(1) and Eq.
+(3) the optimization problem’s restrictions can be reformulated as: $ s(1-x) + c|E_x| \leq S_0 $, where $ x $ is the decision variable.
+Concerning the complexity of this problem, reference [1] demonstrates that it is NP-Hard.
 
@@
 \section{Analysis of the partitioning problem using ESBMC}
+ESBMC pseudocode shows the algorithm with the same restrictions and conditions placed on ILP and GA.
+Two values must be controlled to obtain the results and to perform the optimization.
+One is the initial software cost, as defined in Section III.G.
+The other is the halting condition (code violation) that stops the algorithm.
+
+The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
+also must be defined, as the transposed incidence matrix and the identity matrix, as typically done in MATLAB.
+Here, the matrices A and b are generated.
+At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in [5] and [6].
+
+It is possible to tell the ESBMC with which type of values the variables must be tested.
+Therefore, there is a declaration to populate all the decision variables $ x $ with non-deterministic Boolean values.
+Those values that change for each test will generate a possible solution and obey the restrictions.
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e.,$ A.x \leq b $ ).
+
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
+To every test performed, the hardware hint is compared to the feasible solution.
+This is accomplished by an ASSERT statement at the end of the algorithm, a predicate that controls the halt condition (true-false statement).
+If the predicate is FALSE, then the optimization is finished, i.e., the solution was found.
+The ASSERT statement tests the objective function, i.e., the hardware cost, and will stop if the hardware cost found is lower than or equal to the optimal solution.
+However, if ASSERT returns a TRUE condition, i.e., the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the ASSERT generates a FALSE condition.
+When the FALSE condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
+That is the point in which the solution is presented (minimum HW cost).
+
+In the ESBMC algorithm, which is shown below, it is not necessary to add slack variables because the modulus operation is kept, which reduces the number of variables to be solved.
+
+\begin{lstlisting}
+01. Initialize Variables 
+02. Declare number of nodes and edges
+03. Declare hardware cost of each node as array (h)
+04. Declare software cost of each node as array (s)
+05. Declare communication cost of each edge (c)
+06. Declare the initial software cost of (S0)
+07. Declare transposed incidence matrix graph G (E)
+08. Define the solutions variable (Xi) as Boolean
+09. main {
+10.  for TipH = 0 to Hmax do {
+11.   populate Xi with nondeterministic/test values
+12.   Calculate s(1-x)+c|Ex| and store at variable
+13.   Requirement isured by Assume (Variable <= S0)
+14.   Calculate Hp cost Based on value tested of Xi
+15.   Violation check with Assert(Hp > TipH)
+16.  }
+17. }
+\end{lstlisting}
+
+In the multi-core ESBMC algorithm, the only difference is the fact that the value of $ TipH $ and its range is not declared in the algorithm, as shown in ESBMC Pseudocode.
+The proposed approach is invoked for each test problem, as follows:
+$ esbmc-parallel <Filename.c> \; <hminvalue> \; <Hmax> $
+
+Where $ <Filename.c> $ is the optimization problem described in ANSI-C format, $  <hminvalue> $ is the minimum (zero to HW-SW partitioning problem) and $ <Hmax> $ is the maximum hardware cost for the specified problem.
+
+Therefore, the algorithm starts  different instances of ESBMC using the different optimization values, in ascending order, for $ Hmax $ in order to find a violation.
+If all instances finish and no violation is found, then multi-core ESBMC starts new $ N $ instances.
+When a violation is found, it reports time and hardware cost.
+If multi-core ESBMC tests all the possibilities for the hardware cost and has not found a violation, then it reports: $ Violation not found $.
+
 \section{Analysis of the partitioning problem using vZ}
@@
 
+Nice team.
+
 \section{Experimental Evaluation}
+ESBMC 1.24 running on a 64-bit Ubuntu 14.04.1 LTS operating system was used.
+Version 2.0.1 of Boolector SMT-solver [25] (freely available) was used as well.
+For the ILP and GA formulations, MATLAB R2013a from MathWorks with Parallel Computing Toolbox was used [18].
+MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20].
+The ESBMC multi-core algorithm was implemented in C++1.
+A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used.
+Each time was measured 3 times in GA (average taken) and just once in ESBMC and ILP.
+The reason is that GA times are not so close as ESBMC and ILP.
+A time out condition (TO) is reached when the running time is longer than 7,200 seconds.
+A memory out (MO) occurs when the tool reaches 24GB of memory.
+TABLE I.
+lists the benchmarks1.
+
+\begin{table}[h]
+\caption {Description of Benchmarks}
+\small
+\sffamily\footnotesize
+\tabulinesep=6pt
+\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
+  \toprule[1.5pt]
+  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
+  \midrule
+
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check [21]\\
+\hline
+\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree [21]\\
+\hline
+
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph [21]\\
+\hline
+\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
+\hline
+\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
+\hline
+\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
+\hline
+\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
+
+  \bottomrule[1.5pt]
+\end{tabular}
+\end{table}
+
+The vertices in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area.
+
+The overall performance (TABLE II.
+) shows that ILP is the best solution of all techniques, even if we consider that the Fuzzy benchmark reached time out with ILP.
+Thus, the maximum limit to use ILP is around 329 nodes or less.
+GA was the only technique that could solve all benchmarks, but the error from the exact solution varied from -37.6\% to 29\%.
+
+Multi-core ESBMC had a better performance than that of pure ESBMC.
+The relative speedup obtained ranged from 1.9 to 60.3, which shows a reasonable improvement.
+Until the number of 150 nodes is reached, the ESBMC technique, mainly Multi-core ESBMC, has shown itself to be a good choice to solve HW-SW partitioning.
+This is because the exact solution was found and the execution time was mostly closer to ILP (from the same performance to 4.7 times faster).
+If the complexity of test vectors increases, then pure ESBMC algorithm has the drawback of creating an even more complex problem, because it increases the states created, which controls the hardware cost hint.
+
+\begin{table}[h]
+\caption {Results of the benchmarks}
+\small
+\begin{tabular}[c]{cc|c|c|c|c|c|c|c}
+  \toprule[1.5pt]
+  \head{\begin{turn}{-90}  \end{turn}} &
+  \head{\begin{turn}{-90}  \end{turn}} &
+  \head{\begin{turn}{-90}CRC32\end{turn}} &
+  \head{\begin{turn}{-90}Patricia\end{turn}} &
+  \head{\begin{turn}{-90}Dijkstra\end{turn}} &
+  \head{\begin{turn}{-90}Clustering\end{turn}} &
+  \head{\begin{turn}{-90}RC6\end{turn}} &
+  \head{\begin{turn}{-90}Fuzzy\end{turn}} &
+  \head{\begin{turn}{-90}Mars\end{turn}} \\
+
+  \midrule
+
+\verb| | & \verb|Nodes| & \verb|25| & \verb|21| & \verb|26| & \verb|150| & \verb|329| & \verb|261|  & \verb|417|\\
+\verb| | &\verb|Edges| & \verb|32| & \verb|48| & \verb|69| & \verb|331| & \verb|448| & \verb|442|  & \verb|600|\\
+\verb| | &\verb|S0| & \verb|20| & \verb|10| & \verb|20| & \verb|50| & \verb|600| & \verb|4578|  & \verb|300|\\
+\bottomrule[1.5pt]
+
+%EXACT Solution
+\rowcolor{DarkGray}
+\verb|Exact| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|692|  & \verb|13820| & \verb|876|\\
+\rowcolor{DarkGray}
+\verb|Solution| & \verb|Sp| & \verb|19| & \verb|4| & \verb|19| & \verb|46| & \verb|533|  & \verb|4231| & \verb|297|\\
+
+%vZ
+\verb|vZ| & \verb|T(s)| & \verb|0.2| & \verb|0.3| & \verb|0.6| & \verb|109| & \verb|112|  & \verb|TO| & \verb|TO|\\
+\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|241|  & \verb|-| & \verb|-|\\
+\hline
+
+%ILP
+\rowcolor{Gray}
+\verb|ILP| & \verb|T(s)| & \verb|2| & \verb|1| & \verb|2| & \verb|649| & \verb|1806|  & \verb|TO| & \verb|5.42|\\
+\rowcolor{Gray}
+\verb| | & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|692|  & \verb|-| & \verb|876|\\
+\hline
+
+%GA
+\verb|GA| & \verb|T(s)| & \verb|7| & \verb|7| & \verb|9| & \verb|340| & \verb|2050|  & \verb|1.37| & \verb|5000|\\
+\verb| | & \verb|E%| & \verb|13.3| & \verb|0| & \verb|29| & \verb|1.7| & \verb|-6.5|  & \verb|-37.6| & \verb|-27.5|\\
+\hline
+
+%ESBMC
+\rowcolor{Gray}
+\verb|ESBMC| & \verb|T(s)| & \verb|31| & \verb|362| & \verb|292| & \verb|3010| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\rowcolor{Gray}
+\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\hline
+
+%MultiCore ESBMC
+\verb|ESBMC| & \verb|T(s)| & \verb|2| & \verb|6| & \verb|7| & \verb|1615| & \verb|TO|  & \verb|TO| & \verb|TO|\\
+\verb|MC| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\hline
+
+%ESBMC Parallel sequential
+\rowcolor{Gray}
+\verb|ESBMC| & \verb|T(s)| & \verb|4| & \verb|10| & \verb|11| & \verb|2238| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\rowcolor{Gray}
+\verb|PS| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\hline
+
+%ESBMC Parallel Binary
+\verb|ESBMC| & \verb|T(s)| & \verb|6| & \verb|5| & \verb|6| & \verb|207| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\verb|PB| & \verb|Hp| & \verb|15| & \verb|47| & \verb|38| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\bottomrule[1.5pt]
+
+\end{tabular}
+\end{table}
+
+With the RC6 benchmark (329 nodes), ESBMC was unable to present a solution without exceeding the time limit of 7200 seconds.
+Pure ESBMC had even a worse performance with Fuzzy and Mars, because the execution presented memory out.
+This is a clear indication that the prune method adopted by the ILP’s search tree solver is still more efficient than that adopted by ESBMC solver.
 
@@
 \section{References}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ---- Bibliography ---- %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{thebibliography}{5}
+\providecommand{\natexlab}[1]{#1}
+\providecommand{\url}[1]{{#1}}
+\providecommand{\urlprefix}{URL }
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+\providecommand{\eprint}[2][]{\url{#2}}
+
+%1
+\bibitem{Jackson1995}
+Michael Jackson, ``{The world and the machine},'' {\em ICSE}, pp. 283--292, 1995.
+
+\end{thebibliography}
 

### 2015-08-16 Docs/Paper/LaTex/template.tex
Experimental Evaluation Edited

@@
 %
-
+\usepackage{color}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 \usepackage{booktabs}
@@
 
-Here, we exploit the availability of multi-core processors.
-In particular, a multi-core SMT-based BMC method is applied to the HW-SW partitioning and then is compared to the results with classical integer linear programming (ILP) and genetic algorithm (GA) using a multi-core tool as well.
-To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
+\textcolor{Red}{Aqui, nós exploramos a disponibilidade de processadores multi-core, Em particular, são usados métodos baseados em SMT para analise do particionamento de HW-SW, em seguida, compara-se resultados usando PLI (programacao inteira linear), AG (Algoritmos Geneticos) em uma versão multicore, compara-se os resultados da ferramenta vZ da microsoft que se encontra no estado da arte[32], além de uma versão melhorada da busca em HW-SW para processadores multicores.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
 We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14].
@@
 
-This paper is organized as follows: Section II gives a background on optimization, model checking, and multi-core support with Open MultiProcessing.
-Section III describes informal and formal mathematical modeling.
-Section IV describes briefly the binary integer programming and GA algorithms.
-The SMT-based BMC method is presented in Section V.
-Section VI presents the experimental evaluation.
-Section VII discusses related work.
-Section VIII presents the conclusion and future work.
+\textcolor{Red}{Este artigo está organizado da seguinte forma: a Seção 2 dá um fundo de otimização, otimizacao com a ferramenta vZ, utilizacao da técnica BMC com ESBMC, ESBMC com suporte a multiplos nucelos usando OpenMP, ESBMC Usando técnicas otimas de busca para multiplos nucleos com OpenMP.
+Seção 3 descreve a modelagem matemática informal e formal.
+Seção 4 descreve brevemente ILP e GA.
+O método BMC à base de SMT é apresentado na Seção 5.
+Seção 6 apresenta o modelo de particionamento usando o vZ.
+Seção 7 apresenta a avaliação experimental.
+Seção 8 discute os trabalhos relacionados.
+Seção 9 apresenta as conclusões e trabalhos futuros.}
 
@@
 
-\subsection{Optimization with Vz}
+\subsection{\textcolor{Red}{Optimization with Vz}}
 Um solucionador SMT e uma ferramenta com finalidade de verificar a satisfabilidade de formulas baseada em um conjunto de regras SMT.
@@
 Z3 e implementado em C++.
-
 vZ e uma das ferramentas implementadas no solucionador Z3, a funcao base desta ferramenta e otimizar objetivos dentro do contexto logico das restricoes, este se destaca pelas funcoes que dao a possibilidade de formular criterios de otimizacao.
@@
 Dentre todos os avancos do Z3 usando vZ destaca-se as funcoes: maximize, minimize and assert-soft.
+
 \begin{itemize}
@@
 API in python was used to formulate the optimization problem on the vZ tool.
-The pseudo code below describes the steps to achieve desired results.
 
@@
 
-\subsection{Multi-core ESBMC with OpenMP using Binary Search}
+\subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
 The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
@@
 
-\section{Analysis of the partitioning problem using vZ}
+\section{\textcolor{Red}{Analysis of the partitioning problem using vZ}}
 O pseudocódigo abaixo mostra as condições aplicadas em ILP, GA e ESBMC convertida para a ferramenta vZ descrita em [34] e [35].
@@
 MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20].
-The ESBMC multi-core algorithm was implemented in C++1.
+\textcolor{Red}{A ferramenta vZ incorporada ao Z3[34] disponivel gratuitamente também foi usada.
+uma implementacao paralela do algoritmo ESBMC com busca sequencial ascendente, descrescente e binaria foi implementada em C++1}.
 A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used.
@@
 
-The vertices in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area.
+\textcolor{Green}{The vertices in the graphs correspond to high-level language instructions.
+Software and communication costs are time dimensional, and hardware costs represent the occupied area.}  \textbf{Graphs nao deveria ser Tabela?
+acho que esse texto veio daquele artigo expandido.
+esse paragrafo faz sentido ao senhor?
+}
 
-The overall performance (TABLE II.
-) shows that ILP is the best solution of all techniques, even if we consider that the Fuzzy benchmark reached time out with ILP.
-Thus, the maximum limit to use ILP is around 329 nodes or less.
-GA was the only technique that could solve all benchmarks, but the error from the exact solution varied from -37.6\% to 29\%.
+\textcolor{Red}{Os resultados obtidos destacam as ferramentas vZ e ILP.
+Vz resolveu corretamente 4 de 7 algoritmos, teve um falso positivo no algoritmo RC6, seu resultado mais lento comparado a ILP Foi no algoritmo Patricia onde este foi 3.33 vezes mais rápido, vZ retornou dois TO(Time OUT) em Fuzzy e Mars.}
 
-Multi-core ESBMC had a better performance than that of pure ESBMC.
-The relative speedup obtained ranged from 1.9 to 60.3, which shows a reasonable improvement.
-Until the number of 150 nodes is reached, the ESBMC technique, mainly Multi-core ESBMC, has shown itself to be a good choice to solve HW-SW partitioning.
-This is because the exact solution was found and the execution time was mostly closer to ILP (from the same performance to 4.7 times faster).
-If the complexity of test vectors increases, then pure ESBMC algorithm has the drawback of creating an even more complex problem, because it increases the states created, which controls the hardware cost hint.
+\textcolor{Red}{Em contrapartida, ILP Resolveu corretamente 6 de 7 algoritmos, não teve falso positivo, o tempo de resolucao do problema é maior quando comparamos com ILP/vZ e menor quando comparado com ILP/ESBMC, isso o coloca como uma ferramenta otima em resolucao e intermediaria no quesito tempo.
+}
+
+\textcolor{Red}{A unica tecnica capaz de resolver todos os benchmarks foi GA, entretanto, a precisão não foi satisfatoria, a taxa de erro variou entre -37.6\% até 29.0\%.}
+
+\textcolor{Red}{Todas as versões do ESBMC paralelo obtiveram melhores resultados do que no modo sequencial, destaca-se a versão binaria descrita na secao 2.5, o desempenho se torna cada vez melhor quando se aumenta o numero de nós e arestas.
+o algoritmo Clustering quando processado pelo ESBMC paralelo obteve um desempenho 3.13 vezes melhor do que ILP, seu tempo de 207 segundos é muito proximo do tempo de solucao do Vz que é de 109 segundos.
+}
 
@@
 
-With the RC6 benchmark (329 nodes), ESBMC was unable to present a solution without exceeding the time limit of 7200 seconds.
-Pure ESBMC had even a worse performance with Fuzzy and Mars, because the execution presented memory out.
-This is a clear indication that the prune method adopted by the ILP’s search tree solver is still more efficient than that adopted by ESBMC solver.
+\textcolor{Red}{A Tabela 2 mostra avancos na paralelizacao de algoritmos para problemas de particionamento, ESBMC obteve excelentes resultados quando executado de modo paralelo, as ferramentas vZ e ILP ainda se comportam de forma precisa frente ao ESBMC.}
 

### 2015-08-16 Docs/Paper/LaTex/template.tex
Translate from PTBR to EN

@@
 
-\textcolor{Red}{Aqui, nós exploramos a disponibilidade de processadores multi-core, Em particular, são usados métodos baseados em SMT para analise do particionamento de HW-SW, em seguida, compara-se resultados usando PLI (programacao inteira linear), AG (Algoritmos Geneticos) em uma versão multicore, compara-se os resultados da ferramenta vZ da microsoft que se encontra no estado da arte[32], além de uma versão melhorada da busca em HW-SW para processadores multicores.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
+\textcolor{Red}{Here, we will explore the explore the availability of multi-core processors, in particular SMT methods are used to analyse the partition of HW-SW, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, the results will be compared with vZ tool of Microsoft that is in the state of art [32], besides of the improved version of the search by HW-SW to multi-core processors.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
 We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14].
@@
 
-\textcolor{Red}{Este artigo está organizado da seguinte forma: a Seção 2 dá um fundo de otimização, otimizacao com a ferramenta vZ, utilizacao da técnica BMC com ESBMC, ESBMC com suporte a multiplos nucelos usando OpenMP, ESBMC Usando técnicas otimas de busca para multiplos nucleos com OpenMP.
-Seção 3 descreve a modelagem matemática informal e formal.
-Seção 4 descreve brevemente ILP e GA.
-O método BMC à base de SMT é apresentado na Seção 5.
-Seção 6 apresenta o modelo de particionamento usando o vZ.
-Seção 7 apresenta a avaliação experimental.
-Seção 8 discute os trabalhos relacionados.
-Seção 9 apresenta as conclusões e trabalhos futuros.}
+\textcolor{Red}{This article is organized by the following way: the section 2 gives a background of optimization, optimization with vZ, use of BMC technique with ESBMC, multi-cre ESBMC using OpenMP, ESBMC using optimized techniques of search to multiples cores with OpenMP.
+Section 3 describes the informal and formal mathematical modeling.
+Section 4 briefly describes th ILP and GA.
+The BMC method is based in SMT and is presented in section 5.
+The section 6 presents the paritioning model using vZ.
+The section 7 presents the experimental evaluation.
+The Section 8 discuss about the related works.
+The section 9 is presents the conclusions the future complementary works.}
 
@@
 \subsection{\textcolor{Red}{Optimization with Vz}}
-Um solucionador SMT e uma ferramenta com finalidade de verificar a satisfabilidade de formulas baseada em um conjunto de regras SMT.
-Z3 e um solucionador SMT da Microsoft Research, disponibilizado livremente para a comunidade que integra suporte para uma variedade de teorias.
-Z3 tras consigo um solucionador DPLL juntamente de uma máquina de correspondencia para quantificadores.
-Z3 e implementado em C++.
-vZ e uma das ferramentas implementadas no solucionador Z3, a funcao base desta ferramenta e otimizar objetivos dentro do contexto logico das restricoes, este se destaca pelas funcoes que dao a possibilidade de formular criterios de otimizacao.
-vZ inclui uma versao incremental de MaxRes para MaxSAT e um Simplex para solucionar numeros sem padrao definido, em seu nucleo MaxSat e responsavel pelas restricoes enquanto OptSMT tem como funcao otimizar objetivos de aritmetica linear.
-Dentre todos os avancos do Z3 usando vZ destaca-se as funcoes: maximize, minimize and assert-soft.
+A SMT solver is a tool that verifies formula's satisfiability based in a set of rules SMT.
+Z3 is a SMT solver made by Microsoft Research, freely available to the community, that supports a variety of theories.
+Z3 brings a solver DPLL together with a correspondence machine for quantifiers.
+Z3 is implemented in C++.
+vZ is one of the tools implemented on the Z3 solver, it's base function is to optimize objectives within the logic context of constraints, it stands for the functions that make possible formulate optimized criteria.
+vZ includes an incremental version of MaxRes to MaxSAT and a Simplex to solve numbers without defined patterns, in it's core MaxSAT is responsible to the restrictions while OptSMT optimize the linear arithmetic objectives.
+Among all progress of Z3 using vZ the functions hightlights: maximize, minimize e assert-soft.
 
@@
 \item{\textbf{maximize(T)}
-esta instrucao diz ao solucionador que a variavel T devera ser maximizada, e possível maximizar valores reais, inteiros e vetores de bit.}
+this instruction informs to the solver that a given variable T should be maximized, if possible maximize real, integer and bit vector values.}
 \item{\textbf{minimize(T)}
-esta instrucao diz ao solucionador que a variavel T devera ser minimizada, os tipos aceitos pelo minimize e similar ao maximize.}
+this instruction informs the solver that a given variable T should be minimized, the accepted types are the same as maximize.}
 \item{\textbf{Assert-Soft F :weight n}
-a instrucao Assert-soft e uma restricao sobre F, e possível adicionar um peso n, o padrão e 1.} 
+the instruction Asser-soft is a restriction to F, if possible add a weight n, the default is 1.}
 \end{itemize}
 
-Vamos otimizar (K+W), com restrições em (K \textless 2) e (W-K \textless 1), o resultado da otimização descrita no código abaixo é 2, o modelo gerado pelo vZ mostra que K = 1 e W =1.
+Lets optimize (K+W), with the restrictions in (K \textless 2) and (W-K \textless 1), the expected result of the optimization described in the code below is 2.
+the model generated by vZ shows that K = 1 and W = 1.
 
@@
 
-De acordo com [34] a arquitetura do vZ pode ser descrita na imagem XXX, inicialmente as formulas e os objetivos SMT sao reescritos para variaveis do tipo 0-1, posteriormente os objetivos sao convertidos para problemas MaxSAT, se houver muitos objetivos vZ invoca MaxSAT ou OptSMT.
-Para restricoes sob valores reais usando “Box”, vZ combina todas a aritmetica linear e faz chamada para OptSMT.
-Quando usamos “soft constrains” no modo “lexicographic” vZ invoca MaxSAT.
+Accordingly to [34] the architecture of vZ can be described on the image XXX, initially the formulas and the SMT objectives are converted to problems MaxSAT, if there are many objectives, vZ invokes MaxSAT or OptSAT.
+To restrictions in real values using “Box”, vZ combines all linear arithmetic and calls the OptSMT.
+When we use “soft constrains” in the mode “lexicographic” vZ invokes MaxSAT.
 \begin{figure}[ht]
@@
 \section{\textcolor{Red}{Analysis of the partitioning problem using vZ}}
-O pseudocódigo abaixo mostra as condições aplicadas em ILP, GA e ESBMC convertida para a ferramenta vZ descrita em [34] e [35].
+The code below shows the conditions applied on ILP, GA and ESBMC converted to the vZ tool described in [34] and [35].
 
-Um contexto do vZ é criado, este recebe as restrições e devolve um modelo caso exista uma solução para o conjunto de restrições.
-Posteriormente são declarados a quantidade de nós, quantidade de arestas, o valor de , o custo de hardware, custo de software, custo de comunicação, e a matriz de incidência E.
+A vZ context is created, it receives the restrictions and returns the model if a solution to the set of rectictions exists.
+Later the number of nodes are declared, number of edges, the number of, the cost of hardware, cost of software, cost of communication and the incidence matrix E.
 
-As declarações aritméticas descritas nas linhas 10, 11,12 e 13 do pseudocódigo é uma transcrição da formula $ S(1-x) + C|Ex| \leq S{0} $ descrita na seção III.B, é referente ao custo de software (SF).
-Observe que na linha 11 uma variável temporária chamada TMP é criada para representar $C|Ex|$  , é aplicado então um produto entre o valor absoluto de TMP com o valor do vetor C declarado na linha 07, logo, gera-se o resultado para o custo de comunicação (CMC).
-Na linha 13, a declaração Fobj (Função objetivo) é um produto entre o custo de hardware com um vector que contém valores 0 ou 1.
-Fobj deve ser minimizado para alcançarmos a melhor solução para o hardware.
+The arithmetic declarations described on the lines 10, 11,12 e 13 of the code are a transcription of the formula $ S(1-x) + C|Ex| \leq S{0} $ described on the section III.B, refers to the cost of software (SF).
+Note that in the line 11 a temporary variable called TMP is created to represent $C|Ex|$  , then the product between the absolute value of TMP and the vector C declared in the line 07, then the result of the cost of communication is generated (CMC).
 
-Duas restrições são impostas, a primeira refere-se à soma entre custo de software com o custo de comunicação, a resultante da soma deve ser menor do que , a segunda restrição diz ao vZ que ele deverá minimizar Fobj.
-O modelo então é checado, uma vez que há uma solução que obedeça às restrições, o valor da função objetiva é impressa.
+In the line 13, the Fobj (Objective Function) is declared.
+It is a product between the cost of hardware with the vector that contains the values 0 and 1.
+Fobj should be minimized to get the best hardware solution .
+
+Two restrictions are imposed, the first refers to the sum between the cost of software and communication, the result of the sum should be less than , the second restriction tells to vZ that Fobj should be minimized.
+So the model is checked, once a solution that complains the restrictions, the value of the Fobj is printed.
 

### 2015-08-16 Docs/Paper/LaTex/template.tex
Conclusions Edited

@@
 \section{Conclusions}
-Concerning the comparative tests, with the four techniques presented in this paper to solve HW-SW partitioning, it was evident that none of them is indicated to partition problems with more than 400 nodes.
+\textcolor{Red}{Concerning the comparative tests, with the seven techniques presented in this paper to solve HW-SW partitioning, it was evident that none of them is indicated to partition problems with more than 400 nodes.
 The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
@@
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
-This error may be reduced by changing some parameters.
+This error may be reduced by changing some parameters.}
 
-If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-However, ESBMC has a BSD-style license and can be downloaded and used for free.
+\textcolor{Red}{If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
+However, ESBMC and Vz has BSD-Style license and MIT respectively and can be downloaded and used for free.
 Concerning the two versions of ESBMC, it is possible to conclude that Multi-core ESBMC had better performance results than pure ESBMC.
 Thus, considering that nowadays the processors have more and more cores, when modeling the problem, it is possible to consider multi-core ESBMC as an alternative to solve the partitioning problem.
-Future work can be done to decrease the processing time of ESBMC (solver included).
+Future work can be done to decrease the processing time of ESBMC (solver included).}
 
@@
 In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space.
-In future work, we will exploit other search strategies in the multi-core ESBMC approach and address specifically more complex types of architectures in the HW-SW partitioning problem, including more than one CPU.
+
+\textcolor{Red}{Em trabalhos futuros, vamos abordar melhorias na abordagem do ESBMC, esperamos eliminar a camada de paralelismo da arquitetura do ESBMC implementando open MP diretamente em seu nucleo, almejamos assim otimizar o tempo de processamento.}
+
 \section{References}

### 2015-08-16 Docs/Paper/LaTex/template.tex
Conclusions Fixed

--- 2015-08-16 Docs/Paper/LaTex/template.tex
@@
 In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space.
-In future work, we will exploit other search strategies in the multi-core ESBMC approach and address specifically more complex types of architectures in the HW-SW partitioning problem, including more than one CPU.
+\textcolor{Red}{Em trabalhos futuros, vamos abordar melhorias na abordagem do ESBMC, esperamos eliminar a camada de paralelismo da arquitetura do ESBMC implementando open MP diretamente em seu nucleo, almejamos assim otimizar o tempo de processamento.}
 \section{References}

### 2015-08-17 Docs/Paper/LaTex/template.tex
Added modifications made in docx to LaTex

@@
 \subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
-The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
+\textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
 
-Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.
+Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.}
 \begin{figure}[ht]
@@
 \end{figure}
-So the first approach was to remove the Idle time from the parallel loops by creating workers inside the threads to always execute the next step until a violation is find.
-At first though it seemed to be a great improvement but as ESBMC executes almost the same time the steps, there was almost no optimization.
+\textcolor{Red}{Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
+This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization
 
-The most optimized approach used was to use a parallelized binary search to reduce the complexity of the tasks.
-So was made a controller to return the best step to execute in order to reduce the domain as maximum as possible.
-This is done by dividing the domain in chunks and than returning the middle of the biggest chunk existent, and creating two new chunks.
+The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution.
+As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible.
+The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
 \begin{figure}[ht]
@@
 
-To exemplify, given a problem of domain 1 to 20, first we create an initial chunk  1 – 20.
-When the next available core asks for a step to execute, the controller gets the biggest chunk which in this case is 1 – 20, divide it by 2, creates two new chunks and return the middle of the original chunk.
-So it would be 2 new chunks 1 – 9 and 11 – 20, and the returned step will be 10.
-Additional checks are needed to avoid the creation of empty or invalid chunks.
+\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
+When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval.
+Therefore, there would be 2 new intervals, one from 1 to 9 and another one from 11 to 20, and the returned step would be 10.
+The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals.
+}
 \begin{figure}[ht]
@@
 
-Additionally, since there will be a gap between the steps, produced by the customized binary search algorithm, it is possible that a lot of steps will not be needed to execute.
-For instance, on the example above, if a step 10 return false, it is obvious that every step after 10 will also be a violation.
-On the other hand, if the same step was successful, we can assume that every step before 10 will also be a valid.
+\textcolor{Red}{Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
+For instance, in the example above, if step 10 returns false, then one can conclude that all steps after 10 is false as well.
+However, if the same step 10 is true, we can assume that all steps before 10 is true as well.
 
-That said, was implemented in the controller a method to discard unnecessary steps by removing or shrinking existing chunks.
-It made a very big impact in the calculation time.
-However a step can be running and not be needed anymore, in this case the binary algorithm kills the forked  process and starts a new one.
+As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals.
+This approach leads to a high impact in the verification time.
+However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
 \begin{lstlisting}
@@
 \end{lstlisting}
- The execution is made by executing the procedure described pseudocode before and then starting the process of the ESBMC to execute the returned step.
-While the step is being executed the algorithm query the controller to check if this step is still needed. If not, the ESBMC instance is killed and the worker is free to start another step.
+\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed.
+From line 4 to 9 the algorithm finds the biggest interval.
+Then from the line 10 the biggest interval is removed and the median is calculated in the line 11.
+Then 2 new intervals are created, the left side on line 14 and the right side on the line 16.
+At the end, the median is returned.}
 
@@
 \end{lstlisting}
+\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances.
+The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2).
+While the step is being executed, the controller checks whether this step is still needed (line 4).
+If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}
 
@@
 
-\textcolor{Red}{Os resultados obtidos destacam as ferramentas vZ e ILP.
-Vz resolveu corretamente 4 de 7 algoritmos, teve um falso positivo no algoritmo RC6, seu resultado mais lento comparado a ILP Foi no algoritmo Patricia onde este foi 3.33 vezes mais rápido, vZ retornou dois TO(Time OUT) em Fuzzy e Mars.}
+\textcolor{Red}{The results obtained that standout were the ILP and vZ.
+Vz solved correctly 4 of 7 algorithms, got an false positive in the algorithm RC6, the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}
 
-\textcolor{Red}{Em contrapartida, ILP Resolveu corretamente 6 de 7 algoritmos, não teve falso positivo, o tempo de resolucao do problema é maior quando comparamos com ILP/vZ e menor quando comparado com ILP/ESBMC, isso o coloca como uma ferramenta otima em resolucao e intermediaria no quesito tempo.
-}
+\textcolor{Red}{In contrast, ILP solved correctly 6 of 7 algorithms, do not had any false positive, the resolution time is bigger compared with vZ and lower compared with ESBMC, it shows that ILP is optimized to solve problems but has an average resolution time.}
 
-\textcolor{Red}{A unica tecnica capaz de resolver todos os benchmarks foi GA, entretanto, a precisão não foi satisfatoria, a taxa de erro variou entre -37.6\% até 29.0\%.}
+\textcolor{Red}{The only technique aqble to solve all algorithms was GA, however it's precision was not satisfatory, it had error rate between -37.6\% and 29.0\%.}
 
-\textcolor{Red}{Todas as versões do ESBMC paralelo obtiveram melhores resultados do que no modo sequencial, destaca-se a versão binaria descrita na secao 2.5, o desempenho se torna cada vez melhor quando se aumenta o numero de nós e arestas.
-o algoritmo Clustering quando processado pelo ESBMC paralelo obteve um desempenho 3.13 vezes melhor do que ILP, seu tempo de 207 segundos é muito proximo do tempo de solucao do Vz que é de 109 segundos.
-}
+\textcolor{Red}{All versions of parallel ESBMC got better results compared with the sequential approach, stands out the binary version described on the section 2.5, the performance get better as the number of nodes and edges get bigger.
+The clustering algorithm when processed by the parallel ESBMC had 3.13 better performance than ILP, it`s time was 207 seconds and is very cloe to the solution of vZ that is 109 seconds.}
 
@@
 
-\textcolor{Red}{A Tabela 2 mostra avancos na paralelizacao de algoritmos para problemas de particionamento, ESBMC obteve excelentes resultados quando executado de modo paralelo, as ferramentas vZ e ILP ainda se comportam de forma precisa frente ao ESBMC.}
+\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
 

### 2015-08-17 Docs/Paper/LaTex/template.tex
Fixed Tables, HYP and Titles

@@
 
+\usepackage{hyphenat}
+\usepackage[english]{babel}
+\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams}
+
 \newcommand{\head}[1]{\textnormal{\textbf{#1}}}
@@
 \author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Lucas Cordeiro}
-\institute{Electronic and Information Research Center\\Federal University of Amazonas, Brazil}
+
+\institute{A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \at
+              Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
+%              Tel.: +123-45-678910\\
+%              Fax: +123-45-678910\\
+              \email{\{iurybessa, hussamaibrahim\}@ufam.edu.br and\\{\{rdegelo, esj.galvao\}@gmail.com}}          %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           L. Cordeiro \at
+              Electronic and Information Research Center, Federal University of Amazonas, Brazil
+              \email: lucascordeiro@ufam.edu.br           %  \\
+}
+
 \maketitle
@@
 Fig.1 shows the ESBMC architecture, which consists of the C/C++ parser, GOTO Program, GOTO Symex, and SMT solver [16].
-In particular, ESBMC compiles the C/C++ code into equivalent GOTO-programs (i.e., control-flow graphs) using a gcc-compliant style.
+In particular, ESBMC compiles the C/C++ code into equivalent GOTO\hyp{}programs (i.e., control-flow graphs) using a gcc-compliant style.
 The GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($ C $) and properties ($ P $); finally it generates two sets of equations (i.e.,\:$ C \land \neg P $ ) which are checked by an SMT solver.
@@
 \subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
-\textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
+The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
+Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.
 
-Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.}
 \begin{figure}[ht]
@@
 \end{figure}
-\textcolor{Red}{Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
+
+Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
 This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization
@@
 As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible.
-The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
+The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.
 \begin{figure}[ht]
@@
 
-\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
+As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
 When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval.
@@
 The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals.
-}
 \begin{figure}[ht]
@@
 
-\textcolor{Red}{Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
+Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
 For instance, in the example above, if step 10 returns false, then one can conclude that all steps after 10 is false as well.
@@
 This approach leads to a high impact in the verification time.
-However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
+However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.
 \begin{lstlisting}
@@
 \end{lstlisting}
-\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed.
+The algorithm above describes how the customized binary search calculates and returns the step to be executed.
 From line 4 to 9 the algorithm finds the biggest interval.
@@
 Then 2 new intervals are created, the left side on line 14 and the right side on the line 16.
-At the end, the median is returned.}
+At the end, the median is returned.
 
@@
 \end{lstlisting}
-\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances.
+The algorithm above describes how the worker starts and monitors the ESBMC instances.
 The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2).
 While the step is being executed, the controller checks whether this step is still needed (line 4).
-If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}
+If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.
 
@@
 \small
-\begin{tabular}[c]{cc|c|c|c|c|c|c|c}
+\begin{tabular}[c]{m{1.3cm}m{1.20cm}|m{0.85cm}|m{0.85cm}|m{0.85cm}|m{0.85cm}}
   \toprule[1.5pt]
@@
   \head{\begin{turn}{-90}Dijkstra\end{turn}} &
-  \head{\begin{turn}{-90}Clustering\end{turn}} &
+  \head{\begin{turn}{-90}Clustering\end{turn}} \\
+
+  \midrule
+
+\verb| | & \verb|Nodes| & \verb|25| & \verb|21| & \verb|26| & \verb|150| \\
+\verb| | &\verb|Edges| & \verb|32| & \verb|48| & \verb|69| & \verb|331| \\
+\verb| | &\verb|S0| & \verb|20| & \verb|10| & \verb|20| & \verb|50| \\
+\bottomrule[1.5pt]
+
+%EXACT Solution
+\rowcolor{DarkGray}
+\verb|Exact| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| \\
+\rowcolor{DarkGray}
+\verb|Solution| & \verb|Sp| & \verb|19| & \verb|4| & \verb|19| & \verb|46| \\
+
+%vZ
+\verb|vZ| & \verb|T(s)| & \verb|0.2| & \verb|0.3| & \verb|0.6| & \verb|109|\\
+\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| \\
+\hline
+
+%ILP
+\rowcolor{Gray}
+\verb|ILP| & \verb|T(s)| & \verb|2| & \verb|1| & \verb|2| & \verb|649|\\
+\rowcolor{Gray}
+\verb| | & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
+\hline
+
+%GA
+\verb|GA| & \verb|T(s)| & \verb|7| & \verb|7| & \verb|9| & \verb|340|\\
+\verb| | & \verb|E%| & \verb|13.3| & \verb|0| & \verb|29| & \verb|1.7|\\
+\hline
+
+%ESBMC
+\rowcolor{Gray}
+\verb|ESBMC| & \verb|T(s)| & \verb|31| & \verb|362| & \verb|292| & \verb|3010|\\
+\rowcolor{Gray}
+\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
+\hline
+
+%MultiCore ESBMC
+\verb|ESBMC| & \verb|T(s)| & \verb|2| & \verb|6| & \verb|7| & \verb|1615|\\
+\verb|MC| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
+\hline
+
+%ESBMC Parallel sequential
+\rowcolor{Gray}
+\verb|ESBMC| & \verb|T(s)| & \verb|4| & \verb|10| & \verb|11| & \verb|2238|\\
+\rowcolor{Gray}
+\verb|PS| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
+\hline
+
+%ESBMC Parallel Binary
+\verb|ESBMC| & \verb|T(s)| & \verb|6| & \verb|5| & \verb|6| & \verb|207|\\
+\verb|PB| & \verb|Hp| & \verb|15| & \verb|47| & \verb|38| & \verb|241|\\
+\bottomrule[1.5pt]
+
+\end{tabular}
+\end{table}
+
+\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
+
+\begin{table}[h]
+\caption {Results of the benchmarks}
+\small
+\begin{tabular}[c]{m{1.3cm}m{1.25cm}|m{1.25cm}|m{1.25cm}|m{1.25cm}}
+  \toprule[1.5pt]
+  \head{\begin{turn}{-90}  \end{turn}} &
+  \head{\begin{turn}{-90}  \end{turn}} &
   \head{\begin{turn}{-90}RC6\end{turn}} &
@@
 
-\verb| | & \verb|Nodes| & \verb|25| & \verb|21| & \verb|26| & \verb|150| & \verb|329| & \verb|261|  & \verb|417|\\
-\verb| | &\verb|Edges| & \verb|32| & \verb|48| & \verb|69| & \verb|331| & \verb|448| & \verb|442|  & \verb|600|\\
-\verb| | &\verb|S0| & \verb|20| & \verb|10| & \verb|20| & \verb|50| & \verb|600| & \verb|4578|  & \verb|300|\\
+\verb| | & \verb|Nodes| & \verb|329| & \verb|261|  & \verb|417|\\
+\verb| | &\verb|Edges| &  \verb|448| & \verb|442|  & \verb|600|\\
+\verb| | &\verb|S0| & \verb|600| & \verb|4578|  & \verb|300|\\
 \bottomrule[1.5pt]
@@
 \rowcolor{DarkGray}
-\verb|Exact| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|692|  & \verb|13820| & \verb|876|\\
+\verb|Exact| & \verb|Hp| & \verb|692|  & \verb|13820| & \verb|876|\\
 \rowcolor{DarkGray}
-\verb|Solution| & \verb|Sp| & \verb|19| & \verb|4| & \verb|19| & \verb|46| & \verb|533|  & \verb|4231| & \verb|297|\\
+\verb|Solution| & \verb|Sp| & \verb|533|  & \verb|4231| & \verb|297|\\
 
 %vZ
-\verb|vZ| & \verb|T(s)| & \verb|0.2| & \verb|0.3| & \verb|0.6| & \verb|109| & \verb|112|  & \verb|TO| & \verb|TO|\\
-\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|241|  & \verb|-| & \verb|-|\\
+\verb|vZ| & \verb|T(s)| & \verb|112|  & \verb|TO| & \verb|TO|\\
+\verb|| & \verb|Hp| & \verb|241|  & \verb|-| & \verb|-|\\
 \hline
@@
 \rowcolor{Gray}
-\verb|ILP| & \verb|T(s)| & \verb|2| & \verb|1| & \verb|2| & \verb|649| & \verb|1806|  & \verb|TO| & \verb|5.42|\\
+\verb|ILP| & \verb|T(s)| & \verb|1806|  & \verb|TO| & \verb|5.42|\\
 \rowcolor{Gray}
-\verb| | & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|692|  & \verb|-| & \verb|876|\\
+\verb| | & \verb|Hp| & \verb|692|  & \verb|-| & \verb|876|\\
 \hline
@@
 %GA
-\verb|GA| & \verb|T(s)| & \verb|7| & \verb|7| & \verb|9| & \verb|340| & \verb|2050|  & \verb|1.37| & \verb|5000|\\
-\verb| | & \verb|E%| & \verb|13.3| & \verb|0| & \verb|29| & \verb|1.7| & \verb|-6.5|  & \verb|-37.6| & \verb|-27.5|\\
+\verb|GA| & \verb|T(s)| & \verb|2050|  & \verb|1.37| & \verb|5000|\\
+\verb| | & \verb|E%| &  \verb|-6.5|  & \verb|-37.6| & \verb|-27.5|\\
 \hline
@@
 \rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| & \verb|31| & \verb|362| & \verb|292| & \verb|3010| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\verb|ESBMC| & \verb|T(s)| &  \verb|TO|  & \verb|MO| & \verb|MO|\\
 \rowcolor{Gray}
-\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\verb|| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
 \hline
@@
 %MultiCore ESBMC
-\verb|ESBMC| & \verb|T(s)| & \verb|2| & \verb|6| & \verb|7| & \verb|1615| & \verb|TO|  & \verb|TO| & \verb|TO|\\
-\verb|MC| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\verb|ESBMC| & \verb|T(s)|  & \verb|TO|  & \verb|TO| & \verb|TO|\\
+\verb|MC| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
 \hline
@@
 \rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| & \verb|4| & \verb|10| & \verb|11| & \verb|2238| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\verb|ESBMC| & \verb|T(s)| & \verb|TO|  & \verb|MO| & \verb|MO|\\
 \rowcolor{Gray}
-\verb|PS| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\verb|PS| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
 \hline
@@
 %ESBMC Parallel Binary
-\verb|ESBMC| & \verb|T(s)| & \verb|6| & \verb|5| & \verb|6| & \verb|207| & \verb|TO|  & \verb|MO| & \verb|MO|\\
-\verb|PB| & \verb|Hp| & \verb|15| & \verb|47| & \verb|38| & \verb|241| & \verb|-|  & \verb|-| & \verb|-|\\
+\verb|ESBMC| & \verb|T(s)| & \verb|TO|  & \verb|MO| & \verb|MO|\\
+\verb|PB| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
 \bottomrule[1.5pt]
@@
 \end{table}
-
-\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
 

### 2015-08-17 Docs/Paper/LaTex/template.tex
Paper Updated

@@
 \subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
-The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
-Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.
+\textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
+Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.}
 
@@
 
-Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
-This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization
+\textcolor{Red}{Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
+This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization.}
 
-The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution.
+\textcolor{Red}{The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution.
 As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible.
-The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.
+The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
 \begin{figure}[ht]
@@
 
-As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
+\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
 When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval.
@@
 The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals.
+}
 \begin{figure}[ht]
@@
 
-Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
+\textcolor{Red}{Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
 For instance, in the example above, if step 10 returns false, then one can conclude that all steps after 10 is false as well.
-However, if the same step 10 is true, we can assume that all steps before 10 is true as well.
+However, if the same step 10 is true, we can assume that all steps before 10 is true as well.}
 
-As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals.
+\textcolor{Red}{As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals.
 This approach leads to a high impact in the verification time.
-However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.
+However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
 \begin{lstlisting}
@@
 \end{lstlisting}
-The algorithm above describes how the customized binary search calculates and returns the step to be executed.
+\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed.
 From line 4 to 9 the algorithm finds the biggest interval.
@@
 Then 2 new intervals are created, the left side on line 14 and the right side on the line 16.
-At the end, the median is returned.
+At the end, the median is returned.}
 
@@
 \end{lstlisting}
-The algorithm above describes how the worker starts and monitors the ESBMC instances.
+\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances.
 The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2).
 While the step is being executed, the controller checks whether this step is still needed (line 4).
-If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.
+If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}
 
@@
 MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20].
-\textcolor{Red}{A ferramenta vZ incorporada ao Z3[34] disponivel gratuitamente também foi usada.
-uma implementacao paralela do algoritmo ESBMC com busca sequencial ascendente, descrescente e binaria foi implementada em C++1}.
+\textcolor{Red}{The built in Z3 tool vZ [34] available freely was also used.
+A parallel approach of the ESBMC sequential search ascending, descending and binary was implemented in c++11}.
 A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used.
@@
 In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space.
-\textcolor{Red}{Em trabalhos futuros, vamos abordar melhorias na abordagem do ESBMC, esperamos eliminar a camada de paralelismo da arquitetura do ESBMC implementando open MP diretamente em seu nucleo, almejamos assim otimizar o tempo de processamento.}
+\textcolor{Red}{On future works we will address improvements in the ESBMC, we hope to remove the parallel layer on top of ESBMC and implement it on it's core, it would optimize the processing time.}
 \section{References}

### 2015-08-17 Docs/Paper/LaTex/template.tex
more comments

@@
 \begin{abstract}
+\textcolor{blue}{Atualizar o abstract para descrever brevemente os novos algoritmos desenvolvidos}
 We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing.
@@
 
-\textcolor{Red}{Here, we will explore the explore the availability of multi-core processors, in particular SMT methods are used to analyse the partition of HW-SW, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, the results will be compared with vZ tool of Microsoft that is in the state of art [32], besides of the improved version of the search by HW-SW to multi-core processors.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
+\textcolor{blue}{Deve-se citar as referencias usando o comando cite do latex}
+
+\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
 We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14].

### 2015-08-17 Docs/Paper/LaTex/template.tex
review section 1

@@
 
-\textcolor{Red}{This article is organized by the following way: the section 2 gives a background of optimization, optimization with vZ, use of BMC technique with ESBMC, multi-cre ESBMC using OpenMP, ESBMC using optimized techniques of search to multiples cores with OpenMP.
+\textcolor{blue}{Voces precisam citar as secoes usando o comando ref do latex. Para isso, cada secao deve conter um label.}
+\textcolor{Red}{This article is organized as follows: Section~\ref{background} gives a background on optimization, optimization with vZ, use of BMC technique with ESBMC, multi-cre ESBMC using OpenMP, ESBMC using optimized techniques of search to multiples cores with OpenMP.
 Section 3 describes the informal and formal mathematical modeling.
 Section 4 briefly describes th ILP and GA.
-The BMC method is based in SMT and is presented in section 5.
+The BMC method is based on SMT and is presented in section 5.
 The section 6 presents the paritioning model using vZ.
 The section 7 presents the experimental evaluation.
-The Section 8 discuss about the related works.
-The section 9 is presents the conclusions the future complementary works.}
+The Section 8 discusses about the related works.
+Section 9 presents the conclusions and the future work.}
 
-\section{BACKGROUND}
+%----------------------------------------------
+\section{Background}
+\label{background}
+%----------------------------------------------
+
+\textcolor{blue}{Introduzir uma breve descrição da seção.}
+
+%----------------------------------------------
 \subsection{Optimization}
+%----------------------------------------------
+
 Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9].
@@
 
+%----------------------------------------------
 \subsection{\textcolor{Red}{Optimization with Vz}}
+%----------------------------------------------
+
 A SMT solver is a tool that verifies formula's satisfiability based in a set of rules SMT.
@@
 
+%----------------------------------------------
 \subsection{Bounded Model Checking with ESBMC}
+%----------------------------------------------
+
 Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior [3], [4].
@@
 
+%----------------------------------------------
 \subsection{Multi-core ESBMC with OpenMP}
+%----------------------------------------------
+
 Nowadays, although the CPU used to perform tests usually has a modern multi-core architecture, with the ability to run several threads on different processing cores, ESBMC verification runs are still performed only in a single-core.
@@
 
+%----------------------------------------------
 \subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
+%----------------------------------------------
+
 \textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
@@
 
+%----------------------------------------------
 \section{Mathematical modeling}
+%----------------------------------------------
+
 The mathematical modeling was taken from [1], [2].
+
+%----------------------------------------------
 \subsection{Informal Model (or Assumptions)}
+%----------------------------------------------
+
 The informal model can be described by five characteristics.
@@
 
+%----------------------------------------------
 \subsection{Formal Model}
+%----------------------------------------------
+
 The inputs of the problem are: A directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
@@
 
+%----------------------------------------------
 \section{Partitioning problem using ILP-based,Genetic Algorithms}
 \label{ILPGA}
+%----------------------------------------------
+
 The ILP and GA were taken from [5] and [6].
@@
 
+%----------------------------------------------
 \section{Analysis of the partitioning problem using ESBMC}
+%----------------------------------------------
+
 ESBMC pseudocode shows the algorithm with the same restrictions and conditions placed on ILP and GA.
@@
 
+%----------------------------------------------
 \section{\textcolor{Red}{Analysis of the partitioning problem using vZ}}
+%----------------------------------------------
+
 The code below shows the conditions applied on ILP, GA and ESBMC converted to the vZ tool described in [34] and [35].
@@
 
+%----------------------------------------------
 \section{Experimental Evaluation}
+%----------------------------------------------
+
 ESBMC 1.24 running on a 64-bit Ubuntu 14.04.1 LTS operating system was used.
@@
 
+%----------------------------------------------
 \section{Related Work}
+%----------------------------------------------
+
 Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution [2], to use heuristics to speed up performance time [1], and hybrid ones [22].
@@
 Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories [32].
+
+%----------------------------------------------
 \section{Conclusions}
+%----------------------------------------------
+
 Concerning the comparative tests, with the four techniques presented in this paper to solve HW-SW partitioning, it was evident that none of them is indicated to partition problems with more than 400 nodes.

### 2015-08-18 Docs/Paper/LaTex/template.tex
general comments
Comments Fixed

@@
 \newcommand{\head}[1]{\textnormal{\textbf{#1}}}
+\renewcommand{\lstlistingname}{Algorithm}
 
@@
 The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-We compare the experimental results of our proposed approach with Integer Linear Programming and the Genetic Algorithm.
+\textcolor{Red}{O problema de particionamento de HW-SW foi modelo em diversas plataformas como: MATLAB R2013a da MathWorks[19], Z3 um solucionador de teoremas da Microsoft Research[32] e ESBMC utilizando abordagens single-core e multi-core.
+Os algoritmos implementados são discutidos e suas particularidades destacadas, por fim, faz-se um comparativos dos resultados obtidos.
+}
 \keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
@@
 
-\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
+\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].}
+
+\textcolor{Red}{O algoritmo ILP usa a intlinprog da biblioteca "Optimization Toolbox"[35], sua funcao é procurar o menor valor que satisfaca o problema descrito na Eq.(1).
+entretanto, para determinados tipos de problema ILP se torna inviavel dado o alto custo computacional, GA é uma forma de otimizar o tempo de processamento em detrimento da precisão, uma vez que GA não garante achar o valor máximo ou minimo para a problema.
+vZ usa funcoes de otimizacao e reescreve formulas em SMT para achar a solucao ideal, vZ apoia sua solucao em motores(OptSMT, MaxSMT).}
+
+To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
 We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14].
@@
 
+\textcolor{red}{Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9].
+In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
+The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
+Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].}
 %----------------------------------------------
@@
 %----------------------------------------------
-
-Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9].
-In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
-The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
-Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].
 
@@
 In some cases, the time to find a solution using ILP is impractical.
-Even with the use of powerful computers, a problem can take hours running before an optimal solution is reached.
+Even with the use of powerful computers, a problem can take hours belerunning before an optimal solution is reached.
 If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA [9].
 The only drawback is that the found solution may not be the global minimum or maximum.
+
+\textcolor{red}{Ferramentas como vZ e ESBMC tambem exploram o problema de otimizacao, ambas ferramentas tem como principal finalidade a precisão na resposta, problemas com uma quantidade muito grande de dados torna o tempo um impecilho.
+as secoes 2.2 e 2.3 demonstram como vZ e ESBMC usam respectivamente suas tecnicas para resolucao dos problemas de particionamento, espera-se destas tecnicas uma resposta exata em um tempo razoavel.}
 
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[caption=Code "SMT" using vZ, label=vZ]
 1. (declare-const K Int) 
@@
 Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
+
+%----------------------------------------------
+\section{Mathematical modeling}
+%----------------------------------------------
+
+The mathematical modeling was taken from [1], [2].
+
+%----------------------------------------------
+\subsection{Informal Model (or Assumptions)}
+%----------------------------------------------
+
+The informal model can be described by five characteristics.
+First, there is only one software context, i.e., there is just one general-purpose processor, and there is only one hardware context.
+The components of the system must be mapped to either one of these two contexts.
+Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, and energy consumption.
+Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
+Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
+The consequence of these assumptions is that scheduling does not need to be addressed in this work.
+Hardware components do not need scheduling, because the running time is assumed to be zero.
+Because there is only one processor, software components do not need to be scheduled as well.
+Therefore, the focus is only on the partitioning problem.
+That configuration describes a first-generation co-design, where the focus is on bipartitioning [17].
+
+%----------------------------------------------
+\subsection{Formal Model}
+%----------------------------------------------
+
+The inputs of the problem are: A directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
+The vertices $ V = \{V_1,V_2,\dotso,V_n\} $ represent the nodes that are the components of the system that will be partitioned.
+The edges $ E $ represent communication between the components.
+Additionally, each node  $ V_i $ has a cost $ h(V_i) $ (or $ h_i $ of hardware (if implemented in hardware) and a cost $ s(s_i) $ (or $ s_i $ of software (if implemented in software).
+Finally, $ c(V_i,V_j) $ represents the communication cost between $ V_i $ and $ V_j $ if they are implemented in different contexts (hardware or software).
+
+Based on [1],  is called a hardware-software partition if it is a bipartition of $ V:P = (V_h, V_s) $ , where $ V_h \cup V_s = V $  and $ V_h \cap V_s = 0$  .
+The crossing $ E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h \;or\; v_i \in V_h, v_j \in V_s $ edges are .
+The hardware cost of $ P $  is given by Eq.
+(2), and the software cost of $ P $ (i.e., software cost of the nodes and the communication cost) is given by Eq.
+(3):
+
+\begin{align}
+\ H_p &= \Sigma (v_i \;\in\; _Vh) H_i\\
+  S_p &= \Sigma (v_i \;\in\; _Vs) S_i + \Sigma (_(v_i,v_j) \in\; _Ep)\; C(V_i, V_j)
+\end{align}
+
+Three different optimization and decision problems can be defined.
+In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $ P $ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal (system with hard real-time constraints).
+So, based on Eq.
+(1) and Eq.
+(3) the optimization problem’s restrictions can be reformulated as: $ s(1-x) + c|E_x| \leq S_0 $, where $ x $ is the decision variable.
+Concerning the complexity of this problem, reference [1] demonstrates that it is NP-Hard.
+
+%----------------------------------------------
+\section{Partitioning problem using ILP-based,Genetic Algorithms}
+\label{ILPGA}
+%----------------------------------------------
+
+The ILP and GA were taken from [5] and [6].
+Both use slack variables in order to be possible to represent the constraints and to use commercial tools.
+However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to function ga of MATLAB [18]: the population size was set from 300 to 500, the Elite count changed from 2 (default value) to 50, and the number of Generations changed from 100* NumberOfVariables (default) to 75.
+
+%----------------------------------------------
+\section{Analysis of the partitioning problem using ESBMC}
+%----------------------------------------------
+
+\textcolor{blue}{Introducao da secao.}
 
@@
 However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
-\begin{lstlisting}
+
+\textcolor{blue}{Colocar um caption em todos os algoritmos.}
+
+\begin{lstlisting}[caption=Calculate Steps and Chunks]
 01. GetNextStep(){
@@
 
-\begin{lstlisting}
+\textcolor{blue}{Colocar um caption em todos os algoritmos.}
+
+\begin{lstlisting}[caption=Manager Controller]
 01. step = controller.GetNextStep();
@@
 %----------------------------------------------
-\section{Mathematical modeling}
-%----------------------------------------------
-
-The mathematical modeling was taken from [1], [2].
-
-%----------------------------------------------
-\subsection{Informal Model (or Assumptions)}
-%----------------------------------------------
-
-The informal model can be described by five characteristics.
-First, there is only one software context, i.e., there is just one general-purpose processor, and there is only one hardware context.
-The components of the system must be mapped to either one of these two contexts.
-Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
-Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, and energy consumption.
-Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
-Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
-The consequence of these assumptions is that scheduling does not need to be addressed in this work.
-Hardware components do not need scheduling, because the running time is assumed to be zero.
-Because there is only one processor, software components do not need to be scheduled as well.
-Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, where the focus is on bipartitioning [17].
-
-%----------------------------------------------
-\subsection{Formal Model}
-%----------------------------------------------
-
-The inputs of the problem are: A directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
-The vertices $ V = \{V_1,V_2,\dotso,V_n\} $ represent the nodes that are the components of the system that will be partitioned.
-The edges $ E $ represent communication between the components.
-Additionally, each node  $ V_i $ has a cost $ h(V_i) $ (or $ h_i $ of hardware (if implemented in hardware) and a cost $ s(s_i) $ (or $ s_i $ of software (if implemented in software).
-Finally, $ c(V_i,V_j) $ represents the communication cost between $ V_i $ and $ V_j $ if they are implemented in different contexts (hardware or software).
-
-Based on [1],  is called a hardware-software partition if it is a bipartition of $ V:P = (V_h, V_s) $ , where $ V_h \cup V_s = V $  and $ V_h \cap V_s = 0$  .
-The crossing $ E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h \;or\; v_i \in V_h, v_j \in V_s $ edges are .
-The hardware cost of $ P $  is given by Eq.
-(2), and the software cost of $ P $ (i.e., software cost of the nodes and the communication cost) is given by Eq.
-(3):
-
-\begin{align}
-\ H_p &= \Sigma (v_i \;\in\; _Vh) H_i\\
-  S_p &= \Sigma (v_i \;\in\; _Vs) S_i + \Sigma (_(v_i,v_j) \in\; _Ep)\; C(V_i, V_j)
-\end{align}
-
-Three different optimization and decision problems can be defined.
-In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $ P $ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal (system with hard real-time constraints).
-So, based on Eq.
-(1) and Eq.
-(3) the optimization problem’s restrictions can be reformulated as: $ s(1-x) + c|E_x| \leq S_0 $, where $ x $ is the decision variable.
-Concerning the complexity of this problem, reference [1] demonstrates that it is NP-Hard.
-
-%----------------------------------------------
-\section{Partitioning problem using ILP-based,Genetic Algorithms}
-\label{ILPGA}
-%----------------------------------------------
-
-The ILP and GA were taken from [5] and [6].
-Both use slack variables in order to be possible to represent the constraints and to use commercial tools.
-However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to function ga of MATLAB [18]: the population size was set from 300 to 500, the Elite count changed from 2 (default value) to 50, and the number of Generations changed from 100* NumberOfVariables (default) to 75.
-
-%----------------------------------------------
-\section{Analysis of the partitioning problem using ESBMC}
+\section{Verification Algorithm using ESBMC}
 %----------------------------------------------
@@
 
-\begin{lstlisting}
+\textcolor{blue}{Colocar um caption em todos os algoritmos.}
+
+\begin{lstlisting}[caption=Pseudocode describing ESBMC]
 01. Initialize Variables 
@@
 
-\begin{lstlisting}
+\textcolor{blue}{Colocar um caption em todos os algoritmos.}
+
+\begin{lstlisting}[caption=Pseudocode describing vZ]
 01.#Init Values
@@
 
-\textcolor{Green}{The vertices in the graphs correspond to high-level language instructions.
-Software and communication costs are time dimensional, and hardware costs represent the occupied area.}  \textbf{Graphs nao deveria ser Tabela?
-acho que esse texto veio daquele artigo expandido.
-esse paragrafo faz sentido ao senhor?
-}
-
 \textcolor{Red}{The results obtained that standout were the ILP and vZ.
@@
 The clustering algorithm when processed by the parallel ESBMC had 3.13 better performance than ILP, it`s time was 207 seconds and is very cloe to the solution of vZ that is 109 seconds.}
+
+\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
 
@@
 
-\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
+\textcolor{Red}{A tabela 3 é uma extensão da tabela 2.
+A tabela 3 mostra problemas com uma quantidade maior de nós e arestas, este aumento impacta diretamente no tempo de processamento.
+RC6 obteve time out para todas as versões do ESBMC, vZ e GA não obtiveram resposta correta, e ILP resolveu corretamente o problema.
+Fuzzy teve 3 time outs, 3 memory outs, e uma resposta incorreta.
+ILP foi o unico que conseguiu resolver Mars, GA respondeu incorretamente e todos os outros algoritmos deram TO ou MO.
+}
 
@@
 \end{table}
+\textcolor{Red}{Clustering descrito na tabela 2 parece ser o limiar para testar as ferramentas descritas, é importante destacar o numero de nós, fica evidente que nós superiores a 150 acarretam em TO,MO e respostas erradas por parte das ferramentas.
+ILP mostrou robustez ao conseguir resultados satisfatorios processando uma grande quantidade de nós e arestas.}
 
@@
 %----------------------------------------------
+
+\textcolor{blue}{Descrever mais dois ou três trabalhos relacionados, em especial, os artigos do vZ.}
 
@@
 
-% end of file template.tex
+% end of file template.texe os

### 2015-08-18 Docs/Paper/LaTex/template.tex
Added references

@@
 %1
-\bibitem{Jackson1995}
-Michael Jackson, ``{The world and the machine},'' {\em ICSE}, pp. 283--292, 1995.
+\bibitem{Arató2003}
+Arató, P., Juhász, S., Mann, Z.A., Orbán, A., Papp, D., ``{Hardware/software partitioning in embedded system design.
+In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp.
+192-202 (2003)
+
+%2
+\bibitem{Mann2007}
+Mann, Z.A., Orbán, A., Arató, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.
+
+%3
+\bibitem{Baier2008}
+Baier, C., Katoen, J-P. ``{Principles of Model Checking. The MIT Press, London (2008)}''
+
+%4
+\bibitem{Clarke2009}
+Clarke, E., Emerson, E., Sifakis, J. ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84 (2009)
+
+%5
+\bibitem{Trindade2015}
+Trindade, A., Cordeiro. L. ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York (2015)}''
+
+%6
+\bibitem{Trindade2014}
+Trindade, A., Cordeiro, L.
+``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software.
+In: Brazilian Symposium on Computing Systems Engineering (SBESC), 2014, Manaus – AM, Brazil.
+Anais SBESC},'' pp.
+1-6 (2014).
+
+%7
+\bibitem{Wu2014}
+Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
+``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP.
+In: International Conference on Software Engineering and Service Science (ICSESS)},'' pp.
+921,924, IEEE (2014)
+
+%8
+\bibitem{Tang2009}
+Tang, T., Lin, Y., Ren, X. ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905, IEEE (2010)
+
+%9
+\bibitem{Rao2009}
+Rao, S. ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken (2009)}''
+
+%10
+\bibitem{Biere2009}
+Biere, A. ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481, Amsterdam (2009)}''
+
+%11
+\bibitem{Clarke2004}
+Clarke, E., Kroening, D., Lerda, F.
+``{A Tool for Checking ANSI-C Programs.
+In: Proceedings of the Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 2988}'', pp.
+168-176 (2004)
+
+%12
+\bibitem{Armando2009}
+Armando, A., Mantovani, J., Platania, L.
+``{Bounded model checking of software using SMT solvers instead of SAT solvers.
+In: International Journal on Software Tools for Technology Transfer, Vol.
+11, n.
+1},'' pp.
+69-83 (2009)
+
+%13
+\bibitem{Ganai2006}
+Ganai, M., Gupta, A. ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801 (2006)
+
+%14
+\bibitem{Cordeiro2012}
+Cordeiro, L., Fischer, B., Marques-Silva, J. ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974 (2012)
+
+%15
+\bibitem{Cordeiro2011}
+Cordeiro, L., Fischer, B.
+``{Verifying multi-threaded software using SMT-based context-bounded model checking.
+In: Proceedings of the 33rd International Conference on Software Engineering},'' pp.
+331-340 (2011)
+
+%16
+\bibitem{Ramalho2013}
+Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
+``{SMT-Based Bounded Model Checking of C++ Programs.
+In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp.
+147-156, IEEE (2013)
+
+%17
+\bibitem{Teich2012}
+Teich, J. ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430 (2012)
+
+%18
+\bibitem{TheMathWorks2013}
+The MathWorks, Inc ``{MATLAB (version R2013a). Natick, MA (2013)}''
+
+%19
+\bibitem{Tranquillo2011}
+Tranquillo, J. ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool (2011)}''
+
+%20
+\bibitem{Hong2010}
+Hong, L., Cai, J.
+``{The application guide of mixed programming between MATLAB and other programming languages.
+In: Proceedings of the 2nd International Conference on Computer and Automation Engineering (ICCAE)},'' pp.
+185-189 (2010)
+
+%21
+\bibitem{Guthaus2001}
+Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
+``{MiBench: a free, commercially representative embedded benchmark suite.
+In: Proceedings of the IEEE 4th annual workshop on workload characterization},'' pp.
+3-14 (2001)
+
+%22
+\bibitem{Arató2005}
+Arató, P., Mann, Z.A., Orbán, A.
+``{Algorithmic aspects of hardware/software partitioning.
+In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol.
+1},'' pp.
+136–156 (2005)
+
+%23
+\bibitem{Dagum1998}
+Dagum, L., Menon, R. ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55, IEEE (1998)
+
+%24
+\bibitem{DeMoura2008}
+De Moura, L., Bjørner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)
+
+%25
+\bibitem{Brummayer2009}
+Brummayer, R., Biere, A.
+``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.
+In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 5505},'' pp.
+174–177, Springer (2009)
+
+%26
+\bibitem{Barrett2011}
+Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177, Springer (2011)
+
+%27
+\bibitem{Bozzano2005}
+Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
+``{MathSAT: Tight integration of SAT and mathematical decision procedures.
+In: Journal of Automated Reasoning, Springer (2005)}''
+
+%28
+\bibitem{Dutertre2014}
+Dutertre, B. ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744, Springer (2014)
+
+%29
+\bibitem{Holzmann2011}
+Holzmann, G.J., Joshi, R., Groce, A. ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857, IEEE (2011)
+
+%30
+\bibitem{Holzmann2012}
+Holzmann, G. ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171, Springer (2012)
+
+%31
+\bibitem{Wintersteiger2009}
+Wintersteiger, C., Hamadi, Y., De Moura, L.
+``{A Concurrent Portfolio Approach to SMT Solving.
+In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp.
+715-720, Springer (2009)
+
+%32
+\bibitem{Bjorner2015}
+Bjorner, N., Phan, A-D., Fleckenstein, L.
+``{vZ - An Optimizing SMT Solver.
+In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 9035},'' pp.
+194-199, Springer (2015)
+
+%33
+\bibitem{Qawasmeh2014}
+Qawasmeh, A., Malik, A., Chapman, B.
+``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.
+In: Parallel \& Distributed processing symposium work-shop (IPDPSW), 2014 IEEE International},'' pp.
+1049-1058, IEEE (2014)
+
+%34
+\bibitem{Bjørner2014}
+Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''
 

### 2015-08-18 Docs/Paper/LaTex/template.tex
Translated from PTBR to EN

@@
 The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-\textcolor{Red}{O problema de particionamento de HW-SW foi modelo em diversas plataformas como: MATLAB R2013a da MathWorks[19], Z3 um solucionador de teoremas da Microsoft Research[32] e ESBMC utilizando abordagens single-core e multi-core.
-Os algoritmos implementados são discutidos e suas particularidades destacadas, por fim, faz-se um comparativos dos resultados obtidos.
+\textcolor{Red}{The probem of HW-Sw partitioning was modelled on many platforms such as: MATLAB R2013a by MathWorks[19], Z3 a theorem solver by Microsoft Research[32] and ESBMC using single-core and multi-core approach.
+The implemented algorithms are discussed and it's main features highlighted, finally, a comparison of the results is made.
 }
@@
 
-\textcolor{Red}{O algoritmo ILP usa a intlinprog da biblioteca "Optimization Toolbox"[35], sua funcao é procurar o menor valor que satisfaca o problema descrito na Eq.(1).
-entretanto, para determinados tipos de problema ILP se torna inviavel dado o alto custo computacional, GA é uma forma de otimizar o tempo de processamento em detrimento da precisão, uma vez que GA não garante achar o valor máximo ou minimo para a problema.
-vZ usa funcoes de otimizacao e reescreve formulas em SMT para achar a solucao ideal, vZ apoia sua solucao em motores(OptSMT, MaxSMT).}
+\textcolor{Red}{The ILP algorithm uses intlinprog of the lib "Optimization Toolbox"[35], it's function is to search the lower value that satisfies the problem described in Eq.(1).
+however, for some types of problems is impossible to use ILP due to the high computational cost, GA is a way to optimize the processing time at the expense of precision, since GA does not guarantee to find the maximum or minimum of the problem.
+vZ uses optimization functions to rewrite the SMT formulas to find the ideal solution, vZ supports its solution in engines(OptSMT, MaxSMT).}
 
@@
 
-\textcolor{red}{Ferramentas como vZ e ESBMC tambem exploram o problema de otimizacao, ambas ferramentas tem como principal finalidade a precisão na resposta, problemas com uma quantidade muito grande de dados torna o tempo um impecilho.
-as secoes 2.2 e 2.3 demonstram como vZ e ESBMC usam respectivamente suas tecnicas para resolucao dos problemas de particionamento, espera-se destas tecnicas uma resposta exata em um tempo razoavel.}
+\textcolor{red}{Tools such as vZ and ESBMC also explores the optimization problem, both tools have its main purpose the precision, problems with a high quantity of data make the time an obstacle.
+The sections 2.2 and 2.3 shows how vZ and ESBMC uses its techniques to solve the paritioning problems, from those techniques an exact answer and reasonable time is exprected.}
 
@@
 
-\begin{lstlisting}[caption=Calculate Steps and Chunks]
+\begin{lstlisting}[caption=Steps Calculation using Intervals]
 01. GetNextStep(){
@@
 
-\begin{lstlisting}[caption=Manager Controller]
+\begin{lstlisting}[caption=Worker sample]
 01. step = controller.GetNextStep();
@@
 
-\textcolor{Red}{A tabela 3 é uma extensão da tabela 2.
-A tabela 3 mostra problemas com uma quantidade maior de nós e arestas, este aumento impacta diretamente no tempo de processamento.
-RC6 obteve time out para todas as versões do ESBMC, vZ e GA não obtiveram resposta correta, e ILP resolveu corretamente o problema.
-Fuzzy teve 3 time outs, 3 memory outs, e uma resposta incorreta.
-ILP foi o unico que conseguiu resolver Mars, GA respondeu incorretamente e todos os outros algoritmos deram TO ou MO.
-}
+\textcolor{Red}{The table 3 is an extenstion of table 2.
+The table 3 shows the problems with a higher node and edges quantity, this increase impact directly in the processing time.
+RC6 had time out for all versions of ESBMC, vZ e GA haven't had the right answer, and ILP solved correctly the problem.
+Fuzzy had 3 time outs, 3 memory outs, e a wrong answer.
+ILP was the only one that could solve Mars, GA solved incorrectly and all others had TO or MO.}
 
@@
 \end{table}
-\textcolor{Red}{Clustering descrito na tabela 2 parece ser o limiar para testar as ferramentas descritas, é importante destacar o numero de nós, fica evidente que nós superiores a 150 acarretam em TO,MO e respostas erradas por parte das ferramentas.
-ILP mostrou robustez ao conseguir resultados satisfatorios processando uma grande quantidade de nós e arestas.}
+\textcolor{Red}{Clustering described in the table 2 seems to be the limit to test the described tools, its important highlight that the number of nodes higher than 150 lead on TM or MO and wrong answers.
+ILP showed robustness, getting good results processing a high amount of ndoes and edges.}
 

### 2015-08-19 Docs/Paper/LaTex/template.tex
Fixed tex errors

@@
 Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
+
+%----------------------------------------------
+\subsection{OpenMP}
+%----------------------------------------------
+
+\textcolor{blue}{The OpenMP is a set of directives that augments the C/C++ and Fortran languages. OpenMP uses the fork-join model of parallel execution}
 
@@
 %1
-\bibitem{Arató2003}
-Arató, P., Juhász, S., Mann, Z.A., Orbán, A., Papp, D., ``{Hardware/software partitioning in embedded system design.
+\bibitem{Arato2003}
+Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D., ``{Hardware/software partitioning in embedded system design.
 In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp.
@@
 \bibitem{Mann2007}
-Mann, Z.A., Orbán, A., Arató, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.
+Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.
 
@@
 %22
-\bibitem{Arató2005}
-Arató, P., Mann, Z.A., Orbán, A.
+\bibitem{Arato2005}
+Arat\'o, P., Mann, Z.A., Orb\'an, A.
 ``{Algorithmic aspects of hardware/software partitioning.
@@
 \bibitem{DeMoura2008}
-De Moura, L., Bjørner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)
+De Moura, L., Bjorner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)
 
@@
 %34
-\bibitem{Bjørner2014}
+\bibitem{Bjorner2014}
 Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''

### 2015-08-19 Docs/Paper/LaTex/template.tex
Tex Update

@@
 \usepackage{mathtools} % Serve para as equacoes
+\usepackage{cite}
 
@@
 
-\begin{lstlisting}[caption=Code "SMT" using vZ, label=vZ]
+\begin{lstlisting}[caption=Code ``{SMT}'' using vZ, label=vZ]
 1. (declare-const K Int) 
@@
 
-\textcolor{blue}{The OpenMP is a set of directives that augments the C/C++ and Fortran languages. OpenMP uses the fork-join model of parallel execution}
+\textcolor{red}{The OpenMP is a set of directives for parallel programming that augments the C/C++ and Fortran languages.
+It supports the most processor architectures and operating systems such as Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
+OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
+OpenMP uses the fork-join model of parallel execution \cite{OpenMP1998}}
+
+\textcolor{red}{The most basic directive of OpenMP is the \#omp pragma parallel for. This directive parallelize the enclosing loop. You can see below an sample of its usage:}
+
+\begin{lstlisting}[caption=OpenMP basic sample]
+01.  int i;
+02.  #pragma omp parallel for
+03.  for (i = 0; i < 10; i++)
+04.      a[i] = 2 * i;
+\end{lstlisting}
+
+\textcolor{red}{In the example above, the for loop will be execute in parallel. Each iteration of the loop will be execute in a separated thread.}
 
@@
   \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
-	\caption{gestaucht}
+	\caption{ESBMC Architecture}
 \end{figure}
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
-	\caption{gestaucht}
+	\caption{ESBMC Multi-core}
 \end{figure}
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
-	\caption{gestaucht}
+	\caption{ESBMC Multi-core Optimized Sequential Approach}
 	\label{fig2}
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
-	\caption{gestaucht}
+	\caption{ESBMC Binary Approach}
 	\label{fig2}
@@
   \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
-	\caption{gestaucht}
+	\caption{Binary Step Calculation}
 	\label{fig2}
@@
 
+%35
+\bibitem{OpenMP1998}
+OpenMP Architecture Review Board, OpenMP C and C++
+Application Pogram Interface, Version 1.0, October 1998.
+http://www.openmp.org
+
 \end{thebibliography}

### 2015-08-23 Docs/Paper/LaTex/template.tex
Update Reviews Sec 2.2/3.2/8/9

--- 2015-08-19 Docs/Paper/LaTex/template.tex
@@
 \usepackage[english]{babel}
-\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams}
+\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
 
@@
 
+\renewcommand{\baselinestretch}{0.97}
+
 \begin{document}
 \title{Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems}
-\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Lucas Cordeiro}
+\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}
 
@@
            \and
-           L. Cordeiro \at
-              Electronic and Information Research Center, Federal University of Amazonas, Brazil
-              \email: lucascordeiro@ufam.edu.br           %  \\
+           H. Silva and L. Cordeiro \at
+              Federal University of Amazonas, Brazil
+              \email: prhsilva2012@gmail.com lucascordeiro@ufam.edu.br           %  \\
 }
@@
 \begin{abstract}
-\textcolor{blue}{Atualizar o abstract para descrever brevemente os novos algoritmos desenvolvidos}
 We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing.
-The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker.
+The multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
 Each instance checks for a different optimum value until the optimization problem is satisfied.
 The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-\textcolor{Red}{The probem of HW-Sw partitioning was modelled on many platforms such as: MATLAB R2013a by MathWorks[19], Z3 a theorem solver by Microsoft Research[32] and ESBMC using single-core and multi-core approach.
-The implemented algorithms are discussed and it's main features highlighted, finally, a comparison of the results is made.
-}
+We implement and evaluate our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
+We also compare our approaches to other state-of-the-art optimization tools: Matlab and Z3.
+Experimental results show that no single optimization tool solves all benchmarks; however, Matlab and Z3 are the most efficient ones to solve HW-SW partitioning problems, although ESBMC had a significant performance improvement from its sequential to parallel version.
+\end{abstract}
+
 \keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
-\end{abstract}
-
+
+%---------------------------------
 \section{Introduction}
+\label{Introduction}
+%---------------------------------
+
 Nowadays, with the strong development of embedded systems, the design phase plays an important role.
@@
 If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affects the overall development process, the quality and the lifecycle of the final system.
-Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in [1] and [2].
-
-In any HW and SW design of complex systems, more time is spent on verification than on construction [3].
+Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in ~\cite{Arato2003} and ~\cite{Mann2007}.
+
+In any HW and SW design of complex systems, more time is spent on verification than on construction ~\cite{Baier2008}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
@@
 This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification [4].
+Then, one can try to give a formal proof or otherwise establish that the program meets its specification ~\cite{Clarke2009}.
 Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors.
@@
 
-In [5] and [6] was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
+In ~\cite{Trindade2015} and ~\cite{Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
 The present work extends those studies since there is a substantial improvement in terms of the genetic algorithm and the SMT-based verification method, which has been extended with a multi-core architecture.
-Multi-core processors have been used in all segments of industry to implement high-performance computing [7].
+Multi-core processors have been used in all segments of industry to implement high-performance computing ~\cite{Wu2014}.
 In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution.
@@
 
-\textcolor{blue}{Deve-se citar as referencias usando o comando cite do latex}
-
-\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].}
-
-\textcolor{Red}{The ILP algorithm uses intlinprog of the lib "Optimization Toolbox"[35], it's function is to search the lower value that satisfies the problem described in Eq.(1).
-however, for some types of problems is impossible to use ILP due to the high computational cost, GA is a way to optimize the processing time at the expense of precision, since GA does not guarantee to find the maximum or minimum of the problem.
-vZ uses optimization functions to rewrite the SMT formulas to find the ideal solution, vZ supports its solution in engines(OptSMT, MaxSMT).}
-
+Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem and experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the vZ tool, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while vZ is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
 To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
-We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14].
+We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool ~\cite{Cordeiro2012}.
 As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
 
-\textcolor{blue}{Voces precisam citar as secoes usando o comando ref do latex. Para isso, cada secao deve conter um label.}
-\textcolor{Red}{This article is organized as follows: Section~\ref{background} gives a background on optimization, optimization with vZ, use of BMC technique with ESBMC, multi-cre ESBMC using OpenMP, ESBMC using optimized techniques of search to multiples cores with OpenMP.
-Section 3 describes the informal and formal mathematical modeling.
-Section 4 briefly describes th ILP and GA.
-The BMC method is based on SMT and is presented in section 5.
-The section 6 presents the paritioning model using vZ.
-The section 7 presents the experimental evaluation.
-The Section 8 discusses about the related works.
-Section 9 presents the conclusions and the future work.}
+This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, vZ, ESBMC, and OpenMP tools. 
+Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling.
+Section~\ref{ILPGA} briefly describes the ILP and GA algorithms, while Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using vZ.
+The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}.
+In Section~\ref{Experimental-Evaluation}, we present the results of our experiments using several embedded systems applications.
+In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.
 
@@
 
-\textcolor{blue}{Introduzir uma breve descrição da seção.}
-
-\textcolor{red}{Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9].
+The HW-SW partitioning problem is typically represented as a set of constraints and an objective function in linear programming.
+In this section, we describe the linear programming problem and present related tools that are used to model and solve the HW-SW partitioning problem.
+
+%----------------------------------------------
+\subsection{Optimization}
+\label{Optimization}
+%----------------------------------------------
+
+Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances~\cite{Rao2009}.
 In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
 The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
-Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].}
-%----------------------------------------------
-\subsection{Optimization}
-%----------------------------------------------
-
-There is no single method available for solving all optimization problems efficiently [9].
-The most known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
+Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
+
+There is no single method available for solving all optimization problems efficiently~\cite{Rao2009}.
+The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-Eq.
-(1) shows a typical linear programming problem, where  and  are vectors or matrixes that describe the constraints
+Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
 \begin{equation}
+\label{linear-programming-problem}
   minf^t x \: such that  = 
@@
 In some cases, the time to find a solution using ILP is impractical.
-Even with the use of powerful computers, a problem can take hours belerunning before an optimal solution is reached.
-If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA [9].
+Even with the use of powerful computers, a problem can take hours before an optimal solution is reached.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA~\cite{Rao2009}.
 The only drawback is that the found solution may not be the global minimum or maximum.
-
-\textcolor{red}{Tools such as vZ and ESBMC also explores the optimization problem, both tools have its main purpose the precision, problems with a high quantity of data make the time an obstacle.
-The sections 2.2 and 2.3 shows how vZ and ESBMC uses its techniques to solve the paritioning problems, from those techniques an exact answer and reasonable time is exprected.}
-
-%----------------------------------------------
-\subsection{\textcolor{Red}{Optimization with Vz}}
-%----------------------------------------------
-
-A SMT solver is a tool that verifies formula's satisfiability based in a set of rules SMT.
-Z3 is a SMT solver made by Microsoft Research, freely available to the community, that supports a variety of theories.
-Z3 brings a solver DPLL together with a correspondence machine for quantifiers.
-Z3 is implemented in C++.
-vZ is one of the tools implemented on the Z3 solver, it's base function is to optimize objectives within the logic context of constraints, it stands for the functions that make possible formulate optimized criteria.
-vZ includes an incremental version of MaxRes to MaxSAT and a Simplex to solve numbers without defined patterns, in it's core MaxSAT is responsible to the restrictions while OptSMT optimize the linear arithmetic objectives.
-Among all progress of Z3 using vZ the functions hightlights: maximize, minimize e assert-soft.
+Alternatively, tools such as vZ and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found.
+The following sections describe the main features of vZ and ESBMC tools.
+
+%----------------------------------------------
+\subsection{Solving Optimization Problems with Vz}
+\label{Optimization-with-Vz}
+%----------------------------------------------
+
+An SMT solver is a tool that verifies formula satisfiability based on a set of background theories (e.g., linear arithmetic, bitvectors, and arrays).
+Z3 is built on top of a Davis–Putnam–Logemann–Loveland solver together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}.
+vZ is one of the tools implemented in the SMT solver Z3; its base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.
+vZ includes an incremental version of  \textcolor{red}{Maximum Resiliency (MaxRes) ~\cite{Federica2008} to Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN}} and a Simplex to solve numbers without defined patterns.
+In Vz, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
+Vz provides functions that extend Z3 for solving optimization problems: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
 
@@
 \item{\textbf{maximize(T)}
-this instruction informs to the solver that a given variable T should be maximized, if possible maximize real, integer and bit vector values.}
+this function informs to the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
 \item{\textbf{minimize(T)}
-this instruction informs the solver that a given variable T should be minimized, the accepted types are the same as maximize.}
-\item{\textbf{Assert-Soft F :weight n}
-the instruction Asser-soft is a restriction to F, if possible add a weight n, the default is 1.}
+this function informs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}
+\item{\textbf{Assert-Soft F : weight n}
+the function Assert-Soft adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
 \end{itemize}
 
-Lets optimize (K+W), with the restrictions in (K \textless 2) and (W-K \textless 1), the expected result of the optimization described in the code below is 2.
-the model generated by vZ shows that K = 1 and W = 1.
-
-\begin{lstlisting}[caption=Code "SMT" using vZ, label=vZ]
+As an example, one can optimize $\left(K + W\right)$, with restrictions in $\left(K < 2\right)$ and $\left(W - K < 1\right)$.
+The expected result of this optimization problem described in the code below is $2$.
+In fact, the model generated by vZ shows that $K = 1$ and $W = 1$.
+
+\begin{lstlisting}[caption=SMT formula using vZ, label=vZ]
 1. (declare-const K Int) 
@@
 
-Accordingly to [34] the architecture of vZ can be described on the image XXX, initially the formulas and the SMT objectives are converted to problems MaxSAT, if there are many objectives, vZ invokes MaxSAT or OptSAT.
-To restrictions in real values using “Box”, vZ combines all linear arithmetic and calls the OptSMT.
-When we use “soft constrains” in the mode “lexicographic” vZ invokes MaxSAT.
+The vZ architecture is shown in Fig.~\ref{vZ-Architecture}.
+Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)\textcolor{red}{~\cite{Vasco2005}~\cite{Barth1995}}.
+If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints.
+\textcolor{red}{for box constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
+When we use "soft constrains'' in the mode "lexicographic'' vZ invokes MaxSAT using multiple calls for your engine.}
+%
 \begin{figure}[ht]
@@
   \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
-	\caption{vZ Architecture}
-	\label{fig2}
+	\caption{vZ Architecture~\cite{Bjorner2015}}
+	\label{vZ-Architecture}
 \end{figure}
 
-Z3 is available for platforms like C, C ++, Java, .NET and Python, it is possible to download the Z3 with vZ in http://z3.codeplex.com.
-API in python was used to formulate the optimization problem on the vZ tool.
+Z3 is available for platforms in C, C$++$, Java, .NET and Python; it is possible to download Z3 with vZ from~\cite{Z3API}.
+In this work, the python API is used to formulate the HW-SW partitioning problem in vZ tool.
 
@@
 \subsection{Bounded Model Checking with ESBMC}
-%----------------------------------------------
-
-Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior [3], [4].
+\label{Bounded-Model-Checking-with-ESBMC}
+%----------------------------------------------
+
+Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}.
 These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
-However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components [10].
+However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}.
 Much research has been devoted to mitigate this problem.
@@
 Among the recent techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in [10].
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in ~\cite{Biere2009}.
 In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
 
-The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less [10].
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in [11], [12], and [13].
-
-According to [14] and [15], SMT-based model checking can be used to verify the single- and multi-threaded software.
-In [16], ESBMC can also be used to model check C++ software based on SMT solvers.
-In [5] and [6] it was shown that it is possible to use ESBMC, as an optimization tool.
+The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less ~\cite{Biere2009}.
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in ~\cite{Clarke2004}, ~\cite{Armando2009}, and ~\cite{Ganai2006}.
+
+According to ~\cite{Cordeiro2012} and ~\cite{Cordeiro2011}, SMT-based model checking can be used to verify the single- and multi-threaded software.
+In ~\cite{Ramalho2013}, ESBMC can also be used to model check C++ software based on SMT solvers.
+In ~\cite{Trindade2015} and ~\cite{Trindade2014} it was shown that it is possible to use ESBMC, as an optimization tool.
 
@@
 \subsection{OpenMP}
-%----------------------------------------------
-
-\textcolor{blue}{The OpenMP is a set of directives that augments the C/C++ and Fortran languages. OpenMP uses the fork-join model of parallel execution}
+\label{OpenMP}
+%----------------------------------------------
+The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
+OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
+OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
+In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}
+
+The most basic directive of OpenMP is the ``\#pragma omp parallel for'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:
+
+\textcolor{blue}{Nao existem outras diretivas?
+Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao.
+Foi somente o ``\#pragma omp parallel for''??}
+
+\begin{lstlisting}[caption=OpenMP basic sample]
+01.  int i;
+02.  #pragma omp parallel for
+03.  for (i = 0; i < 10; i++)
+04.      a[i] = 2 * i;
+\end{lstlisting}
+
+In the above example, the for loop is executed in parallel \textcolor{blue}{Como?
+Cada posicao do array eh executada em um nucleo diferente?}.
+Each iteration of the loop is executed in a separated thread.
 
@@
 \section{Mathematical modeling}
-%----------------------------------------------
-
-The mathematical modeling was taken from [1], [2].
+\label{Mathematical-modeling}
+%----------------------------------------------
+
+The mathematical modeling of the HW-SW partitioning problem was taken from~\cite{Arato2003,Mann2007}.
 
@@
 \subsection{Informal Model (or Assumptions)}
+\label{Informal-Model-or-Assumptions}
 %----------------------------------------------
@@
 Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, where the focus is on bipartitioning [17].
+That configuration describes a first-generation co-design, where the focus is on bipartitioning ~\cite{Teich2012}.
 
@@
 \subsection{Formal Model}
-%----------------------------------------------
-
-The inputs of the problem are: A directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
-The vertices $ V = \{V_1,V_2,\dotso,V_n\} $ represent the nodes that are the components of the system that will be partitioned.
-The edges $ E $ represent communication between the components.
-Additionally, each node  $ V_i $ has a cost $ h(V_i) $ (or $ h_i $ of hardware (if implemented in hardware) and a cost $ s(s_i) $ (or $ s_i $ of software (if implemented in software).
-Finally, $ c(V_i,V_j) $ represents the communication cost between $ V_i $ and $ V_j $ if they are implemented in different contexts (hardware or software).
-
-Based on [1],  is called a hardware-software partition if it is a bipartition of $ V:P = (V_h, V_s) $ , where $ V_h \cup V_s = V $  and $ V_h \cap V_s = 0$  .
-The crossing $ E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h \;or\; v_i \in V_h, v_j \in V_s $ edges are .
-The hardware cost of $ P $  is given by Eq.
-(2), and the software cost of $ P $ (i.e., software cost of the nodes and the communication cost) is given by Eq.
-(3):
-
+\label{Formal-Model}
+%----------------------------------------------
+
+The inputs of the problem are: a directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
+The vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned.
+The edges $E$ represent communication between components.
+Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(s_i)$ (or $ s_i $) of software if implemented in software.
+Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).
+
+Based on Arat\'o {\it et al.}~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
+The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $v_i \in V_h, v_j \in V_s $.
+The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
+%
 \begin{align}
-\ H_p &= \Sigma (v_i \;\in\; _Vh) H_i\\
-  S_p &= \Sigma (v_i \;\in\; _Vs) S_i + \Sigma (_(v_i,v_j) \in\; _Ep)\; C(V_i, V_j)
+\label{hardware-costs}
+ H_p &= \Sigma_{\left(v_i \;\in\; V_h\right)} h_i,
 \end{align}
+%
+\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
+%
+\begin{align}
+\label{software-communication-costs}
+  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; E_p}\; c(V_i, V_j).
+\end{align}
 
 Three different optimization and decision problems can be defined.
-In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $ P $ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal (system with hard real-time constraints).
-So, based on Eq.
-(1) and Eq.
-(3) the optimization problem’s restrictions can be reformulated as: $ s(1-x) + c|E_x| \leq S_0 $, where $ x $ is the decision variable.
-Concerning the complexity of this problem, reference [1] demonstrates that it is NP-Hard.
+In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints).
+Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
+%
+\begin{align}
+\label{hw-sw-partitioning}
+s\left(1-x\right) + c|E_x| \leq S_0, 
+\end{align}
+%
+\noindent where $x$ represents the decision variable.
+Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard \textcolor{red}{\cite[p.~763]{Cormem}}.
 
@@
 
-The ILP and GA were taken from [5] and [6].
-Both use slack variables in order to be possible to represent the constraints and to use commercial tools.
+The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2014}.
+Both use slack variables in order to be possible to represent constraints and to use commercial tools.
 However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to function ga of MATLAB [18]: the population size was set from 300 to 500, the Elite count changed from 2 (default value) to 50, and the number of Generations changed from 100* NumberOfVariables (default) to 75.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
+
+%----------------------------------------------
+\section{Analysis of the partitioning problem using vZ}
+\label{Analysis-of-the-partitioning-problem-using-vZ}
+%----------------------------------------------
+
+Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using vZ functions~\cite{Bjorner2014}.
+A vZ logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
+Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
+
+The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
+Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
+In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
+\textit{Fobj} should be minimized to obtain the optimal hardware solution.
+To achieve this, two constraints are imposed to vZ: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to vZ that \textit{Fobj} should be minimized.
+Finally, the model is checked by Vz and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
+
+\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode]
+01.#Initialize Variables
+02.  Create vZ context 
+03.  Create binary vector (x)
+04.  Declare number of nodes, edges and S0
+05.  Declare hardware cost of each node as array (h) 
+06.  Declare software cost of each node as array (s)
+07.  Declare communication cost of each edge (c)
+08.  Declare transposed incidence matrix graph G (E)
+09.#Arithmetic Expressions
+10.  SC = s(1-x)
+11.  CMC = c*|EX|
+12.  Fobj =  x[i] * h[i]
+13.#Assert Constraints
+14.  Add constraints (SF + CMC <= S0)
+15.  Add constraints to minimize Fobj
+16.  Check Model
+17.  Print Result
+\end{lstlisting}
 
@@
 \section{Analysis of the partitioning problem using ESBMC}
-%----------------------------------------------
-
-\textcolor{blue}{Introducao da secao.}
+\label{Analysis-of-the-partitioning-problem-using-ESBMC}
+%----------------------------------------------
+
+As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
+This section proposes two multi-core model checking algorithms in order to speed up the HW-SW partitioning verification if compared to the sequential solution.
+
+%----------------------------------------------
+\section{Verification Algorithm using Sequential ESBMC}
+\label{Verification-Algorithm-using-ESBMC}
+%----------------------------------------------
+
+ESBMC pseudocode shows the algorithm with the same constraints and conditions placed on ILP and GA.
+Two values must be controlled to obtain the results and to perform the optimization.
+One is the initial software cost, as defined in Section~\ref{Formal-Model}.
+The other is the halting condition (code violation) that stops the algorithm.
+
+The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
+$S_0$ must also be defined, as the transposed incidence matrix and the identity matrix, as typically done in MATLAB.
+Here, matrices $A$ and $b$ are generated.
+At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015} and~\cite{Trindade2014}.
+
+It is possible to inform to ESBMC with which type of values the variables must be tested.
+Therefore, there is a declaration to populate all the decision variables $x$ with non-deterministic Boolean values.
+Those values that change for each test will generate a possible solution and obey the constraints.
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e.,$A.x \leq b$).
+
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
+To every test performed, the hardware hint is compared to the feasible solution.
+This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (\textit{true-false} statement).
+If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.
+
+The \textit{ASSERT} statement tests the objective function, {\it i.e.}, the hardware cost, and will stop if the hardware cost found is lower than or equal to the optimal solution.
+However, if \textit{ASSERT} returns a \textit{true} condition, {\it i.e.}, the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the \textit{ASSERT} generates a \textit{false} condition.
+When the \textit{false} condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
+That is the point in which the solution is presented (minimum HW cost).
+
+In the ESBMC algorithm, which is shown below, it is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.
+
+\begin{lstlisting}[caption=Pseudocode describing ESBMC]
+01. Initialize Variables 
+02. Declare number of nodes and edges
+03. Declare hardware cost of each node as array (h)
+04. Declare software cost of each node as array (s)
+05. Declare communication cost of each edge (c)
+06. Declare the initial software cost of (S0)
+07. Declare transposed incidence matrix graph G (E)
+08. Define the solutions variable (Xi) as Boolean
+09. main {
+10.  for TipH = 0 to Hmax do {
+11.   populate Xi with nondeterministic/test values
+12.   Calculate s(1-x)+c|Ex| and store at variable
+13.   Requirement isured by Assume (Variable <= S0)
+14.   Calculate Hp cost Based on value tested of Xi
+15.   Violation check with Assert(Hp > TipH)
+16.  }
+17. }
+\end{lstlisting}
+
+%In the multi-core ESBMC algorithm, the only difference is the fact that the value of $ TipH $ and its range is not declared in the algorithm, %as shown in ESBMC Pseudocode.
+The proposed approach is invoked for each test problem, as follows:
+%$ esbmc-parallel <Filename.c> \; <hminvalue> \; <Hmax> $
+
+%Where $ <Filename.c> $ is the optimization problem described in ANSI-C format, $  <hminvalue> $ is the minimum (zero to HW-SW partitioning %problem) and $ <Hmax> $ is the maximum hardware cost for the specified problem.
+
+%Therefore, the algorithm starts different ESBMC instances using different optimization values, in ascending order, for $ Hmax $ in order to %find a violation.
+If all instances finish and no violation is found, then multi-core ESBMC starts new $ N $ instances.
+When a violation is %found, it reports time and hardware cost.
+If multi-core ESBMC tests all the possibilities for the hardware cost and has not found a violation, %then it reports: $ Violation not found $.
 
@@
 \subsection{Multi-core ESBMC with OpenMP}
-%----------------------------------------------
-
-Nowadays, although the CPU used to perform tests usually has a modern multi-core architecture, with the ability to run several threads on different processing cores, ESBMC verification runs are still performed only in a single-core.
-For instance, if the processor has 8 processing cores available, only one is used for the verification and the others remain idle.
-There is a significant unused hardware resource during this process.
-
-Fig.1 shows the ESBMC architecture, which consists of the C/C++ parser, GOTO Program, GOTO Symex, and SMT solver [16].
-In particular, ESBMC compiles the C/C++ code into equivalent GOTO\hyp{}programs (i.e., control-flow graphs) using a gcc-compliant style.
-The GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($ C $) and properties ($ P $); finally it generates two sets of equations (i.e.,\:$ C \land \neg P $ ) which are checked by an SMT solver.
+\label{Multi-core-ESBMC-with-OpenMP}
+%----------------------------------------------
+
+Typically, ESBMC verification runs are performed only in a single-core.
+If the processor provides $8$ processing cores, only one is used for the verification and the others remain idle.
+Thus, there is a significant unused hardware resource during this process.
+Fig.~\ref{ESBMC-Architecture} shows the ESBMC architecture, which consists of the C/C++ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}.
+In particular, ESBMC compiles the C/C++ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
+The GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
 
 The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
-Currently, the SMT solvers supported by ESBMC are: Z3 [24], Boolector [25], MathSAT [26], CVC4 [27], and Yices [28].
+Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}.
 Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
@@
   \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
-	\caption{gestaucht}
+	\caption{ESBMC Architecture}
+	\label{ESBMC-Architecture}
 \end{figure}
 
-To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library [23] is used in this present work as a front-end for ESBMC.
-
+To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC.
+
+\textcolor{blue}{Mover este texto para a secao de background sobre OpenMP?...
 OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications.
-The API provides a directive-based programming approach to write parallel versions of C/C++ programs [33].
-In OpenMP, the implementation is based on the fork-join model.
+The API provides a directive-based programming approach to write parallel versions of C/C++ programs ~\cite{Qawasmeh2014}.}
+
+As described in Section~\ref{OpenMP}, in OpenMP the implementation is based on the fork-join model.
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes (i.e., the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode [7].
-Fig.
-2 shows our approach called “Multi-core ESBMC”.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
+Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
+%
 \begin{figure}[ht]
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
-	\caption{gestaucht}
+	\caption{ESBMC Multi-core.}
+	\label{ESBMC-Multi-core}
 \end{figure}
 
-Multi-core ESBMC obtains the problem specification represented by a C program, which is violated when the correct optimum value () parameter is reached; Multi-core ESBMC starts a parallel region with  different instances of ESBMC, based on the number of available processing cores.
-All these ESBMC instances run independently of each other, as shown in Fig.
-2; note that there is no shared-memory (or message-passing) mechanism among the threads.
+Multi-core ESBMC obtains the problem specification represented by a C program.
+The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; Multi-core ESBMC starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
+All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}.
+Note that there is no shared-memory (or message-passing) mechanism among the threads.
 In particular, different threads are managed by the OpenMP API, which is responsible for the thread lifecycle: start, running, and dead states, using different values as condition.
-After executing  instances, if there is no code violation, then multi-core ESBMC starts  new instances again.
+After executing $N$ instances, if there is no code violation, then multi-core ESBMC starts new instances again.
 During the parallel region execution, if a violation is found in any running thread, then it presents the counterexample with the violation condition and the verification time.
@@
 %----------------------------------------------
-\subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
-%----------------------------------------------
-
-\textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.
-Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.}
+\subsection{Multi-core ESBMC with OpenMP using Binary Search}
+\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
+%----------------------------------------------
+
+The previous parallelization is implemented by continuously forking ESBMC instances until the first violation is found.
+However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some period of time.
 
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
-	\caption{gestaucht}
-	\label{fig2}
+	\caption{ESBMC Multi-core Optimized Sequential Approach. \textcolor{blue}{A fonte desta figura esta diferente da Fig.~\ref{ESBMC-Multi-core}}}
+	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
 \end{figure}
 
-\textcolor{Red}{Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found.
-This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization.}
-
-\textcolor{Red}{The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution.
-As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible.
-The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
+Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available.
+This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.
+
+The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution.
+A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced as much as possible.
+The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
+%
 \begin{figure}[ht]
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
-	\caption{gestaucht}
-	\label{fig2}
+	\caption{ESBMC Binary Approach}
+	\label{ESBMC-Binary-Approach}
 \end{figure}
 
-\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20.
-When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval.
-Therefore, there would be 2 new intervals, one from 1 to 9 and another one from 11 to 20, and the returned step would be 10.
-The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals.
-}
+As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$.
+When the next available core asks for a step to be executed, the controller obtains the largest interval ({\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$).
+The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
+%
 \begin{figure}[ht]
@@
   \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
-	\caption{gestaucht}
-	\label{fig2}
+	\caption{Binary Step Calculation}
+	\label{Binary-Step-Calculation}
 \end{figure}
 
-\textcolor{Red}{Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed.
-For instance, in the example above, if step 10 returns false, then one can conclude that all steps after 10 is false as well.
-However, if the same step 10 is true, we can assume that all steps before 10 is true as well.}
-
-\textcolor{Red}{As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals.
+Note that there might gaps between steps, which are produced by the customized binary search.
+For instance, in the example shown in~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well.
+However, if the same step $10$ returns \textit{true}, we can assume that all steps before $10$ is \textit{true} as well.
+As a result, an auxiliary method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals.
 This approach leads to a high impact in the verification time.
-However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
-
-\textcolor{blue}{Colocar um caption em todos os algoritmos.}
-
-\begin{lstlisting}[caption=Steps Calculation using Intervals]
+However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.
+
+\textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}
+
+\begin{lstlisting}[caption=Steps Calculation using Intervals,label=Steps-Calculation-using-Intervals]
 01. GetNextStep(){
@@
 \end{lstlisting}
-\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed.
-From line 4 to 9 the algorithm finds the biggest interval.
-Then from the line 10 the biggest interval is removed and the median is calculated in the line 11.
-Then 2 new intervals are created, the left side on line 14 and the right side on the line 16.
-At the end, the median is returned.}
-
-\textcolor{blue}{Colocar um caption em todos os algoritmos.}
-
-\begin{lstlisting}[caption=Worker sample]
+
+Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
+From lines $4$ to $9$, the algorithm finds the largest interval.
+Then, from the line $10$ the largest interval is removed and the median is calculated in line $11$.
+After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$).
+At the end, the median is returned.
+
+\begin{lstlisting}[caption=Worker sample,label=worker-sample]
 01. step = controller.GetNextStep();
@@
 \end{lstlisting}
-\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances.
-The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2).
-While the step is being executed, the controller checks whether this step is still needed (line 4).
-If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}
-
-%----------------------------------------------
-\section{Verification Algorithm using ESBMC}
-%----------------------------------------------
-
-ESBMC pseudocode shows the algorithm with the same restrictions and conditions placed on ILP and GA.
-Two values must be controlled to obtain the results and to perform the optimization.
-One is the initial software cost, as defined in Section III.G.
-The other is the halting condition (code violation) that stops the algorithm.
-
-The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
-also must be defined, as the transposed incidence matrix and the identity matrix, as typically done in MATLAB.
-Here, the matrices A and b are generated.
-At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in [5] and [6].
-
-It is possible to tell the ESBMC with which type of values the variables must be tested.
-Therefore, there is a declaration to populate all the decision variables $ x $ with non-deterministic Boolean values.
-Those values that change for each test will generate a possible solution and obey the restrictions.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e.,$ A.x \leq b $ ).
-
-A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
-To every test performed, the hardware hint is compared to the feasible solution.
-This is accomplished by an ASSERT statement at the end of the algorithm, a predicate that controls the halt condition (true-false statement).
-If the predicate is FALSE, then the optimization is finished, i.e., the solution was found.
-The ASSERT statement tests the objective function, i.e., the hardware cost, and will stop if the hardware cost found is lower than or equal to the optimal solution.
-However, if ASSERT returns a TRUE condition, i.e., the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the ASSERT generates a FALSE condition.
-When the FALSE condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
-That is the point in which the solution is presented (minimum HW cost).
-
-In the ESBMC algorithm, which is shown below, it is not necessary to add slack variables because the modulus operation is kept, which reduces the number of variables to be solved.
-
-\textcolor{blue}{Colocar um caption em todos os algoritmos.}
-
-\begin{lstlisting}[caption=Pseudocode describing ESBMC]
-01. Initialize Variables 
-02. Declare number of nodes and edges
-03. Declare hardware cost of each node as array (h)
-04. Declare software cost of each node as array (s)
-05. Declare communication cost of each edge (c)
-06. Declare the initial software cost of (S0)
-07. Declare transposed incidence matrix graph G (E)
-08. Define the solutions variable (Xi) as Boolean
-09. main {
-10.  for TipH = 0 to Hmax do {
-11.   populate Xi with nondeterministic/test values
-12.   Calculate s(1-x)+c|Ex| and store at variable
-13.   Requirement isured by Assume (Variable <= S0)
-14.   Calculate Hp cost Based on value tested of Xi
-15.   Violation check with Assert(Hp > TipH)
-16.  }
-17. }
-\end{lstlisting}
-
-In the multi-core ESBMC algorithm, the only difference is the fact that the value of $ TipH $ and its range is not declared in the algorithm, as shown in ESBMC Pseudocode.
-The proposed approach is invoked for each test problem, as follows:
-$ esbmc-parallel <Filename.c> \; <hminvalue> \; <Hmax> $
-
-Where $ <Filename.c> $ is the optimization problem described in ANSI-C format, $  <hminvalue> $ is the minimum (zero to HW-SW partitioning problem) and $ <Hmax> $ is the maximum hardware cost for the specified problem.
-
-Therefore, the algorithm starts  different instances of ESBMC using the different optimization values, in ascending order, for $ Hmax $ in order to find a violation.
-If all instances finish and no violation is found, then multi-core ESBMC starts new $ N $ instances.
-When a violation is found, it reports time and hardware cost.
-If multi-core ESBMC tests all the possibilities for the hardware cost and has not found a violation, then it reports: $ Violation not found $.
-
-%----------------------------------------------
-\section{\textcolor{Red}{Analysis of the partitioning problem using vZ}}
-%----------------------------------------------
-
-The code below shows the conditions applied on ILP, GA and ESBMC converted to the vZ tool described in [34] and [35].
-
-A vZ context is created, it receives the restrictions and returns the model if a solution to the set of rectictions exists.
-Later the number of nodes are declared, number of edges, the number of, the cost of hardware, cost of software, cost of communication and the incidence matrix E.
-
-The arithmetic declarations described on the lines 10, 11,12 e 13 of the code are a transcription of the formula $ S(1-x) + C|Ex| \leq S{0} $ described on the section III.B, refers to the cost of software (SF).
-Note that in the line 11 a temporary variable called TMP is created to represent $C|Ex|$  , then the product between the absolute value of TMP and the vector C declared in the line 07, then the result of the cost of communication is generated (CMC).
-
-In the line 13, the Fobj (Objective Function) is declared.
-It is a product between the cost of hardware with the vector that contains the values 0 and 1.
-Fobj should be minimized to get the best hardware solution .
-
-Two restrictions are imposed, the first refers to the sum between the cost of software and communication, the result of the sum should be less than , the second restriction tells to vZ that Fobj should be minimized.
-So the model is checked, once a solution that complains the restrictions, the value of the Fobj is printed.
-
-\textcolor{blue}{Colocar um caption em todos os algoritmos.}
-
-\begin{lstlisting}[caption=Pseudocode describing vZ]
-01.#Init Values
-02.  Create vZ context 
-03.  Create binary vector (x)
-04.  Declare number of nodes, edges and S0
-05.  Declare hardware cost of each node as array (h) 
-06.  Declare software cost of each node as array (s)
-07.  Declare communication cost of each edge (c)
-08.  Declare transposed incidence matrix graph G (E)
-09.#Arithmetic
-10.  SF receive s(1-x)
-11.  TMP vector receive E|x| 
-12.  CMC receive c*|EX|
-13.  Fobj receive  x[i] * h[i]
-14.#Asserts
-15.  Add restrictions (SF + CMC <= S0)
-16.  Add restrictions to minimize Fobj
-17.  Check Model
-18.  Print Result
-\end{lstlisting}
-
-Nice team.
+
+Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
+The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$).
+While the step is being executed, the controller checks whether this step is still needed (line $4$).
+If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
 
@@
 \section{Experimental Evaluation}
-%----------------------------------------------
-
-ESBMC 1.24 running on a 64-bit Ubuntu 14.04.1 LTS operating system was used.
-Version 2.0.1 of Boolector SMT-solver [25] (freely available) was used as well.
-For the ILP and GA formulations, MATLAB R2013a from MathWorks with Parallel Computing Toolbox was used [18].
-MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20].
-\textcolor{Red}{The built in Z3 tool vZ [34] available freely was also used.
-A parallel approach of the ESBMC sequential search ascending, descending and binary was implemented in c++11}.
-A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used.
-Each time was measured 3 times in GA (average taken) and just once in ESBMC and ILP.
-The reason is that GA times are not so close as ESBMC and ILP.
-A time out condition (TO) is reached when the running time is longer than 7,200 seconds.
-A memory out (MO) occurs when the tool reaches 24GB of memory.
-TABLE I.
-lists the benchmarks1.
+\label{Experimental-Evaluation}
+%----------------------------------------------
+
+This section is split into two parts.
+The setup is described in Section~\ref{Experimental-Setup} while Section~\ref{Experimental-Results} describes a comparison among Matlab~\cite{TheMathWorks2013}, vZ~\cite{Bjorner2015}, and ESBMC~\cite{Trindade2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
+
+%----------------------------------------------
+\subsection{Experimental Setup}
+\label{Experimental-Setup}
+%----------------------------------------------
+
+To perform the experiments, some test vectors provided by Mann {\it et al.}~\cite{Mann2007} are used, as shown in Table~\ref{Description-of-Benchmarks}.
+The vertices in the graphs correspond to high-level language instructions.
+Software and communication costs are time dimensional, and hardware costs represent the occupied area.
+The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
+The clustering and fuzzy test vectors benchmarks are designed from Mann et al.~\cite{Mann2007} and are significantly larger benchmarks.
+From the same authors,  very complex benchmarks to test the limits of the applicability of techniques are collected (RC$6$ and Mars).
 
@@
 
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check [21]\\
-\hline
-\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree [21]\\
-\hline
-
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph [21]\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\hline
+\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
+\hline
+
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
 \hline
@@
 \end{tabular}
+\label{Description-of-Benchmarks}
 \end{table}
 
-\textcolor{Red}{The results obtained that standout were the ILP and vZ.
-Vz solved correctly 4 of 7 algorithms, got an false positive in the algorithm RC6, the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}
-
-\textcolor{Red}{In contrast, ILP solved correctly 6 of 7 algorithms, do not had any false positive, the resolution time is bigger compared with vZ and lower compared with ESBMC, it shows that ILP is optimized to solve problems but has an average resolution time.}
-
-\textcolor{Red}{The only technique aqble to solve all algorithms was GA, however it's precision was not satisfatory, it had error rate between -37.6\% and 29.0\%.}
-
-\textcolor{Red}{All versions of parallel ESBMC got better results compared with the sequential approach, stands out the binary version described on the section 2.5, the performance get better as the number of nodes and edges get bigger.
-The clustering algorithm when processed by the parallel ESBMC had 3.13 better performance than ILP, it`s time was 207 seconds and is very cloe to the solution of vZ that is 109 seconds.}
-
-\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
+ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used.
+A parallel approach of the ESBMC sequential ascending, descending, and binary search are implemented in C++$11$.
+Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
+For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}.
+MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
+vZ as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
+
+A desktop with $24$GB of RAM and i$7$ ($8$-cores) from Intel with CPU clock of $3$.$40$ GHz was used.
+Each time was measured $3$ times in GA (average taken) and just once in vZ, ESBMC, and ILP.
+The reason is that GA times are not so close as ILP, vZ, and ESBMC.
+A time out condition (TO) is reached when the running time is longer than $7200$ seconds.
+A memory out (MO) occurs when the tool reaches $24$GB of memory.
+
+%----------------------------------------------
+\subsection{Experimental Results}
+\label{Experimental-Results}
+%----------------------------------------------
+
+ESBMC implement four approaches: ESBMC, ESBMC Multicore (MC), ESBMC Parallel Sequential (PS), and ESBMC Parallel binary (PB).
+
+\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS.}
+
+\begin{itemize}
+\item{\textbf{ESBMC: }\textcolor{Red}{
+This strategy uses only one core to solve the partitioning problem, it is described in the section 2.3.}}
+\item{\textbf{ESBMC MC:  }\textcolor{Red}{
+Uses a sequential strategy \{1\:,2\:,\:...\:, \:Hmax\} , there is not parallel controller in this approach, it is described in the section 5.1.}}
+\item{\textbf{ESBMC PS:  }\textcolor{Red}{
+This approach is similar with ESBMC MC, however it uses a more optimized way to launch the ESBMC instances, it is described in the section 5.2.}}
+\item{\textbf{ESBMC PB:  }\textcolor{Red}{
+The binary approach uses a parallel binary search, it is described in the section 5.2.}}
+\end{itemize}
+
+\textcolor{red}{There is no single tool for solving all benchmarks efficiently.
+In particular, Vz solves $4$ out of $7$ benchmarks, in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}
+
+In contrast to vZ, ILP solves $6$ out of $7$ benchmarks.
+When ILP produces a result, it always provides the optimal solution.
+On the one hand, ILP execution time is slower than vZ in all benchmarks, which are supported by vZ.
+On the other hand, ILP is faster than ESBMC in all benchmarks, except for the clustering.
+
+\textcolor{blue}{Falta descrever os resultados da melhor abordagem do ESBMC quando comparado ao vZ e ILP.}
+
+The only technique that is able to solve all benchmarks is GA; however, its precision is not satisfactory since it produces an error rate between $-37.6$\% and $29.0$\%.
+
+Note that all ESBMC parallel versions produce better results than the sequential one.
+In particular, the ESBMC-PB implementation outperforms all other ESBMC approaches; the ESBMC-PB performance improves as the number of nodes and edges increase.
+One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than vZ.
+
+Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC-PB) tools.
 
 \begin{table}[h]
-\caption {Results of the benchmarks}
+\caption {Experimental results of the simple benchmarks}
 \small
@@
 \end{tabular}
+\label{experimental-results-matlab-vz-esbmc}
 \end{table}
 
-\textcolor{Red}{The table 3 is an extenstion of table 2.
-The table 3 shows the problems with a higher node and edges quantity, this increase impact directly in the processing time.
-RC6 had time out for all versions of ESBMC, vZ e GA haven't had the right answer, and ILP solved correctly the problem.
-Fuzzy had 3 time outs, 3 memory outs, e a wrong answer.
-ILP was the only one that could solve Mars, GA solved incorrectly and all others had TO or MO.}
+Table~\ref{Experimental-results-of-the-complex-benchmarks} is an extension of Table~\ref{experimental-results-matlab-vz-esbmc}, where complex benchmarks are used.
+In particular, Table~\ref{Experimental-results-of-the-complex-benchmarks} shows problems with a higher number of nodes and edges; this increase directly influences the processing time of all tools.
+RC$6$ produced time out for all versions of ESBMC, vZ e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one.
+Fuzzy produced time-outs and memory-outs in all tools.
+ILP was the only one to solve Mars, while GA solved incorrectly all benchmarks.
 
 \begin{table}[h]
-\caption {Results of the benchmarks}
+\caption{Experimental results of the complex benchmarks}
 \small
@@
 \end{tabular}
+\label{Experimental-results-of-the-complex-benchmarks}
 \end{table}
-\textcolor{Red}{Clustering described in the table 2 seems to be the limit to test the described tools, its important highlight that the number of nodes higher than 150 lead on TM or MO and wrong answers.
-ILP showed robustness, getting good results processing a high amount of ndoes and edges.}
+
+Clustering described in Table~\ref{experimental-results-matlab-vz-esbmc} seems to be the limit to test the described tools, note that more than $150$ nodes lead to TO and MO.
+ILP shows robustness and produces results even for a high amount of nodes and edges.
 
@@
 \section{Related Work}
-%----------------------------------------------
-
-\textcolor{blue}{Descrever mais dois ou três trabalhos relacionados, em especial, os artigos do vZ.}
-
-Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution [2], to use heuristics to speed up performance time [1], and hybrid ones [22].
+\label{Related-Work}
+%----------------------------------------------
+
+Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.
 
@@
 In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages (e.g., C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
-In [16] it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and [14] uses the ESBMC model checker for embedded ANSI-C software.
-In [5] and [6] it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification [29], and modifications of internal search engines to support parallelism [30], but there is still the need for initiatives related to parallel SMT solvers [31].
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories [32].
+In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software.
+In~\cite{Trindade2015} and~\cite{Trindade2014} it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to support parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}.
+
+\textcolor{Red}{A ferramenta vZ ~\cite{Bjorner2014} e ~\cite{Bjorner2015} oferece ganhos substanciais em problemas de otimizacao.
+O trabalho descrito em ~\cite{Pavlinovic2015} relata erros em compiladores e suas confusas mensagens, a abordagem classica é mostrar ao programador qual o local de erro e um dica sobre o mesmo, entretanto, outras fontes de erros não são consideradas, a abordagem mais indicada seria considerar todas as fontes de erros possiveis.
+Para modelar o problema são geradas as restricoes usando EasyOCaml, e vZ é responsavel por computar a menor caminho de erros.
+o Algoritmo descrito em ~\cite{Pavlinovic2015} mostrou-se eficiente frente as outras abordagens.}
+
+\textcolor{Red}{O problema abordado neste trabalho utiliza objetivo unico, minimizacao da funcao objetivo, em ~\cite{Patrick2015} é comparada as ferramentas OptiMathSAT com vZ para problemas de verificacao de SW.
+OptiMathSAT usando multiplos objetivos funciona muito melhor do que vZ com mulitplos objetivos, contudo, para problemas com objetivos unicos vZ se comparta melhor do que OptiMathSAT.}
 
@@
 \section{Conclusions}
-%----------------------------------------------
-
-Concerning the comparative tests, with the four techniques presented in this paper to solve HW-SW partitioning, it was evident that none of them is indicated to partition problems with more than 400 nodes.
-The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
-If we consider less than 400 nodes, then it is possible to use ILP as the best solution provider.
-If the problem to be solved has 150 nodes or less, then ESBMC represents a feasible alternative.
-GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
-This error may be reduced by changing some parameters.
+\label{Conclusions}
+%----------------------------------------------
+
+\textcolor{Red}{After presented the 7 techniques and the experimental results to the partitioning problem solution of HW-SW became evident that for a quantity of nodes bigger than 300, the best option is ILP.
+Below 300 the best option turns out to be vZ, its response time is superior and notorious.
+ESBMC is a viable tool for a quantity of nodes lower than 150.}  GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
+This error may be reduced by changing some parameters.The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
 
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-However, ESBMC has a BSD-style license and can be downloaded and used for free.
-Concerning the two versions of ESBMC, it is possible to conclude that Multi-core ESBMC had better performance results than pure ESBMC.
-Thus, considering that nowadays the processors have more and more cores, when modeling the problem, it is possible to consider multi-core ESBMC as an alternative to solve the partitioning problem.
-Future work can be done to decrease the processing time of ESBMC (solver included).
+However, ESBMC and Vz has BSD-Style license and MIT respectively and can be downloaded and used for free.\textcolor{Red}{ The benchmarks results shows the improvement of ESBMC when using a parallel approach, all three parallel techniques mentioned in this paper had expressive results.
+The biggest highlight goes to the ESBMC PB (Parallel Binary) which behaves very well for an intermediate amount of edges and nodes.}Thus, considering that nowadays the processors have more and more cores, when modeling the problem, it is possible to consider multi-core ESBMC as an alternative to solve the partitioning problem.
 
@@
 \textcolor{Red}{On future works we will address improvements in the ESBMC, we hope to remove the parallel layer on top of ESBMC and implement it on it's core, it would optimize the processing time.}
-\section{References}
+
+%----------------------------------------------
+%\section{References}
+%\label{References}
+%----------------------------------------------
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%35
+\bibitem{OpenMP1998}
+OpenMP Architecture Review Board, OpenMP C and C++
+Application Pogram Interface, Version 1.0, October 1998.
+http://www.openmp.org
+
+%36
+\bibitem{Z3API}
+Magellan, ``{Source code and documentation},''
+  \url{https://github.com/Z3Prover/z3}, Accessed 18 August 2015.
+
+%37
+\bibitem{GA}
+URFJ, ``{Algoritmos Genéticos: Fundamentos e Aplicações. Marcio Nunes de Miranda},''
+  \url{http://www.nce.ufrj.br/GINAPE/VIDA/alggenet.htm}, Accessed 18 August 2015.
+
+%38
+\bibitem{NarodytskaN}
+Narodytska, N., Bacchus, F. {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution'', Proceedings of the Twenty-Eighth AAAI Conference on Artificial Intelligence.}
+
+%39
+\bibitem{Federica2008}
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B., {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364/2008, 116-131
+
+%40
+\bibitem{Barth1995}Barth, P., Davis-Putnam, A., {``Enumeration Algorithm for Linear
+Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science, 1995.
+
+%41
+\bibitem{Vasco2005}Vasco, M., Marques-Silva, J., {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
+
+%42
+\bibitem{Pavlinovic2015}Pavlinovic, Z., King, T., Wies, T.,{``Practical SMT-Based Type Error Localization''}, ICFP’15, August 31 – September 2, 2015, Vancouver, BC, Canada c 2015 ACM.
+978-1-4503-3669-7/15/08
+
+%43
+\bibitem{Patrick2015}Sebastiani, R., Trentin, T., {``OptiMathSAT: A Tool for Optimization Modulo Theories''}
+
+%43
+\bibitem{Cormem}Cormem, H., Charles, E., {``Algoritmos, Teoria e Prática''}, Chapter 34, Pag 763.
+
 \end{thebibliography}

### 2015-08-24 Docs/Paper/LaTex/template.tex
review conclusions

@@
 %              Fax: +123-45-678910\\
-              \email{\{iurybessa, hussamaibrahim\}@ufam.edu.br and\\{\{rdegelo, esj.galvao\}@gmail.com}}          %  \\
+              \email{\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com}          %  \\
 %             \emph{Present address:} of F. Author  %  if needed
@@
 
-\textcolor{Red}{After presented the 7 techniques and the experimental results to the partitioning problem solution of HW-SW became evident that for a quantity of nodes bigger than 300, the best option is ILP.
-Below 300 the best option turns out to be vZ, its response time is superior and notorious.
-ESBMC is a viable tool for a quantity of nodes lower than 150.}  GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
-This error may be reduced by changing some parameters.The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
+We presented four approaches to solve the HW-SW partitioning problem and compared them to other three state-of-the-art techniques.
+Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
+Below that, the best option turns out to be vZ since its execution time is faster and notorious.
+ESBMC is a viable alternative for a number of nodes lower than $150$.
+GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
+This error may be reduced by changing some parameters.
+
+%The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
 
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-However, ESBMC and Vz has BSD-Style license and MIT respectively and can be downloaded and used for free.\textcolor{Red}{ The benchmarks results shows the improvement of ESBMC when using a parallel approach, all three parallel techniques mentioned in this paper had expressive results.
-The biggest highlight goes to the ESBMC PB (Parallel Binary) which behaves very well for an intermediate amount of edges and nodes.}Thus, considering that nowadays the processors have more and more cores, when modeling the problem, it is possible to consider multi-core ESBMC as an alternative to solve the partitioning problem.
-
-Finally, there is an issue about 150 nodes problem, since it seems to be the limit of ESBMC.
+However, ESBMC and Vz have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+Experimental results also pointed to an improvement of ESBMC, when using a parallel approach.
+In particular, all three parallel approaches described in this paper produced expressive results.
+The fastest ESBMC approaches is ESBMC-PB (Parallel Binary), which produces good results for an intermediate amount of edges and nodes.
+Thus, considering that nowadays processors have more and more cores, when modeling the problem, it is possible to consider multi-core model checking as an alternative to solve the HW-SW partitioning problem.
+
+Finally, there is an issue about $150$ nodes problem, since it seems to be the limit of ESBMC.
 It really depends on the modeling granularity of the problem.
@@
 This may lead to thousands of nodes or even more.
-Others defend coarse-grained models, where decisions are made for bigger components, thus even complex systems may consist of just some dozens of nodes to partition.
-In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space.
-\textcolor{Red}{On future works we will address improvements in the ESBMC, we hope to remove the parallel layer on top of ESBMC and implement it on it's core, it would optimize the processing time.}
+Others defend coarse-grained models, where decisions are made for larger components, thus even complex systems may consist of just some dozens of nodes to partition.
+In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the search space size.
+In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time.
 

### 2015-08-24 Docs/Paper/LaTex/template.tex
review experimental evaluation

@@
 \begin{itemize}
-\item{\textbf{ESBMC: }\textcolor{Red}{
-This strategy uses only one core to solve the partitioning problem, it is described in the section 2.3.}}
-\item{\textbf{ESBMC MC:  }\textcolor{Red}{
-Uses a sequential strategy \{1\:,2\:,\:...\:, \:Hmax\} , there is not parallel controller in this approach, it is described in the section 5.1.}}
-\item{\textbf{ESBMC PS:  }\textcolor{Red}{
-This approach is similar with ESBMC MC, however it uses a more optimized way to launch the ESBMC instances, it is described in the section 5.2.}}
-\item{\textbf{ESBMC PB:  }\textcolor{Red}{
-The binary approach uses a parallel binary search, it is described in the section 5.2.}}
+\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
+\item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
+\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}
+\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
 \end{itemize}
 
-\textcolor{red}{There is no single tool for solving all benchmarks efficiently.
-In particular, Vz solves $4$ out of $7$ benchmarks, in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}
+There is no single tool for solving all benchmarks efficiently.
+In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; \textcolor{blue}{Nao entendi nada desta frase...
+the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}
 
@@
 
-Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC-PB) tools.
+Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC-MC, ESBMC-PS, ESBMC-PB) tools.
 

### 2015-08-24 Docs/Paper/LaTex/template.tex
Translated Edilson's text and implemented Lucas's comments

@@
 OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
-In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}
+
+In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}.
+The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
 
@@
 Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao.
-Foi somente o ``\#pragma omp parallel for''??}
+Foi somente o ``\#pragma omp parallel for''??.
+Professor, usei tambem regiao critica}
 
@@
 In the above example, the for loop is executed in parallel \textcolor{blue}{Como?
-Cada posicao do array eh executada em um nucleo diferente?}.
+Cada posicao do array eh executada em um nucleo diferente?
+Não é garantido que use.
+Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}.
 Each iteration of the loop is executed in a separated thread.
+\textcolor{red}{Each thread may use an idle processor}.
+
+There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time.
+To create a critical region   the directive ``\#pragma omp critical'' should be used.
 
@@
 
-\textcolor{blue}{Mover este texto para a secao de background sobre OpenMP?...
-OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications.
-The API provides a directive-based programming approach to write parallel versions of C/C++ programs ~\cite{Qawasmeh2014}.}
-
-As described in Section~\ref{OpenMP}, in OpenMP the implementation is based on the fork-join model.
-The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP using Binary Search}
-\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
+\subsection{Multi-core ESBMC with OpenMP using Workers}
+\label{Multi-core-ESBMC-with-OpenMP-using-workers}
 %----------------------------------------------
@@
 
+%----------------------------------------------
+\subsection{Multi-core ESBMC with OpenMP using Binary Search}
+\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
+%----------------------------------------------
+
 The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution.
@@
 \textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}
+\textcolor{red}{The algorithm below is called from each worker in order to get the next step to execute if it exists, if not, zero or a negative number will be returned.}
 
@@
 
-\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS.}
+\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS. Feito}
 
@@
 \item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
-\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}
+\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
 \item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
@@
 
-\textcolor{Red}{A ferramenta vZ ~\cite{Bjorner2014} e ~\cite{Bjorner2015} oferece ganhos substanciais em problemas de otimizacao.
-O trabalho descrito em ~\cite{Pavlinovic2015} relata erros em compiladores e suas confusas mensagens, a abordagem classica é mostrar ao programador qual o local de erro e um dica sobre o mesmo, entretanto, outras fontes de erros não são consideradas, a abordagem mais indicada seria considerar todas as fontes de erros possiveis.
-Para modelar o problema são geradas as restricoes usando EasyOCaml, e vZ é responsavel por computar a menor caminho de erros.
-o Algoritmo descrito em ~\cite{Pavlinovic2015} mostrou-se eficiente frente as outras abordagens.}
-
-\textcolor{Red}{O problema abordado neste trabalho utiliza objetivo unico, minimizacao da funcao objetivo, em ~\cite{Patrick2015} é comparada as ferramentas OptiMathSAT com vZ para problemas de verificacao de SW.
-OptiMathSAT usando multiplos objetivos funciona muito melhor do que vZ com mulitplos objetivos, contudo, para problemas com objetivos unicos vZ se comparta melhor do que OptiMathSAT.}
+\textcolor{Red}{The vZ tool ~\cite{Bjorner2014} and ~\cite{Bjorner2015} offer substantial improvements on optimization problems.
+The work described in ~\cite{Pavlinovic2015} reports compiler errors and its confuse messages, the classic approach is to show to the programmer the error location and a hint about it, however, another error sources are not considered, the most appropriate approach would be to consider all possible error sources.
+To model the problem the restrictions are generated using EasyOCaml, and vZ is responsible to compute the best error path.
+The algorithm described in ~\cite{Pavlinovic2015} shows efficient against the other approaches.}
+
+\textcolor{Red}{The problem adressed in this work uses a single objective, minimizing of the objective function, in ~\cite{Patrick2015} is compared the tools  OptiMathSAT and vZ for software optimization problems.
+OptiMathSAT using multiple objectives works way better than vZ, however, for problems with single objectives vZ behaves better than OptiMathSAT.}
 

### 2015-08-25 Docs/Paper/LaTex/template.tex
Alessandro Review Fixed

@@
 %
+
 \RequirePackage{fix-cm}
@@
 \usepackage{color}
+\usepackage{multirow}
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
@@
 \renewcommand{\lstlistingname}{Algorithm}
-
+\renewcommand{\arraystretch}{1.3}
+\usepackage[table]{xcolor}
 \usepackage{color}
@@
 \label{linear-programming-problem}
-  minf^t x \: such that  = 
+  minf^t x \: such \; that  = 
   \begin{cases}
@@
 %----------------------------------------------
+\subsection{Bounded Model Checking with ESBMC}
+\label{Bounded-Model-Checking-with-ESBMC}
+%----------------------------------------------
+
+Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}.
+These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
+However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}.
+Much research has been devoted to mitigate this problem.
+
+Among the recent techniques, there is one that combines model checking with satisﬁability solving.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in ~\cite{Biere2009}.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
+
+The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less ~\cite{Biere2009}.
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in ~\cite{Clarke2004}, ~\cite{Armando2009}, and ~\cite{Ganai2006}.
+
+According to ~\cite{Cordeiro2012} and ~\cite{Cordeiro2011}, SMT-based model checking can be used to verify the single- and multi-threaded software.
+In ~\cite{Ramalho2013}, ESBMC can also be used to model check C++ software based on SMT solvers.
+In ~\cite{Trindade2015} and ~\cite{Trindade2014} it was shown that it is possible to use ESBMC, as an optimization tool.
+
+There are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
+The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition or code violation (minimum hardware cost).
+Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
+
+%----------------------------------------------
+\subsection{OpenMP}
+\label{OpenMP}
+%----------------------------------------------
+The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
+OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
+OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
+
+In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}.
+The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
+
+The most basic directive of OpenMP is the ``\#pragma omp parallel for'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:
+
+\textcolor{blue}{Nao existem outras diretivas?
+Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao.
+Foi somente o ``\#pragma omp parallel for''??.
+Professor, usei tambem regiao critica}
+
+\begin{lstlisting}[caption=OpenMP basic sample]
+01.  int i;
+02.  #pragma omp parallel for
+03.  for (i = 0; i < 10; i++)
+04.      a[i] = 2 * i;
+\end{lstlisting}
+
+In the above example, the for loop is executed in parallel \textcolor{blue}{Como?
+Cada posicao do array eh executada em um nucleo diferente?
+Não é garantido que use.
+Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}.
+Each iteration of the loop is executed in a separated thread.
+\textcolor{red}{Each thread may use an idle processor}.
+
+There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time.
+To create a critical region   the directive ``\#pragma omp critical'' should be used.
+%----------------------------------------------
 \subsection{Solving Optimization Problems with Vz}
@@
 An SMT solver is a tool that verifies formula satisfiability based on a set of background theories (e.g., linear arithmetic, bitvectors, and arrays).
-Z3 is built on top of a Davis–Putnam–Logemann–Loveland solver together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}.
+\textcolor{red}{Z3 is built on the a Davis–Putnam–Logemann–Loveland algorithm together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}}.
 vZ is one of the tools implemented in the SMT solver Z3; its base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.
@@
 In this work, the python API is used to formulate the HW-SW partitioning problem in vZ tool.
-
-%----------------------------------------------
-\subsection{Bounded Model Checking with ESBMC}
-\label{Bounded-Model-Checking-with-ESBMC}
-%----------------------------------------------
-
-Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}.
-These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
-However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}.
-Much research has been devoted to mitigate this problem.
-
-Among the recent techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in ~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
-
-The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less ~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in ~\cite{Clarke2004}, ~\cite{Armando2009}, and ~\cite{Ganai2006}.
-
-According to ~\cite{Cordeiro2012} and ~\cite{Cordeiro2011}, SMT-based model checking can be used to verify the single- and multi-threaded software.
-In ~\cite{Ramalho2013}, ESBMC can also be used to model check C++ software based on SMT solvers.
-In ~\cite{Trindade2015} and ~\cite{Trindade2014} it was shown that it is possible to use ESBMC, as an optimization tool.
-
-There are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
-The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition or code violation (minimum hardware cost).
-Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
-
-%----------------------------------------------
-\subsection{OpenMP}
-\label{OpenMP}
-%----------------------------------------------
-The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
-OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
-OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
-
-In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}.
-The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
-
-The most basic directive of OpenMP is the ``\#pragma omp parallel for'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:
-
-\textcolor{blue}{Nao existem outras diretivas?
-Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao.
-Foi somente o ``\#pragma omp parallel for''??.
-Professor, usei tambem regiao critica}
-
-\begin{lstlisting}[caption=OpenMP basic sample]
-01.  int i;
-02.  #pragma omp parallel for
-03.  for (i = 0; i < 10; i++)
-04.      a[i] = 2 * i;
-\end{lstlisting}
-
-In the above example, the for loop is executed in parallel \textcolor{blue}{Como?
-Cada posicao do array eh executada em um nucleo diferente?
-Não é garantido que use.
-Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}.
-Each iteration of the loop is executed in a separated thread.
-\textcolor{red}{Each thread may use an idle processor}.
-
-There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time.
-To create a critical region   the directive ``\#pragma omp critical'' should be used.
 
@@
 \item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
-\item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
+\item{\textbf{ESBMC-MC:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
 \item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
@@
 
-There is no single tool for solving all benchmarks efficiently.
-In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; \textcolor{blue}{Nao entendi nada desta frase...
-the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}
+\textcolor{red}{There is no single tool for solving all benchmarks efficiently.
+In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}
 
@@
 
-Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC-MC, ESBMC-PS, ESBMC-PB) tools.
-
-\begin{table}[h]
-\caption {Experimental results of the simple benchmarks}
-\small
-\begin{tabular}[c]{m{1.3cm}m{1.20cm}|m{0.85cm}|m{0.85cm}|m{0.85cm}|m{0.85cm}}
-  \toprule[1.5pt]
-  \head{\begin{turn}{-90}  \end{turn}} &
-  \head{\begin{turn}{-90}  \end{turn}} &
-  \head{\begin{turn}{-90}CRC32\end{turn}} &
-  \head{\begin{turn}{-90}Patricia\end{turn}} &
-  \head{\begin{turn}{-90}Dijkstra\end{turn}} &
-  \head{\begin{turn}{-90}Clustering\end{turn}} \\
-
-  \midrule
-
-\verb| | & \verb|Nodes| & \verb|25| & \verb|21| & \verb|26| & \verb|150| \\
-\verb| | &\verb|Edges| & \verb|32| & \verb|48| & \verb|69| & \verb|331| \\
-\verb| | &\verb|S0| & \verb|20| & \verb|10| & \verb|20| & \verb|50| \\
-\bottomrule[1.5pt]
-
-%EXACT Solution
-\rowcolor{DarkGray}
-\verb|Exact| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| \\
-\rowcolor{DarkGray}
-\verb|Solution| & \verb|Sp| & \verb|19| & \verb|4| & \verb|19| & \verb|46| \\
-
-%vZ
-\verb|vZ| & \verb|T(s)| & \verb|0.2| & \verb|0.3| & \verb|0.6| & \verb|109|\\
-\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241| \\
-\hline
-
-%ILP
-\rowcolor{Gray}
-\verb|ILP| & \verb|T(s)| & \verb|2| & \verb|1| & \verb|2| & \verb|649|\\
-\rowcolor{Gray}
-\verb| | & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
-\hline
-
-%GA
-\verb|GA| & \verb|T(s)| & \verb|7| & \verb|7| & \verb|9| & \verb|340|\\
-\verb| | & \verb|E%| & \verb|13.3| & \verb|0| & \verb|29| & \verb|1.7|\\
-\hline
-
-%ESBMC
-\rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| & \verb|31| & \verb|362| & \verb|292| & \verb|3010|\\
-\rowcolor{Gray}
-\verb|| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
-\hline
-
-%MultiCore ESBMC
-\verb|ESBMC| & \verb|T(s)| & \verb|2| & \verb|6| & \verb|7| & \verb|1615|\\
-\verb|MC| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
-\hline
-
-%ESBMC Parallel sequential
-\rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| & \verb|4| & \verb|10| & \verb|11| & \verb|2238|\\
-\rowcolor{Gray}
-\verb|PS| & \verb|Hp| & \verb|15| & \verb|47| & \verb|31| & \verb|241|\\
-\hline
-
-%ESBMC Parallel Binary
-\verb|ESBMC| & \verb|T(s)| & \verb|6| & \verb|5| & \verb|6| & \verb|207|\\
-\verb|PB| & \verb|Hp| & \verb|15| & \verb|47| & \verb|38| & \verb|241|\\
-\bottomrule[1.5pt]
-
-\end{tabular}
-\label{experimental-results-matlab-vz-esbmc}
-\end{table}
-
-Table~\ref{Experimental-results-of-the-complex-benchmarks} is an extension of Table~\ref{experimental-results-matlab-vz-esbmc}, where complex benchmarks are used.
-In particular, Table~\ref{Experimental-results-of-the-complex-benchmarks} shows problems with a higher number of nodes and edges; this increase directly influences the processing time of all tools.
+Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB) tools.
+
 RC$6$ produced time out for all versions of ESBMC, vZ e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one.
@@
 
-\begin{table}[h]
+Clustering described in Table~\ref{Experimental-results-of-the-complex-benchmarks} seems to be the limit to test the described tools, note that more than $150$ nodes lead to TO and MO.
+ILP shows robustness and produces results even for a high amount of nodes and edges.
+
+\begin{table*}[t]
+  \centering
   \caption{Experimental results of the complex benchmarks}  
-\small
-\begin{tabular}[c]{m{1.3cm}m{1.25cm}|m{1.25cm}|m{1.25cm}|m{1.25cm}}
-  \toprule[1.5pt]
-  \head{\begin{turn}{-90}  \end{turn}} &
-  \head{\begin{turn}{-90}  \end{turn}} &
-  \head{\begin{turn}{-90}RC6\end{turn}} &
-  \head{\begin{turn}{-90}Fuzzy\end{turn}} &
-  \head{\begin{turn}{-90}Mars\end{turn}} \\
-
-  \midrule
-
-\verb| | & \verb|Nodes| & \verb|329| & \verb|261|  & \verb|417|\\
-\verb| | &\verb|Edges| &  \verb|448| & \verb|442|  & \verb|600|\\
-\verb| | &\verb|S0| & \verb|600| & \verb|4578|  & \verb|300|\\
+  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
+
+ &  & \textbf{CRC32} & \textbf{Patricia} & \textbf{Dijkstra} & \textbf{Clustering} & \textbf{RC6} & \textbf{Fuzzy} & \textbf{Mars} \\[0.15cm]
+\cmidrule(r){3-9}
+
+&\textbf{Nodes} &25 &21 &26 &150 &329 &261 &417\\
+&\textbf{Edges} &32 &48 &69 &331 &448 &442 &600\\
+&\textbf{S0} &20 &10 &20 &50 &600 &4578 &300\\
+
+%EXACT Solution
 \bottomrule[1.5pt]
-
-%EXACT Solution
-\rowcolor{DarkGray}
-\verb|Exact| & \verb|Hp| & \verb|692|  & \verb|13820| & \verb|876|\\
-\rowcolor{DarkGray}
-\verb|Solution| & \verb|Sp| & \verb|533|  & \verb|4231| & \verb|297|\\
+\rowcolors{1}{}{lightgray}
+
+\multirow{2}{*}{\textbf{Exact Solution}}
+&  Hp   &  15   &  47   &  31   &  241   &  692    &  13820   &  876 \\
+&  Sp   &  19   &  4   &  19   &  46   &  533    &  4231   &  297  \\
 
 %vZ
-\verb|vZ| & \verb|T(s)| & \verb|112|  & \verb|TO| & \verb|TO|\\
-\verb|| & \verb|Hp| & \verb|241|  & \verb|-| & \verb|-|\\
+\bottomrule[1.5pt]
+\multirow{2}{*}{\textbf{vZ}}
+&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\
 \hline
@@
 %ILP
-\rowcolor{Gray}
-\verb|ILP| & \verb|T(s)| & \verb|1806|  & \verb|TO| & \verb|5.42|\\
-\rowcolor{Gray}
-\verb| | & \verb|Hp| & \verb|692|  & \verb|-| & \verb|876|\\
+\multirow{2}{*}{\textbf{ILP}}  
+&  T(s)   &  2   &  1   &  2   &  649   &  1806    &  TO   &  5.42  \\
+&  Hp   &  15   &  47   &  31   &  241   &  692    &  -   &  876  \\
 \hline
@@
 %GA
-\verb|GA| & \verb|T(s)| & \verb|2050|  & \verb|1.37| & \verb|5000|\\
-\verb| | & \verb|E%| &  \verb|-6.5|  & \verb|-37.6| & \verb|-27.5|\\
+\multirow{2}{*}{\textbf{GA}}
+&  T(s)   &  7   &  7   &  9   &  340   &  2050    &  1.37   &  5000  \\
+&  Error \%   &  13.3   &  0   &  29   &  1.7   &  -6.5    &  -37.6   &  -27.5  \\
 \hline
@@
 %ESBMC
-\rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| &  \verb|TO|  & \verb|MO| & \verb|MO|\\
-\rowcolor{Gray}
-\verb|| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
+\multirow{2}{*}{\textbf{ESBMC}}
+&  T(s)   &  31   &  362   &  292   &  3010   &  TO    &  MO   &  MO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
 \hline
@@
 %MultiCore ESBMC
-\verb|ESBMC| & \verb|T(s)|  & \verb|TO|  & \verb|TO| & \verb|TO|\\
-\verb|MC| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
+\multirow{2}{*}{\textbf{ESBMC Multicore}}
+&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
 \hline
@@
 %ESBMC Parallel sequential
-\rowcolor{Gray}
-\verb|ESBMC| & \verb|T(s)| & \verb|TO|  & \verb|MO| & \verb|MO|\\
-\rowcolor{Gray}
-\verb|PS| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
+\multirow{2}{*}{\textbf{ESBMC Parallel Sequential}}
+&  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
 \hline
@@
 %ESBMC Parallel Binary
-\verb|ESBMC| & \verb|T(s)| & \verb|TO|  & \verb|MO| & \verb|MO|\\
-\verb|PB| & \verb|Hp| & \verb|-|  & \verb|-| & \verb|-|\\
+\multirow{2}{*}{\textbf{ESBMC Parallel Binary}}
+&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
+&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
 \bottomrule[1.5pt]
-
 \end{tabular}
 \label{Experimental-results-of-the-complex-benchmarks}
-\end{table}
-
-Clustering described in Table~\ref{experimental-results-matlab-vz-esbmc} seems to be the limit to test the described tools, note that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high amount of nodes and edges.
+\end{table*}
 

### 2015-08-26 Docs/Paper/LaTex/template.tex
Fix 8.2 / Algorithms and Mail features

@@
 
-\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode]
+\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode, mathescape]
 01.#Initialize Variables
@@
 03.  Create binary vector (x)
-04.  Declare number of nodes, edges and S0
+04.  Declare number of nodes, edges and $S_{0}$
 05.  Declare hardware cost of each node as array (h) 
@@
 13.#Assert Constraints
-14.  Add constraints (SF + CMC <= S0)
+14.  Add constraints (SF + CMC <= $S_{0}$)
 15.  Add constraints to minimize Fobj
@@
 
-\begin{lstlisting}[caption=Pseudocode describing ESBMC]
+\begin{lstlisting}[caption=Pseudocode describing ESBMC, mathescape]
 01. Initialize Variables 
@@
 05. Declare communication cost of each edge (c)
-06. Declare the initial software cost of (S0)
+06. Declare the initial software cost of ($S_{0}$)
 07. Declare transposed incidence matrix graph G (E)
-08. Define the solutions variable (Xi) as Boolean
+08. Define the solutions variable ($X_{i}$ ) as Boolean
 09. main {
 10.  for TipH = 0 to Hmax do {
-11.   populate Xi with nondeterministic/test values
-12.   Calculate s(1-x)+c|Ex| and store at variable
-13.   Requirement isured by Assume (Variable <= S0)
-14.   Calculate Hp cost Based on value tested of Xi
-15.   Violation check with Assert(Hp > TipH)
+11.   populate $X_{i}$ with nondeterministic/test values
+12.   Calculate s(1-x)+c|$E_{x}$| and store at variable
+13.   Requirement isued by Assume (Variable <= $S_{0}$)
+14.   Calculate Hp cost Based on value tested of $X_{i}$
+15.   Violation check with Assert($H_{p}$ > TipH)
 16.  }
@@
 
-\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS. Feito}
-
 \begin{itemize}
@@
 
-\textcolor{blue}{Falta descrever os resultados da melhor abordagem do ESBMC quando comparado ao vZ e ILP.}
-
-The only technique that is able to solve all benchmarks is GA; however, its precision is not satisfactory since it produces an error rate between $-37.6$\% and $29.0$\%.
-
 Note that all ESBMC parallel versions produce better results than the sequential one.
@@
 One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than vZ.
+
+\textcolor{red}{A versão PB do ESBMC descrita Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}, demonstra um avanco significativo na ferramenta; quando a quantidade de nós é baixa, em torno de 30, ESBMC-PB não demonstra eficiencia frente as tecnicas usadas em vZ e ILP, contudo, em torno de 150 nós, ESBMC se torna 3 vezes mais rapido do que ILP (A tecnicas mais robusta apresentada aqui).
+vZ para pequeno nós foi 30 vezes mais rapido (CRC32) do que ESBMC-PB e para nós intermediarios esse valor caiu para aproximadmente 1.9 (Clustering).
+Quando analisados os algoritmos RC6, Fuzzy e Mars, ESBMC-PB obteve TO ou MO em todos os casos.
+Os resultados são promissores levando em consideracao que as ferramentas vZ e Matlab são estados da arte em suas respectivas funcoes.
+}
+
+The only technique that is able to solve all benchmarks is GA; however, its precision is not satisfactory since it produces an error rate between $-37.6$\% and $29.0$\%.
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
emphasize i.e. and e.g.

@@
 Even with the use of powerful computers, a problem can take hours before an optimal solution is reached.
-If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA~\cite{Rao2009}.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}.
 The only drawback is that the found solution may not be the global minimum or maximum.
@@
 The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
-OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
+OpenMP supports most processor architectures and operating systems, {\it e.g.}, Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
 OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
@@
 
-An SMT solver is a tool that verifies formula satisfiability based on a set of background theories (e.g., linear arithmetic, bitvectors, and arrays).
+An SMT solver is a tool that verifies formula satisfiability based on a set of background theories ({\it e.g.}, linear arithmetic, bitvectors, and arrays).
 \textcolor{red}{Z3 is built on the a Davis–Putnam–Logemann–Loveland algorithm together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}}.
@@
 
-Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, i.e., to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.
+Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.
 
@@
 
-In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages (e.g., C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
 In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software.

### 2015-09-01 Docs/Paper/LaTex/template.tex
2.3 OpenMP

@@
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode~\cite{Wu2014}.
 
@@
 Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}.
-Each iteration of the loop is executed in a separated thread.
-\textcolor{red}{Each thread may use an idle processor}.
-
-There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time.
-To create a critical region   the directive ``\#pragma omp critical'' should be used.
+Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor.
+
+There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time.
+To create a critical region, the ``\#pragma omp critical'' directive should be used.
 %----------------------------------------------

### 2015-09-01 Docs/Paper/LaTex/template.tex
2.4 Solving Optimization Problems with Vz

@@
 
-An SMT solver is a tool that verifies formula satisfiability based on a set of background theories ({\it e.g.}, linear arithmetic, bitvectors, and arrays).
-\textcolor{red}{Z3 is built on the a Davis–Putnam–Logemann–Loveland algorithm together with auxiliary algorithms for solving quantifiers formulas~\cite{Bjorner2014}}.
-vZ is one of the tools implemented in the SMT solver Z3; its base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.
-vZ includes an incremental version of  \textcolor{red}{Maximum Resiliency (MaxRes) ~\cite{Federica2008} to Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN}} and a Simplex to solve numbers without defined patterns.
+SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.
+In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem~\cite{Bjorner2014}.
+In particular, we exploit the use of vZ, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; Vz base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~vZ also includes an incremental version of the Maximum Resiliency (MaxRes) \cite{Federica2008} in order to achieve Maximum Satisfiability (MaxSAT) \cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
 In Vz, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
-Vz provides functions that extend Z3 for solving optimization problems: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
+In summary, Vz provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
 
@@
 \item{\textbf{Assert-Soft F : weight n}
-the function Assert-Soft adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
+the function \textit{assert-soft} adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
 \end{itemize}
@@
 
-\begin{lstlisting}[caption=SMT formula using vZ, label=vZ]
+\begin{lstlisting}[caption=Example of SMT formula using vZ, label=vZ]
 1. (declare-const K Int) 
@@
 The vZ architecture is shown in Fig.~\ref{vZ-Architecture}.
-Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)\textcolor{red}{~\cite{Vasco2005}~\cite{Barth1995}}.
+Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}.
 If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints.
-\textcolor{red}{for box constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
-When we use "soft constrains'' in the mode "lexicographic'' vZ invokes MaxSAT using multiple calls for your engine.}
+\textcolor{red}{Qual seria o ``box constraints''?} For box constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
+When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine.
+\textcolor{red}{Qual ``engine''?}
 %
@@
 
-Z3 is available for platforms in C, C$++$, Java, .NET and Python; it is possible to download Z3 with vZ from~\cite{Z3API}.
-In this work, the python API is used to formulate the HW-SW partitioning problem in vZ tool.
+Z3 is available for platforms in C, C$++$, Java, .NET, and Python; it is possible to download Z3 with vZ from its github repository~\cite{Z3API}.
+In this work, the python API is used to formulate HW-SW partitioning problems using the vZ tool.
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
3.2 Formal Model
7.3 Multi-core ESBMC with OpenMP using Binary Search

@@
 %
-\noindent where $x$ represents the decision variable.
-Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard \textcolor{red}{\cite[p.~763]{Cormem}}.
+\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
 
@@
 
-\textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}
-\textcolor{red}{The algorithm below is called from each worker in order to get the next step to execute if it exists, if not, zero or a negative number will be returned.}
+Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
8.2 Experimental Results

@@
 
-\textcolor{red}{There is no single tool for solving all benchmarks efficiently.
-In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}
+There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
+In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; vZ is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, vZ returns two TOs (time-outs) in Fuzzy and Mars benchmarks.
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
refactor background section

@@
 
-\renewcommand{\baselinestretch}{0.97}
+\renewcommand{\baselinestretch}{0.96}
+
+\newcommand{\comment}[1]{}
 
@@
 
+\comment{
 Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}.
@@
 Much research has been devoted to mitigate this problem.
-
-Among the recent techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in ~\cite{Biere2009}.
+}
+
+Among the recent model checking techniques, there is one that combines model checking with satisﬁability solving.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
 In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
 
-The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $ M $, a property $ \phi $, and a bound $ K $, BMC unrolls the system  times and translates it into a verification condition (VC) $ \varphi $  such that $ \varphi $   is satisfiable if and only if $ \phi $ has a counterexample of depth $ K $ or less ~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in ~\cite{Clarke2004}, ~\cite{Armando2009}, and ~\cite{Ganai2006}.
-
-According to ~\cite{Cordeiro2012} and ~\cite{Cordeiro2011}, SMT-based model checking can be used to verify the single- and multi-threaded software.
-In ~\cite{Ramalho2013}, ESBMC can also be used to model check C++ software based on SMT solvers.
-In ~\cite{Trindade2015} and ~\cite{Trindade2014} it was shown that it is possible to use ESBMC, as an optimization tool.
-
-There are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
+The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less~\cite{Biere2009}.
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Armando2009},\cite{Ganai2006},\cite{Cordeiro2012}.
+
+In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}.
+According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
+In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers.
+In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2014}, it was shown that it is possible to use ESBMC also as an optimization tool.
+
+In particular, there are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
 The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition or code violation (minimum hardware cost).
@@
 %----------------------------------------------
+\subsubsection{ESBMC Architecture}
+\label{ESBMCArchitecture}
+%----------------------------------------------
+
+Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}.
+In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
+GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
+The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
+Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}.
+Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
+%
+\begin{figure}[ht]
+	\centering
+  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
+	\caption{ESBMC Architecture}
+	\label{ESBMC-Architecture}
+\end{figure}
+
+%----------------------------------------------
 \subsection{OpenMP}
@@
 %----------------------------------------------
+
 The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP}
+\subsection{Multi-core ESBMC with OpenMP (ESBMC-MC)}
 \label{Multi-core-ESBMC-with-OpenMP}
@@
 Thus, there is a significant unused hardware resource during this process.
-Fig.~\ref{ESBMC-Architecture} shows the ESBMC architecture, which consists of the C/C++ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}.
-In particular, ESBMC compiles the C/C++ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
-The GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
-
-The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
-Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}.
-Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
-\begin{figure}[ht]
-	\centering
-  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
-	\caption{ESBMC Architecture}
-	\label{ESBMC-Architecture}
-\end{figure}
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
minor corrections

@@
 If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints.
-\textcolor{red}{Qual seria o ``box constraints''?} For box constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
+For constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
 When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine.
@@
 As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
-This section proposes two multi-core model checking algorithms in order to speed up the HW-SW partitioning verification if compared to the sequential solution.
-
-%----------------------------------------------
-\section{Verification Algorithm using Sequential ESBMC}
+This section describes the verification algorithm using sequential ESBMC, followerd by three multi-core model checking algorithms, in order to speed up the HW-SW partitioning verification if compared to the sequential solution.
+
+%----------------------------------------------
+\subsection{Verification Algorithm using Sequential ESBMC}
 \label{Verification-Algorithm-using-ESBMC}

### 2015-09-01 Docs/Paper/LaTex/template.tex
rename ESBMC solution in Table 2

@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP using Workers}
+\subsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
 \label{Multi-core-ESBMC-with-OpenMP-using-workers}
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP using Binary Search}
+\subsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
 \label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
@@
 %MultiCore ESBMC
-\multirow{2}{*}{\textbf{ESBMC Multicore}}
+\multirow{2}{*}{\textbf{ESBMC-MC}}
 &  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
@@
 %ESBMC Parallel sequential
-\multirow{2}{*}{\textbf{ESBMC Parallel Sequential}}
+\multirow{2}{*}{\textbf{ESBMC-PS}}
 &  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
@@
 %ESBMC Parallel Binary
-\multirow{2}{*}{\textbf{ESBMC Parallel Binary}}
+\multirow{2}{*}{\textbf{ESBMC-PB}}
 &  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\

### 2015-09-01 Docs/Paper/LaTex/template.tex
fix references

@@
 \bibitem{Arato2003}
-Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D., ``{Hardware/software partitioning in embedded system design.
+Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
+(2003), ``{Hardware/software partitioning in embedded system design.
 In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp.
-192-202 (2003)
+192-202.
 
@@
 \bibitem{Baier2008}
-Baier, C., Katoen, J-P. ``{Principles of Model Checking. The MIT Press, London (2008)}''
+Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking. The MIT Press, London}''.
 
@@
 \bibitem{Clarke2009}
-Clarke, E., Emerson, E., Sifakis, J. ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84 (2009)
+Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84.
 
@@
 \bibitem{Trindade2015}
-Trindade, A., Cordeiro. L. ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York (2015)}''
+Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York.}''
 
@@
 \bibitem{Trindade2014}
-Trindade, A., Cordeiro, L.
-``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software.
-In: Brazilian Symposium on Computing Systems Engineering (SBESC), 2014, Manaus – AM, Brazil.
-Anais SBESC},'' pp.
-1-6 (2014).
+Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC)},'' pp. 1-6.
 
@@
 Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP.
+(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP.
 In: International Conference on Software Engineering and Service Science (ICSESS)},'' pp.
-921,924, IEEE (2014)
+921,924.
 
@@
 \bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905, IEEE (2010)
+Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905.
 
@@
 \bibitem{Rao2009}
-Rao, S. ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken (2009)}''
+Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken}''.
 
@@
 \bibitem{Biere2009}
-Biere, A. ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481, Amsterdam (2009)}''
+Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481.}''
 
@@
 Clarke, E., Kroening, D., Lerda, F.
-``{A Tool for Checking ANSI-C Programs.
+(2004), ``{A Tool for Checking ANSI-C Programs.
 In: Proceedings of the Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 2988}'', pp.
-168-176 (2004)
+168-176.
 
@@
 Armando, A., Mantovani, J., Platania, L.
-``{Bounded model checking of software using SMT solvers instead of SAT solvers.
+(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers.
 In: International Journal on Software Tools for Technology Transfer, Vol.
@@
 1},'' pp.
-69-83 (2009)
+69-83.
 
@@
 \bibitem{Ganai2006}
-Ganai, M., Gupta, A. ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801 (2006)
+Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801.
 
@@
 \bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974 (2012)
+Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974.
 
@@
 Cordeiro, L., Fischer, B.
-``{Verifying multi-threaded software using SMT-based context-bounded model checking.
+(2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.
 In: Proceedings of the 33rd International Conference on Software Engineering},'' pp.
-331-340 (2011)
+331-340.
 
@@
 Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
-``{SMT-Based Bounded Model Checking of C++ Programs.
+(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.
 In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp.
-147-156, IEEE (2013)
+147-156.
 
@@
 \bibitem{Teich2012}
-Teich, J. ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430 (2012)
+Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430.
 
@@
 \bibitem{TheMathWorks2013}
-The MathWorks, Inc ``{MATLAB (version R2013a). Natick, MA (2013)}''
+The MathWorks, Inc. (2013), ``{MATLAB (version R2013a). Natick, MA}''.
 
@@
 \bibitem{Tranquillo2011}
-Tranquillo, J. ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool (2011)}''
+Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool}''.
 
@@
 Hong, L., Cai, J.
-``{The application guide of mixed programming between MATLAB and other programming languages.
+(2010), ``{The application guide of mixed programming between MATLAB and other programming languages.
 In: Proceedings of the 2nd International Conference on Computer and Automation Engineering (ICCAE)},'' pp.
-185-189 (2010)
+185-189.
 
@@
 Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
-``{MiBench: a free, commercially representative embedded benchmark suite.
+(2001), ``{MiBench: a free, commercially representative embedded benchmark suite.
 In: Proceedings of the IEEE 4th annual workshop on workload characterization},'' pp.
-3-14 (2001)
+3-14.
 
@@
 Arat\'o, P., Mann, Z.A., Orb\'an, A.
-``{Algorithmic aspects of hardware/software partitioning.
+(2005), ``{Algorithmic aspects of hardware/software partitioning.
 In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol.
 1},'' pp.
-136–156 (2005)
+136–156.
 
@@
 \bibitem{Dagum1998}
-Dagum, L., Menon, R. ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55, IEEE (1998)
+Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55.
 
@@
 \bibitem{DeMoura2008}
-De Moura, L., Bjorner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)
+De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340.
 
@@
 Brummayer, R., Biere, A.
-``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.
+(2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.
 In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 5505},'' pp.
-174–177, Springer (2009)
+174–177.
 
@@
 \bibitem{Barrett2011}
-Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177, Springer (2011)
+Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177.
 
@@
 Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
-``{MathSAT: Tight integration of SAT and mathematical decision procedures.
-In: Journal of Automated Reasoning, Springer (2005)}''
+(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures.
+In: Journal of Automated Reasoning.}''
 
@@
 \bibitem{Dutertre2014}
-Dutertre, B. ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744, Springer (2014)
+Dutertre, B. (2014), ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744.
 
@@
 \bibitem{Holzmann2011}
-Holzmann, G.J., Joshi, R., Groce, A. ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857, IEEE (2011)
+Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857.
 
@@
 \bibitem{Holzmann2012}
-Holzmann, G. ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171, Springer (2012)
+Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171.
 
@@
 \bibitem{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y., De Moura, L.
-``{A Concurrent Portfolio Approach to SMT Solving.
-In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp.
-715-720, Springer (2009)
+Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving. In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp. 715-720.
 
@@
 Bjorner, N., Phan, A-D., Fleckenstein, L.
-``{vZ - An Optimizing SMT Solver.
+(2015), ``{vZ - An Optimizing SMT Solver.
 In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 9035},'' pp.
-194-199, Springer (2015)
+194-199.
 
@@
 Qawasmeh, A., Malik, A., Chapman, B.
-``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.
+(2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.
 In: Parallel \& Distributed processing symposium work-shop (IPDPSW), 2014 IEEE International},'' pp.
-1049-1058, IEEE (2014)
+1049-1058.
 
@@
 \bibitem{Bjorner2014}
-Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''
+Bjorner, N. and Phan, A. D. (2014), ``{vZ - Maximal Satisfaction with Z3. 6th International Symposium on Symbolic Computation in Software Science (SCSS).}''
 
@@
 \bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B., {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364/2008, 116-131
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
+(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364, 116-131
 
 %40
-\bibitem{Barth1995}Barth, P., Davis-Putnam, A., {``Enumeration Algorithm for Linear
-Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science, 1995.
+\bibitem{Barth1995}
+Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
+Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
 

### 2015-09-01 Docs/Paper/LaTex/template.tex
fix references

@@
 (2003), ``{Hardware/software partitioning in embedded system design.
-In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp.
-192-202.
+In: Proc.
+of the Intl.
+Symposium of Intelligent Signal Processing},'' pp.
+192--202.
 
@@
 \bibitem{Mann2007}
-Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.
+Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design},'' v. 31, n. 3 pp. 241--263.
 
@@
 \bibitem{Baier2008}
-Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking. The MIT Press, London}''.
+Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking}'', The MIT Press, London.
 
@@
 \bibitem{Clarke2009}
-Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84.
+Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery},'' v. 52, n. 11, pp. 74--84.
 
@@
 \bibitem{Trindade2015}
-Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York.}''
+Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems (to appear).}''
 
@@
 \bibitem{Trindade2014}
-Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC)},'' pp. 1-6.
+Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC)},'' pp. 1--6.
 
@@
 (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP.
-In: International Conference on Software Engineering and Service Science (ICSESS)},'' pp.
-921,924.
+In: Proc.
+of the Intl.
+Conference on Software Engineering and Service Science},'' pp.
+921--924.
 
@@
 \bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905.
+Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. Intl. Conference on Computer Science Education (ICCSE)},'' pp. 1900--1905.
 
@@
 \bibitem{Rao2009}
-Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken}''.
+Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
 
@@
 \bibitem{Biere2009}
-Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481.}''
+Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
 
@@
 \bibitem{Clarke2004}
-Clarke, E., Kroening, D., Lerda, F.
-(2004), ``{A Tool for Checking ANSI-C Programs.
-In: Proceedings of the Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 2988}'', pp.
-168-176.
+Clarke, E., Kroening, D., Lerda, F. (2004), ``{A Tool for Checking ANSI-C Programs. In: Proc. of the Tools and Algorithms for the Construction and Analysis of Systems}'', LNCS 2988, pp. 168--176.
 
@@
 (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers.
-In: International Journal on Software Tools for Technology Transfer, Vol.
+In: International Journal on Software Tools for Technology Transfer},'' v.
 11, n.
-1},'' pp.
-69-83.
+1, pp.
+69--83.
 
@@
 \bibitem{Ganai2006}
-Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801.
+Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking. In: Proc. of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794-–801.
 
@@
 \bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974.
+Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering},'' v. 38, n. 4, pp. 957--974.
 
@@
 In: Proceedings of the 33rd International Conference on Software Engineering},'' pp.
-331-340.
+331--340.
 
@@
 In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp.
-147-156.
+147--156.
 
@@
 \bibitem{Teich2012}
-Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430.
+Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proc. of the IEEE, Special Centennial Issue},''  v. 100, pp. 1411--1430.
 
@@
 \bibitem{TheMathWorks2013}
-The MathWorks, Inc. (2013), ``{MATLAB (version R2013a). Natick, MA}''.
+The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
 
@@
 \bibitem{Tranquillo2011}
-Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool}''.
+Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
 
@@
 (2010), ``{The application guide of mixed programming between MATLAB and other programming languages.
-In: Proceedings of the 2nd International Conference on Computer and Automation Engineering (ICCAE)},'' pp.
-185-189.
+In: Proc.
+of the 2nd Intl.
+Conference on Computer and Automation Engineering},'' pp.
+185--189.
 
@@
 (2001), ``{MiBench: a free, commercially representative embedded benchmark suite.
-In: Proceedings of the IEEE 4th annual workshop on workload characterization},'' pp.
-3-14.
+In: Proc.
+of the IEEE 4th annual workshop on workload characterization},'' pp.
+3--14.
 
@@
 (2005), ``{Algorithmic aspects of hardware/software partitioning.
-In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol.
-1},'' pp.
-136–156.
+In: Association Computing Machinery Transactions on Design Automation of Electronic Systems},'' v.
+1, pp.
+136–-156.
 
@@
 \bibitem{Dagum1998}
-Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55.
+Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming.},'' In: Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
 
@@
 \bibitem{DeMoura2008}
-De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340.
+De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems},'' LNCS 4963, pp. 337–-340.
 
@@
 \bibitem{Brummayer2009}
-Brummayer, R., Biere, A.
-(2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.
-In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 5505},'' pp.
-174–177.
+Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays. In: Tools and Algorithms for the Construction and Analysis of Systems},'' LNCS 5505, pp. 174-–177.
 
@@
 \bibitem{Barrett2011}
-Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177.
+Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4. In: Computer-Aided Verification},'' LNCS 6806, pp. 171--177.
 
@@
 Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
-(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures.
-In: Journal of Automated Reasoning.}''
+(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
+35, n.
+1-3, pp.
+265--293.
 
@@
 \bibitem{Dutertre2014}
-Dutertre, B. (2014), ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744.
+Dutertre, B. (2014), ``{Yices 2.2. In: Computer-Aided Verification (CAV)},'' LNCS 8559, pp. 737–-744.
 
@@
 \bibitem{Holzmann2011}
-Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857.
+Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
 
@@
 \bibitem{Holzmann2012}
-Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171.
+Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the 19th Intl. Conference on Model Checking Software},'' LNCS 7385, pp. 155--171.
 
@@
 \bibitem{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving. In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp. 715-720.
+Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conference on Computer-Aided Verification, LNCS 5643, pp. 715--720.
 
@@
 Bjorner, N., Phan, A-D., Fleckenstein, L.
-(2015), ``{vZ - An Optimizing SMT Solver.
-In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 9035},'' pp.
-194-199.
+(2015), ``{vZ - An Optimizing SMT Solver},'' In: Proc.
+of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
+194--199.
 
@@
 Qawasmeh, A., Malik, A., Chapman, B.
-(2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.
-In: Parallel \& Distributed processing symposium work-shop (IPDPSW), 2014 IEEE International},'' pp.
-1049-1058.
+(2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc.
+of the Intl.
+Parallel \& Distributed processing symposium workshop, pp.
+1049--1058.
 
@@
 \bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{vZ - Maximal Satisfaction with Z3. 6th International Symposium on Symbolic Computation in Software Science (SCSS).}''
+Bjorner, N. and Phan, A. D. (2014), ``{vZ - Maximal Satisfaction with Z3},'' In: Prof. of the 6th Intl. Symposium on Symbolic Computation in Software Science, pp. 1--10.
 
@@
 Magellan, ``{Source code and documentation},''
-  \url{https://github.com/Z3Prover/z3}, Accessed 18 August 2015.
+  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
 
@@
 URFJ, ``{Algoritmos Genéticos: Fundamentos e Aplicações. Marcio Nunes de Miranda},''
-  \url{http://www.nce.ufrj.br/GINAPE/VIDA/alggenet.htm}, Accessed 18 August 2015.
+  \url{http://www.nce.ufrj.br/GINAPE/VIDA/alggenet.htm}, Accessed 18th August 2015.
 
@@
 \bibitem{NarodytskaN}
-Narodytska, N., Bacchus, F. {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution'', Proceedings of the Twenty-Eighth AAAI Conference on Artificial Intelligence.}
+Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the Twenty-Eighth AAAI Conference on Artificial Intelligence, pp. 2717--2723.
 
@@
 \bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
-(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364, 116-131
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Service-Oriented Computing, LNCS 5364, pp. 116--131
 
@@
 %43
-\bibitem{Cormem}Cormem, H., Charles, E., {``Algoritmos, Teoria e Prática''}, Chapter 34, Pag 763.
+\bibitem{Cormem}
+Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, 1--1292.
 

### 2015-09-07 Docs/Paper/LaTex/template.tex
Fixed eq and Final Text

@@
 
-\textcolor{blue}{Nao existem outras diretivas?
-Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao.
-Foi somente o ``\#pragma omp parallel for''??.
-Professor, usei tambem regiao critica}
-
 \begin{lstlisting}[caption=OpenMP basic sample]
@@
 
-In the above example, the for loop is executed in parallel \textcolor{blue}{Como?
-Cada posicao do array eh executada em um nucleo diferente?
-Não é garantido que use.
-Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}.
+In the above example, the for loop is executed in parallel.
 Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor.
-
 There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time.
@@
 When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine.
-\textcolor{red}{Qual ``engine''?}
 %
@@
 \label{hardware-costs}
- H_p &= \Sigma_{\left(v_i \;\in\; V_h\right)} h_i,
+H_p  &= \Sigma_{v_i \in V_H} h_i
 \end{align}
@@
 %
+%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
 \begin{align}
 \label{software-communication-costs}
-  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; E_p}\; c(V_i, V_j).
+  S_p &= \Sigma_{v_i \in V_s}\:s_i + \Sigma_{(v_i,v_j)\in\:E_p} c(V_i,V_j)
 \end{align}
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
-	\caption{ESBMC Multi-core Optimized Sequential Approach. \textcolor{blue}{A fonte desta figura esta diferente da Fig.~\ref{ESBMC-Multi-core}}}
+	\caption{ESBMC Multi-core Optimized Sequential Approach. }
 	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
@@
 
-\textcolor{red}{A versão PB do ESBMC descrita Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}, demonstra um avanco significativo na ferramenta; quando a quantidade de nós é baixa, em torno de 30, ESBMC-PB não demonstra eficiencia frente as tecnicas usadas em vZ e ILP, contudo, em torno de 150 nós, ESBMC se torna 3 vezes mais rapido do que ILP (A tecnicas mais robusta apresentada aqui).
-vZ para pequeno nós foi 30 vezes mais rapido (CRC32) do que ESBMC-PB e para nós intermediarios esse valor caiu para aproximadmente 1.9 (Clustering).
-Quando analisados os algoritmos RC6, Fuzzy e Mars, ESBMC-PB obteve TO ou MO em todos os casos.
-Os resultados são promissores levando em consideracao que as ferramentas vZ e Matlab são estados da arte em suas respectivas funcoes.
-}
+\textcolor{red}{The PB version of esbmc described in Section 6.4, demonstrates a significant advance in tool; when the quantity of nodes is low, around 30, ESBMC-PB not shows efficiency in front of techniques used in vZ and ILP.
+however, around 150 nodes, ESBMC becomes 3 times more fast than ILP( the technique more robust in here).
+vZ using little quantity of nodes was 30 times more fast (CRC32) than ESBMC-PB and for intermediate nodes this value approximately falls to 1.9 (Clustering).
+When analysed the algorithms: RC6, Fuzzy and Mars, ESBMC-PB obtained TO or MO in all cases.
+The results are promising taking into consideration that vZ and Matlab tools are art states in their respective functions.}
 

### 2015-09-08 Docs/Paper/LaTex/template.tex
review 7.2 Experimental Results

@@
 
-\textcolor{red}{The PB version of esbmc described in Section 6.4, demonstrates a significant advance in tool; when the quantity of nodes is low, around 30, ESBMC-PB not shows efficiency in front of techniques used in vZ and ILP.
-however, around 150 nodes, ESBMC becomes 3 times more fast than ILP( the technique more robust in here).
-vZ using little quantity of nodes was 30 times more fast (CRC32) than ESBMC-PB and for intermediate nodes this value approximately falls to 1.9 (Clustering).
-When analysed the algorithms: RC6, Fuzzy and Mars, ESBMC-PB obtained TO or MO in all cases.
-The results are promising taking into consideration that vZ and Matlab tools are art states in their respective functions.}
+\textcolor{red}{The ESBMC-PB implementation described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search} shows a significant performance improvement; when the amount of nodes is around $30$, ESBMC-PB does not outperform the optimization techniques employed by vZ and ILP tools.
+However, when the amount of nodes is approximately $150$, ESBMC-PB becomes three times faster than ILP, which is the most robust technique.
+When vZ explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$9$ ({\it e.g.}, Clustering).
+When analyzing all benchmarks: RC$6$, Fuzzy, and Mars, ESBMC-PB produces TO or MO; however, the results are still promising if we take into consideration that vZ and Matlab are state-of-the-art tools with respect to optimization problems.}
 

### 2015-09-08 Docs/Paper/LaTex/template.tex
review related work

@@
 
-Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem and experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the vZ tool, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while vZ is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
+Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem and experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the $\nu$Z tool, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
 To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
@@
 
-This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, vZ, ESBMC, and OpenMP tools. 
+This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, $\nu$Z, ESBMC, and OpenMP tools. 
 Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling.
-Section~\ref{ILPGA} briefly describes the ILP and GA algorithms, while Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using vZ.
+Section~\ref{ILPGA} briefly describes the ILP and GA algorithms, while Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z.
 The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}.
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-Alternatively, tools such as vZ and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found.
-The following sections describe the main features of vZ and ESBMC tools.
+Alternatively, tools such as $\nu$Z and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found.
+The following sections describe the main features of $\nu$Z and ESBMC tools.
 
@@
 %----------------------------------------------
-\subsection{Solving Optimization Problems with Vz}
+\subsection{Solving Optimization Problems with $\nu$Z}
 \label{Optimization-with-Vz}
@@
 In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem~\cite{Bjorner2014}.
-In particular, we exploit the use of vZ, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; Vz base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~vZ also includes an incremental version of the Maximum Resiliency (MaxRes) \cite{Federica2008} in order to achieve Maximum Satisfiability (MaxSAT) \cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
-In Vz, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
-In summary, Vz provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
+In particular, we exploit the use of $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes) \cite{Federica2008} in order to achieve Maximum Satisfiability (MaxSAT) \cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
+In summary, $\nu$Z provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
 
@@
 The expected result of this optimization problem described in the code below is $2$.
-In fact, the model generated by vZ shows that $K = 1$ and $W = 1$.
-
-\begin{lstlisting}[caption=Example of SMT formula using vZ, label=vZ]
+In fact, the model generated by $\nu$Z shows that $K = 1$ and $W = 1$.
+
+\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z, label=vZ]
 1. (declare-const K Int) 
@@
 
-The vZ architecture is shown in Fig.~\ref{vZ-Architecture}.
+The $\nu$Z architecture is shown in Fig.~\ref{vZ-Architecture}.
 Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}.
-If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints.
-For constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT.
-When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine.
+If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints.
+For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT.
+When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
 %
@@
   \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
-	\caption{vZ Architecture~\cite{Bjorner2015}}
+	\caption{$\nu$Z Architecture~\cite{Bjorner2015}}
 	\label{vZ-Architecture}
@@
 
-Z3 is available for platforms in C, C$++$, Java, .NET, and Python; it is possible to download Z3 with vZ from its github repository~\cite{Z3API}.
-In this work, the python API is used to formulate HW-SW partitioning problems using the vZ tool.
+Z3 is available for platforms in C, C$++$, Java, .NET, and Python; it is possible to download Z3 with $\nu$Z from its github repository~\cite{Z3API}.
+In this work, the python API is used to formulate HW-SW partitioning problems using the $\nu$Z tool.
 
@@
 %----------------------------------------------
-\section{Analysis of the partitioning problem using vZ}
+\section{Analysis of the partitioning problem using $\nu$Z}
 \label{Analysis-of-the-partitioning-problem-using-vZ}
@@
 
-Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using vZ functions~\cite{Bjorner2014}.
-A vZ logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
+Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}.
+A $\nu$Z logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
 Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
@@
 \textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to vZ: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to vZ that \textit{Fobj} should be minimized.
-Finally, the model is checked by Vz and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
-\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode, mathescape]
+To achieve this, two constraints are imposed to $\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to $\nu$Z that \textit{Fobj} should be minimized.
+Finally, the model is checked by $\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
+
+\begin{lstlisting}[caption=Pseudocode describing $\nu$Z,label=vZ-pseudocode, mathescape]
 01.#Initialize Variables
@@
 This section is split into two parts.
-The setup is described in Section~\ref{Experimental-Setup} while Section~\ref{Experimental-Results} describes a comparison among Matlab~\cite{TheMathWorks2013}, vZ~\cite{Bjorner2015}, and ESBMC~\cite{Trindade2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
+The setup is described in Section~\ref{Experimental-Setup} while Section~\ref{Experimental-Results} describes a comparison among Matlab~\cite{TheMathWorks2013}, $\nu$Z~\cite{Bjorner2015}, and ESBMC~\cite{Trindade2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
 
@@
 MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
-vZ as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
+$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
 
 A desktop with $24$GB of RAM and i$7$ ($8$-cores) from Intel with CPU clock of $3$.$40$ GHz was used.
-Each time was measured $3$ times in GA (average taken) and just once in vZ, ESBMC, and ILP.
-The reason is that GA times are not so close as ILP, vZ, and ESBMC.
+Each time was measured $3$ times in GA (average taken) and just once in $\nu$Z, ESBMC, and ILP.
+The reason is that GA times are not so close as ILP, $\nu$Z, and ESBMC.
 A time out condition (TO) is reached when the running time is longer than $7200$ seconds.
@@
 There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; vZ is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, vZ returns two TOs (time-outs) in Fuzzy and Mars benchmarks.
-
-In contrast to vZ, ILP solves $6$ out of $7$ benchmarks.
+In particular, $\nu$Z solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; $\nu$Z is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, $\nu$Z returns two TOs (time-outs) in Fuzzy and Mars benchmarks.
+
+In contrast to $\nu$Z, ILP solves $6$ out of $7$ benchmarks.
 When ILP produces a result, it always provides the optimal solution.
-On the one hand, ILP execution time is slower than vZ in all benchmarks, which are supported by vZ.
+On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z.
 On the other hand, ILP is faster than ESBMC in all benchmarks, except for the clustering.
@@
 In particular, the ESBMC-PB implementation outperforms all other ESBMC approaches; the ESBMC-PB performance improves as the number of nodes and edges increase.
-One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than vZ.
-
-\textcolor{red}{The ESBMC-PB implementation described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search} shows a significant performance improvement; when the amount of nodes is around $30$, ESBMC-PB does not outperform the optimization techniques employed by vZ and ILP tools.
+One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than $\nu$Z.
+
+The ESBMC-PB implementation described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search} shows a significant performance improvement; when the amount of nodes is around $30$, ESBMC-PB does not outperform the optimization techniques employed by $\nu$Z and ILP tools.
 However, when the amount of nodes is approximately $150$, ESBMC-PB becomes three times faster than ILP, which is the most robust technique.
-When vZ explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$9$ ({\it e.g.}, Clustering).
-When analyzing all benchmarks: RC$6$, Fuzzy, and Mars, ESBMC-PB produces TO or MO; however, the results are still promising if we take into consideration that vZ and Matlab are state-of-the-art tools with respect to optimization problems.}
+When $\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$9$ ({\it e.g.}, Clustering).
+When analyzing all benchmarks: RC$6$, Fuzzy, and Mars, ESBMC-PB produces TO or MO; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
 
@@
 
-Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB) tools.
-
-RC$6$ produced time out for all versions of ESBMC, vZ e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one.
+Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using $\nu$Z, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB) tools.
+
+RC$6$ produced time out for all versions of ESBMC, $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one.
 Fuzzy produced time-outs and memory-outs in all tools.
@@
 
-\textcolor{Red}{The vZ tool ~\cite{Bjorner2014} and ~\cite{Bjorner2015} offer substantial improvements on optimization problems.
-The work described in ~\cite{Pavlinovic2015} reports compiler errors and its confuse messages, the classic approach is to show to the programmer the error location and a hint about it, however, another error sources are not considered, the most appropriate approach would be to consider all possible error sources.
-To model the problem the restrictions are generated using EasyOCaml, and vZ is responsible to compute the best error path.
-The algorithm described in ~\cite{Pavlinovic2015} shows efficient against the other approaches.}
-
-\textcolor{Red}{The problem adressed in this work uses a single objective, minimizing of the objective function, in ~\cite{Patrick2015} is compared the tools  OptiMathSAT and vZ for software optimization problems.
-OptiMathSAT using multiple objectives works way better than vZ, however, for problems with single objectives vZ behaves better than OptiMathSAT.}
+$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
+As an application example, Pavlinovic {\it et al.}~\cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
+The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.
+The approach described by Pavlinovic {\it et al.}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.
+
+The problem addressed in this present paper uses a single objective function for minimization.
+In Partrick {\it et al.}~\cite{Patrick2015},  OptiMathSAT and $\nu$Z are compared for software optimization problems.
+OptiMathSAT using multiple objective functions works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.
 
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-Below that, the best option turns out to be vZ since its execution time is faster and notorious.
+Below that, the best option turns out to be $\nu$Z since its execution time is faster and notorious.
 ESBMC is a viable alternative for a number of nodes lower than $150$.
@@
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-However, ESBMC and Vz have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
 Experimental results also pointed to an improvement of ESBMC, when using a parallel approach.
@@
 \bibitem{Mann2007}
-Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design},'' v. 31, n. 3 pp. 241--263.
+Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.
 
@@
 \bibitem{Clarke2009}
-Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery},'' v. 52, n. 11, pp. 74--84.
+Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging},'' In: Communications of the Association Computing Machinery, v. 52, n. 11, pp. 74--84.
 
@@
 \bibitem{Trindade2014}
-Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC)},'' pp. 1--6.
+Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software},'' In: Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1--6.
 
@@
 Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP.
-In: Proc.
+(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
 of the Intl.
-Conference on Software Engineering and Service Science},'' pp.
+Conference on Software Engineering and Service Science, pp.
 921--924.
@@
 \bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. Intl. Conference on Computer Science Education (ICCSE)},'' pp. 1900--1905.
+Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education (ICCSE)},'' pp. 1900--1905.
 
@@
 \bibitem{Clarke2004}
-Clarke, E., Kroening, D., Lerda, F. (2004), ``{A Tool for Checking ANSI-C Programs. In: Proc. of the Tools and Algorithms for the Construction and Analysis of Systems}'', LNCS 2988, pp. 168--176.
+Clarke, E., Kroening, D., Lerda, F.
+(2004), ``{A Tool for Checking ANSI-C Programs}'', In: Proc.
+of the Intl.
+Conf.
+on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 2988, pp.
+168--176.
 
@@
 Armando, A., Mantovani, J., Platania, L.
-(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers.
-In: International Journal on Software Tools for Technology Transfer},'' v.
+(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: International Journal on Software Tools for Technology Transfer, v.
 11, n.
@@
 \bibitem{Ganai2006}
-Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking. In: Proc. of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794-–801.
+Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM International Conference on Computer-Aided Design, pp. 794-–801.
 
@@
 \bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering},'' v. 38, n. 4, pp. 957--974.
+Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
 
@@
 \bibitem{Cordeiro2011}
-Cordeiro, L., Fischer, B.
-(2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.
-In: Proceedings of the 33rd International Conference on Software Engineering},'' pp.
-331--340.
+Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the 33rd Intl Conf. on Software Engineering, pp. 331--340.
 
@@
 Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
-(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.
-In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp.
+(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl.
+Conf.
+and Workshops on the Engineering of Computer-Based Systems, pp.
 147--156.
@@
 \bibitem{Teich2012}
-Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proc. of the IEEE, Special Centennial Issue},''  v. 100, pp. 1411--1430.
+Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
 
@@
 Hong, L., Cai, J.
-(2010), ``{The application guide of mixed programming between MATLAB and other programming languages.
-In: Proc.
+(2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
 of the 2nd Intl.
-Conference on Computer and Automation Engineering},'' pp.
+Conference on Computer and Automation Engineering, pp.
 185--189.
@@
 Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
-(2001), ``{MiBench: a free, commercially representative embedded benchmark suite.
-In: Proc.
-of the IEEE 4th annual workshop on workload characterization},'' pp.
+(2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
+of the IEEE 4th annual workshop on workload characterization, pp.
 3--14.
@@
 Arat\'o, P., Mann, Z.A., Orb\'an, A.
-(2005), ``{Algorithmic aspects of hardware/software partitioning.
-In: Association Computing Machinery Transactions on Design Automation of Electronic Systems},'' v.
+(2005), ``{Algorithmic aspects of hardware/software partitioning.},'' In: Proc.
+of the Association Computing Machinery Transactions on Design Automation of Electronic Systems, v.
 1, pp.
@@
 \bibitem{Dagum1998}
-Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming.},'' In: Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
+Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming.},'' In: Proc. of the Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
 
@@
 \bibitem{DeMoura2008}
-De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems},'' LNCS 4963, pp. 337–-340.
+De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
 
@@
 \bibitem{Brummayer2009}
-Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays. In: Tools and Algorithms for the Construction and Analysis of Systems},'' LNCS 5505, pp. 174-–177.
+Brummayer, R., Biere, A.
+(2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc.
+of the Intl.
+Conf.
+on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp.
+174-–177.
 
@@
 \bibitem{Barrett2011}
-Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4. In: Computer-Aided Verification},'' LNCS 6806, pp. 171--177.
+Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Computer-Aided Verification, LNCS 6806, pp. 171--177.
 
@@
 \bibitem{Dutertre2014}
-Dutertre, B. (2014), ``{Yices 2.2. In: Computer-Aided Verification (CAV)},'' LNCS 8559, pp. 737–-744.
+Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Computer-Aided Verification (CAV)},'' LNCS 8559, pp. 737–-744.
 
@@
 \bibitem{Holzmann2012}
-Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the 19th Intl. Conference on Model Checking Software},'' LNCS 7385, pp. 155--171.
+Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the 19th Intl. Conf. on Model Checking Software},'' LNCS 7385, pp. 155--171.
 
@@
 \bibitem{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conference on Computer-Aided Verification, LNCS 5643, pp. 715--720.
+Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
 
@@
 Bjorner, N., Phan, A-D., Fleckenstein, L.
-(2015), ``{vZ - An Optimizing SMT Solver},'' In: Proc.
-of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
+(2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
+of the Intl.
+Conf.
+on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
 194--199.
@@
 \bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{vZ - Maximal Satisfaction with Z3},'' In: Prof. of the 6th Intl. Symposium on Symbolic Computation in Software Science, pp. 1--10.
+Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the 6th Intl. Symposium on Symbolic Computation in Software Science, pp. 1--10.
 
@@
 \bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Service-Oriented Computing, LNCS 5364, pp. 116--131
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
+(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
+of the Service-Oriented Computing, LNCS 5364, pp.
+116--131
 
@@
 %41
-\bibitem{Vasco2005}Vasco, M., Marques-Silva, J., {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
+\bibitem{Vasco2005}
+Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
 
 %42
-\bibitem{Pavlinovic2015}Pavlinovic, Z., King, T., Wies, T.,{``Practical SMT-Based Type Error Localization''}, ICFP’15, August 31 – September 2, 2015, Vancouver, BC, Canada c 2015 ACM.
-978-1-4503-3669-7/15/08
+\bibitem{Pavlinovic2015}
+Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
 
 %43
-\bibitem{Patrick2015}Sebastiani, R., Trentin, T., {``OptiMathSAT: A Tool for Optimization Modulo Theories''}
+\bibitem{Patrick2015}
+Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Computer Aided Verification, LNCS 9206, pp. 447--454.
 
@@
 \bibitem{Cormem}
-Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, 1--1292.
+Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
 

### 2015-09-08 Docs/Paper/LaTex/template.tex
fix references

@@
 Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
-(2003), ``{Hardware/software partitioning in embedded system design.
-In: Proc.
+(2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc.
 of the Intl.
-Symposium of Intelligent Signal Processing},'' pp.
+Symp.
+of Intelligent Signal Processing, pp.
 192--202.
@@
 Armando, A., Mantovani, J., Platania, L.
-(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: International Journal on Software Tools for Technology Transfer, v.
+(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl.
+Journal on Software Tools for Technology Transfer, v.
 11, n.
@@
 \bibitem{Ganai2006}
-Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM International Conference on Computer-Aided Design, pp. 794-–801.
+Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.
 
@@
 \bibitem{Cordeiro2011}
-Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the 33rd Intl Conf. on Software Engineering, pp. 331--340.
+Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
 
@@
 (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
-of the 2nd Intl.
-Conference on Computer and Automation Engineering, pp.
+of the Intl.
+Conf.
+on Computer and Automation Engineering, pp.
 185--189.
@@
 (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
-of the IEEE 4th annual workshop on workload characterization, pp.
+of the annual workshop on workload characterization, pp.
 3--14.
@@
 \bibitem{Barrett2011}
-Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Computer-Aided Verification, LNCS 6806, pp. 171--177.
+Barrett, C., Conway, C.
+Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C.
+(2011), ``{CVC4},'' In: Proc.
+of the Intl.
+Conf.
+on Computer-Aided Verification, LNCS 6806, pp.
+171--177.
 
@@
 \bibitem{Dutertre2014}
-Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Computer-Aided Verification (CAV)},'' LNCS 8559, pp. 737–-744.
+Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
 
@@
 \bibitem{Holzmann2012}
-Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the 19th Intl. Conf. on Model Checking Software},'' LNCS 7385, pp. 155--171.
+Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
 
@@
 of the Intl.
-Parallel \& Distributed processing symposium workshop, pp.
+Symp.
+on Parallel \& Distributed processing, pp.
 1049--1058.
@@
 \bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the 6th Intl. Symposium on Symbolic Computation in Software Science, pp. 1--10.
+Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
 
@@
 \bibitem{NarodytskaN}
-Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the Twenty-Eighth AAAI Conference on Artificial Intelligence, pp. 2717--2723.
+Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
 
@@
 (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
-of the Service-Oriented Computing, LNCS 5364, pp.
+of the Intl.
+Conf.
+on Service-Oriented Computing, LNCS 5364, pp.
 116--131
@@
 \bibitem{Patrick2015}
-Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Computer Aided Verification, LNCS 9206, pp. 447--454.
+Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
 

### 2015-09-08 Docs/Paper/LaTex/template.tex
major improvements for abstract and introduction

@@
 \begin{abstract}
-We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing.
-The multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
+We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing.
+In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
 Each instance checks for a different optimum value until the optimization problem is satisfied.
-The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
 We implement and evaluate our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
-We also compare our approaches to other state-of-the-art optimization tools: Matlab and Z3.
-Experimental results show that no single optimization tool solves all benchmarks; however, Matlab and Z3 are the most efficient ones to solve HW-SW partitioning problems, although ESBMC had a significant performance improvement from its sequential to parallel version.
+We also integrate the $\nu$Z tool into ESBMC, which is a state-of-art optimization tool based on SMT.
+We compare all our approaches to another state-of-the-art optimization tool (Matlab).
+Experimental results show that no single optimization tool solves all HW-SW partitioning benchmarks; however, Matlab and $\nu$Z are the most efficient ones to solve HW-SW partitioning problems, although ESBMC had a significant performance improvement in particular cases.
 \end{abstract}
@@
 At early stages, the design is split into separated flows: hardware and software.
-Consequently, the partitioning decision process, which deals with the decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology.
-If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affects the overall development process, the quality and the lifecycle of the final system.
+The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology.
+If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affects the overall development process, the quality, and the lifecycle of the final system.
 Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in ~\cite{Arato2003} and ~\cite{Mann2007}.
@@
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Programs may be viewed as mathematical objects with behavior that is, in principle, well determined.
-This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification ~\cite{Clarke2009}.
+Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined.
+This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior.
+Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}.
 Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors.
@@
 
-In ~\cite{Trindade2015} and ~\cite{Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
-The present work extends those studies since there is a substantial improvement in terms of the genetic algorithm and the SMT-based verification method, which has been extended with a multi-core architecture.
-Multi-core processors have been used in all segments of industry to implement high-performance computing ~\cite{Wu2014}.
-In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution.
-However, most verification algorithms still disregard the limitations of the CMOS technology, which limits the increase of the chip’s frequency after it reaches 4 GHz.
-
-Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem and experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the $\nu$Z tool, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
+The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core binary-search approach, as well as, the integration of the $\nu$Z tool into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
+In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}.
+However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.
+
+Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using multi-core ESBMC with OpenMP:  ESBMC-MC using a sequential-search, ESBMC-PS using a parallel-search, and ESBMC-PB using a binary-search.
+Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the $\nu$Z tool, which supports only a single-core approach~\cite{Bjorner2015}.
 The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
-To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems.
-We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool ~\cite{Cordeiro2012}.
-As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
+All multi-core ESBMC with OpenMP approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
+
+\textbf{Contributions.} The main contribution of the present study is to show that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
+Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
+Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool that is typically used for software verification.
+To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.
+
+\textbf{Availability of Data and Tools.
+}Our experiments are based on a set of publicly available benchmarks.
+All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.
 
@@
 \bibitem{Trindade2015}
-Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems (to appear).}''
+Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).
+
+%5
+\bibitem{Trindade2016}
+Trindade, A.
+B., Ismail, H.
+I., Cordeiro, L.
+C.
+(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
+1-4.
 
@@
 
+%44
+\bibitem{Holzmann11}
+Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
+
 \end{thebibliography}

### 2015-09-08 Docs/Paper/LaTex/template.tex
minor corrections

@@
 In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
-The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core binary-search approach, as well as, the integration of the $\nu$Z tool into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the MaxSMT solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
 Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
@@
 
-Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using multi-core ESBMC with OpenMP:  ESBMC-MC using a sequential-search, ESBMC-PS using a parallel-search, and ESBMC-PB using a binary-search.
-Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the $\nu$Z tool, which supports only a single-core approach~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
-All multi-core ESBMC with OpenMP approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
+Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
+All multi-core ESBMC approaches with OpenMP, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
 
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP (ESBMC-MC)}
+\subsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
 \label{Multi-core-ESBMC-with-OpenMP}
@@
 \item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
-\item{\textbf{ESBMC-MC:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
+\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
 \item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
@@
 %MultiCore ESBMC
-\multirow{2}{*}{\textbf{ESBMC-MC}}
+\multirow{2}{*}{\textbf{ESBMC-SS}}
 &  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\

### 2015-09-09 Docs/Paper/LaTex/template.tex
refactor abstract, introduction, and background

@@
 \begin{document}
-\title{Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems}
+\title{Applying Multi-Core Model Checking and Maximum Satisfiability to Hardware-Software Partitioning}
 \author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}
@@
 Each instance checks for a different optimum value until the optimization problem is satisfied.
-We implement and evaluate our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
-We also integrate the $\nu$Z tool into ESBMC, which is a state-of-art optimization tool based on SMT.
+We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and also integrate the maximum satisfiability solver $\nu$Z tool into ESBMC.
 We compare all our approaches to another state-of-the-art optimization tool (Matlab).
-Experimental results show that no single optimization tool solves all HW-SW partitioning benchmarks; however, Matlab and $\nu$Z are the most efficient ones to solve HW-SW partitioning problems, although ESBMC had a significant performance improvement in particular cases.
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve HW-SW partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
 \end{abstract}
@@
 The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology.
-If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affects the overall development process, the quality, and the lifecycle of the final system.
-Starting at the 1990s, intensive research was performed, and several approaches proposed, as shown in ~\cite{Arato2003} and ~\cite{Mann2007}.
-
-In any HW and SW design of complex systems, more time is spent on verification than on construction ~\cite{Baier2008}.
+If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affect the overall development process, the quality, and the lifecycle of the final system.
+
+\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction ~\cite{Baier2008}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
@@
 Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-The system models are accompanied by algorithms that systematically explore all the states of the system model.
-
-In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems.
-The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the MaxSMT solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
-Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
+The system models are accompanied by algorithms that systematically explore all the states of the system model.}
+
+Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in ~\cite{Arato2003} and~\cite{Mann2007}.
+In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
+The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+
+\comment{Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
 In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}.
-However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.
+However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.}
 
@@
 Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions.
-All multi-core ESBMC approaches with OpenMP, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
-
-\textbf{Contributions.} The main contribution of the present study is to show that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
+
+% in which its main function is to check the satisfiability of logical formulas based on objective functions
+
+\textbf{Contributions.} The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
+Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
 Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool that is typically used for software verification.
+Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.
 To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.
@@
 The HW-SW partitioning problem is typically represented as a set of constraints and an objective function in linear programming.
-In this section, we describe the linear programming problem and present related tools that are used to model and solve the HW-SW partitioning problem.
+We describe the linear programming problem and present related tools that are used to model and solve the HW-SW partitioning problem.
 
@@
 
-Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances~\cite{Rao2009}.
-In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
+Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}. 
+\comment{In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
 The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
-Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
-
-There is no single method available for solving all optimization problems efficiently~\cite{Rao2009}.
+Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.}
+There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}.
 The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
@@
 In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
-According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
+\comment{According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
 In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers.
-In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2014}, it was shown that it is possible to use ESBMC also as an optimization tool.
-
-In particular, there are two directives in C/C++ that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
-The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition or code violation (minimum hardware cost).
+In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2014}, it was shown that it is possible to use ESBMC also as an optimization tool.}
+In particular, there are two directives in ESBMC that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
+The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost).
 Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
@@
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
-GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
+GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
 The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
@@
 There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time.
-To create a critical region, the ``\#pragma omp critical'' directive should be used.
+To create a critical region, the ``\#pragma omp critical'' directive is used.
+
 %----------------------------------------------
@@
 
-SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.
+\comment{SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.}
+
 In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem~\cite{Bjorner2014}.
-In particular, we exploit the use of $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes) \cite{Federica2008} in order to achieve Maximum Satisfiability (MaxSAT) \cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes)~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+
 In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
@@
 
-The $\nu$Z architecture is shown in Fig.~\ref{vZ-Architecture}.
+Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
 Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}.
@@
   \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
-	\caption{$\nu$Z Architecture~\cite{Bjorner2015}}
+	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}}
 	\label{vZ-Architecture}

### 2015-09-09 Docs/Paper/LaTex/template.tex
refactor main section

@@
 Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling.
-Section~\ref{ILPGA} briefly describes the ILP and GA algorithms, while Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z.
-The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}.
-In Section~\ref{Experimental-Evaluation}, we present the results of our experiments using several embedded systems applications.
+The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}, and in particular, Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z.
+In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications.
 In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.
@@
 
+\comment{
 %----------------------------------------------
@@
 The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
-
-%----------------------------------------------
-\section{Analysis of the partitioning problem using $\nu$Z}
-\label{Analysis-of-the-partitioning-problem-using-vZ}
-%----------------------------------------------
-
-Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}.
-A $\nu$Z logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
-Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
-
-The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
-In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
-\textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to $\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to $\nu$Z that \textit{Fobj} should be minimized.
-Finally, the model is checked by $\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
-\begin{lstlisting}[caption=Pseudocode describing $\nu$Z,label=vZ-pseudocode, mathescape]
-01.#Initialize Variables
-02.  Create vZ context 
-03.  Create binary vector (x)
-04.  Declare number of nodes, edges and $S_{0}$
-05.  Declare hardware cost of each node as array (h) 
-06.  Declare software cost of each node as array (s)
-07.  Declare communication cost of each edge (c)
-08.  Declare transposed incidence matrix graph G (E)
-09.#Arithmetic Expressions
-10.  SC = s(1-x)
-11.  CMC = c*|EX|
-12.  Fobj =  x[i] * h[i]
-13.#Assert Constraints
-14.  Add constraints (SF + CMC <= $S_{0}$)
-15.  Add constraints to minimize Fobj
-16.  Check Model
-17.  Print Result
-\end{lstlisting}
+}
 
@@
 %----------------------------------------------
+\subsection{Analysis of the partitioning problem using $\nu$Z (ESBMC-$\nu$Z)}
+\label{Analysis-of-the-partitioning-problem-using-vZ}
+%----------------------------------------------
+
+Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}.
+A $\nu$Z logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
+Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
+
+The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
+Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
+In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
+\textit{Fobj} should be minimized to obtain the optimal hardware solution.
+To achieve this, two constraints are imposed to $\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to $\nu$Z that \textit{Fobj} should be minimized.
+Finally, the model is checked by $\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
+
+\begin{lstlisting}[caption=Pseudocode describing $\nu$Z,label=vZ-pseudocode, mathescape]
+01.#Initialize Variables
+02.  Create vZ context 
+03.  Create binary vector (x)
+04.  Declare number of nodes, edges and $S_{0}$
+05.  Declare hardware cost of each node as array (h) 
+06.  Declare software cost of each node as array (s)
+07.  Declare communication cost of each edge (c)
+08.  Declare transposed incidence matrix graph G (E)
+09.#Arithmetic Expressions
+10.  SC = s(1-x)
+11.  CMC = c*|EX|
+12.  Fobj =  x[i] * h[i]
+13.#Assert Constraints
+14.  Add constraints (SF + CMC <= $S_{0}$)
+15.  Add constraints to minimize Fobj
+16.  Check Model
+17.  Print Result
+\end{lstlisting}
+
+%----------------------------------------------
 \section{Experimental Evaluation}
@@
   \centering
-  \caption{Experimental results of the complex benchmarks}  
+  \caption{Experimental results of the HW-SW partitioning benchmarks}  
   \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
@@
 &  Sp   &  19   &  4   &  19   &  46   &  533    &  4231   &  297  \\
-
-%vZ
-\bottomrule[1.5pt]
-\multirow{2}{*}{\textbf{vZ}}
-&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\
-\hline
 
@@
 &  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
+\hline
+
+%vZ
+\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
+&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\
+
 \bottomrule[1.5pt]

### 2015-09-09 Docs/Paper/LaTex/template.tex
review up to Section 4

@@
 As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
-This section describes the verification algorithm using sequential ESBMC, followerd by three multi-core model checking algorithms, in order to speed up the HW-SW partitioning verification if compared to the sequential solution.
+This section describes the verification algorithm using sequential ESBMC, followed by three multi-core model checking algorithms and the integration of the MaxSMT solver $\nu$Z, in order to speed up the HW-SW partitioning verification.
 
@@
 
-ESBMC pseudocode shows the algorithm with the same constraints and conditions placed on ILP and GA.
+Algorithm~\ref{Pseudocode-describing-ESBMC} shows ESBMC pseudocode with the same constraints and conditions placed on ILP and GA.
 Two values must be controlled to obtain the results and to perform the optimization.
@@
 It is possible to inform to ESBMC with which type of values the variables must be tested.
-Therefore, there is a declaration to populate all the decision variables $x$ with non-deterministic Boolean values.
+Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
 Those values that change for each test will generate a possible solution and obey the constraints.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e.,$A.x \leq b$).
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e., $A.x \leq b$).
 
@@
 To every test performed, the hardware hint is compared to the feasible solution.
-This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (\textit{true-false} statement).
+This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement).
 If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.
@@
 
-\begin{lstlisting}[caption=Pseudocode describing ESBMC, mathescape]
+\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC, label={Pseudocode-describing-ESBMC}, mathescape]
 01. Initialize Variables 
@@
 To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC.
-
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
-	\caption{ESBMC Multi-core.}
+	\caption{ESBMC-SS Approach.}
 	\label{ESBMC-Multi-core}
@@
 
-Multi-core ESBMC obtains the problem specification represented by a C program.
-The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; Multi-core ESBMC starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
+ESBMC-SS obtains the problem specification represented by a C program.
+The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
 All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}.
@@
 After executing $N$ instances, if there is no code violation, then multi-core ESBMC starts new instances again.
-During the parallel region execution, if a violation is found in any running thread, then it presents the counterexample with the violation condition and the verification time.
-If all threads of the batch processing are terminated, then multi-core ESBMC finishes its execution.
+During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time.
+If all threads of the batch processing are terminated, then ESBMC-SS finishes its execution.
 
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
-	\caption{ESBMC Multi-core Optimized Sequential Approach. }
+	\caption{ESBMC-PS Approach. }
 	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
@@
 
-Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available.
+Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
 This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.
@@
 The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution.
-A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced as much as possible.
+A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced.
 The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
-	\caption{ESBMC Binary Approach}
+	\caption{ESBMC-PB Approach}
 	\label{ESBMC-Binary-Approach}
@@
 As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$.
-When the next available core asks for a step to be executed, the controller obtains the largest interval ({\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$).
+When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$).
 The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
@@
 Note that there might gaps between steps, which are produced by the customized binary search.
-For instance, in the example shown in~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well.
+For instance, in the example shown in Fig.~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well.
 However, if the same step $10$ returns \textit{true}, we can assume that all steps before $10$ is \textit{true} as well.
@@
 
-Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
+Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
 
@@
 
-Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
+Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
 From lines $4$ to $9$, the algorithm finds the largest interval.

### 2015-09-10 Docs/Paper/LaTex/template.tex
refactor experimental evaluation

@@
 
-This section is split into two parts.
-The setup is described in Section~\ref{Experimental-Setup} while Section~\ref{Experimental-Results} describes a comparison among Matlab~\cite{TheMathWorks2013}, $\nu$Z~\cite{Bjorner2015}, and ESBMC~\cite{Trindade2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
+This section is split into three parts.
+The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
+Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, Multi-Core ESBMC, and MaxSMT $\nu$Z~\cite{Bjorner2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
 
@@
 
-To perform the experiments, some test vectors provided by Mann {\it et al.}~\cite{Mann2007} are used, as shown in Table~\ref{Description-of-Benchmarks}.
-The vertices in the graphs correspond to high-level language instructions.
+ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used.
+A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11.
+Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
+For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}.
+MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
+ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
+
+All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits.
+Each time was measured $3$ times in GA (average taken) and just once in ESBMC, $\nu$Z, and ILP.
+The reason is that GA times are not so close as ESBMC, $\nu$Z, and ILP.
+A time out condition (TO) is reached when the verification time is longer than $7200$ seconds.
+A memory out (MO) occurs when the tool reaches $24$GB of memory.
+
+%----------------------------------------------
+\subsection{Description of Benchmarks}
+\label{Benchmarks-Description}
+%----------------------------------------------
+
+To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{Description-of-Benchmarks}.
+The nodes in the graphs correspond to high-level language instructions.
 Software and communication costs are time dimensional, and hardware costs represent the occupied area.
 The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
-The clustering and fuzzy test vectors benchmarks are designed from Mann et al.~\cite{Mann2007} and are significantly larger benchmarks.
-From the same authors,  very complex benchmarks to test the limits of the applicability of techniques are collected (RC$6$ and Mars).
+The clustering and fuzzy benchmarks are designed from Mann {\it et al.}~\cite{Mann2007} and are significantly large benchmarks.
+From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
 
@@
 
-ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used.
-A parallel approach of the ESBMC sequential ascending, descending, and binary search are implemented in C++$11$.
-Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
-For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}.
-MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
-
-A desktop with $24$GB of RAM and i$7$ ($8$-cores) from Intel with CPU clock of $3$.$40$ GHz was used.
-Each time was measured $3$ times in GA (average taken) and just once in $\nu$Z, ESBMC, and ILP.
-The reason is that GA times are not so close as ILP, $\nu$Z, and ESBMC.
-A time out condition (TO) is reached when the running time is longer than $7200$ seconds.
-A memory out (MO) occurs when the tool reaches $24$GB of memory.
-
 %----------------------------------------------
@@
 
-ESBMC implement four approaches: ESBMC, ESBMC Multicore (MC), ESBMC Parallel Sequential (PS), and ESBMC Parallel binary (PB).
+ESBMC implement four approaches: ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z.
 
@@
 \item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
-\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
-\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
+\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}, where there is no parallel controller, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
+\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC-SS; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
 \item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}

### 2015-09-10 Docs/Paper/LaTex/template.tex
Change of title
review 5.3 Experimental Results

@@
 \begin{document}
-\title{Applying Multi-Core Model Checking and Maximum Satisfiability to Hardware-Software Partitioning}
+\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
 \author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}
@@
 
-ESBMC implement four approaches: ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z.
-
-\begin{itemize}
-\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
-\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}, where there is no parallel controller, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
-\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC-SS; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
-\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
-\end{itemize}
+Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.
 
 There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, $\nu$Z solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; $\nu$Z is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, $\nu$Z returns two TOs (time-outs) in Fuzzy and Mars benchmarks.
-
-In contrast to $\nu$Z, ILP solves $6$ out of $7$ benchmarks.
-When ILP produces a result, it always provides the optimal solution.
+In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns two TOs (time-outs) related to Fuzzy and Mars benchmarks.
+
+In contrast to ESBMC-$\nu$Z, ILP solves $6$ out of $7$ benchmarks.
+When ILP produces a result, it typically provides the optimal solution.
 On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z.
-On the other hand, ILP is faster than ESBMC in all benchmarks, except for the clustering.
-
-Note that all ESBMC parallel versions produce better results than the sequential one.
-In particular, the ESBMC-PB implementation outperforms all other ESBMC approaches; the ESBMC-PB performance improves as the number of nodes and edges increase.
-One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than $\nu$Z.
-
-The ESBMC-PB implementation described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search} shows a significant performance improvement; when the amount of nodes is around $30$, ESBMC-PB does not outperform the optimization techniques employed by $\nu$Z and ILP tools.
-However, when the amount of nodes is approximately $150$, ESBMC-PB becomes three times faster than ILP, which is the most robust technique.
-When $\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$9$ ({\it e.g.}, Clustering).
-When analyzing all benchmarks: RC$6$, Fuzzy, and Mars, ESBMC-PB produces TO or MO; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
+On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.
+
+Note further that all multi-core ESBMC implementations produce better results than the sequential one.
+In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase.
+One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z.
+However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools.
+When analyzing all benchmarks, ESBMC-PB produces TO or MO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
+
+%When ESBMC-$\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$8$ ({\it e.g.}, Clustering).
 
@@
 
-Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using $\nu$Z, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB) tools.
-
-RC$6$ produced time out for all versions of ESBMC, $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one.
-Fuzzy produced time-outs and memory-outs in all tools.
-ILP was the only one to solve Mars, while GA solved incorrectly all benchmarks.
-
-Clustering described in Table~\ref{Experimental-results-of-the-complex-benchmarks} seems to be the limit to test the described tools, note that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high amount of nodes and edges.
+Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution.
+ILP was the only one to solve Mars, while GA solved all benchmarks incorrectly.
+
+The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO.
+ILP shows robustness and produces results even for a high number of nodes and edges.
 
@@
 
+\bottomrule[1.5pt]
 %ILP

### 2015-09-10 Docs/Paper/LaTex/template.tex
review 6 Related Work

@@
 
-Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.
+Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution~\cite{Mann2007}, to use heuristics to speed up performance time~\cite{Arato2003}, and hybrid ones~\cite{Arato2005}.
 
 In the first group, the exact solution to the HW-SW partitioning problem is found.
-The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithm.
-The difference is based only in terms of the technique chosen to solve the problem.
+The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithms.
+The difference is based only on the technique chosen to solve the problem.
 Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution.
-The difference between this kind of solutions and SMT-based verification is based on two facts: ESBMC is guaranteed to find the exact solution, but the heuristics are faster when the complexity is greater.
+The difference of this kind of solution to SMT-based verification and maximum satisfiability is based on two facts: all ESBMC implementations guarantee to find the exact solution, but heuristics are faster, when the complexity is greater.
 
@@
 
-In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
-In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software.
-In~\cite{Trindade2015} and~\cite{Trindade2014} it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to support parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}.
-
+In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
+In~\cite{Trindade2015} and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.
+
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
 $\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
@@
 In Partrick {\it et al.}~\cite{Patrick2015},  OptiMathSAT and $\nu$Z are compared for software optimization problems.
-OptiMathSAT using multiple objective functions works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.
+OptiMathSAT, using multiple objective functions, works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.
 

### 2015-09-10 Docs/Paper/LaTex/template.tex
final adjustments

@@
 Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in ~\cite{Arato2003} and~\cite{Mann2007}.
-In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
+In~\cite{Trindade2015,Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
 The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
@@
 In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers.
-In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2014}, it was shown that it is possible to use ESBMC also as an optimization tool.}
+In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2016}, it was shown that it is possible to use ESBMC also as an optimization tool.}
 In particular, there are two directives in ESBMC that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
@@
   \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
-	\caption{ESBMC Architecture}
+	\caption{ESBMC Architecture.}
 	\label{ESBMC-Architecture}
@@
 
-\begin{lstlisting}[caption=OpenMP basic sample]
+\begin{lstlisting}[caption=OpenMP basic sample.]
 01.  int i;
@@
 
-\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z, label=vZ]
+\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
 1. (declare-const K Int) 
@@
   \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
-	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}}
+	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
 	\label{vZ-Architecture}
@@
 
-The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2014}.
+The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
 Both use slack variables in order to be possible to represent constraints and to use commercial tools.
@@
 Here, matrices $A$ and $b$ are generated.
-At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015} and~\cite{Trindade2014}.
+At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.
 
@@
 
-\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC, label={Pseudocode-describing-ESBMC}, mathescape]
+\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
 01. Initialize Variables 
@@
   \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
-	\caption{ESBMC-PB Approach}
+	\caption{ESBMC-PB Approach.}
 	\label{ESBMC-Binary-Approach}
@@
   \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
-	\caption{Binary Step Calculation}
+	\caption{Binary Step Calculation.}
 	\label{Binary-Step-Calculation}
@@
 
-\begin{lstlisting}[caption=Steps Calculation using Intervals,label=Steps-Calculation-using-Intervals]
+\begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
 01. GetNextStep(){
@@
 
-\begin{lstlisting}[caption=Worker sample,label=worker-sample]
+\begin{lstlisting}[caption=Worker sample.,label=worker-sample]
 01. step = controller.GetNextStep();
@@
 
-\begin{lstlisting}[caption=Pseudocode describing $\nu$Z,label=vZ-pseudocode, mathescape]
+\begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
 01.#Initialize Variables
@@
 \begin{table}[h]
-\caption {Description of Benchmarks}
+\caption {Description of Benchmarks.}
 \small
@@
   \centering
-  \caption{Experimental results of the HW-SW partitioning benchmarks}  
+  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
   \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
@@
 
-We presented four approaches to solve the HW-SW partitioning problem and compared them to other three state-of-the-art techniques.
+We presented five approaches to solve the HW-SW partitioning problem and compared them to other state-of-the-art techniques.
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-Below that, the best option turns out to be $\nu$Z since its execution time is faster and notorious.
-ESBMC is a viable alternative for a number of nodes lower than $150$.
+Below that, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and notorious.
+ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
-This error may be reduced by changing some parameters.
-
-%The computing time to solve the optimization problem reached some hours of execution on a standard desktop computer.
 
@@
 In particular, all three parallel approaches described in this paper produced expressive results.
-The fastest ESBMC approaches is ESBMC-PB (Parallel Binary), which produces good results for an intermediate amount of edges and nodes.
+The fastest ESBMC approaches is ESBMC-PB, which produces good results for an intermediate amount of edges and nodes.
 Thus, considering that nowadays processors have more and more cores, when modeling the problem, it is possible to consider multi-core model checking as an alternative to solve the HW-SW partitioning problem.
 
-Finally, there is an issue about $150$ nodes problem, since it seems to be the limit of ESBMC.
-It really depends on the modeling granularity of the problem.
+Finally, there is an issue about $150$ nodes problem, since it seems to be the limit of multi-core ESBMC.
+However, it really depends on the modeling granularity of the problem.
 Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW.
@@
 %6
-\bibitem{Trindade2014}
-Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software},'' In: Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1--6.
-
-%7
 \bibitem{Wu2014}
@@
 of the Intl.
-Conference on Software Engineering and Service Science, pp.
+Conf.
+on Software Engineering and Service Science, pp.
 921--924.
@@
 \bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education (ICCSE)},'' pp. 1900--1905.
+Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.
 
@@
 \bibitem{Arato2005}
-Arat\'o, P., Mann, Z.A., Orb\'an, A.
-(2005), ``{Algorithmic aspects of hardware/software partitioning.},'' In: Proc.
-of the Association Computing Machinery Transactions on Design Automation of Electronic Systems, v.
-1, pp.
-136–-156.
+Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
 

### 2015-09-10 Docs/Paper/LaTex/template.tex
fix references

@@
 
-\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction ~\cite{Baier2008}.
+\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
@@
 
-Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
 Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}.
@@
 \comment{
-Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}.
+Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}.
 These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
@@
 The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Armando2009},\cite{Ganai2006},\cite{Cordeiro2012}.
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.
 
@@
 Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}.
-A $\nu$Z logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints.
+A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the set of constraints.
 Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
@@
 %3
-\bibitem{Baier2008}
-Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking}'', The MIT Press, London.
-
-%4
-\bibitem{Clarke2009}
-Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging},'' In: Communications of the Association Computing Machinery, v. 52, n. 11, pp. 74--84.
-
-%5
 \bibitem{Trindade2015}
@@
 
-%5
+%4
 \bibitem{Trindade2016}
@@
 
-%6
-\bibitem{Wu2014}
-Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
+%5
+\bibitem{Bjorner2015}
+Bjorner, N., Phan, A-D., Fleckenstein, L.
+(2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
 of the Intl.
 Conf.
-on Software Engineering and Service Science, pp.
-921--924.
-
-%8
+on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
+194--199.
+
+%6
 \bibitem{Tang2009}
 Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.
+
+%7
+\bibitem{OpenMP1998}
+OpenMP Architecture Review Board, OpenMP C and C++
+Application Pogram Interface, Version 1.0, October 1998.
+http://www.openmp.org
+
+%8
+\bibitem{Cordeiro2012}
+Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
 
@@
 \bibitem{Biere2009}
-Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
+Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
 
 %11
-\bibitem{Clarke2004}
-Clarke, E., Kroening, D., Lerda, F.
-(2004), ``{A Tool for Checking ANSI-C Programs}'', In: Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 2988, pp.
-168--176.
-
-%12
 \bibitem{Armando2009}
@@
 
-%13
+%12
 \bibitem{Ganai2006}
@@
 
-%14
-\bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
-
-%15
-\bibitem{Cordeiro2011}
-Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
-
-%16
+%13
 \bibitem{Ramalho2013}
@@
 
-%17
-\bibitem{Teich2012}
-Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
-
-%18
-\bibitem{TheMathWorks2013}
-The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
-
-%19
-\bibitem{Tranquillo2011}
-Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
-
-%20
-\bibitem{Hong2010}
-Hong, L., Cai, J.
-(2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
-of the Intl.
-Conf.
-on Computer and Automation Engineering, pp.
-185--189.
-
-%21
-\bibitem{Guthaus2001}
-Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
-(2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
-of the annual workshop on workload characterization, pp.
-3--14.
-
-%22
-\bibitem{Arato2005}
-Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
-
-%23
-\bibitem{Dagum1998}
-Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming.},'' In: Proc. of the Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
-
-%24
+%14
 \bibitem{DeMoura2008}
@@
 
-%25
+%15
 \bibitem{Brummayer2009}
@@
 
-%26
+%16
 \bibitem{Barrett2011}
@@
 
-%27
+%17
 \bibitem{Bozzano2005}
@@
 
-%28
+%18
 \bibitem{Dutertre2014}
@@
 
+%19
+\bibitem{Wu2014}
+Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
+(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
+of the Intl.
+Conf.
+on Software Engineering and Service Science, pp.
+921--924.
+
+%20
+\bibitem{Bjorner2014}
+Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
+
+%21
+\bibitem{Federica2008}
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
+(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
+of the Intl.
+Conf.
+on Service-Oriented Computing, LNCS 5364, pp.
+116--131
+
+%22
+\bibitem{NarodytskaN}
+Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
+
+%23
+\bibitem{Barth1995}
+Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
+Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
+
+%24
+\bibitem{Vasco2005}
+Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
+
+%25
+\bibitem{Z3API}
+Magellan, ``{Source code and documentation},''
+  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
+
+%26
+\bibitem{Cormem}
+Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
+
+%27
+\bibitem{Dagum1998}
+Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
+
+%28
+\bibitem{TheMathWorks2013}
+The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
+
 %29
+\bibitem{Tranquillo2011}
+Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
+
+%30
+\bibitem{Hong2010}
+Hong, L., Cai, J.
+(2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
+of the Intl.
+Conf.
+on Computer and Automation Engineering, pp.
+185--189.
+
+%31
+\bibitem{Cordeiro2011}
+Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
+
+%32
+\bibitem{Teich2012}
+Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
+
+%33
+\bibitem{Guthaus2001}
+Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
+(2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
+of the annual workshop on workload characterization, pp.
+3--14.
+
+%34
+\bibitem{Arato2005}
+Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
+
+%35
 \bibitem{Holzmann2011}
@@
 
-%30
+%36
 \bibitem{Holzmann2012}
@@
 
-%31
+%37
 \bibitem{Wintersteiger2009}
@@
 
-%32
-\bibitem{Bjorner2015}
-Bjorner, N., Phan, A-D., Fleckenstein, L.
-(2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
-194--199.
-
-%33
+%38
 \bibitem{Qawasmeh2014}
@@
 
-%34
-\bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
-
-%35
-\bibitem{OpenMP1998}
-OpenMP Architecture Review Board, OpenMP C and C++
-Application Pogram Interface, Version 1.0, October 1998.
-http://www.openmp.org
-
-%36
-\bibitem{Z3API}
-Magellan, ``{Source code and documentation},''
-  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
-
-%37
-\bibitem{GA}
-URFJ, ``{Algoritmos Genéticos: Fundamentos e Aplicações. Marcio Nunes de Miranda},''
-  \url{http://www.nce.ufrj.br/GINAPE/VIDA/alggenet.htm}, Accessed 18th August 2015.
-
-%38
-\bibitem{NarodytskaN}
-Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
-
 %39
-\bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
-(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
-of the Intl.
-Conf.
-on Service-Oriented Computing, LNCS 5364, pp.
-116--131
-
-%40
-\bibitem{Barth1995}
-Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
-Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
-
-%41
-\bibitem{Vasco2005}
-Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
-
-%42
 \bibitem{Pavlinovic2015}
@@
 
-%43
+%40
 \bibitem{Patrick2015}
@@
 
-%43
-\bibitem{Cormem}
-Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
-
-%44
+%41
 \bibitem{Holzmann11}

### 2015-09-18 Docs/TODAES/paper.tex
including first version of TODAES template

--- 2015-09-10 Docs/Paper/LaTex/template.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
+% v2-acmsmall-sample.tex, dated March 6 2012
+% This is a sample file for ACM small trim journals
+%
+% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
+% (c) 2010 Association for Computing Machinery (ACM)
+%
+% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
+% Users can also go through the FAQs available on the journal's submission webpage.
+%
+% Steps to compile: latex, bibtex, latex latex
+%
+% For tracking purposes => this is v1.3 - March 2012
+
+\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+
 \usepackage{color}
@@
 \usepackage{cite}
-
 \usepackage{hyphenat}
 \usepackage[english]{babel}
+
 \hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
 
-\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
-\renewcommand{\lstlistingname}{Algorithm}
-\renewcommand{\arraystretch}{1.3}
-\usepackage[table]{xcolor}
-\usepackage{color}
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-\definecolor{Gray}{gray}{0.93}
-\definecolor{DarkGray}{gray}{0.70}
-
-\lstset{frame=tb,
-  language=c,
-  aboveskip=3mm,
-  belowskip=3mm,
-  showstringspaces=false,
-  columns=flexible,
-  basicstyle={\small\ttfamily},
-  numbers=none,
-  numberstyle=\tiny\color{gray},
-  keywordstyle=\color{black},
-  commentstyle=\color{dkgreen},
-  stringstyle=\color{mauve},
-  breaklines=true,
-  breakatwhitespace=true,
-  tabsize=3
+% Package to generate and customize Algorithm as per ACM style
+\usepackage[ruled]{algorithm2e}
+\renewcommand{\algorithmcfname}{ALGORITHM}
+\SetAlFnt{\small}
+\SetAlCapFnt{\small}
+\SetAlCapNameFnt{\small}
+\SetAlCapHSkip{0pt}
+\IncMargin{-\parindent}
+
+% Metadata Information
+\acmVolume{9}
+\acmNumber{4}
+\acmArticle{39}
+\acmYear{2010}
+\acmMonth{3}
+
+% Copyright
+\setcopyright{rightsretained}
+
+% DOI
+\doi{0000001.0000001}
+
+%ISSN
+\issn{1234-56789}
+
+% Document starts
+\begin{document}
+
+% Page heads
+\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}
+
+\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
+
+% Title portion
+\author{
+Alessandro Trindade
+\affil{Federal University of Amazonas}
+Hussama Ismail
+\affil{Federal University of Amazonas}
+Edilson Galv\~ao\
+\affil{Federal University of Amazonas}
+Helder Silva
+\affil{Federal University of Amazonas}
+Lucas Cordeiro\affil{Federal University of Amazonas}
 }
-\DeclareGraphicsExtensions{.pdf,.png,.jpg}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-
-\renewcommand{\baselinestretch}{0.96}
-
-\newcommand{\comment}[1]{}
-
-\begin{document}
-\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
-\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}
-
-\institute{A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \at
-              Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
-%              Tel.: +123-45-678910\\
-%              Fax: +123-45-678910\\
-              \email{\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com}          %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           H. Silva and L. Cordeiro \at
-              Federal University of Amazonas, Brazil
-              \email: prhsilva2012@gmail.com lucascordeiro@ufam.edu.br           %  \\
-}
-
-\maketitle
+
+% NOTE! Affiliations placed here should be for the institution where the
+%       BULK of the research was done. If the author has gone to a new
+%       institution, before publication, the (above) affiliation should NOT be changed.
+%       The authors 'current' address may be given in the "Author's addresses:" block (below).
+%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
+%       currently affiliated with NASA.
 
@@
 
-\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+%\begin{CCSXML}
+%<ccs2012>
+% <concept>
+%  <concept_id>10010520.10010553.10010562</concept_id>
+%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%  <concept_significance>500</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010575.10010755</concept_id>
+%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%  <concept_significance>300</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010553.10010554</concept_id>
+%  <concept_desc>Computer systems organization~Robotics</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10003033.10003083.10003095</concept_id>
+%  <concept_desc>Networks~Network reliability</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+%</ccs2012>  
+%\end{CCSXML}
+
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
+
+%
+% End generated code
+%
+
+%\terms{Design, Algorithms, Performance}
+
+\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP. }
+
+%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
+%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
+%designed for  wireless sensor network applications.}
+% At a minimum you need to supply the author names, year and a title.
+% IMPORTANT:
+% Full first names whenever they are known, surname last, followed by a period.
+% In the case of two authors, 'and' is placed between them.
+% In the case of three or more authors, the serial comma is used, that is, all author names
+% except the last one but including the penultimate author's name are followed by a comma,
+% and then 'and' is placed before the final author's name.
+% If only first and middle initials are known, then each initial
+% is followed by a period and they are separated by a space.
+% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
+
+\begin{bottomstuff}
+A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \\
+Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
+\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ \\
+\and\\ \\
+H. Silva and L. Cordeiro \\
+Federal University of Amazonas, Brazil\\
+prhsilva2012@gmail.com lucascordeiro@ufam.edu.br      \\
+\end{bottomstuff}
+
+\maketitle
 
@@
 
-\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}.
+%In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
@@
 Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-The system models are accompanied by algorithms that systematically explore all the states of the system model.}
+The system models are accompanied by algorithms that systematically explore all the states of the system model.
 
@@
 
-\comment{Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
+%Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
 In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}.
-However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.}
+However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.
 
@@
 Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}.
-\comment{In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
+
+%In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
 The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
-Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.}
+Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
+
 There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}.
@@
 
-\comment{
-Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}.
+%Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}.
 These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
@@
 Much research has been devoted to mitigate this problem.
-}
 
@@
 In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
-\comment{According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
+%According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
 In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers.
@@
 	\centering
-  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
+  \includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
 	\caption{ESBMC Architecture.}
@@
 
-\comment{SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.}
+%SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.
 
@@
 	\centering
-  \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
+  \includegraphics[width=0.49\textwidth, height=95px]{figures/vzArch.png} 
 	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
@@
 
-\comment{
-%----------------------------------------------
-\section{Partitioning problem using ILP-based,Genetic Algorithms}
-\label{ILPGA}
-%----------------------------------------------
-
-The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
-Both use slack variables in order to be possible to represent constraints and to use commercial tools.
-However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
-}
+%\comment{
+%----------------------------------------------
+%\section{Partitioning problem using ILP-based,Genetic Algorithms}
+%\label{ILPGA}
+%----------------------------------------------
+
+%The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
+Both use slack variables in order to be %possible to represent constraints and to use commercial tools.
+However, GA had improvements from the parameters of related %studies in order to increase the solution accuracy without producing timeout.
+The tuning was performed by empirical tests and %resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the %population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of %generations changed from $100*NumberOfVariables$ (default) to $75$.
+%}
 
@@
 	\centering
-  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
+  \includegraphics[scale=0.75]{figures/esbmc-parallel.pdf} 
 	\caption{ESBMC-SS Approach.}
@@
 	\centering
-  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
+  \includegraphics[scale=0.75]{figures/esbmc-parallel.png} 
 	\caption{ESBMC-PS Approach. }
@@
 	\centering
-  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
+  \includegraphics[scale=0.75]{figures/esbmc-parallel-Controler.png} 
 	\caption{ESBMC-PB Approach.}
@@
 	\centering
-  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
+  \includegraphics[width=0.49\textwidth, height=75px]{figures/Fig4.png}
 	\caption{Binary Step Calculation.}
@@
   \toprule[1.5pt]
-  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
+%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
   \midrule
@@
 
-\begin{thebibliography}{5}
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{{#1}}
-\providecommand{\urlprefix}{URL }
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-  \urlstyle{rm}\Url}\fi
-\providecommand{\eprint}[2][]{\url{#2}}
+% Bibliography
+%\bibliographystyle{ACM-Reference-Format-Journals}
+%\providecommand{\natexlab}[1]{#1}
+%\providecommand{\url}[1]{{#1}}
+%\providecommand{\urlprefix}{URL }
+%\expandafter\ifx\csname urlstyle\endcsname\relax
+%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
+%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
+%  \urlstyle{rm}\Url}\fi
+%\providecommand{\eprint}[2][]{\url{#2}}
 
 %1
-\bibitem{Arato2003}
-Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
-(2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc.
+%\bibitem{Arato2003}
+%Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
+(2003), ``{Hardware/software partitioning in embedded system %design},'' In: Proc.
 of the Intl.
@@
 %2
-\bibitem{Mann2007}
-Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.
+%\bibitem{Mann2007}
+%Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System %Design, v. 31, n. 3 pp. 241--263.
 
 %3
-\bibitem{Trindade2015}
-Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).
+%\bibitem{Trindade2015}
+%Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded %systems,}'' In: Design Automation for Embedded Systems (to appear).
 
 %4
-\bibitem{Trindade2016}
-Trindade, A.
+%\bibitem{Trindade2016}
+%Trindade, A.
 B., Ismail, H.
@@
 C.
-(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
+(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in %Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
 1-4.
@@
 %5
-\bibitem{Bjorner2015}
-Bjorner, N., Phan, A-D., Fleckenstein, L.
+%\bibitem{Bjorner2015}
+%Bjorner, N., Phan, A-D., Fleckenstein, L.
 (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
@@
 Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
+on %Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
 194--199.
@@
 %6
-\bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.
+%\bibitem{Tang2009}
+%Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. %on Computer Science Education},'' pp. 1900--1905.
 
 %7
-\bibitem{OpenMP1998}
-OpenMP Architecture Review Board, OpenMP C and C++
-Application Pogram Interface, Version 1.0, October 1998.
-http://www.openmp.org
+%\bibitem{OpenMP1998}
+%OpenMP Architecture Review Board, OpenMP C and C++
+%Application Pogram Interface, Version 1.0, October 1998.
+%http://www.openmp.org%
 
 %8
-\bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
+%\bibitem{Cordeiro2012}
+%Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: %IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
 
 %9
-\bibitem{Rao2009}
-Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
+%\bibitem{Rao2009}
+%Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
 
 %10
-\bibitem{Biere2009}
-Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
+%\bibitem{Biere2009}
+%Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of %Satisfiability, IOS Press, pp. 457–-481.
 
 %11
-\bibitem{Armando2009}
-Armando, A., Mantovani, J., Platania, L.
-(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl.
+%\bibitem{Armando2009}
+%Armando, A., Mantovani, J., Platania, L.
+(2009), ``{Bounded model checking of software using SMT solvers instead of SAT %solvers},'' In: Intl.
 Journal on Software Tools for Technology Transfer, v.
@@
 %12
-\bibitem{Ganai2006}
-Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.
+%\bibitem{Ganai2006}
+%Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on %Computer-Aided Design, pp. 794-–801.
 
 %13
-\bibitem{Ramalho2013}
-Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
-(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl.
+%\bibitem{Ramalho2013}
+%Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
+(2013), ``{SMT-Based Bounded Model Checking of C++ %Programs.},'' In: Intl.
 Conf.
@@
 %14
-\bibitem{DeMoura2008}
-De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
+%\bibitem{DeMoura2008}
+%De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for %the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
 
 %15
-\bibitem{Brummayer2009}
-Brummayer, R., Biere, A.
+%\bibitem{Brummayer2009}
+%Brummayer, R., Biere, A.
 (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc.
 of the Intl.
-Conf.
+%Conf.
 on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp.
@@
 %16
-\bibitem{Barrett2011}
-Barrett, C., Conway, C.
+%\bibitem{Barrett2011}
+%Barrett, C., Conway, C.
 Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C.
-(2011), ``{CVC4},'' In: Proc.
+(2011), ``{CVC4},'' In: %Proc.
 of the Intl.
@@
 %17
-\bibitem{Bozzano2005}
-Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
-(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
+%\bibitem{Bozzano2005}
+%Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
+(2005), ``{MathSAT: Tight %integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
 35, n.
@@
 %18
-\bibitem{Dutertre2014}
-Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
+%\bibitem{Dutertre2014}
+%Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
 
 %19
-\bibitem{Wu2014}
-Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
+%\bibitem{Wu2014}
+%Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
+(2014), ``{Research on OpenMP model of the parallel programming %technology for homogeneous multicore DSP},'' In: Proc.
 of the Intl.
@@
 on Software Engineering and Service Science, pp.
-921--924.
+%921--924.
 
 %20
-\bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
+%\bibitem{Bjorner2014}
+%Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic %Computation in Software Science, pp. 1--10.
 
 %21
-\bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
-(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
+%\bibitem{Federica2008}
+%Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
+(2008), {``Authorization and User Failure Resiliency for WS-BPEL business %processes''}, In: Proc.
 of the Intl.
@@
 %22
-\bibitem{NarodytskaN}
-Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
+%\bibitem{NarodytskaN}
+%Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI %Conf. on Artificial Intelligence, pp. 2717--2723.
 
 %23
-\bibitem{Barth1995}
-Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
-Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
+%\bibitem{Barth1995}
+%Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
+%Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
 
 %24
-\bibitem{Vasco2005}
-Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
+%\bibitem{Vasco2005}
+%Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, %Technical University of Lisbon, Portugal.
 
 %25
-\bibitem{Z3API}
-Magellan, ``{Source code and documentation},''
-  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
+%\bibitem{Z3API}
+%Magellan, ``{Source code and documentation},''
+%  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
 
 %26
-\bibitem{Cormem}
-Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
+%\bibitem{Cormem}
+%Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
 
 %27
-\bibitem{Dagum1998}
-Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
+%\bibitem{Dagum1998}
+%Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
 
 %28
-\bibitem{TheMathWorks2013}
-The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
+%\bibitem{TheMathWorks2013}
+%The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
 
 %29
-\bibitem{Tranquillo2011}
-Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
+%\bibitem{Tranquillo2011}
+%Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
 
 %30
-\bibitem{Hong2010}
-Hong, L., Cai, J.
+%\bibitem{Hong2010}
+%Hong, L., Cai, J.
 (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
@@
 %31
-\bibitem{Cordeiro2011}
-Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
+%\bibitem{Cordeiro2011}
+%Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
 
 %32
-\bibitem{Teich2012}
-Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
+%\bibitem{Teich2012}
+%Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
 
 %33
-\bibitem{Guthaus2001}
-Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
+%\bibitem{Guthaus2001}
+%Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
 (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
@@
 %34
-\bibitem{Arato2005}
-Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
+%\bibitem{Arato2005}
+%Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
 
 %35
-\bibitem{Holzmann2011}
-Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
+%\bibitem{Holzmann2011}
+%Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
 
 %36
-\bibitem{Holzmann2012}
-Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
+%\bibitem{Holzmann2012}
+%Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
 
 %37
-\bibitem{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
+%\bibitem{Wintersteiger2009}
+%Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
 
 %38
-\bibitem{Qawasmeh2014}
-Qawasmeh, A., Malik, A., Chapman, B.
+%\bibitem{Qawasmeh2014}
+%Qawasmeh, A., Malik, A., Chapman, B.
 (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc.
@@
 %39
-\bibitem{Pavlinovic2015}
-Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
+%\bibitem{Pavlinovic2015}
+%Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
 
 %40
-\bibitem{Patrick2015}
-Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
+%\bibitem{Patrick2015}
+%Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
 
 %41
-\bibitem{Holzmann11}
-Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
-
-\end{thebibliography}
+%\bibitem{Holzmann11}
+%Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
+
+%\end{thebibliography}
+
+% Appendix
+%\appendix
+%\section*{APPENDIX}
+%\setcounter{section}{1}
+%In this appendix, we measure
+%the channel switching time of Micaz [CROSSBOW] sensor devices.
+%In our experiments, one mote alternatingly switches between Channels
+%11 and 12. Every time after the node switches to a channel, it sends
+%%out a packet immediately and then changes to a new channel as soon
+%as the transmission is finished. We measure the
+%number of packets the test mote can send in 10 seconds, denoted as
+%$%N_{1}$. In contrast, we also measure the same value of the test
+%mote without switching channels, denoted as $N_{2}$. We calculate
+%the channel-switching time $s$ as
+%\begin{eqnarray}%
+%s=\frac{10}{N_{1}}-\frac{10}{N_{2}}. \nonumber
+%\end{eqnarray}%
+%By repeating the experiments 100 times, we get the average
+%channel-switching time of Micaz motes: 24.3$\mu$s.
+
+%\appendixhead{ZHOU}
+
+% Acknowledgments
+\begin{acks}
+The authors would like to thank Dr. Maura Turolla of Telecom
+Italia for providing specifications about the application scenario.
+\end{acks}
+
+% Bibliography
+%\bibliographystyle{ACM-Reference-Format-Journals}
+%\bibliography{acmsmall-sample-bibfile}
+                             % Sample .bib file with references that match those in
+                             % the 'Specifications Document (V1.5)' as well containing
+                             % 'legacy' bibs and bibs with 'alternate codings'.
+                             % Gerry Murray - March 2012
+
+% History dates
+%\received{February 2007}{March 2009}{June 2009}
+
+% Electronic Appendix
+%\elecappendix
+
+\medskip
+
+\section{This is an example of Appendix section head}
+
+Channel-switching time is measured as the time length it takes for
+motes to successfully switch from one channel to another. This
+parameter impacts the maximum network throughput, because motes
+cannot receive or send any packet during this period of time, and it
+also affects the efficiency of toggle snooping in MMSN, where motes
+need to sense through channels rapidly.
+
+By repeating experiments 100 times, we get the average
+channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
+the same experiments with different Micaz motes, as well as
+experiments with the transmitter switching from Channel 11 to other
+channels. In both scenarios, the channel-switching time does not have
+obvious changes. (In our experiments, all values are in the range of
+23.6 $\mu$s to 24.9 $\mu$s.)
+
+\section{Appendix section head}
+
+The primary consumer of energy in WSNs is idle listening. The key to
+reduce idle listening is executing low duty-cycle on nodes. Two
+primary approaches are considered in controlling duty-cycles in the
+MAC layer.
 
 \end{document}
-
-% end of file template.texe os
+% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2015-09-18 Docs/TODAES/paper.tex
minor changes
SBESC reviewer's suggestions done + new vZ times

@@
 \renewcommand{\algorithmcfname}{ALGORITHM}
+
 \SetAlFnt{\small}
@@
 % Page heads
-\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}
+\markboth{A. Trindade et al.}{Multi-Core Model Checking and Maximum Satisfiability Applied to HW/SW Partitioning}
 
@@
 \begin{abstract}
-We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing.
+We present an alternative approach to solve the hardware and software partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing.
 In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
@@
 We compare all our approaches to another state-of-the-art optimization tool (Matlab).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve HW-SW partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
+Experimental results show that there is no single optimization tool to solve all hardware-software partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve hardware-software partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
 \end{abstract}
@@
 All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits.
-Each time was measured $3$ times in GA (average taken) and just once in ESBMC, $\nu$Z, and ILP.
-The reason is that GA times are not so close as ESBMC, $\nu$Z, and ILP.
+Each time was measured $3$ times (average taken).
+Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP.
 A time out condition (TO) is reached when the verification time is longer than $7200$ seconds.
@@
 \multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
-&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\
+&  T(s)   &  0.3   &  0.3   &  0.7   &  86.4   &  TO    &  TO   &  TO  \\
+&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
 

### 2015-09-23 Docs/TODAES/paper.tex
modifications in figures and journal structure

@@
 \usepackage[english]{babel}
+\usepackage[skip=\baselineskip]{caption}
+\captionsetup[lstlisting]{font={small,tt}}
 
@@
 Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
+
 \begin{equation}
@@
 
+\vspace{5 mm}
 In some cases, the time to find a solution using ILP is impractical.
@@
 Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
-%
+
 \begin{figure}[ht]
 	\centering
-  \includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
+  \includegraphics[scale=1.25]{figures/esbmc-arch-new.pdf} 
 	\caption{ESBMC Architecture.}
@@
 
-\begin{lstlisting}[caption=OpenMP basic sample.]
+\begin{lstlisting}[caption="OpenMP basic sample."]
+
 01.  int i;
@@
 
+\vspace{3 mm}
 In the above example, the for loop is executed in parallel.
@@
 \begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
+
 1. (declare-const K Int) 
@@
 
+\vspace{3 mm}
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
@@
 When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
-%
+
 \begin{figure}[ht]
 	\centering
-  \includegraphics[width=0.49\textwidth, height=95px]{figures/vzArch.png} 
+  \includegraphics[scale=0.3]{figures/vzArch.png} 
 	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
@@
 The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
-%
+
 \begin{align}
@@
 \end{align}
-%
+
+\vspace{3 mm}
 \noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
-%
+
 %  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
@@
 
+\vspace{3 mm}
 Three different optimization and decision problems can be defined.
@@
 Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
-%
+
 \begin{align}
@@
 \end{align}
-%
+
+\vspace{3 mm}
 \noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
@@
 \begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
+
 01. Initialize Variables 
@@
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
-%
+
 \begin{figure}[ht]
 	\centering
-  \includegraphics[scale=0.75]{figures/esbmc-parallel.pdf} 
+  \includegraphics[scale=1.0]{figures/esbmc-ss.pdf} 
 	\caption{ESBMC-SS Approach.}
@@
 	\centering
-  \includegraphics[scale=0.75]{figures/esbmc-parallel.png} 
+  \includegraphics[scale=1.0]{figures/esbmc-ps.pdf} 
 	\caption{ESBMC-PS Approach. }
@@
 The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
-%
+
 \begin{figure}[ht]
 	\centering
-  \includegraphics[scale=0.75]{figures/esbmc-parallel-Controler.png} 
+  \includegraphics[scale=1.0]{figures/esbmc-pb.pdf} 
 	\caption{ESBMC-PB Approach.}
@@
 The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
-%
+
 \begin{figure}[ht]
 	\centering
-  \includegraphics[width=0.49\textwidth, height=75px]{figures/Fig4.png}
+  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
 	\caption{Binary Step Calculation.}
@@
 \begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
+
 01. GetNextStep(){
@@
 
+\vspace{3 mm}
 Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
@@
 \begin{lstlisting}[caption=Worker sample.,label=worker-sample]
+
 01. step = controller.GetNextStep();
@@
 
+\vspace{3 mm}
 Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
@@
 \begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
+
 01.#Initialize Variables
@@
 \begin{table}[h]
+\centering
 \caption {Description of Benchmarks.}

### 2015-09-26 Docs/TODAES/acmsmall-sample.tex
including references and adjusting table of results

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

% Document starts
\begin{document}

% Page heads
\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}

% Title portion
\title{A Multifrequency MAC Specially Designed for Wireless Sensor Network Applications}
\author{GANG ZHOU
\affil{College of William and Mary}
YAFENG WU
\affil{University of Virginia}
TING YAN
\affil{Eaton Innovation Center}
TIAN HE
\affil{University of Minnesota}
CHENGDU HUANG
\affil{Google}
JOHN A. STANKOVIC
\affil{University of Virginia}
TAREK F. ABDELZAHER
\affil{University of Illinois at Urbana-Champaign}}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
Multifrequency media access control has been well understood in
general wireless ad hoc networks, while in wireless sensor networks,
researchers still focus on single frequency solutions. In wireless
sensor networks, each device is typically equipped with a single
radio transceiver and applications adopt much smaller packet sizes
compared to those in general wireless ad hoc networks. Hence, the
multifrequency MAC protocols proposed for general wireless ad hoc
networks are not suitable for wireless sensor network applications,
which we further demonstrate through our simulation experiments. In
this article, we propose MMSN, which takes advantage of
multifrequency availability while, at the same time, takes into
consideration the restrictions of wireless sensor networks. Through
extensive experiments, MMSN exhibits the prominent ability to utilize
parallel transmissions among neighboring nodes. When multiple physical
frequencies are available, it also achieves increased energy
efficiency, demonstrating the ability to work against radio
interference and the tolerance to a wide range of measured time
synchronization errors.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

% We no longer use \terms command
%\terms{Design, Algorithms, Performance}

\keywords{Wireless sensor networks, media access control,
multi-channel, radio interference, time synchronization}

\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
designed for  wireless sensor network applications.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
This work is supported by the National Science Foundation, under
grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.

Author's addresses: G. Zhou, Computer Science Department,
College of William and Mary; Y. Wu  {and} J. A. Stankovic,
Computer Science Department, University of Virginia; T. Yan,
Eaton Innovation Center; T. He, Computer Science Department,
University of Minnesota; C. Huang, Google; T. F. Abdelzaher,
(Current address) NASA Ames Research Center, Moffett Field, California 94035.
\end{bottomstuff}

\maketitle

\section{Introduction}

As a new technology, Wireless Sensor Networks (WSNs) has a wide
range of applications [Culler 2001,Bahl 2002,Akyildiz 2001], including
environment monitoring, smart buildings, medical care, industrial and
military applications. Among them, a recent trend is to develop
commercial sensor networks that require pervasive sensing of both
environment and human beings, for example, assisted living
[Akyildiz 2002,Harvard 2001,CROSSBOW] and smart homes
[Harvard 2001,Adya 2001,CROSSBOW].
% quote
\begin{quote}
``For these applications, sensor devices are incorporated into human
cloths [Natarajan 2001,Zhou 2006,Bahl 2002,Adya 2001] for monitoring
health related information like EKG readings, fall detection, and voice recognition".
\end{quote}
While collecting all these multimedia information
[Akyildiz 2002] requires a high network throughput, off-the-shelf
sensor devices only provide very limited bandwidth in a single
channel: 19.2Kbps in MICA2 [Bahl 2002] and 250Kbps in MICAz.

In this article, we propose MMSN, abbreviation for Multifrequency
Media access control for wireless Sensor Networks. The main
contributions of this work can be summarized as follows.
% itemize
\begin{itemize}
\item To the best of our knowledge, the MMSN protocol is the first
multifrequency MAC protocol especially designed for WSNs, in which
each device is equipped with a single radio transceiver and
the MAC layer packet size is very small.
\item Instead of using pairwise RTS/CTS frequency negotiation
[Adya 2001,Culler 2001; Tzamaloukas 2001; Zhou 2006],
we propose lightweight frequency assignments, which are good choices
for many deployed comparatively static WSNs.
\item We develop new toggle transmission and snooping techniques to
enable a single radio transceiver in a sensor device to achieve
scalable performance, avoiding the nonscalable ``one
control channel + multiple data channels'' design [Natarajan 2001].
\end{itemize}

% Head 1
\section{MMSN Protocol}

% Head 2
\subsection{Frequency Assignment}

We propose a suboptimal distribution to be used by each node, which is
easy to compute and does not depend on the number of competing
nodes. A natural candidate is an increasing geometric sequence, in
which
% Numbered Equation
\begin{equation}
\label{eqn:01}
P(t)=\frac{b^{\frac{t+1}{T+1}}-b^{\frac{t}{T+1}}}{b-1},
\end{equation}
where $t=0,{\ldots}\,,T$, and $b$ is a number greater than $1$.

In our algorithm, we use the suboptimal approach for simplicity and
generality. We need to make the distribution of the selected back-off
time slice at each node conform to what is shown in Equation
(\ref{eqn:01}). It is implemented as follows: First, a random
variable $\alpha$ with a uniform distribution within the interval
$(0, 1)$ is generated on each node, then time slice $i$ is selected
according to the following equation:
% Unnumbered Equation
\[
i=\lfloor(T+1)\log_b[\alpha(b-1)+1]\rfloor.
\]
It can be easily proven that the distribution of $i$ conforms to Equation
(\ref{eqn:01}).

So protocols [Bahl 2002,Culler 2001,Zhou 2006,Adya 2001,Culler 2001;
Tzamaloukas-01; Akyildiz-01] that use RTS/CTS
controls\footnote{RTS/CTS controls are required to be implemented by
802.11-compliant devices. They can be used as an optional mechanism
to avoid Hidden Terminal Problems in the 802.11 standard and
protocols based on those similar to [Akyildiz 2001] and
[Adya 2001].} for frequency negotiation and reservation are not
suitable for WSN applications, even though they exhibit good
performance in general wireless ad hoc
networks.

% Head 3
\subsubsection{Exclusive Frequency Assignment}

In exclusive frequency assignment, nodes first exchange their IDs
among two communication hops so that each node knows its two-hop
neighbors' IDs. In the second broadcast, each node beacons all
neighbors' IDs it has collected during the first broadcast period.

% Head 4
\paragraph{Eavesdropping}

Even though the even selection scheme leads to even sharing of
available frequencies among any two-hop neighborhood, it involves a
number of two-hop broadcasts. To reduce the communication cost, we
propose a lightweight eavesdropping scheme.

\subsection{Basic Notations}

As Algorithm~\ref{alg:one} states, for each frequency
number, each node calculates a random number (${\textit{Rnd}}_{\alpha}$) for
itself and a random number (${\textit{Rnd}}_{\beta}$) for each of its two-hop
neighbors with the same pseudorandom number generator.
% Algorithm
\begin{algorithm}[t]
\SetAlgoNoLine
\KwIn{Node $\alpha$'s ID ($ID_{\alpha}$), and node $\alpha$'s
neighbors' IDs within two communication hops.}
\KwOut{The frequency number ($FreNum_{\alpha}$) node $\alpha$ gets assigned.}
$index$ = 0; $FreNum_{\alpha}$ = -1\;
\Repeat{$FreNum_{\alpha} > -1$}{
        $Rnd_{\alpha}$ = Random($ID_{\alpha}$, $index$)\;
        $Found$ = $TRUE$\;
        \For{each node $\beta$ in $\alpha$'s two communication hops
    }{
      $Rnd_{\beta}$ = Random($ID_{\beta}$, $index$)\;
      \If{($Rnd_{\alpha} < Rnd_{\beta}$) \text{or} ($Rnd_{\alpha}$ ==
          $Rnd_{\beta}$ \text{and} $ID_{\alpha} < ID_{\beta}$)\;
      }{
        $Found$ = $FALSE$; break\;
      }
        }
     \eIf{$Found$}{
           $FreNum_{\alpha}$ = $index$\;
         }{
           $index$ ++\;
     }
      }
\caption{Frequency Number Computation}
\label{alg:one}
\end{algorithm}

Bus masters are divided into two disjoint sets, $\mathcal{M}_{RT}$
and $\mathcal{M}_{NRT}$.
% description
\begin{description}
\item[RT Masters]
$\mathcal{M}_{RT}=\{ \vec{m}_{1},\dots,\vec{m}_{n}\}$ denotes the
$n$ RT masters issuing real-time constrained requests. To model the
current request issued by an $\vec{m}_{i}$ in $\mathcal{M}_{RT}$,
three parameters---the recurrence time $(r_i)$, the service cycle
$(c_i)$, and the relative deadline $(d_i)$---are used, with their
relationships.
\item[NRT Masters]
$\mathcal{M}_{NRT}=\{ \vec{m}_{n+1},\dots,\vec{m}_{n+m}\}$ is a set
of $m$ masters issuing nonreal-time constrained requests. In our
model, each $\vec{m}_{j}$ in $\mathcal{M}_{NRT}$ needs only one
parameter, the service cycle, to model the current request it
issues.
\end{description}

Here, a question may arise, since each node has a global ID. Why
don't we just map nodes' IDs within two hops into a group of
frequency numbers and assign those numbers to all nodes within two
hops?

\section{Simulator}
\label{sec:sim}

If the model checker requests successors of a state which are not
created yet, the state space uses the simulator to create the
successors on-the-fly. To create successor states the simulator
conducts the following steps.
% enumerate
\begin{enumerate}
\item Load state into microcontroller model.
\item Determine assignments needed for resolving nondeterminism.
\item For each assignment.
      \begin{enumerate}
      \item either call interrupt handler or simulate effect of next instruction, or
      \item evaluate truth values of atomic propositions.
      \end{enumerate}
\item Return resulting states.
\end{enumerate}
Figure~\ref{fig:one} shows a typical microcontroller C program that
controls an automotive power window lift. The program is one of the
programs used in the case study described in Section~\ref{sec:sim}.
At first sight, the programs looks like an ANSI~C program. It
contains function calls, assignments, if clauses, and while loops.
% Figure
\begin{figure}
\centerline{\includegraphics{acmsmall-mouse}}
\caption{Code before preprocessing.}
\label{fig:one}
\end{figure}

\subsection{Problem Formulation}

The objective of variable coalescence-based offset assignment is to find
both the coalescence scheme and the MWPC on the coalesced graph. We start
with a few definitions and lemmas for variable coalescence.

% Enunciations
\begin{definition}[Coalesced Node (C-Node)]A C-node is a set of
live ranges (webs) in the AG or IG that are coalesced. Nodes within the same
C-node cannot interfere with each other on the IG. Before any coalescing is
done, each live range is a C-node by itself.
\end{definition}

\begin{definition}[C-AG (Coalesced Access Graph)]The C-AG is the access
graph after node coalescence, which is composed of all C-nodes and C-edges.
\end{definition}

\begin{lemma}
The C-MWPC problem is NP-complete.
\end{lemma}
\begin{proof} C-MWPC can be easily reduced to the MWPC problem assuming a
coalescence graph without any edge or a fully connected interference graph.
Therefore, each C-node is an uncoalesced live range after value separation
and C-PC is equivalent to PC. A fully connected interference graph is made
possible when all live ranges interfere with each other. Thus, the C-MWPC
problem is NP-complete.
\end{proof}

\begin{lemma}[Lemma Subhead]The solution to the C-MWPC problem is no
worse than the solution to the MWPC.
\end{lemma}
\begin{proof}
Simply, any solution to the MWPC is also a solution to the
C-MWPC. But some solutions to C-MWPC may not apply to the MWPC (if any
coalescing were made).
\end{proof}

\section{Performance Evaluation}

During all the experiments, the Geographic Forwarding (GF)
[Akyildiz 2001] routing protocol is used. GF exploits geographic
information of nodes and conducts local data-forwarding to achieve
end-to-end routing. Our simulation is
configured according to the settings in
Table~\ref{tab:one}. Each run lasts for 2 minutes and
repeated 100 times. For each data value we present in the results,
we also give its 90\% confidence interval.
% Table
\begin{table}%
\tbl{Simulation Configuration\label{tab:one}}{%
\begin{tabular}{|l|l|}
\hline
TERRAIN{$^a$}   & (200m$\times$200m) Square\\\hline
Node Number     & 289\\\hline
Node Placement  & Uniform\\\hline
Application     & Many-to-Many/Gossip CBR Streams\\\hline
Payload Size    & 32 bytes\\\hline
Routing Layer   & GF\\\hline
MAC Layer       & CSMA/MMSN\\\hline
Radio Layer     & RADIO-ACCNOISE\\\hline
Radio Bandwidth & 250Kbps\\\hline
Radio Range     & 20m--45m\\\hline
\end{tabular}}
\begin{tabnote}%
\Note{Source:}{This is a table
sourcenote. This is a table sourcenote. This is a table
sourcenote.}
\vskip2pt
\Note{Note:}{This is a table footnote.}
\tabnoteentry{$^a$}{This is a table footnote. This is a
table footnote. This is a table footnote.}
\end{tabnote}%
\end{table}%

\section{Conclusions}

In this article, we develop the first multifrequency MAC protocol for
WSN applications in which each device adopts a
single radio transceiver. The different MAC design requirements for
WSNs and general wireless ad-hoc networks are
compared, and a complete WSN multifrequency MAC design (MMSN) is
put forth. During the MMSN design, we analyze and evaluate different
choices for frequency assignments and also discuss the nonuniform
back-off algorithms for the slotted media access design.

% Start of "Sample References" section

\section{Typical references in new ACM Reference Format}
A paginated journal article \cite{Abril07}, an enumerated
journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96},
a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation \cite{Editor00}
followed by the same example, however we only output the series if the volume number is given
\cite{Editor00a} (so Editor00a's series should NOT be present since it has no vol. no.),
a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book
in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97},
an article in a proceedings (of a conference, symposium, workshop for example)
(paginated proceedings article) \cite{Andler79}, a proceedings article
with all possible elements \cite{Smith10}, an example of an enumerated
proceedings article \cite{VanGundy07},
an informally published work \cite{Harel78}, a doctoral dissertation \cite{Clarkson85},
a master's thesis: \cite{anisi03}, an online document / world wide web resource \cite{Thornburg01}, \cite{Ablamowicz07},
\cite{Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03}
and \cite{Lee05} and (Case 3) a patent \cite{JoeScientist001},
work accepted for publication \cite{rous08}, 'YYYYb'-test for prolific author
\cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might contain
'duplicate' DOI and URLs (some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}.
Boris / Barbara Beeton: multi-volume works as books
\cite{MR781536} and \cite{MR781537}.

% Appendix
\appendix
\section*{APPENDIX}
\setcounter{section}{1}
In this appendix, we measure
the channel switching time of Micaz [CROSSBOW] sensor devices.
In our experiments, one mote alternatingly switches between Channels
11 and 12. Every time after the node switches to a channel, it sends
out a packet immediately and then changes to a new channel as soon
as the transmission is finished. We measure the
number of packets the test mote can send in 10 seconds, denoted as
$N_{1}$. In contrast, we also measure the same value of the test
mote without switching channels, denoted as $N_{2}$. We calculate
the channel-switching time $s$ as
\begin{eqnarray}%
s=\frac{10}{N_{1}}-\frac{10}{N_{2}}. \nonumber
\end{eqnarray}%
By repeating the experiments 100 times, we get the average
channel-switching time of Micaz motes: 24.3$\mu$s.

\appendixhead{ZHOU}

% Acknowledgments
\begin{acks}
The authors would like to thank Dr. Maura Turolla of Telecom
Italia for providing specifications about the application scenario.
\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{acmsmall-sample-bibfile}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
\received{February 2007}{March 2009}{June 2009}

% Electronic Appendix
\elecappendix

\medskip

\section{This is an example of Appendix section head}

Channel-switching time is measured as the time length it takes for
motes to successfully switch from one channel to another. This
parameter impacts the maximum network throughput, because motes
cannot receive or send any packet during this period of time, and it
also affects the efficiency of toggle snooping in MMSN, where motes
need to sense through channels rapidly.

By repeating experiments 100 times, we get the average
channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
the same experiments with different Micaz motes, as well as
experiments with the transmitter switching from Channel 11 to other
channels. In both scenarios, the channel-switching time does not have
obvious changes. (In our experiments, all values are in the range of
23.6 $\mu$s to 24.9 $\mu$s.)

\section{Appendix section head}

The primary consumer of energy in WSNs is idle listening. The key to
reduce idle listening is executing low duty-cycle on nodes. Two
primary approaches are considered in controlling duty-cycles in the
MAC layer.

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2015-09-26 Docs/TODAES/paper.tex
including references and adjusting table of results

@@
 \usepackage[skip=\baselineskip]{caption}
-\captionsetup[lstlisting]{font={small,tt}}
+\captionsetup[lstlisting]{font={normalsize,tt}}
 
@@
   \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
-
- &  & \textbf{CRC32} & \textbf{Patricia} & \textbf{Dijkstra} & \textbf{Clustering} & \textbf{RC6} & \textbf{Fuzzy} & \textbf{Mars} \\[0.15cm]
+\\
+ &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
 \cmidrule(r){3-9}
 
-&\textbf{Nodes} &25 &21 &26 &150 &329 &261 &417\\
-&\textbf{Edges} &32 &48 &69 &331 &448 &442 &600\\
-&\textbf{S0} &20 &10 &20 &50 &600 &4578 &300\\
+&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
+&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
+&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\
 
@@
 
-\multirow{2}{*}{\textbf{Exact Solution}}
-&  Hp   &  15   &  47   &  31   &  241   &  692    &  13820   &  876 \\
-&  Sp   &  19   &  4   &  19   &  46   &  533    &  4231   &  297  \\
+\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
+& & & & & & & & & \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
+&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
+& & & & & & & & & \\
 
@@
 %ILP
-\multirow{2}{*}{\textbf{ILP}}  
-&  T(s)   &  2   &  1   &  2   &  649   &  1806    &  TO   &  5.42  \\
-&  Hp   &  15   &  47   &  31   &  241   &  692    &  -   &  876  \\
+\multirow{4}{*}{\textbf{\normalsize{ILP}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{2}   &  \normalsize{1}  &  \normalsize{2}   &  \normalsize{649}   &  \normalsize{1806}    &  \normalsize{TO}   &  \normalsize{5.42}  \\
+&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  \normalsize{876}  \\
+& & & & & & & & & \\
 \hline
@@
 %GA
-\multirow{2}{*}{\textbf{GA}}
-&  T(s)   &  7   &  7   &  9   &  340   &  2050    &  1.37   &  5000  \\
-&  Error \%   &  13.3   &  0   &  29   &  1.7   &  -6.5    &  -37.6   &  -27.5  \\
+\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{7}   &  \normalsize{7}   &  \normalsize{9}   &  \normalsize{340}   &  \normalsize{2050}    &  \normalsize{1.37}   &  \normalsize{5000}  \\
+&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0}   &  \normalsize{29}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  \normalsize{-27.5}  \\
+& & & & & & & & & \\
 \hline
@@
 %ESBMC
-\multirow{2}{*}{\textbf{ESBMC}}
-&  T(s)   &  31   &  362   &  292   &  3010   &  TO    &  MO   &  MO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{ 31}   &  \normalsize{362}   &  \normalsize{292}   &  \normalsize{3010}   & \normalsize{ TO}    &  \normalsize{MO}   &  \normalsize{MO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
 \hline
@@
 %MultiCore ESBMC
-\multirow{2}{*}{\textbf{ESBMC-SS}}
-&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{ 2 }  &  \normalsize{6}   &  \normalsize{7 }  &  \normalsize{1615}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
+& & & & & & & & & \\
 \hline
@@
 %ESBMC Parallel sequential
-\multirow{2}{*}{\textbf{ESBMC-PS}}
-&  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
+\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)} &  \normalsize{4} &  \normalsize{10}   &  \normalsize{11}   &  \normalsize{2238}   &  \normalsize{TO}    &  \normalsize{MO}   &  \normalsize{MO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
 \hline
@@
 %ESBMC Parallel Binary
-\multirow{2}{*}{\textbf{ESBMC-PB}}
-&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
-&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{6}   & \normalsize{ 5}   &  \normalsize{6}   &  \normalsize{207}   &  \normalsize{TO}    & \normalsize{MO}   & \normalsize{MO} \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
 \hline
@@
 %vZ
-\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
-&  T(s)   &  0.3   &  0.3   &  0.7   &  86.4   &  TO    &  TO   &  TO  \\
-&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
 
@@
 % Bibliography
-%\bibliographystyle{ACM-Reference-Format-Journals}
-%\providecommand{\natexlab}[1]{#1}
-%\providecommand{\url}[1]{{#1}}
-%\providecommand{\urlprefix}{URL }
-%\expandafter\ifx\csname urlstyle\endcsname\relax
-%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-%  \urlstyle{rm}\Url}\fi
-%\providecommand{\eprint}[2][]{\url{#2}}
+\begin{thebibliography}{5}
+
+\providecommand{\natexlab}[1]{#1}
+\providecommand{\url}[1]{{#1}}
+\providecommand{\urlprefix}{URL }
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+\providecommand{\eprint}[2][]{\url{#2}}
+\bibliographystyle{ACM-Reference-Format-Journals}
 
 %1
-%\bibitem{Arato2003}
-%Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
-(2003), ``{Hardware/software partitioning in embedded system %design},'' In: Proc.
+\bibitem{Arato2003}
+Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
+(2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc.
 of the Intl.
@@
 %2
-%\bibitem{Mann2007}
-%Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System %Design, v. 31, n. 3 pp. 241--263.
+\bibitem{Mann2007}
+Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.
 
 %3
-%\bibitem{Trindade2015}
-%Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded %systems,}'' In: Design Automation for Embedded Systems (to appear).
+\bibitem{Trindade2015}
+Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).
 
 %4
-%\bibitem{Trindade2016}
-%Trindade, A.
+\bibitem{Trindade2016}
+Trindade, A.
 B., Ismail, H.
@@
 C.
-(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in %Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
+(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
 1-4.
@@
 %5
-%\bibitem{Bjorner2015}
-%Bjorner, N., Phan, A-D., Fleckenstein, L.
+\bibitem{Bjorner2015}
+Bjorner, N., Phan, A-D., Fleckenstein, L.
 (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
@@
 Conf.
-on %Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
+on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
 194--199.
@@
 %6
-%\bibitem{Tang2009}
-%Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. %on Computer Science Education},'' pp. 1900--1905.
+\bibitem{Tang2009}
+Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.
 
 %7
-%\bibitem{OpenMP1998}
-%OpenMP Architecture Review Board, OpenMP C and C++
-%Application Pogram Interface, Version 1.0, October 1998.
-%http://www.openmp.org%
+\bibitem{OpenMP1998}
+OpenMP Architecture Review Board, OpenMP C and C++
+Application Pogram Interface, Version 1.0, October 1998.
+http://www.openmp.org%
 
 %8
-%\bibitem{Cordeiro2012}
-%Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: %IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
+\bibitem{Cordeiro2012}
+Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
 
 %9
-%\bibitem{Rao2009}
-%Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
+\bibitem{Rao2009}
+Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
 
 %10
-%\bibitem{Biere2009}
-%Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of %Satisfiability, IOS Press, pp. 457–-481.
+\bibitem{Biere2009}
+Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
 
 %11
-%\bibitem{Armando2009}
-%Armando, A., Mantovani, J., Platania, L.
-(2009), ``{Bounded model checking of software using SMT solvers instead of SAT %solvers},'' In: Intl.
+\bibitem{Armando2009}
+Armando, A., Mantovani, J., Platania, L.
+(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl.
 Journal on Software Tools for Technology Transfer, v.
@@
 %12
-%\bibitem{Ganai2006}
-%Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on %Computer-Aided Design, pp. 794-–801.
+\bibitem{Ganai2006}
+Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.
 
 %13
-%\bibitem{Ramalho2013}
-%Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
-(2013), ``{SMT-Based Bounded Model Checking of C++ %Programs.},'' In: Intl.
+\bibitem{Ramalho2013}
+Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
+(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl.
 Conf.
@@
 %14
-%\bibitem{DeMoura2008}
-%De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for %the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
+\bibitem{DeMoura2008}
+De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
 
 %15
-%\bibitem{Brummayer2009}
-%Brummayer, R., Biere, A.
+\bibitem{Brummayer2009}
+Brummayer, R., Biere, A.
 (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc.
 of the Intl.
-%Conf.
+Conf.
 on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp.
@@
 %16
-%\bibitem{Barrett2011}
-%Barrett, C., Conway, C.
+\bibitem{Barrett2011}
+Barrett, C., Conway, C.
 Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C.
-(2011), ``{CVC4},'' In: %Proc.
+(2011), ``{CVC4},'' In: Proc.
 of the Intl.
@@
 %17
-%\bibitem{Bozzano2005}
-%Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
-(2005), ``{MathSAT: Tight %integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
+\bibitem{Bozzano2005}
+Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
+(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
 35, n.
@@
 %18
-%\bibitem{Dutertre2014}
-%Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
+\bibitem{Dutertre2014}
+Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
 
 %19
-%\bibitem{Wu2014}
-%Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-(2014), ``{Research on OpenMP model of the parallel programming %technology for homogeneous multicore DSP},'' In: Proc.
+\bibitem{Wu2014}
+Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
+(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
 of the Intl.
@@
 on Software Engineering and Service Science, pp.
-%921--924.
+921--924.
 
 %20
-%\bibitem{Bjorner2014}
-%Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic %Computation in Software Science, pp. 1--10.
+\bibitem{Bjorner2014}
+Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
 
 %21
-%\bibitem{Federica2008}
-%Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
-(2008), {``Authorization and User Failure Resiliency for WS-BPEL business %processes''}, In: Proc.
+\bibitem{Federica2008}
+Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
+(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
 of the Intl.
@@
 %22
-%\bibitem{NarodytskaN}
-%Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI %Conf. on Artificial Intelligence, pp. 2717--2723.
+\bibitem{NarodytskaN}
+Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
 
 %23
-%\bibitem{Barth1995}
-%Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
-%Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
+\bibitem{Barth1995}
+Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
+Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
 
 %24
-%\bibitem{Vasco2005}
-%Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, %Technical University of Lisbon, Portugal.
+\bibitem{Vasco2005}
+Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
 
 %25
-%\bibitem{Z3API}
-%Magellan, ``{Source code and documentation},''
-%  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
+\bibitem{Z3API}
+Magellan, ``{Source code and documentation},''
+  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
 
 %26
-%\bibitem{Cormem}
-%Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
+\bibitem{Cormem}
+Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
 
 %27
-%\bibitem{Dagum1998}
-%Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
+\bibitem{Dagum1998}
+Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
 
 %28
-%\bibitem{TheMathWorks2013}
-%The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
+\bibitem{TheMathWorks2013}
+The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
 
 %29
-%\bibitem{Tranquillo2011}
-%Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
+\bibitem{Tranquillo2011}
+Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
 
 %30
-%\bibitem{Hong2010}
-%Hong, L., Cai, J.
+\bibitem{Hong2010}
+Hong, L., Cai, J.
 (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
@@
 %31
-%\bibitem{Cordeiro2011}
-%Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
+\bibitem{Cordeiro2011}
+Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
 
 %32
-%\bibitem{Teich2012}
-%Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
+\bibitem{Teich2012}
+Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
 
 %33
-%\bibitem{Guthaus2001}
-%Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
+\bibitem{Guthaus2001}
+Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
 (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
@@
 %34
-%\bibitem{Arato2005}
-%Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
+\bibitem{Arato2005}
+Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
 
 %35
-%\bibitem{Holzmann2011}
-%Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
+\bibitem{Holzmann2011}
+Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
 
 %36
-%\bibitem{Holzmann2012}
-%Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
+\bibitem{Holzmann2012}
+Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
 
 %37
-%\bibitem{Wintersteiger2009}
-%Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
+\bibitem{Wintersteiger2009}
+Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
 
 %38
-%\bibitem{Qawasmeh2014}
-%Qawasmeh, A., Malik, A., Chapman, B.
+\bibitem{Qawasmeh2014}
+Qawasmeh, A., Malik, A., Chapman, B.
 (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc.
@@
 %39
-%\bibitem{Pavlinovic2015}
-%Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
+\bibitem{Pavlinovic2015}
+Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
 
 %40
-%\bibitem{Patrick2015}
-%Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
+\bibitem{Patrick2015}
+Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
 
 %41
-%\bibitem{Holzmann11}
-%Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
-
-%\end{thebibliography}
+\bibitem{Holzmann11}
+Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
+
+\end{thebibliography}
 
@@
 % Acknowledgments
-\begin{acks}
-The authors would like to thank Dr. Maura Turolla of Telecom
-Italia for providing specifications about the application scenario.
-\end{acks}
-
+%\begin{acks}
+%The authors would like to thank Dr. Maura Turolla of Telecom
+%Italia for providing specifications about the application scenario.
+%\end{acks}
+
+% Bibliography
 % Bibliography
@@
 
-\medskip
-
-\section{This is an example of Appendix section head}
-
-Channel-switching time is measured as the time length it takes for
-motes to successfully switch from one channel to another. This
-parameter impacts the maximum network throughput, because motes
-cannot receive or send any packet during this period of time, and it
-also affects the efficiency of toggle snooping in MMSN, where motes
-need to sense through channels rapidly.
-
-By repeating experiments 100 times, we get the average
-channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
-the same experiments with different Micaz motes, as well as
-experiments with the transmitter switching from Channel 11 to other
-channels. In both scenarios, the channel-switching time does not have
-obvious changes. (In our experiments, all values are in the range of
-23.6 $\mu$s to 24.9 $\mu$s.)
-
-\section{Appendix section head}
-
-The primary consumer of energy in WSNs is idle listening. The key to
-reduce idle listening is executing low duty-cycle on nodes. Two
-primary approaches are considered in controlling duty-cycles in the
-MAC layer.
+%\medskip
+
+%\section{This is an example of Appendix section head}
+
+%Channel-switching time is measured as the time length it takes for
+%motes to successfully switch from one channel to another. This
+%parameter impacts the maximum network throughput, because motes
+%cannot receive or send any packet during this period of time, and it
+%also affects the efficiency of toggle snooping in MMSN, where motes
+%need to sense through channels rapidly.
+
+%By repeating experiments 100 times, we get the average
+%channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
+%the same experiments with different Micaz motes, as well as
+%experiments with the transmitter switching from Channel 11 to other
+%channels. In both scenarios, the channel-switching time does not have
+%obvious changes. (In our experiments, all values are in the range of
+%23.6 $\mu$s to 24.9 $\mu$s.)
+
+%\section{Appendix section head}
+
+%The primary consumer of energy in WSNs is idle listening. The key to
+%reduce idle listening is executing low duty-cycle on nodes. Two
+%primary approaches are considered in controlling duty-cycles in the
+%MAC layer.
 

### 2015-09-28 Docs/TODAES/paper.tex
changes in benchmarks table
add Renato as co-author
review introduction

@@
 Edilson Galv\~ao\
+\affil{Federal University of Amazonas}
+Renato Degelo\
 \affil{Federal University of Amazonas}
@@
 At early stages, the design is split into separated flows: hardware and software.
-The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology.
-If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affect the overall development process, the quality, and the lifecycle of the final system.
+The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which one in software (SW), must be supported by any well-structured methodology.
+If there is no methodology support, a number of issues, {\it e.g.}, design flow interruptions, redesigns, and undesired iterations may affect the overall development process, the quality, and the life-cycle of the final system.
 
@@
 The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3.
-All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.
+All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.
 
@@
 \small
-\sffamily\footnotesize
+\sffamily\small
 \tabulinesep=6pt
-\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
+\begin{tabular}[c]{m{1.9cm}m{0.9cm}m{0.9cm}m{9.0cm}}
+\\
 \toprule[1.5pt]
-%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
+\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
 \midrule
-
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\\
+\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\\
 \hline
+\\
 \verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
+\\
 \hline
-
+\\
 \verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
+\\
 \hline
+\\
 \verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
+\\
 \hline
+\\
 \verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
+\\
 \hline
+\\
 \verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
+\\
 \hline
+\\
 \verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
-
+\\
 \bottomrule[1.5pt]

### 2015-09-28 Docs/TODAES/paper.tex
review Section 2

@@
 
-\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax
 
@@
 \begin{document}
+
+\lstset{language=C,basicstyle=\small}
+\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
+\lstset{tabsize=2}
+\lstset{firstnumber=1}
+\lstset{frame=single}
+\lstset{
+  language={C},
+  morekeywords={assert,uchar}
+}
 
@@
 Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}. 
-
 %In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
@@
 Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
-
 There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}.
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-Alternatively, tools such as $\nu$Z and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found.
-The following sections describe the main features of $\nu$Z and ESBMC tools.
+Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found.
+The following sections describe the main features of ESBMC and $\nu$Z tools.
 
@@
 
-%Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}.
-These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry.
-However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}.
-Much research has been devoted to mitigate this problem.
-
 Among the recent model checking techniques, there is one that combines model checking with satisﬁability solving.
 This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem~\cite{Clarke2001}.
 
@@
 In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
-%According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems.
-In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers.
-In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2016}, it was shown that it is possible to use ESBMC also as an optimization tool.}
-In particular, there are two directives in ESBMC that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT.
+In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT.
 The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost).
@@
 GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
-The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver).
+
+The main factor for ESBMC to use only a single-core relies on its back-end ({\it i.e.}, SMT Solver).
 Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}.
@@
 	\centering
-  \includegraphics[scale=1.25]{figures/esbmc-arch-new.pdf} 
+  \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
 	\caption{ESBMC Architecture.}
@@
 
-The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages.
+The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages~\cite{OpenMP1998}.
 OpenMP supports most processor architectures and operating systems, {\it e.g.}, Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
-OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.
-
-In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}.
+OpenMP uses a portable and very robust model to facilitate the development of parallel applications for a variety of platforms.
+
+In particular, OpenMP uses the \textit{fork-join} model of parallel execution~\cite{OpenMP1998}.
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
@@
 
-\begin{lstlisting}[caption="OpenMP basic sample."]
-
-01.  int i;
-02.  #pragma omp parallel for
-03.  for (i = 0; i < 10; i++)
-04.      a[i] = 2 * i;
+\begin{lstlisting}[caption=OpenMP basic example.]
+int i;
+#pragma omp parallel for
+for (i = 0; i < 10; i++)
+  a[i] = 2 * i;
 \end{lstlisting}
@@
 There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time.
-To create a critical region, the ``\#pragma omp critical'' directive is used.
+To create a critical region, the ``\#pragma omp critical'' directive is routinely used.
 
@@
 
-As an example, one can optimize $\left(K + W\right)$, with restrictions in $\left(K < 2\right)$ and $\left(W - K < 1\right)$.
+As an example, one can optimize $\left(K + W\right)$, which is subject to restrictions in $\left(K < 2\right)$ and $\left(W - K < 1\right)$.
 The expected result of this optimization problem described in the code below is $2$.
@@
 \begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
-
-1. (declare-const K Int) 
-2. (declare-const W Int)
-3. (assert (< K 2)) 
-4. (assert (< (- W K) 1))
-5. (maximize (+ K W)) 
-6. (check-sat)
+(declare-const K Int) 
+(declare-const W Int)
+(assert (< K 2)) 
+(assert (< (- W K) 1))
+(maximize (+ K W)) 
+(check-sat)
 \end{lstlisting}
@@
 \begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
-
-01. Initialize Variables 
-02. Declare number of nodes and edges
-03. Declare hardware cost of each node as array (h)
-04. Declare software cost of each node as array (s)
-05. Declare communication cost of each edge (c)
-06. Declare the initial software cost of ($S_{0}$)
-07. Declare transposed incidence matrix graph G (E)
-08. Define the solutions variable ($X_{i}$ ) as Boolean
-09. main {
-10.  for TipH = 0 to Hmax do {
-11.   populate $X_{i}$ with nondeterministic/test values
-12.   Calculate s(1-x)+c|$E_{x}$| and store at variable
-13.   Requirement isued by Assume (Variable <= $S_{0}$)
-14.   Calculate Hp cost Based on value tested of $X_{i}$
-15.   Violation check with Assert($H_{p}$ > TipH)
-16.  }
-17. }
+ Initialize Variables 
+ Declare number of nodes and edges
+ Declare hardware cost of each node as array (h)
+ Declare software cost of each node as array (s)
+ Declare communication cost of each edge (c)
+ Declare the initial software cost of ($S_{0}$)
+ Declare transposed incidence matrix graph G (E)
+ Define the solutions variable ($X_{i}$ ) as Boolean
+ main {
+  for TipH = 0 to Hmax do {
+   populate $X_{i}$ with nondeterministic/test values
+   Calculate s(1-x)+c|$E_{x}$| and store at variable
+   Requirement isued by Assume (Variable <= $S_{0}$)
+   Calculate Hp cost Based on value tested of $X_{i}$
+   Violation check with Assert($H_{p}$ > TipH)
+  }
+ }
 \end{lstlisting}
@@
 	\centering
-  \includegraphics[scale=1.0]{figures/esbmc-ss.pdf} 
+  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
 	\caption{ESBMC-SS Approach.}
@@
 	\centering
-  \includegraphics[scale=1.0]{figures/esbmc-ps.pdf} 
+  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
 	\caption{ESBMC-PS Approach. }
@@
 	\centering
-  \includegraphics[scale=1.0]{figures/esbmc-pb.pdf} 
+  \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
 	\caption{ESBMC-PB Approach.}
@@
 \begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
-
-01. GetNextStep(){
-02.  int largestChunk = -1;
-03.  chunk largest;
-04.  for each(chunk in chunks){
-05.     if(chunk.right - chunk.left > largestChunk){
-06.           largestChunk = chunk.right - chunk.left;
-07.           largest = chunk;
-08.     }
-09.   }	
-10.   chunks.remove(largest);	
-11.   int median = largest.left + floor((largest.right - largest.left) / 2)
-12.   if(median > 0){
-13.      if(largest.right - largest.left > 1)
-14.         chunks.add(new chunk(largest.left, median - 1));	
-15.      if(largest.right != largest.left)
-16.         chunks.add(new chunk(median + 1, largest.right);
-17.    }
-18.   return median;
-19. }
+ GetNextStep(){
+  int largestChunk = -1;
+  chunk largest;
+  for each(chunk in chunks){
+     if(chunk.right - chunk.left > largestChunk){
+           largestChunk = chunk.right - chunk.left;
+           largest = chunk;
+     }
+   }	
+   chunks.remove(largest);	
+   int median = largest.left + floor((largest.right - largest.left) / 2)
+   if(median > 0){
+      if(largest.right - largest.left > 1)
+         chunks.add(new chunk(largest.left, median - 1));	
+      if(largest.right != largest.left)
+         chunks.add(new chunk(median + 1, largest.right);
+    }
+   return median;
+ }
 \end{lstlisting}
@@
 \begin{lstlisting}[caption=Worker sample.,label=worker-sample]
-
-01. step = controller.GetNextStep();
-02. int pid = ExecuteStep(step);
-03. while(isRunning(pid)){
-04.   if(!controller.isNeeded(step))
-05.    kill(pid);
-06. }     
+ step = controller.GetNextStep();
+ int pid = ExecuteStep(step);
+ while(isRunning(pid)){
+   if(!controller.isNeeded(step))
+    kill(pid);
+ }     
 \end{lstlisting}
@@
 \begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
-
-01.#Initialize Variables
-02.  Create vZ context 
-03.  Create binary vector (x)
-04.  Declare number of nodes, edges and $S_{0}$
-05.  Declare hardware cost of each node as array (h) 
-06.  Declare software cost of each node as array (s)
-07.  Declare communication cost of each edge (c)
-08.  Declare transposed incidence matrix graph G (E)
-09.#Arithmetic Expressions
-10.  SC = s(1-x)
-11.  CMC = c*|EX|
-12.  Fobj =  x[i] * h[i]
-13.#Assert Constraints
-14.  Add constraints (SF + CMC <= $S_{0}$)
-15.  Add constraints to minimize Fobj
-16.  Check Model
-17.  Print Result
+#Initialize Variables
+  Create vZ context 
+  Create binary vector (x)
+  Declare number of nodes, edges and $S_{0}$
+  Declare hardware cost of each node as array (h) 
+  Declare software cost of each node as array (s)
+  Declare communication cost of each edge (c)
+  Declare transposed incidence matrix graph G (E)
+#Arithmetic Expressions
+  SC = s(1-x)
+  CMC = c*|EX|
+  Fobj =  x[i] * h[i]
+#Assert Constraints
+  Add constraints (SF + CMC <= $S_{0}$)
+  Add constraints to minimize Fobj
+  Check Model
+  Print Result
 \end{lstlisting}
@@
 %11
+\bibitem{Clarke2001}
+E. M. Clarke, A. Biere, R. Raimi, Y. Zhu (2001), ``{Bounded model checking using satisfiability solving}'', Formal Methods in System Design v. 19 n. 1, pp. 7--34.
+
+%12
 \bibitem{Armando2009}
@@
 
-%12
+%13
 \bibitem{Ganai2006}
@@
 
-%13
+%14
 \bibitem{Ramalho2013}
@@
 
-%14
+%15
 \bibitem{DeMoura2008}
@@
 
-%15
+%16
 \bibitem{Brummayer2009}
@@
 
-%16
+%17
 \bibitem{Barrett2011}
@@
 
-%17
+%18
 \bibitem{Bozzano2005}
@@
 
-%18
+%19
 \bibitem{Dutertre2014}
@@
 
-%19
+%20
 \bibitem{Wu2014}
@@
 
-%20
+%21
 \bibitem{Bjorner2014}
@@
 
-%21
+%22
 \bibitem{Federica2008}
@@
 
-%22
+%23
 \bibitem{NarodytskaN}
@@
 
-%23
+%24
 \bibitem{Barth1995}
@@
 
-%24
+%25
 \bibitem{Vasco2005}
@@
 
-%25
+%26
 \bibitem{Z3API}
@@
 
-%26
+%27
 \bibitem{Cormem}
@@
 
-%27
+%28
 \bibitem{Dagum1998}
@@
 
-%28
+%29
 \bibitem{TheMathWorks2013}
@@
 
-%29
+%30
 \bibitem{Tranquillo2011}
@@
 
-%30
+%31
 \bibitem{Hong2010}
@@
 
-%31
+%32
 \bibitem{Cordeiro2011}
@@
 
-%32
+%33
 \bibitem{Teich2012}
@@
 
-%33
+%34
 \bibitem{Guthaus2001}
@@
 
-%34
+%35
 \bibitem{Arato2005}
@@
 
-%35
+%36
 \bibitem{Holzmann2011}
@@
 
-%36
+%37
 \bibitem{Holzmann2012}
@@
 
-%37
+%38
 \bibitem{Wintersteiger2009}
@@
 
-%38
+%39
 \bibitem{Qawasmeh2014}
@@
 
-%39
+%40
 \bibitem{Pavlinovic2015}
@@
 
-%40
+%41
 \bibitem{Patrick2015}
@@
 
-%41
+%42
 \bibitem{Holzmann11}

### 2015-09-28 Docs/TODAES/paper.tex
review section 3

@@
 The informal model can be described by five characteristics.
-First, there is only one software context, i.e., there is just one general-purpose processor, and there is only one hardware context.
+First, there is only one software context, {\it i.e.}, there is just one general-purpose processor, and there is only one hardware context.
 The components of the system must be mapped to either one of these two contexts.
@@
 Three different optimization and decision problems can be defined.
-In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints).
+In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints.
 Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
@@
 
-%\comment{
-%----------------------------------------------
-%\section{Partitioning problem using ILP-based,Genetic Algorithms}
-%\label{ILPGA}
-%----------------------------------------------
-
-%The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
-Both use slack variables in order to be %possible to represent constraints and to use commercial tools.
-However, GA had improvements from the parameters of related %studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and %resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the %population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of %generations changed from $100*NumberOfVariables$ (default) to $75$.
-%}
-
-%----------------------------------------------
-\section{Analysis of the partitioning problem using ESBMC}
+%----------------------------------------------
+\section{Analysis of the partitioning problem}
 \label{Analysis-of-the-partitioning-problem-using-ESBMC}
@@
 As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
-This section describes the verification algorithm using sequential ESBMC, followed by three multi-core model checking algorithms and the integration of the MaxSMT solver $\nu$Z, in order to speed up the HW-SW partitioning verification.
+This section describes the verification algorithm using sequential ESBMC, followed by three multi-core model checking algorithms and the integration of the MaxSMT solver $\nu$Z into ESBMC, in order to speed up the HW-SW partitioning verification.
+HW-SW partitioning using ILP-based and Genetic Algorithms are also explained.
+
+%----------------------------------------------
+\subsection{Partitioning problem using ILP-based,Genetic Algorithms}
+\label{ILPGA}
+%----------------------------------------------
+
+The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
+Both use slack variables in order to be possible to represent constraints and to use commercial tools.
+However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
 
@@
 Those values that change for each test will generate a possible solution and obey the constraints.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of constrains (i.e., $A.x \leq b$).
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (i.e., $A.x \leq b$).
 
@@
 
-To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC.
-Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
+To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC.
+Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
 
@@
 All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}.
-Note that there is no shared-memory (or message-passing) mechanism among the threads.
-In particular, different threads are managed by the OpenMP API, which is responsible for the thread lifecycle: start, running, and dead states, using different values as condition.
-After executing $N$ instances, if there is no code violation, then multi-core ESBMC starts new instances again.
+Note that there is no shared-memory (or message-passing) mechanism among threads.
+In particular, different threads are managed by the OpenMP API, which is responsible for the thread life-cycle: start, running, and dead states, using different values as condition.
+After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment.
 During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time.
@@
 
-The previous parallelization is implemented by continuously forking ESBMC instances until the first violation is found.
+The previous parallelization is implemented by continuously forking ESBMC instances in a sequential manner until the first violation is found.
 However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some period of time.
@@
 
-The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution.
+The most optimized approach applies a parallelized binary-search to reduce the amount of steps to be executed in order to find the optimal solution.
 A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced.
@@
 As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$.
-When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$).
+When the next available core requests a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$).
 The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
@@
 
-Note that there might gaps between steps, which are produced by the customized binary search.
+Note that there might gaps between steps, which are produced by the customized binary-search.
 For instance, in the example shown in Fig.~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well.
@@
 From lines $4$ to $9$, the algorithm finds the largest interval.
-Then, from the line $10$ the largest interval is removed and the median is calculated in line $11$.
+Then, from line $10$ the largest interval is removed and the median is calculated in line $11$.
 After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$).

### 2015-09-28 Docs/TODAES/paper.tex
final reviews

@@
 \textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to $\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to $\nu$Z that \textit{Fobj} should be minimized.
-Finally, the model is checked by $\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
-\begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
+To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
+Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
+
+\begin{lstlisting}[caption=Pseudocode describing ESBMC-$\nu$Z.,label=vZ-pseudocode, mathescape]
 #Initialize Variables
@@
 The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
-Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, Multi-Core ESBMC, and MaxSMT $\nu$Z~\cite{Bjorner2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
+Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
 
@@
 Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
+ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
 For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}.
 MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
-ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
 
@@
 Each time was measured $3$ times (average taken).
-Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP.
+\textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP}.
 A time out condition (TO) is reached when the verification time is longer than $7200$ seconds.

### 2015-09-29 Source/ESBMCParallel/Release/Benchmarks/mainESBMC2modPATRICIA_parallel.c
Added ESBMC Parallel source code

@@ -1,0 +1,109 @@
+//#include <math.h>
+// Patricia Insert com módulo execucao paralela com OpenMP
+#define MAXn 21 //máximo número de nodes
+#define MAXe 48 //máximo número de edges (arestas)
+
+_Bool nondet_bool();
+int nondet_int();
+int tmp[MAXe];
+int h [MAXn] = {3,1,2,3,3,3,0,3,3,2,1,1,2,3,1,14,2,1,3,3,2};
+
+int faux (void) {
+  int i, j, k, aux=0, softcost=0, comcost=0;
+  _Bool x[MAXn]; 
+
+int s [MAXn] = {1,1,1,1,1,1,1,1,1,1,1,1,1,1,5,5,1,1,1,1,1};
+int c [MAXe] = {22,21,12,20,3,15,28,26,30,27,8,26,2,24,28,16,2,5,17,29,10,21,22,18,15,10,16,27,13,27,5,14,9,27,18,20,8,3,28,18,0,25,22,8,8,8,13,12};
+int E [MAXe] [MAXn] = {{-1.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
+{-1.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
+{-1.0, 0.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
[…]

### 2015-09-29 Source/ESBMCParallel/src/ESBMCParallel.cpp

@@ -1,0 +1,466 @@
+/*
+ #
+ # ESBMC - Parallel Runner
+ #
+ #               Universidade Federal do Amazonas - UFAM
+ # Author:       Hussama Ismail <hussamaismail@gmail.com>
+ #
+ # ------------------------------------------------------
+ #
+ # Execute many esbmc instances using OpenMP Library
+ #
+ # Usage Example:
+ # $ ./esbmc-parallel filename hmax
+ #
+ # ------------------------------------------------------
+ #
+ */
+
+#include <iostream>
+#include <omp.h>
+#include <string>
+#include <string.h>
+#include <stdio.h>
+#include <ctime>
+#include <vector>
+#include <time.h>
+#include <cstdlib>
+
+#include <sys/types.h>
+#include <sys/wait.h>
+#include <unistd.h>
+#include <signal.h>
+#include <sstream>
+#include <algorithm>
+#include <fcntl.h>
+#include <poll.h>
+
+#include "ParallelController.h"
+
+#define READ 0
+#define WRITE 1
+
+enum Order { ASC, DESC };
+
+std::time_t start;
+std::string executable = "./esbmc";
+std::string filename;
+std::string esbmc_parameters = "--boolector --quiet";
+
+pid_t popen2(const char *command, int *infp, int *outfp) {
+	int p_stdin[2], p_stdout[2];
+	pid_t pid;
+
+	if (pipe(p_stdin) != 0 || pipe(p_stdout) != 0)
+		return -1;
+
+	pid = fork();
+
+	if (pid < 0)
+		return pid;
+	else if (pid == 0) {
+		setpgid(0, 0);
+
+		dup2(p_stdin[READ], STDIN_FILENO);
+		dup2(p_stdout[WRITE], STDOUT_FILENO);
+
+		//close unuse descriptors on child process.
+		close(p_stdin[READ]);
+		close(p_stdin[WRITE]);
+		close(p_stdout[READ]);
+		close(p_stdout[WRITE]);
+
+		//can change to any exec* function family.
+		execl("/bin/bash", "bash", "-c", command, NULL);
+		perror("execl");
+		exit(1);
+	}
+
+	// close unused descriptors on parent process.
+	close(p_stdin[READ]);
+	close(p_stdout[WRITE]);
+
+	if (infp == NULL)
+		close(p_stdin[WRITE]);
+	else
+		*infp = p_stdin[WRITE];
+
[…]

### 2015-09-29 Source/ESBMCParallel/src/ParallelController.cpp

@@ -1,0 +1,81 @@
+/*
+ * ParallelController.cpp
+ *
+ *  Created on: Jul 7, 2015
+ *      Author: rdegelo
+ */
+
+#include "ParallelController.h"
+#include <cmath>
+#include <algorithm>
+#include <iostream>
+#include <set>
+
+ParallelController::ParallelController(int hmin, int hmax) {
+	this->hmin = hmin;
+	this->hmax = hmax;
+
+	chunks.push_back(std::make_pair(hmin, hmax));
+}
+
+ParallelController::~ParallelController() {
+
+}
+
+int ParallelController::getNextStep() {
+	int largestChunk = -1;
+	std::pair<int, int> largestChunkPair;
+
+	for(auto &c : chunks) {
+	    if(c.second -c.first > largestChunk) {
+	    	largestChunkPair = c;
+	    	largestChunk = c.second -c.first;
+	    }
+	}
+
+	chunks.erase(std::remove(chunks.begin(), chunks.end(), largestChunkPair), chunks.end());
+
+	int median = largestChunkPair.first + floor((largestChunkPair.second - largestChunkPair.first) / 2.0);
+	if(median > 0) {
+		if(largestChunkPair.second - largestChunkPair.first > 1)
+			chunks.push_back(std::make_pair(largestChunkPair.first, median - 1));
+
+		if(largestChunkPair.second != largestChunkPair.first)
+			chunks.push_back(std::make_pair(median + 1, largestChunkPair.second));
+	}
+
+	return median;
+}
+
+bool ParallelController::isStepNeeded(int threadNum) {
+	//std::cout << "isStepNeededRequested" << std::endl;
+
+	return threadNum >= hmin && threadNum <= hmax;
+}
+
+void ParallelController::setStepResult(int threadNum, bool result) {
+	if(isStepNeeded(threadNum)) {
+		if(result == true && hmin < threadNum) {
+			hmin = threadNum;
+		} else if(hmax > threadNum) {
+			hmax = threadNum;
+		}
+
+		std::vector<std::pair<int, int>> toErase;
+
+		for(auto& c : chunks) {
+			if(c.first > hmax) {
+				toErase.push_back(c);
+			} else if(c.second < hmin) {
+				toErase.push_back(c);
+			} else {
+				c.first = std::max(hmin, c.first);
+				c.second = std::min(hmax, c.second);
+			}
+		}
+
+		for(auto &c : toErase) {
[…]

### 2015-09-29 Source/ESBMCParallel/src/ParallelController.h

@@ -1,0 +1,28 @@
+/*
+ * ParallelController.h
+ *
+ *  Created on: Jul 7, 2015
+ *      Author: rdegelo
+ */
+
+#ifndef PARALLELCONTROLLER_H_
+#define PARALLELCONTROLLER_H_
+
+#include <vector>
+
+
+class ParallelController {
+public:
+	ParallelController(int hmin, int hmax);
+	virtual ~ParallelController();
+
+	int getNextStep();
+	void setStepResult(int threadNum, bool result);
+	bool isStepNeeded(int threadNum);
+private:
+	int hmin;
+	int hmax;
+	std::vector<std::pair<int, int>> chunks;
+};
+
+#endif /* PARALLELCONTROLLER_H_ */

### 2015-10-01 Docs/TODAES/paper.tex
minor changes

@@
 
-\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
+\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
 
@@
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
-GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
+GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
 
@@
   \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
-	\caption{ESBMC Architecture.}
+	\caption{ESBMC architecture.}
 	\label{ESBMC-Architecture}
@@
 
-The most basic directive of OpenMP is the ``\#pragma omp parallel for'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:
+The most basic directive of OpenMP is the ``\textit{\#pragma omp parallel for}'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:
 
@@
 There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time.
-To create a critical region, the ``\#pragma omp critical'' directive is routinely used.
+To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.
 
@@
   \includegraphics[scale=0.3]{figures/vzArch.png} 
-	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
+	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
 	\label{vZ-Architecture}
@@
 In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints.
-Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
+Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
 
@@
 Those values that change for each test will generate a possible solution and obey the constraints.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (i.e., $A.x \leq b$).
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).
 
@@
   \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
-	\caption{ESBMC-SS Approach.}
+	\caption{ESBMC-SS approach.}
 	\label{ESBMC-Multi-core}
@@
 
-ESBMC-SS obtains the problem specification represented by a C program.
+ESBMC-SS obtains the problem specification represented by a ANSI-C program.
 The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
@@
   \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
-	\caption{ESBMC-PS Approach. }
+	\caption{ESBMC-PS approach.}
 	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
@@
   \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
-	\caption{ESBMC-PB Approach.}
+	\caption{ESBMC-PB approach.}
 	\label{ESBMC-Binary-Approach}
@@
   \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
-	\caption{Binary Step Calculation.}
+	\caption{Binary step calculation.}
 	\label{Binary-Step-Calculation}
@@
 
-\begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
+\begin{lstlisting}[caption=Steps calculation using intervals.,label=Steps-Calculation-using-Intervals]
  GetNextStep(){

### 2015-10-01 Docs/TODAES/paper.tex
add CCS concepts

@@
 %
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>  
-%\end{CCSXML}
-
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10010583.10010682.10010684.10010686</concept_id>
+<concept_desc>Hardware~Hardware-software codesign</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10010583.10010682.10010712.10010715</concept_id>
+<concept_desc>Hardware~Software tools for EDA</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
+<concept_desc>Software and its engineering~Model checking</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998.10010999</concept_id>
+<concept_desc>Software and its engineering~Software verification</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Hardware~Hardware-software codesign}
+\ccsdesc[500]{Hardware~Software tools for EDA}
+\ccsdesc[500]{Software and its engineering~Model checking}
+\ccsdesc[500]{Software and its engineering~Software verification}
 

### 2015-10-17 Docs/TODAES/paper.tex
Fixed References and Libraries

@@
-% v2-acmsmall-sample.tex, dated March 6 2012
-% This is a sample file for ACM small trim journals
-%
-% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
-% (c) 2010 Association for Computing Machinery (ACM)
-%
-% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
-% Users can also go through the FAQs available on the journal's submission webpage.
-%
-% Steps to compile: latex, bibtex, latex latex
-%
-% For tracking purposes => this is v1.3 - March 2012
-
-\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax
-
+\documentclass[prodmode,acmtrets]{acmsmall} % Aptara syntax
+
+\usepackage{listings} % Codes
+%\lstset{
+ % language=C,                % choose the language of the code
+ % numbers=left,                   % where to put the line-numbers
+ % stepnumber=1,                   % the step between two line-numbers.        
+ % numbersep=5pt,                  % how far the line-numbers are from the code
+ % backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
+ % showspaces=false,               % show spaces adding particular underscores
+ % showstringspaces=false,         % underline spaces within strings
+ % showtabs=false,                 % show tabs within strings adding particular underscores
+ % tabsize=2,                      % sets default tabsize to 2 spaces
+ % captionpos=b,                   % sets the caption-position to bottom
+ % breaklines=true,                % sets automatic line breaking
+ % breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
+ % title=\lstname,                 % show the filename of files included with \lstinputlisting;
+%}
+
+\usepackage{mathtools} % Serve para as equacoes
+
+%Montar os Gráficos, cores e divisões.
 \usepackage{color}
@@
 \usepackage{amsmath,array}  
-\usepackage[utf8]{inputenc} 
-\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
+\usepackage{tabularx} % in the preamble
 \usepackage{graphicx} %Imagens
-\usepackage{listings} % Codes
-\usepackage{tabularx} % in the preamble
-\usepackage{mathtools} % Serve para as equacoes
-\usepackage{cite}
+
+\usepackage{minted}
+\newcolumntype{C}[1]{>{\Centering}m{#1}}
+\renewcommand\tabularxcolumn[1]{C{#1}}
+\usepackage{tabularx,ragged2e,booktabs,caption}
+
+%\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+%\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
+
 \usepackage{hyphenat}
-\usepackage[english]{babel}
-\usepackage[skip=\baselineskip]{caption}
-\captionsetup[lstlisting]{font={normalsize,tt}}
-
 \hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
@@
 \renewcommand{\algorithmcfname}{ALGORITHM}
-
 \SetAlFnt{\small}
@@
 
+%\usepackage[skip=\baselineskip]{caption}
+%\captionsetup[lstlisting]{font={small,tt}}
+
 % Metadata Information
@@
 \acmArticle{39}
-\acmYear{2010}
+\acmYear{2015}
 \acmMonth{3}
@@
 % Copyright
-\setcopyright{rightsretained}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
 
@@
 \begin{document}
-
-\lstset{language=C,basicstyle=\small}
-\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
-\lstset{tabsize=2}
-\lstset{firstnumber=1}
-\lstset{frame=single}
-\lstset{
-  language={C},
-  morekeywords={assert,uchar}
-}
 
@@
 
-\begin{lstlisting}[caption=OpenMP basic example.]
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
 int i;
@@
 a[i] = 2 * i;
-\end{lstlisting}
+\end{minted}
+\caption{OpenMP basic Example.}
+\label{lst:example}
+\end{listing}
 
@@
 
-\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
-(declare-const K Int) 
-(declare-const W Int)
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
+(Declare-Const K Int) 
+(Declare-Const W Int)
 (assert (< K 2)) 
@@
 (check-sat)
-\end{lstlisting}
+\end{minted}
+\caption{Example of SMT formula using $\nu$Z.}
+\label{vZ}
+\end{listing}
 
@@
 
-\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
  Initialize Variables 
@@
  Declare communication cost of each edge (c)
- Declare the initial software cost of ($S_{0}$)
+ Declare the initial software cost of (S0)
  Declare transposed incidence matrix graph G (E)
- Define the solutions variable ($X_{i}$ ) as Boolean
+ Define the solutions variable (Xi) as Boolean
  main {
-  for TipH = 0 to Hmax do {
-   populate $X_{i}$ with nondeterministic/test values
-   Calculate s(1-x)+c|$E_{x}$| and store at variable
-   Requirement isued by Assume (Variable <= $S_{0}$)
-   Calculate Hp cost Based on value tested of $X_{i}$
-   Violation check with Assert($H_{p}$ > TipH)
+  For TipH = 0 to Hmax Do {
+   populate Xi with nondeterministic/test values
+   Calculate s(1-x)+c|Ex| and store at variable
+   Requirement isued by Assume (Variable <= S0)
+   Calculate Hp cost Based on value tested of Xi
+   Violation check with Assert(Hp > TipH)
   }
  }
-\end{lstlisting}
+\end{minted}
+\caption{Pseudocode describing sequential ESBMC}
+\label{Pseudocode-describing-ESBMC}
+\end{listing}
 
@@
 Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
-
-\begin{lstlisting}[caption=Steps calculation using intervals.,label=Steps-Calculation-using-Intervals]
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
   GetNextStep(){
@@
  }
-\end{lstlisting}
+\end{minted}
+\caption{Steps calculation using intervals.}
+\label{Steps-Calculation-using-Intervals}
+\end{listing}
 
@@
 
-\begin{lstlisting}[caption=Worker sample.,label=worker-sample]
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
  step = controller.GetNextStep();
@@
  }
-\end{lstlisting}
+\end{minted}
+\caption{Worker sample.}
+\label{worker-sample}
+\end{listing}
 
@@
 
-\begin{lstlisting}[caption=Pseudocode describing ESBMC-$\nu$Z.,label=vZ-pseudocode, mathescape]
-#Initialize Variables
+\begin{listing}[H]
+\begin{minted}[mathescape,
+               linenos,
+               numbersep=7pt,
+               gobble=0,
+               frame=lines,
+               framesep=2mm]{c++}
+--Initialize Variables
   Create vZ context 
   Create binary vector (x)
-  Declare number of nodes, edges and $S_{0}$
+  Declare number of nodes, edges and S0
   Declare hardware cost of each node as array (h) 
@@
   Declare transposed incidence matrix graph G (E)
-#Arithmetic Expressions
+--Arithmetic Expressions
   SC = s(1-x)
@@
   Fobj =  x[i] * h[i]
-#Assert Constraints
-  Add constraints (SF + CMC <= $S_{0}$)
+--Assert Constraints
+  Add constraints (SF + CMC <= S0)
   Add constraints to minimize Fobj
@@
   Print Result
-\end{lstlisting}
+\end{minted}
+\caption{Pseudocode describing ESBMC-$\nu$Z.}
+\label{vZ-pseudocode}
+\end{listing}
 
@@
 
-\begin{table}[h]
+\begin{minipage}{\linewidth}
 \centering
-\caption {Description of Benchmarks.}
 \small
@@
 \tabulinesep=6pt
-\begin{tabular}[c]{m{1.9cm}m{0.9cm}m{0.9cm}m{9.0cm}}
+\captionof{table}{Description of Benchmarks.} \label{tab:Description-of-Benchmarks} 
+\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
 \\
@@
 \bottomrule[1.5pt]
-\end{tabular}
-\label{Description-of-Benchmarks}
-\end{table}
+\end{tabular}\par
+\bigskip
+\end{minipage}
+
+%\begin{table}[h]
+%\centering
+%\caption {Description of Benchmarks.}
+%\small
+%\sffamily\small
+%\tabulinesep=6pt
+
+%\label{Description-of-Benchmarks}
+%\end{table}
 
@@
 
-%----------------------------------------------
-%\section{References}
-%\label{References}
-%----------------------------------------------
 %%%%%%%%%%%%%%%%%%%%%%%%%%
 % ---- Bibliography ---- %
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Bibliography
-\begin{thebibliography}{5}
-
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{{#1}}
-\providecommand{\urlprefix}{URL }
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-  \urlstyle{rm}\Url}\fi
-\providecommand{\eprint}[2][]{\url{#2}}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{ACM-Reference-Format-Journals}
-
-%1
-\bibitem{Arato2003}
-Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D.
-(2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc.
-of the Intl.
-Symp.
-of Intelligent Signal Processing, pp.
-192--202.
-
-%2
-\bibitem{Mann2007}
-Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.
-
-%3
-\bibitem{Trindade2015}
-Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).
-
-%4
-\bibitem{Trindade2016}
-Trindade, A.
-B., Ismail, H.
-I., Cordeiro, L.
-C.
-(2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp.
-1-4.
-
-%5
-\bibitem{Bjorner2015}
-Bjorner, N., Phan, A-D., Fleckenstein, L.
-(2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp.
-194--199.
-
-%6
-\bibitem{Tang2009}
-Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.
-
-%7
-\bibitem{OpenMP1998}
-OpenMP Architecture Review Board, OpenMP C and C++
-Application Pogram Interface, Version 1.0, October 1998.
-http://www.openmp.org%
-
-%8
-\bibitem{Cordeiro2012}
-Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.
-
-%9
-\bibitem{Rao2009}
-Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.
-
-%10
-\bibitem{Biere2009}
-Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.
-
-%11
-\bibitem{Clarke2001}
-E. M. Clarke, A. Biere, R. Raimi, Y. Zhu (2001), ``{Bounded model checking using satisfiability solving}'', Formal Methods in System Design v. 19 n. 1, pp. 7--34.
-
-%12
-\bibitem{Armando2009}
-Armando, A., Mantovani, J., Platania, L.
-(2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl.
-Journal on Software Tools for Technology Transfer, v.
-11, n.
-1, pp.
-69--83.
-
-%13
-\bibitem{Ganai2006}
-Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.
-
-%14
-\bibitem{Ramalho2013}
-Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L.
-(2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl.
-Conf.
-and Workshops on the Engineering of Computer-Based Systems, pp.
-147--156.
-
-%15
-\bibitem{DeMoura2008}
-De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.
-
-%16
-\bibitem{Brummayer2009}
-Brummayer, R., Biere, A.
-(2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp.
-174-–177.
-
-%17
-\bibitem{Barrett2011}
-Barrett, C., Conway, C.
-Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C.
-(2011), ``{CVC4},'' In: Proc.
-of the Intl.
-Conf.
-on Computer-Aided Verification, LNCS 6806, pp.
-171--177.
-
-%18
-\bibitem{Bozzano2005}
-Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R.
-(2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v.
-35, n.
-1-3, pp.
-265--293.
-
-%19
-\bibitem{Dutertre2014}
-Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.
-
-%20
-\bibitem{Wu2014}
-Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N.
-(2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc.
-of the Intl.
-Conf.
-on Software Engineering and Service Science, pp.
-921--924.
-
-%21
-\bibitem{Bjorner2014}
-Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.
-
-%22
-\bibitem{Federica2008}
-Federica, P., Rodolfo, F., Yuqing , S., Elisa, B.
-(2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc.
-of the Intl.
-Conf.
-on Service-Oriented Computing, LNCS 5364, pp.
-116--131
-
-%23
-\bibitem{NarodytskaN}
-Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.
-
-%24
-\bibitem{Barth1995}
-Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
-Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
-
-%25
-\bibitem{Vasco2005}
-Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.
-
-%26
-\bibitem{Z3API}
-Magellan, ``{Source code and documentation},''
-  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.
-
-%27
-\bibitem{Cormem}
-Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.
-
-%28
-\bibitem{Dagum1998}
-Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.
-
-%29
-\bibitem{TheMathWorks2013}
-The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.
-
-%30
-\bibitem{Tranquillo2011}
-Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.
-
-%31
-\bibitem{Hong2010}
-Hong, L., Cai, J.
-(2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc.
-of the Intl.
-Conf.
-on Computer and Automation Engineering, pp.
-185--189.
-
-%32
-\bibitem{Cordeiro2011}
-Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.
-
-%33
-\bibitem{Teich2012}
-Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.
-
-%34
-\bibitem{Guthaus2001}
-Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R.
-(2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc.
-of the annual workshop on workload characterization, pp.
-3--14.
-
-%35
-\bibitem{Arato2005}
-Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.
-
-%36
-\bibitem{Holzmann2011}
-Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.
-
-%37
-\bibitem{Holzmann2012}
-Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.
-
-%38
-\bibitem{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.
-
-%39
-\bibitem{Qawasmeh2014}
-Qawasmeh, A., Malik, A., Chapman, B.
-(2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc.
-of the Intl.
-Symp.
-on Parallel \& Distributed processing, pp.
-1049--1058.
-
-%40
-\bibitem{Pavlinovic2015}
-Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.
-
-%41
-\bibitem{Patrick2015}
-Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.
-
-%42
-\bibitem{Holzmann11}
-Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
-
-\end{thebibliography}
-
-% Appendix
-%\appendix
-%\section*{APPENDIX}
-%\setcounter{section}{1}
-%In this appendix, we measure
-%the channel switching time of Micaz [CROSSBOW] sensor devices.
-%In our experiments, one mote alternatingly switches between Channels
-%11 and 12. Every time after the node switches to a channel, it sends
-%%out a packet immediately and then changes to a new channel as soon
-%as the transmission is finished. We measure the
-%number of packets the test mote can send in 10 seconds, denoted as
-%$%N_{1}$. In contrast, we also measure the same value of the test
-%mote without switching channels, denoted as $N_{2}$. We calculate
-%the channel-switching time $s$ as
-%\begin{eqnarray}%
-%s=\frac{10}{N_{1}}-\frac{10}{N_{2}}. \nonumber
-%\end{eqnarray}%
-%By repeating the experiments 100 times, we get the average
-%channel-switching time of Micaz motes: 24.3$\mu$s.
-
-%\appendixhead{ZHOU}
-
-% Acknowledgments
-%\begin{acks}
-%The authors would like to thank Dr. Maura Turolla of Telecom
-%Italia for providing specifications about the application scenario.
-%\end{acks}
-
-% Bibliography
-% Bibliography
-%\bibliographystyle{ACM-Reference-Format-Journals}
-%\bibliography{acmsmall-sample-bibfile}
-                             % Sample .bib file with references that match those in
-                             % the 'Specifications Document (V1.5)' as well containing
-                             % 'legacy' bibs and bibs with 'alternate codings'.
-                             % Gerry Murray - March 2012
-
-% History dates
-%\received{February 2007}{March 2009}{June 2009}
-
-% Electronic Appendix
-%\elecappendix
-
-%\medskip
-
-%\section{This is an example of Appendix section head}
-
-%Channel-switching time is measured as the time length it takes for
-%motes to successfully switch from one channel to another. This
-%parameter impacts the maximum network throughput, because motes
-%cannot receive or send any packet during this period of time, and it
-%also affects the efficiency of toggle snooping in MMSN, where motes
-%need to sense through channels rapidly.
-
-%By repeating experiments 100 times, we get the average
-%channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
-%the same experiments with different Micaz motes, as well as
-%experiments with the transmitter switching from Channel 11 to other
-%channels. In both scenarios, the channel-switching time does not have
-%obvious changes. (In our experiments, all values are in the range of
-%23.6 $\mu$s to 24.9 $\mu$s.)
-
-%\section{Appendix section head}
-
-%The primary consumer of energy in WSNs is idle listening. The key to
-%reduce idle listening is executing low duty-cycle on nodes. Two
-%primary approaches are considered in controlling duty-cycles in the
-%MAC layer.
+\bibliography{Ref.bib}
 
 \end{document}
-% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2015-10-22 Docs/TODAES/paper.tex
paper new version: table and comments updated

@@
 
-All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits.
+All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits.
 Each time was measured $3$ times (average taken).
-\textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP}.
-A time out condition (TO) is reached when the verification time is longer than $7200$ seconds.
-A memory out (MO) occurs when the tool reaches $24$GB of memory.
+\textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (pure, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA}.
+A time out condition (TO) is reached when the verification time is longer than $3600$ seconds.
+A memory out (MO) occurs when the tool reaches $15$GB of memory.
 
@@
 There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns two TOs (time-outs) related to Fuzzy and Mars benchmarks.
-
-In contrast to ESBMC-$\nu$Z, ILP solves $6$ out of $7$ benchmarks.
-When ILP produces a result, it typically provides the optimal solution.
+In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (time-outs) related to RC6, Fuzzy and Mars benchmarks.
+
+In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks.
+When ILP produces a result, it provides the optimal solution.
 On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z.
@@
 However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools.
-When analyzing all benchmarks, ESBMC-PB produces TO or MO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
+When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
 
@@
 Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution.
-ILP was the only one to solve Mars, while GA solved all benchmarks incorrectly.
+No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.
 
 The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high number of nodes and edges.
+ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.
 
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{2}   &  \normalsize{1}  &  \normalsize{2}   &  \normalsize{649}   &  \normalsize{1806}    &  \normalsize{TO}   &  \normalsize{5.42}  \\
-&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  \normalsize{876}  \\
+&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
 & & & & & & & & & \\
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{7}   &  \normalsize{7}   &  \normalsize{9}   &  \normalsize{340}   &  \normalsize{2050}    &  \normalsize{1.37}   &  \normalsize{5000}  \\
-&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0}   &  \normalsize{29}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  \normalsize{-27.5}  \\
+&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
+&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
 & & & & & & & & & \\
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{ 31}   &  \normalsize{362}   &  \normalsize{292}   &  \normalsize{3010}   & \normalsize{ TO}    &  \normalsize{MO}   &  \normalsize{MO } \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
 & & & & & & & & & \\
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{ 2 }  &  \normalsize{6}   &  \normalsize{7 }  &  \normalsize{1615}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
 &  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)} &  \normalsize{4} &  \normalsize{10}   &  \normalsize{11}   &  \normalsize{2238}   &  \normalsize{TO}    &  \normalsize{MO}   &  \normalsize{MO}  \\
+&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
 &  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
@@
 & & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{6}   & \normalsize{ 5}   &  \normalsize{6}   &  \normalsize{207}   &  \normalsize{TO}    & \normalsize{MO}   & \normalsize{MO} \\
+&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
 &  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\

### 2015-10-22 Docs/TODAES/paper.tex
update files
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 
-Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in ~\cite{Arato2003} and~\cite{Mann2007}.
+Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
 In~\cite{Trindade2015,Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.

### 2015-10-22 Docs/TODAES/paper.tex
update files
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
 All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.
@@
 \tabulinesep=6pt
-\captionof{table}{Description of Benchmarks.} \label{tab:Description-of-Benchmarks} 
+\captionof{table}{Description of Benchmarks.} 
 \begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
@@
 \bottomrule[1.5pt]
+\label{tab:Description-of-Benchmarks} 
 \end{tabular}\par

### 2015-10-22 Docs/TODAES/paper.tex
update files
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 \vspace{3 mm}
-In the above example, the for loop is executed in parallel.
+In the above example, the {\it for} loop is executed in parallel.
 Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor.
@@
 
-\vspace{3 mm}
 Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
@@
 
-\vspace{3 mm}
 Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
@@
 Each time was measured $3$ times (average taken).
-\textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (pure, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA}.
+Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
 A time out condition (TO) is reached when the verification time is longer than $3600$ seconds.
@@
 The problem addressed in this present paper uses a single objective function for minimization.
-In Partrick {\it et al.}~\cite{Patrick2015},  OptiMathSAT and $\nu$Z are compared for software optimization problems.
+In~\cite{Patrick2015}, OptiMathSAT and $\nu$Z are compared for software optimization problems.
 OptiMathSAT, using multiple objective functions, works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.

### 2015-10-22 Docs/TODAES/paper.tex
fixing reference to table
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 
-To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{Description-of-Benchmarks}.
+To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
 The nodes in the graphs correspond to high-level language instructions.

### 2015-10-22 Docs/TODAES/paper.tex
minor changes

@@
 
-Based on Arat\'o {\it et al.}~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
+Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
 The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $v_i \in V_h, v_j \in V_s $.

### 2015-10-23 Docs/TODAES/paper.tex
replace timeouts and memory-outs
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 \usepackage{minted}
+\usemintedstyle{bw}
+
 \newcolumntype{C}[1]{>{\Centering}m{#1}}
@@
                frame=lines,
-               framesep=2mm]{c++}
-int i;
+               framesep=2mm]{matlab}
+int k;
 #pragma omp parallel for
-for (i = 0; i < 10; i++)
-  a[i] = 2 * i;
+for (k = 0; k < 10; k++)
+  a[k] = 2*k;
 \end{minted}
@@
 Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
-A time out condition (TO) is reached when the verification time is longer than $3600$ seconds.
-A memory out (MO) occurs when the tool reaches $15$GB of memory.
+A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.
+A memory-out (MO) occurs when the tool reaches $15$GB of memory.
 
@@
 There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (time-outs) related to RC6, Fuzzy and Mars benchmarks.
+In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
 
@@
 
-Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution.
+Note that RC$6$ produced timeout for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution.
 No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.

### 2015-10-23 Docs/TODAES/paper.tex
fix formulas
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 The edges $E$ represent communication between components.
-Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(s_i)$ (or $ s_i $) of software if implemented in software.
+Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(V_i)$ (or $ s_i $) of software if implemented in software.
 Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).
@@
 Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
-The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $v_i \in V_h, v_j \in V_s $.
+The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $.
 The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
@@
 \label{hardware-costs}
-H_p  &= \Sigma_{v_i \in V_H} h_i
+H_p  &= \Sigma_{V_i \in V_h} h_i
 \end{align}
@@
 \label{software-communication-costs}
-  S_p &= \Sigma_{v_i \in V_s}\:s_i + \Sigma_{(v_i,v_j)\in\:E_p} c(V_i,V_j)
+  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j)
 \end{align}
@@
 \label{hw-sw-partitioning}
-s\left(1-x\right) + c|E_x| \leq S_0, 
+s\left(1-x\right) + c|EX| \leq S_0, 
 \end{align}

### 2015-10-23 Docs/TODAES/paper.tex
fix formulas
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>
fix references
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 \vspace{3 mm}
-\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
+\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
 
@@
 A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.
-A memory-out (MO) occurs when the tool reaches $15$GB of memory.
+A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
 
@@
 
-To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
+To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
 The nodes in the graphs correspond to high-level language instructions.
@@
 The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
-The clustering and fuzzy benchmarks are designed from Mann {\it et al.}~\cite{Mann2007} and are significantly large benchmarks.
+The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
 From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
@@
 $\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
-As an application example, Pavlinovic {\it et al.}~\cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
+As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
 The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.
-The approach described by Pavlinovic {\it et al.}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.
+The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.
 

### 2015-10-23 Docs/TODAES/paper.tex
review experimental evaluation
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

@@
 \usepackage{hyphenat}
-\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
+\hyphenation{ESBMC par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
 
@@
 \\
-\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
 \\
@@
 
-Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.
+Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}SS, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.
 
 There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
+In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
 
@@
 When ILP produces a result, it provides the optimal solution.
-On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z.
+On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by ESBMC-$\nu$Z.
 On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.
@@
 In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase.
-One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z.
+One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $2$.$5$ times slower than ESBMC-$\nu$Z.
 However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools.
@@
 
-Note that RC$6$ produced timeout for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution.
+Note that RC$6$ produced timeouts for all implementations of ESBMC; GA did not produce the correct answer, and ILP solves correctly most benchmarks, except for Mars and Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution.
 No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.

### 2015-10-24 Docs/TODAES/paper.tex
modifications in algorithms listing and paper structure

@@
 \usepackage{graphicx} %Imagens
-
-\usepackage{minted}
-\usemintedstyle{bw}
+\renewcommand{\lstlistingname}{Algorithm}
+%\usepackage{minted}
+%\usemintedstyle{bw}
 
@@
 
-\ccsdesc[500]{Hardware~Hardware-software codesign}
-\ccsdesc[500]{Hardware~Software tools for EDA}
-\ccsdesc[500]{Software and its engineering~Model checking}
-\ccsdesc[500]{Software and its engineering~Software verification}
+\ccsdesc[500]{Hardware~ Hardware-software codesign}
+\ccsdesc[500]{Hardware~ Software tools for EDA}
+\ccsdesc[500]{Software and its engineering~ Model checking}
+\ccsdesc[500]{Software and its engineering~ Software verification}
 
@@
 
-\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP. }
+\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}
 
@@
 \begin{bottomstuff}
-A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \\
+A. Trindade, H. Ismail, R. Degelo, and E. Galv\~ao \\
 Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
-\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ \\
-\and\\ \\
-H. Silva and L. Cordeiro \\
+\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ 
+\\
+H. Silva, and L. Cordeiro \\
 Federal University of Amazonas, Brazil\\
-prhsilva2012@gmail.com lucascordeiro@ufam.edu.br      \\
+prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br      \\
 \end{bottomstuff}
@@
 
-\vspace{5 mm}
+\vspace{3 mm}
 In some cases, the time to find a solution using ILP is impractical.
@@
 
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{matlab}
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%               framesep=2mm]{matlab}
+%int k;
+%#pragma omp parallel for
+%for (k = 0; k < 10; k++)
+%  a[k] = 2*k;
+%\end{minted}
+%\caption{OpenMP basic Example.}
+%\label{lst:example}
+%\end{listing}
+
+\vspace{3 mm}
+\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 int k;
@@
   a[k] = 2*k;
-\end{minted}
-\caption{OpenMP basic Example.}
-\label{lst:example}
-\end{listing}
-
-\vspace{3 mm}
+\end{lstlisting}
+
+\vspace{1.5 mm}
 In the above example, the {\it for} loop is executed in parallel.
@@
 
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{c++}
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%              framesep=2mm]{c++}
+%(Declare-Const K Int) 
+%(Declare-Const W Int)
+%(assert (< K 2)) 
+%(assert (< (- W K) 1))
+%(maximize (+ K W)) 
+%(check-sat)
+%\end{minted}
+%\caption{Example of SMT formula using $\nu$Z.}
+%\label{vZ}
+%\end{listing}
+
+\vspace{3 mm}
+\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 (Declare-Const K Int) 
@@
 (check-sat)
-\end{minted}
-\caption{Example of SMT formula using $\nu$Z.}
-\label{vZ}
-\end{listing}
-
-\vspace{3 mm}
+\end{lstlisting}
+
+\vspace{1.5 mm}
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
@@
 The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
-
+%
 \begin{align}
 \label{hardware-costs}
-H_p  &= \Sigma_{V_i \in V_h} h_i
+H_p  &= \Sigma_{V_i \in V_h} h_i,
 \end{align}
-
-\vspace{3 mm}
+%
+\vspace{2 mm}
 \noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
-
+%
+%
 %  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
@@
 \label{software-communication-costs}
-  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j)
+  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
 \end{align}
 
-\vspace{3 mm}
+\vspace{2 mm}
 Three different optimization and decision problems can be defined.
@@
 Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
-
+%
+\vspace{1 mm}
 \begin{align}
@@
 
-\vspace{3 mm}
+\vspace{2 mm}
 \noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
@@
 
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{c++}
- Initialize Variables 
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%               framesep=2mm]{c++}
+% Initialize Variables 
+% Declare number of nodes and edges
+% Declare hardware cost of each node as array (h)
+% Declare software cost of each node as array (s)
+% Declare communication cost of each edge (c)
+% Declare the initial software cost of (S0)
+% Declare transposed incidence matrix graph G (E)
+% Define the solutions variable (Xi) as Boolean
+% main {
+%  For TipH = 0 to Hmax Do {
+%   populate Xi with nondeterministic/test values
+%   Calculate s(1-x)+c|Ex| and store at variable
+%   Requirement isued by Assume (Variable <= S0)
+%   Calculate Hp cost Based on value tested of Xi
+%   Violation check with Assert(Hp > TipH)
+%  }
+% }
+%\end{minted}
+%\caption{Pseudocode describing sequential ESBMC}
+%\label{Pseudocode-describing-ESBMC}
+%\end{listing}
+
+\vspace{1.5 mm}
+\begin{lstlisting}[caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+Initialize variables 
 Declare number of nodes and edges
@@
 Declare communication cost of each edge (c)
- Declare the initial software cost of (S0)
+Declare the initial software cost of ($S_0$)
 Declare transposed incidence matrix graph G (E)
- Define the solutions variable (Xi) as Boolean
+Define the solutions variable ($X_i$) as Boolean
 main {
   For TipH = 0 to Hmax Do {
-   populate Xi with nondeterministic/test values
+    Populate $X_i$ with nondeterministic / test values
     Calculate s(1-x)+c|Ex| and store at variable
-   Requirement isued by Assume (Variable <= S0)
-   Calculate Hp cost Based on value tested of Xi
+    Requirement isued by Assume (Variable <= $S_0$)
+    Calculate Hp cost Based on value tested of $X_i$
     Violation check with Assert(Hp > TipH)
@@
 }
-\end{minted}
-\caption{Pseudocode describing sequential ESBMC}
-\label{Pseudocode-describing-ESBMC}
-\end{listing}
+\end{lstlisting}
 
@@
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
-
-\begin{figure}[ht]
+\begin{figure}[h]
 	\centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
 	\centering
@@
 Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{c++}
+
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%               framesep=2mm]{c++}
+%  GetNextStep(){
+%  int largestChunk = -1;
+%  chunk largest;
+%  for each(chunk in chunks){
+%     if(chunk.right - chunk.left > largestChunk){
+%           largestChunk = chunk.right - chunk.left;
+%           largest = chunk;
+%     }
+%   }	
+%   chunks.remove(largest);	
+%   int median = largest.left + floor((largest.right - largest.left) / 2)
+%   if(median > 0){
+%      if(largest.right - largest.left > 1)
+%         chunks.add(new chunk(largest.left, median - 1));	
+%      if(largest.right != largest.left)
+%         chunks.add(new chunk(median + 1, largest.right);
+%    }
+%   return median;
+% }
+%\end{minted}
+%\caption{Steps calculation using intervals.}
+%\label{Steps-Calculation-using-Intervals}
+%\end{listing}
+\vspace {2 mm}
+\begin{lstlisting}[caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 GetNextStep(){
@@
   chunks.remove(largest);	
-   int median = largest.left + floor((largest.right - largest.left) / 2)
+  int median = largest.left + floor((largest.right-largest.left)/2)
   if(median > 0){
@@
 }
-\end{minted}
-\caption{Steps calculation using intervals.}
-\label{Steps-Calculation-using-Intervals}
-\end{listing}
+\end{lstlisting}
 
@@
 
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{c++}
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%               framesep=2mm]{c++}
+% step = controller.GetNextStep();
+% int pid = ExecuteStep(step);
+% while(isRunning(pid)){
+%   if(!controller.isNeeded(step))
+%    kill(pid);
+% }
+%\end{minted}
+%\caption{Worker sample.}
+%\label{worker-sample}
+%\end{listing}
+
+\vspace {2 mm}
+\begin{lstlisting}[caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 step = controller.GetNextStep();
@@
 }
-\end{minted}
-\caption{Worker sample.}
-\label{worker-sample}
-\end{listing}
+\end{lstlisting}
 
@@
 
-\begin{listing}[H]
-\begin{minted}[mathescape,
-               linenos,
-               numbersep=7pt,
-               gobble=0,
-               frame=lines,
-               framesep=2mm]{c++}
+%\begin{listing}[H]
+%\begin{minted}[mathescape,
+%               linenos,
+%               numbersep=7pt,
+%               gobble=0,
+%               frame=lines,
+%               framesep=2mm]{c++}
+%--Initialize Variables
+%  Create vZ context 
+%  Create binary vector (x)
+%  Declare number of nodes, edges and S0
+%  Declare hardware cost of each node as array (h) 
+%  Declare software cost of each node as array (s)
+%  Declare communication cost of each edge (c)
+%  Declare transposed incidence matrix graph G (E)
+%--Arithmetic Expressions
+%  SC = s(1-x)
+%  CMC = c*|EX|
+%  Fobj =  x[i] * h[i]
+%--Assert Constraints
+%  Add constraints (SF + CMC <= S0)
+%  Add constraints to minimize Fobj
+%  Check Model
+%  Print Result
+%\end{minted}
+%\caption{Pseudocode describing ESBMC-$\nu$Z.}
+%\label{vZ-pseudocode}
+%\end{listing}
+
+\vspace {2 mm}
+\begin{lstlisting}[caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
 --Initialize Variables
@@
   Create binary vector (x)
-  Declare number of nodes, edges and S0
+  Declare number of nodes, edges and $S_0$
   Declare hardware cost of each node as array (h) 
@@
   Declare communication cost of each edge (c)
-  Declare transposed incidence matrix graph G (E)
+  Declare transposed incidence matrix graph G(E)
 --Arithmetic Expressions
@@
 --Assert Constraints
-  Add constraints (SF + CMC <= S0)
+  Add constraints (SF + CMC <= $S_0$)
   Add constraints to minimize Fobj
@@
   Print Result
-\end{minted}
-\caption{Pseudocode describing ESBMC-$\nu$Z.}
-\label{vZ-pseudocode}
-\end{listing}
+\end{lstlisting}
 
@@
 
+\vspace{1.5 mm}
+\begin{minipage}{\linewidth}
+\centering
+\small
+\sffamily\small
+\tabulinesep=4pt
+\captionof{table}{Description of Benchmarks.} 
+\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{8.9cm}}
+\\
+\toprule[1.5pt]
+\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
+\midrule
+\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\\
+\hline
+\\
+\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
+\\
+\hline
+\\
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
+\\
+\hline
+\\
+\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
+\\
+\hline
+\\
+\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
+\\
+\hline
+\\
+\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
+\\
+\hline
+\\
+\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
+\\
+\bottomrule[1.5pt]
+\label{tab:Description-of-Benchmarks} 
+\end{tabular}\par
+\bigskip
+\end{minipage}
+
 To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
@@
 
-\begin{minipage}{\linewidth}
-\centering
-\small
-\sffamily\small
-\tabulinesep=6pt
-\captionof{table}{Description of Benchmarks.} 
-\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
-\\
-\toprule[1.5pt]
-\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
-\midrule
-\\
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
-\\
-\hline
-\\
-\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
-\\
-\hline
-\\
-\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
-\\
-\hline
-\\
-\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
-\\
-\bottomrule[1.5pt]
-\label{tab:Description-of-Benchmarks} 
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
 %\begin{table}[h]
@@
 %----------------------------------------------
+%
+\begin{table*}[h]
+  \centering
+  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
+  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
+\\
+ &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
+\cmidrule(r){3-9}
+
+&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
+&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
+&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\
+
+%EXACT Solution
+\bottomrule[1.5pt]
+\rowcolors{1}{}{lightgray}
+
+\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
+& & & & & & & & & \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
+&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
+& & & & & & & & & \\
+
+\bottomrule[1.5pt]
+%ILP
+\multirow{4}{*}{\textbf{\normalsize{ILP}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%GA
+\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
+&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%MultiCore ESBMC
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC Parallel sequential
+\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC Parallel Binary
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%vZ
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+
+\bottomrule[1.5pt]
+\end{tabular}
+\label{Experimental-results-of-the-complex-benchmarks}
+\end{table*}
 
@@
 ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.
-
-\begin{table*}[t]
-  \centering
-  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
-  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
-\\
- &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
-\cmidrule(r){3-9}
-
-&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
-&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
-&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\
-
-%EXACT Solution
-\bottomrule[1.5pt]
-\rowcolors{1}{}{lightgray}
-
-\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
-& & & & & & & & & \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
-&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
-& & & & & & & & & \\
-
-\bottomrule[1.5pt]
-%ILP
-\multirow{4}{*}{\textbf{\normalsize{ILP}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%GA
-\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
-&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%MultiCore ESBMC
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC Parallel sequential
-\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC Parallel Binary
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%vZ
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-
-\bottomrule[1.5pt]
-\end{tabular}
-\label{Experimental-results-of-the-complex-benchmarks}
-\end{table*}
 

### 2015-10-24 Docs/TODAES/paper.tex
minor changes

@@
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
-GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.
+GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$), which are checked for satisfiability by an SMT solver.
 

### 2015-10-24 Docs/TODAES/paper.tex
minor changes

@@
 
-ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used.
+ESBMC v$2$.$0$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used.
 A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11.
@@
 
-All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits.
+All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits.
 Each time was measured $3$ times (average taken).

### 2015-10-24 Docs/TODAES/paper.tex
minor changes
minor changes to use ACM pattern for algorithm

@@
-\documentclass[prodmode,acmtrets]{acmsmall} % Aptara syntax
+\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax
 
@@
 
-\vspace{3 mm}
-\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\vspace{2 mm}
+\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 int k;
@@
 
-\vspace{1.5 mm}
 In the above example, the {\it for} loop is executed in parallel.
@@
 
-\vspace{3 mm}
-\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\vspace{2 mm}
+\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 (Declare-Const K Int) 
@@
 
-\vspace{1.5 mm}
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
@@
 \end{align}
-%
+
 \vspace{2 mm}
-\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
+\noindent
+and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
 %
@@
 
-\vspace{1.5 mm}
-\begin{lstlisting}[caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+\vspace{2 mm}
+\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
 Initialize variables 
@@
 Declare the initial software cost of ($S_0$)
-Declare transposed incidence matrix graph G (E)
+Declare transposed incidence matrix graph G(E)
 Define the solutions variable ($X_i$) as Boolean
@@
 \vspace {2 mm}
-\begin{lstlisting}[caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 GetNextStep(){
@@
   chunks.remove(largest);	
-  int median = largest.left + floor((largest.right-largest.left)/2)
+  int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
@@
 \vspace {2 mm}
-\begin{lstlisting}[caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
 --Initialize Variables

### 2015-10-25 Docs/TODAES/paper.tex
minor changes

@@
   chunks.remove(largest);	
-  int median = largest.left + floor((largest.right - largest.left) / 2)
+  int median = largest.left + floor((largest.right - largest.left) / 2);
   if(median > 0){
@@
 \bibliographystyle{ACM-Reference-Format-Journals}
-\bibliography{Ref.bib}
+\bibliography{Ref}
 

### 2015-11-22 Docs/IJES/Appendix/sample (double column).tex
including initial version of IJES

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{doublecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs,amsmath,upgreek}

\def\newblock{\hskip .11em plus .33em minus .07em}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}
\newtheorem{question}{Question}
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter

\def\Reals{\mathbb{R}}
\def\Ints{\mathbb{Z}}
\def\Nats{\mathbb{N}}

\def\theequation{\arabic{equation}}

\def\tc{\textcolor{red}}

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -30pt%
%%\vskip -35pt%
\end{table}%
%\def\tc{\textcolor}{red}
} \makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\thispagestyle{plain}

\setcounter{page}{1}

\LRH{xxxx}

\RRH{xxxx}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

%\BottomCatch

%\CLline

%\subtitle{}

\title{xxxx}

\authorA{xxxx}

\affA{xxxx*\\
*Corresponding author}

\authorB{xxxx}
\affB{xxxx}

\begin{abstract}
xxxxx
\end{abstract}

\KEYWORD{xxxx}

\REF{to this paper should be made as follows: xxxx (xxxx) `xxxx',
{\it xxxx}, Vol.~x, No.~x, pp.xxx--xxx.}

\begin{bio}
\tc{AUTHOR PLEASE SUPPLY CAREER HISTORY OF NO MORE THAN 100 WORDS
FOR EACH AUTHOR.}
\end{bio}

\maketitle

\section{Introduction}
\label{sec-introduction}

\section{Performance evaluation}
\label{sec-performance}

\section{Related work}
\label{sec-related}

\section{Conclusions}
\label{sec-conclusion}

\section*{Acknowledgements}

\begin{thebibliography}{99}

\bibitem[\protect\citeauthoryear{xxxx}{2011}]{Zhang11}
xxxx (2011) `Reliable packets delivery over segment-based multi-path
in wireless ad hoc networks', {\it Pervasive Computing and
Applications (ICPCA), 2011 6th International Conference on},
pp.300-–306. \tc{AUTHOR PLEASE SUPPLY LOCATION.}

\end{thebibliography}

\section*{Appendx}

We have proposed the CSD scheme that makes use of multiple bridge
nodes within the close neighbourhood of the source and insecure
neighbours. These bridge nodes cooperatively help to deliver secret
link key information from the source towards the insecure
neighbours. In the delivery process, no secret information is
disclosed to any node en route. These routers simply forward the
encrypted data. Even the bridge nodes only get to know partial
information about the secrets that they help to deliver.

\end{document}

%\def\notesname{Note}
%
%\theendnotes

%\section*{Query}
%
%\tc{AQ1: AUTHOR PLEASE CITE FIGURE 8 IN TEXT.}

\end{document}

### 2015-11-22 Docs/IJES/Double column/sample.tex
including initial version of IJES

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{doublecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}

\def\newblock{\hskip .11em plus .33em minus .07em}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Question}[section]
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter
\def\theequation{\arabic{equation}}

%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
%Processing,
%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}
\makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\setcounter{page}{1}

\LRH{F. Wang et~al.}

\RRH{Metadata Based Management and Sharing of Distributed Biomedical
Data}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

\BottomCatch

%\CLline

\PUBYEAR{2012}

\subtitle{}

\title{Metadata Based Management and Sharing of Distributed Biomedical Data}

%
\authorA{Fusheng Wang}
%
\affA{Department of Biomedical Informatics,\\ Emory University,\\ Atlanta, GA, USA \\
Fax: +1 \qquad E-mail: fusheng.wang@emory.edu}
%
%
\authorB{Fusheng Wang}
\affB{Department of Biomedical Informatics,\\ Emory University,\\ Atlanta, GA, USA \\
Fax: +1 \qquad E-mail: fusheng.wang@emory.edu}
%

%
%\authorA{Fusheng Wang\footnote{Work done while working at Siemens Corporate Research.} }
%
%\affA{Department of Biomedical Informatics, Emory University
%\newline
%36 Eagle Row, Ste 589, Atlanta, GA 30322, USA}
%
%
%
%\authorB{\footnotesize Cristobal Vergara-Niedermayr\footnote{Work done while working at Siemens Corporate Research.}}
%\affB{Oracle \newline
 %New Jersey, USA}
%
%
\authorC{Peiya Liu}
\affC{Department of Integrated Data Systems, Siemens Corporate
Research \newline 755 College Road East, Princeton 08540, USA}

\begin{abstract}
Biomedical research becomes reliant on multi-disciplinary,
multi-institutional collaboration, and data sharing is becoming increasingly important for researchers to reuse experiments, pool expertise and validate approaches. However, there are many hurdles for data sharing, including the unwillingness to share,  lack of flexible data model for providing context information for shared data,  difficulty to share syntactically and semantically consistent data across distributed institutions, and expensive cost to provide tools to share the data.  In our work,  we develop a Web-based collaborative biomedical data sharing platform {\em SciPort} to support biomedical data sharing across distributed organizations. SciPort provides a generic metadata model for researchers to flexibly customize and organize the data. To enable convenient data sharing, SciPort provides a central server based data sharing architecture, where data can be shared by one click through publishing metadata to the central server. To enable consistent data sharing, SciPort provides collaborative distributed schema management across distributed sites. To enable semantic consistency for data sharing, SciPort provides semantic tagging through controlled vocabularies. SciPort is lightweight and can be easily deployed for building data sharing communities for biomedical research.
\end{abstract}

\KEYWORD{Metadata; Scientific Data Management; Data Sharing;  Data Integration; Computer Supported Collaborative Work.}

\REF{to this paper should be made as follows: Rodr\'{\i}guez
Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
corporate environmental disclosures on the internet: the case of
IBEX 35 Spanish companies', {\it International Journal of Metadata,
Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
Manuel Pedro Rodr\'iguez Bol\'ivar received his PhD in Accounting at
the University of Granada. He is a Lecturer at the Department of
Accounting and Finance, University of Granada. His research
interests include issues related to conceptual frameworks of
accounting, diffusion of financial information on Internet, Balanced
Scorecard applications and environmental accounting. He is author of
a great deal of research studies published at national and
international journals, conference proceedings as well as book
chapters, one of which has been edited by Kluwer Academic
Publishers.\vs{9}

\noindent Bel\'en Sen\'es Garc\'ia received her PhD in Accounting at
the University of Granada. She is a Lecturer at the Department of
Accounting and Finance, University of Granada. Her research
interests are related to cultural, institutional and historic
accounting and in environmental accounting. She has published
research papers at national and international journals, conference
proceedings as well as chapters of books.\vs{8}

\noindent Both authors have published a book about environmental
accounting edited by the Institute of Accounting and Auditing,
Ministry of Economic Affairs, in Spain in October 2003.
\end{bio}

\maketitle

 \section{Introduction}

%The needs for data sharing
With increased complexity of scientific problems, biomedical
research is increasingly a collaborative effort across multiple
institutions and disciplines.  Data sharing is becoming critical for
validating approaches and ensuring that future research can build on
previous efforts and discoveries. As a result, data sharing is often
required by scientific funding agencies to share the data produced
in grant projects. For example,  the National Institutes of Health
(NIH) of US requires data sharing for NIH funded projects of
\$500,000 or more in direct costs in any one year.

To support large scale collaborative biomedical research, NIH
provides large-scale collaborative project awards  for a team of
independently funded investigators to synergize and integrate their
efforts, and the awards mandate the research results and data to be
shared \cite{nih03datasharing,nih08policy}.  The Network for
Translational Research (NTR): Optical Imaging in Multimodality
Platforms\cite{ntr} is one of such collaborative projects on the
development, optimization, and validation of imaging methods and
protocols for rapid translation to clinical environments.  It
requires not only managing the complex scientific research results,
but also sharing the data across hundreds of research collaborators.
As another example, Siemens Healthcare has research collaborations
with hundreds of research sites distributed across the US, each
providing Siemens marketing support by periodically delivering white
papers, case reports, clinic methods, clinic protocols,
state-of-the-art images, etc. In the past, there were no convenient
methods for research partners to share data with Siemens, and mostly
data were delivered through media such as emails, CDs and hard
copies. This made it very difficult to organize, query and integrate
the shared data.

Sharing biomedical research data is important but difficult
\cite{piwowar08culture,birnholtz03data}. One major difficulty is the
unwillingness to share, as investigators may restrict access to data
to maximize the professional development and economic benefit
\cite{bekelman03}. With increased awareness of this issue, the
government and funding agencies are developing  strategies and
policies to promote and enforce the sharing of data
\cite{piwowar08culture,dsic,cabigconnected}. While the social issue
of data sharing is challenging, this paper will mainly focus on the
development of a biomedical data sharing system which makes data
sharing becoming flexible and easy for humans on collaborative
research.

\subsection{Complexity of Biomedical Data}

Biomedical data can be in heterogeneous formats such as structured
data, standard based medical images such as DICOM \cite{dicom}, non
standard medical images such as optical images, raw equipment data,
spreadsheets, PDF files,  XML documents, and many others. Thus, the
data are  a mix of structured data (often deeply hierarchical) and
files. Meanwhile, the data structures of biomedical research data
can be very complex, ranging from different primitive data types, to
lists and tables, from flat structures to deep nested structures,
and so on.  It is often difficult for investigators to create a
sophisticated schema that can capture enough context information or
metadata information, if the data types do not have a public,
centralized, and well-recognized database. During our interviews
with more than a dozen biomedical research investigators, we found
that major investigators use spreadsheet like tools and manage their
data through operating system folder organized files. To reduce the
cost and complexity for data sharing, a data sharing system needs to
provide an extensible architecture that can be easily customized by
researchers with their own metadata models, even without programming
skills.

\subsection{Management of Data Sharing}

Even with willingness to share data, in many cases an investigator
would like to control when to share data, and who can access the
data. An investigator may want to keep unpublished data only to his
or her own group or collaborative partners, and selectively publish
a subset of data for sharing. An investigator may also want to stop
sharing certain data at any time, for example, when he or she finds
a quality problem of the data. An investigator may also have new
results added on existing shared data and want to keep the data
current. A manageable data sharing system with convenient operations
can potentially increase the willingness for users to share, as the
effort for data sharing can be much reduced.

\subsection{Data Sharing Architecture}

There are three major types of data sharing architectures: i)
Centralized, multiple datasets hosted at a single location in a
common schema. For example, the Cancer Genome Atlas (TCGA) Data
Portal \cite{tcga} manages genome related data; National Biomedical
Imaging Archive \cite{nbia} manages DICOM based medical research
data. ii) Federated, with a virtual view of physically separate
datasets. For example, Cancer Biomedical Informatics Grid
(caBIG{\small \textregistered})  \cite{cabig} is a Grid based data
federation infrastructure that supports a CQL query language across
distributed data sources.  iii) Distributed, physically and
virtually separate datasets.  Centralized approach is often limited
to common data types. Biomedical research, however,  generates
complex data and often new data types.  Distributed approach is
often difficult to retrieve, interpret and aggregate results, and
lacks data consistency between research sites.  While caGrid is
becoming widely used in biomedical research community, caGrid itself
has a complex infrastructure and the effort is significant.

Considering the high dynamic nature of biomedical research and the
need of  cost effective data sharing, we develop a hybrid
architecture which combines the benefits of the centralized approach
and the distributed approach. In this approach, a data sharing
central server is provided for multiple distributed data sources,
and stores only published metadata (not raw data or images with
large sizes) from distributed data sources. Users can have flexible
management of data sharing through publishing or unpublishing data
with  a simple operation. The metadata contain context information
of original data sources (including raw data) which are still
managed at distributed research sites. The central server provides
an integrated view of all shared data, and shared data can be easily
aggregated and retrieved from the central server. This architecture
not only is lightweight, but also provides support of consistent
data sharing through collaboratively managing schemas and
semantically tagging of data.

\subsection{Inconsistency of Shared Data}

Another difficulty on sharing data is the incompatible
representation of data between sharing partners. Each site may use
different schemas (e.g., data templates) and represent data in
different formats; and even if multiple partners choose to use the
same schema, the schema may evolve as research progresses. For
example, a field name may be changed or additional constraints may
be added in a schema. Data generated from different versions of a
schema  may not match when searched together. For example, if a
field named ``age'' is changed to ``patient\_age'',  these two field
names will lead to structurally different fields and can not be
searched together as a single field.   Semantic consistency is on
using the same vocabulary to represent knowledge. For example,  one
investigator may use ``Malignant Tumor'' to describe a lesion, and
another investigator  may use `cancer'.    While semantics
annotations can be added to data to enhance semantic
interoperability between shared data, there is a lack of integrated
tools and architecture that can support semantic annotations from
controlled vocabularies.

\subsection{Our Contributions}

To meet the requirements of a data sharing system and overcome the
challenges, we develop SciPort, a Web-based collaborative biomedical
data sharing platform to support collaborative biomedical research.
SciPort brings together the following essential components to
support biomedical data sharing:

\begin{itemize}

\item Generic biomedical experiment metadata model and XML based biomedical data management for research sites to flexibly customize and organize their data (Section
\ref{sec:datamanagementoverview});

\item Hybrid, lightweight data sharing architecture through a Central
Server, and data sharing can be conveniently managed by investigators (Section \ref{sec:sharing});

\item Easy sharing of schemas between distributed research partners (Section \ref{sec:sharingschema});

\item Collaborative management of schemas and their evolution between distributed research sites to maintain syntactic data consistency  (Section \ref{sec:collaborativeschema});

\item Semantic tagging of data to achieve semantically consistent data sharing (Section \ref{sec:tag}).
\end{itemize}

This paper has been significantly extended from previous work
\cite{wang08com}, which discussed preliminary work and the technique
aspect on distributed scientific data management. The work presents
here represents latest results and software development, and has a
major new focus on the human and sharing aspects of biomedical data.
The paper also covers new work on metadata modeling for data
sharing, collaborative tagging for data sharing, user experience on
real world deployment, and so on.

\section{Generic Biomedical Experiment Metadata Modeling and Management} \label{sec:datamanagementoverview}

As discussed in \cite{birnholtz03data}, metadata models serve as the
abstraction of data, and are essential for understanding shared
data. However, metadata  are often incomplete, and important context
information of data \cite{chin04context} is often ignored. However,
many domain specific applications or data models are specific to
certain types of data and limited to a small set of context
information.  To precisely capture as sufficient metadata and
context information as possible for biomedical data sharing,
researchers themselves should be also to customize their own
metadata models easily to meet their research need and data sharing
need.

SciPort was first developed as a biomedical data management system  with
metadata  modeling, authoring, management, viewing, searching and
exchange.

%SciPort takes an XML based approach for data modeling, schema representation, and storage  and queries.

\subsection{Generic Meta Data Modeling for Biomedical Data}

To meaningfuly represent each dataset, we develop a {\em SciPort document} model to represent the metadata and context information of the data.
A SciPort Document can represent both (nested) structured data, files and images.

A SciPort document includes several objects: i) Primitive Data
Types/Fields. Primitive data types are used to represent structural
data, including {\em integer}, {\em float}, {\em date}, {\em text},
and Web-based data types such as {\em textarea}, {\em radiobutton},
{\em checkbox}, {\em URL}, etc.; ii) File. Files can be linked to a
document through the file object; iii) \textit{Reference.}  A
reference type links to another SciPort document; iv) Group. A group
is similar to a table, which aggregates a collection of fields or
nested groups.  There can be multiple instances for a group, like
rows of a table; v)Category. A category relates a list of fields,
e.g., ``patient data'' category, ``experiment data'' category, etc.
Categories are used only at the top level of the content, and
categories are not nested.

Figure \ref{fig:sampledocument} shows an example SciPort document
that describes image annotations on top of medical images.  This
document captures generic information such as the tile, description,
author, creation date and modification date; patient information
such as the age and gender; annotation data such as a number of
annotated tumors marked up on top of the image, and the link to the
image file from which annotations were generated.  Note that in the
example, we can easily represent nested complex information such as
multiple tumors, multiple spatial coordinates and different  data
types such as images and files.

%\begin{figure*}[t]
 %\centering
  %\framebox[4.1in][c]{
% \includegraphics[width=4in]{sampledocument}}
%  \caption{A Sample SciPort Document}
% \inv \label{fig:sampledocument}
%\end{figure*}

\subsection{XML Based Implementation and the Benefits}

The hierarchical nature of the data model fits perfectly with the
tree based XML data model, and we take an XML based approach to
implement the data model -- we call it \textit{SciPort Exchange
Document}.  Users can also easily define their own schemas which are
internally represented with an XML-based schema definition language.
Besides, To provide an intuitive way to present data,  we also
develop a hierarchical model based on XML to organize biomedical
data, thus documents can be quickly browsed and identified through
the hierarchy. For example, we can define a hierarchy with levels of
``site''$\rightarrow$  ``patient'' $\rightarrow$ ``measurement'',
and attach documents at different folder levels. SciPort also
provides fine grained access control  at folder level for the data
in the database \cite{wang09security}.

The self-describing and rich structure of XML makes it possible to
represent arbitrary complex biomedical research data. By modeling
the data as XML documents, we can take advantage of native XML
database technologies to manage biomedical data, thus we can avoid
complex data model and query translation between XML and RDBMS. This
is especially beneficial since users can define arbitrary structured
and nested data formats for their data.  Moreover, powerful queries
can be supported directly on XML databases with the standard XML
query language XQuery \cite{xquery}.

A salient characteristic of SciPort is that the system is highly
adaptable.  SciPort provides a Web-based schema authoring tool to
easily create complex hierarchical metadata schema  model without
any need of programming.  The organizational hierarchy is also
customizable with its hierarchy authoring tool. This allows users to
configure their own biomedical data repository without requiring
expensive and time-consuming services or software development
effort.

\section{Sharing Distributed Biomedical Data} \label{sec:sharing}

While investigators can share their data simply through giving login
information to collaborators, a more systematic approach for sharing
data across research consortia or networks can provide more
flexibility and benefits. SciPort comes with comprehensive data
sharing capabilities: i) Convenience: data sharing is performed by a
single action and data can be selectively shared; ii) Ownership of
data: researchers own and manage their data by their own;  iii)
Flexible sharing control: data sharing can also be revoked by
researchers at any time;  iv) Up-to-date of shared data. As data are
updated or removed, corresponding shared data also need to be
synchronized accordingly to stay current;  v) Consistently
aggregated shared data from distributed sites; and vi) Lightweight.
Sharing is manipulated through metadata, no copy of large volume
data is needed.

These sharing capabilities are implemented through a lightweight,
central server based approach, as discussed next.

\subsection{Sharing Data through a Central Server}

SciPort provides a distributed architecture to share and integrate
data through a Central Server (Figure \ref{fig:integration}). In
this architecture, each research site will have its own Local
SciPort Server which itself functions as an independent Server for
data collection and management. In addition, there will be an
additional Central  Server upon which Local Servers are able to
selectively publish their data (structured documents) (Figure
\ref{fig:docpublish}). Images/files, which are often the major
source of data volume, are still stored on corresponding Local
Servers but are linked from the published documents on the Central
Server. Once a user on the Central Server begins to download a
document from the Central Server, actual data files are downloaded
from the corresponding Local Server that holds the data.

Thus, the Central Server provides a global view of shared data across all
distributed sites, and can also be used as a hub for sharing schemas among
multiple sites. Since data are shared through the metadata (SciPort
Documents), the integration is lightweight. Users on the Central Server will
only have read access to the data.

Figure \ref{fig:integration} illustrates an example SciPort sharing
architecture formed by four Local Servers at four universities: UCI,
UCSF, Dartmouth and Penn. Each Local Server is used for data
collection and management of clinical trial data at its local
institution. Since these clinical trials are under the same research
consortium, they would share their data together by publishing their
data (documents) to the Central Server located at UCI. Members at
NTR research consortia are granted read access on such shared data
through the Central Server. Once the user identifies a data set from
the Central Server and wants to download the data, the user will be
redirected to the corresponding hosting Local Server to download the
data to the client.

%\begin{figure*}[t]
% \centering
% \framebox[2.9in][c]{
% \includegraphics[width=2.7in]{integration}
%}
 % \caption{The Central Server Based Architecture for Data Sharing}
  %\inv \label{fig:integration}
%\end{figure*}

%\begin{figure*}[t]
 %\centering
  %\framebox[3.7in][c]{
% \includegraphics[width=3.6in]{docpublish}
%}
 % \caption{An Example of Publishing an Existing Document}
% \inv \label{fig:docpublish}
%\end{figure*}

\subsection{Data Synchronization}

Shared data may become outdated as new results or analysis are
generated on the data. SciPort provides automated data
synchronization on shared data through synchronization enforcement
in the following operations: i) Create. When a document is created,
the author or publisher has the option to publish this document
(Figure \ref{fig:editpublish}). Once the document is   published, a
``published'' status is added to the document. A user can   also set
up an automatic publishing flag so all new documents will be
automatically published; ii) Update. When an update is performed on
a published document, the document will automatically be republished
to the Central Server; iii) Delete. When a published document is
deleted, it will also be automatically removed from the Central
Server;  iv) Unpublish. A user can stop sharing a document by
selecting the ``unpublish'' operation.  Unpublished documents will
be removed from the Central Server.

%\begin{figure*}[t]
 %\centering
  %\framebox[3.7in][c]{
% \includegraphics[width=3.6in]{editpublish}
%}
 % \caption{An Example of Publishing a New Document}
% \inv \label{fig:editpublish}
%\end{figure*}

\subsection{Security and Trust between Local Servers and the Central Server}

\textbf{Server Verification.} The trust between Local Servers and
the Central Server is implemented through security tokens. For a
Local Server to be accepted into the network, it will be granted a
security token to access the Central Server services. The token will
be imported at the setup step. When a Local Server tries to connect
to the Central Server, the Central Server verifies if the token
matches.

\textbf{Single Sign-on and Security.} One issue for sharing data
from distributed databases is that it is not feasible for Central
Server users to login to every distributed database. When a user
publishes a document, the user already grants the read access of the
document (including the files linked to the document) to the users
on the Central Server, thus another authentication is unnecessary.
Therefore, users on the Central Server should be able to
automatically access shared data from a Local Server in a
transparent way. To support this, the Local Server Document Access
Control Manager has to make sure that the remote download requests
really come from Central Server users who are currently logging on.
We develop a single sign-on method to guarantee the security of the
data sharing, by verifying if an incoming data request to a Local
Server comes from the Central Server and if the current request user
is currently logged in on the Central Server.

\subsection{Sharing Data in Multiple Data Networks}

Data can  be shared not only in a single data network through one
Central Server, but also in multiple data networks through multiple
Central Servers. One organization may want to share the same data in
multiple networks, as demonstrated in an example (Figure
\ref{fig:multiserverintegration}).  There are two networks,  one
centered at UCI and another centered at Stanford. UCI is
collaborating with both networks and needs to share data with both
networks.  UCI will be granted as a partner site and its Local
Server will be configured for both networks. A document can then be
published to any of the Central Servers or both.  This sharing
architecture makes it possible for very flexible data sharing across
different research networks.

%\begin{figure*}[t]
% \centering
% \framebox[4.5in][c]{
% \includegraphics[width=4.3in]{multiserverintegration}
%}
 % \caption{Sharing Data in Multiple Data Networks}
%  \inv \label{fig:multiserverintegration}
%\end{figure*}

Besides data sharing, SciPort also provides sharing of schemas
between distributed research sites (Figure
\ref{fig:collaborativearchitecture}), discussed in Section
\ref{sec:sharingschema}.

%\begin{figure*}[t]
% \centering
% \framebox[3.8in][c]{
% \includegraphics[width=3.4in]{collaborativearchitecture}
%}
 % \caption{Types of Information Sharing in SciPort}
%  \inv \label{fig:collaborativearchitecture}
%\end{figure*}

\subsection{The Benefits of Our Hybrid Data Sharing Architecture}

The architecture of SciPort is a hybrid of centralized approach and
distributed approach.  Centralized approach can provide high
visibility, easy retrieval, easy aggregation within the repository,
but suffers from limited data types or flexibility of customizing
new data types. Distributed approach allows users to flexibly
manage, customize and control their data and data sharing,  but
often suffers from low visibility, difficulty on retrieval,
interpretation, and aggregation, and lacks of data consistency. Our
hybrid approach benefits from both. The Central Server provides high
data visibility, easy retrieval and aggregation of all shared data
from distributed sites.   SciPort allows users to conveniently
customize their data types through creating and updating schemas.
Users can flexibly manage their data sharing through simple
publishing or unpulishing operations.  Data consistency is
maintained through collaborative schema sharing and management
(discussed in next two Sections). The hybrid approach is also
lightweight, as it does not store directly original data such as raw
data or medical images -- which can have high data volumes, but only
metadata or structured documents that describe and abstract the
data.

\section{Sharing Schemas} \label{sec:sharingschema}

Schemas are used to define structures and constraints of documents.
The former includes a mix of (possibly nested) object types defined
in the data model, and the latter includes i) number of instance
constraints for file and group types, ii) minimal and maximal value
constraints; and iii) controlled values.  Schemas are an essential
component  since they are used for i) data validation; ii) document
authoring form generation; iii) data presentation -- templates are
defined based on schemas; and iv) search form generation.

Sharing schemas are critical for sharing data, since the Central
Server glues data together using shared schemas to present and
search data. How to keep data from multiple Local Servers coherent
is also dependent on at what level and how schemas can be shared
consistently.

\subsection{Publishing Schemas}

Schemas can be shared by publishing them to the Central Server. From
a  Local Server {\em Schema Management} menu, schemas created on the
Local Server can be selectively published to target Central Servers,
as shown in the example in Figure \ref{fig:schemapublish}. When a
new document is being published to the Central Server, the
availability of the corresponding schema on the Central Server will
be checked. If the schema is not present, then the schema will also
be published together with the document.

The {\em owner of a schema} is defined as the Local Server on which
the schema is first created.  A schema is identified by its owner
and schema ID.  SciPort also provides comprehensive access control
management \cite{wang09security}, and two roles are related to
schema management: i) {\em organizer} role with privileges to author
and update schemas and ii) {\em publisher} role with  privileges to
publish documents and schemas.

Once a schema is published, it can be shared through the Central
Server. Other Local Servers can reuse schemas by importing schemas
from the Central Server, as shown in Figure \ref{fig:schemaimport}.
A schema can be unpublished from a Central Server by a Local Server,
thus the schema is not available on the Central Server for further
sharing.  Users on the Central Server with an ``organizer'' role can
remove a schema from the Central Server if no document on Central
Server is depending on this schema. This can be used to clean up
non-used schemas.

%\begin{figure*}[t]
% \centering
% \framebox[3.8in][c]{
% \includegraphics[width=3.7in]{schemapublish}
%}
 % \caption{An Example of Publishing Schemas from a Local Server}
  %\inv \label{fig:schemapublish}
%\end{figure*}

%\begin{figure*}[t]
 %\centering
% \framebox[4in][c]{
% \includegraphics[width=3.9in]{schemaimport}
%}
 % \caption{An Example of Importing Schemas to a Local Server}
  %\inv \label{fig:schemaimport}
%\end{figure*}

\subsection{Three Scenarios of Schemas Sharing}

Based on the use cases, there are three typical scenarios of schema sharing:

\textbf{Static Schema} A schema is fixed and will not be changed.
For example, some common standard based schemas are not likely to
change. Once a schema is authored and changed to the final status,
it can be published to the Central Server to be shared by every
Local Server (Figure \ref{fig:fixeddistributedschema}). This is the
simplest scenario, as schemas can be created once and shared
directly through the Central Server.

\textbf{Uniform Evolving Schema} A Schema can be changed and a uniform
version is shared by all Local Servers, thus data consistency is maintained
across all sites.  The schema is owned by its original creating Local Server,
and the owner can make certain changes.

\textbf{Multiform Evolving Schema} A ``seed'' schema is first
created and shared as public -- every Local Server becomes the owner
and can update the schema. The Central Server maintains a version of
the schema that conditionally merges updates from Local Servers,
thus all documents published on the Central Server will be
compatible under this schema.

%\begin{figure*}[t]
 %\centering
 %\framebox[3.9in][c]{
% \includegraphics[width=3.8in]{fixeddistributedschema}
%}
 % \caption{Static Schemas Sharing}
  %\inv \label{fig:fixeddistributedschema}
%\end{figure*}

%\begin{figure*}[t]
 %\centering
% \framebox[3.9in][c]{
 %\includegraphics[width=3.8in]{distributedschema}
%}
 % \caption{Uniform Schema Sharing}
%  \inv \label{fig:distributedschema}
%\end{figure*}

%\begin{figure*}[t]
 %\centering
% \framebox[3.9in][c]{
 %\includegraphics[width=3.8in]{publicdistributedschema}
%}
 % \caption{Multiform Schema Sharing}
  %\inv \label{fig:publicdistributedschema}
%\end{figure*}

Next, we will discuss how to manage schemas and their evolution for the last
two scenarios (static schema management is straightforward and ignored here.)

\section{Collaborative Management of Schemas for Consistent Data Sharing}
\label{sec:collaborativeschema}

Since schemas can be shared and used across multiple distributed
data sources, one challenging issue is how to manage schema
evolution while keeping shared documents consistent and compatible
with their schemas in a distributed environment. To solve this
problem, we first define the following favorable rules for schema
management and sharing in a distributed environment:
\begin{itemize}

\item {\em Minimal administration}. Human based manual schema
management can be difficult, especially for schemas that may be
updated by different sites.  To minimize human effort for managing
schemas across distributed sites, it would be ideal if the data
sharing system can facilitate the management of schemas, for
example, relying on an information exchange hub  based on the
Central Server.

\item {\em Data consistency}.  Schema evolution has to be backward compatible otherwise the integrity of documents will be broken.

\item {\em Control of schemas}. To prevent arbitrary update of
schemas, by default, only the owner (the user who creates the
initial schema on a Local Server) of a schema can update a schema.

\item {\em Current of Schemas}: The Central Server always has the
up-to-date version of a schema if that schema is shared by the
owner, to guarantee no outdated schemas are shared across sites.

\item {\em Sharing Maximization}: Since shared schemas on the Central
Server can be unpublished by local database users and removed from
the Central Server, to promote sharing, only the last time publisher
of this schema can unpublish a schema.

\end{itemize}

These rules will help to automate schema management in a distributed
environment, minimize conflicts of updates, maintain coherent shared
data on the Central Server, and reduce the effort from humans.  To
achieve this, we enforce the rules for schema operations on both
Local Servers and Central Servers. Schema operations on Local
Servers include create, update, delete, import, publish, and
unpublish, and schema operations on Central Servers include remove.

\begin{eqnarray}
x(k + 1) = \left[{\theta (k)A_1  + \left( {1 - \theta (k)}
\right)A_2} \right]x(k) + \left[ {\theta (k)B_1  + \left({1 - \theta
(k)} \right)B_2 } \right]u(k)\nonumber
\end{eqnarray}

\subsection{Uniform Schema Management}

In this scenario, a Schema can be changed and a uniform version is
shared by all Local Servers, thus data consistency is maintained
across all sites and the Central Server.   Next we discuss how
schema management rules are enforced in each schema operation.

\textbf{Create and Delete}

A schema can be created on a Local Server if the user has the
organizer role. This Local Server will become the owner of this
schema. A schema can be  deleted  if the user has the organizer
role, and there are no documents using this schema on this Local
Server.  If the Local Server is the owner of the schema, and the
schema is never published,  deleting a schema will eliminate the
schema forever. If the schema was once published, it may still be
alive and used on other Local Servers.

\textbf{Update}

Incompatible update of a schema is the one that can lead to
inconsistency between the new schema version and existing documents.
Incompatible updates are not allowed unless the following conditions
are met:  i) only the owner of a schema can make updates to the
schema; ii) there are no existing documents created based on  this
schema on this Local Server; and iii) the schema was never
published, i.e., there will no other Local Servers using this schema
to create documents.
%A publishing status is associated with each schema.

Compatible update of a schema will not lead to inconsistency between
the new schema version and existing documents. The following
conditions are required for compatible update.   i){\em Ownership.}
The Local Server is the owner of the schema, and the user is the
organizer on this Local Server; ii){\em Field Containment.}  All the
fields in the last schema are present in the  new schema and belong
to the same category or group, and new categories and fields added.
iii){\em Type Compatibility.} All the fields in the new schema have
the same type   or a compatible type, i.e., a more general type.
iv){\em Relaxed Value Range Constraints.} No new value constraints
are permitted  for  existing fields which do not have any
constraint. Value constraints can be updated with more relaxed
ranges. Constraints on new fields are permitted. v){\em Relaxed
Controlled Values.} For field with controlled values, the extent is
enlarged with more options. vi){\em Relaxed Constraints on Number of
Instances.} For group field or file field, there can be a constraint
on the minimal and/or maximal number of instances.  No instance
number constraint is permitted on existing fields, and instance
number constraint can be updated with more relaxed range. Change of
a field's order within its sibling is not considered incompatible.

Once a schema is updated on the Local Server, it will be automatically
republished to the Central Server (if any) onto which the schema has been
published. This will ensure the Central Server always maintains up-to-date
versions of schemas.

\textbf{Publish and Unpublish}

A schema can be published to one or multiple Central Servers if the
user has a publisher role and there is no newer version of this
schema on the Central Server.  There are three scenarios of schema
publishing: i) Schemas can be manually  published from the schema
publishing interfaces; ii) The schema of a document is automatically
published when a document is published. When a document is
published, the Local Server will check the Central Server if the
schema is available or up-to-date. Otherwise the schema is
republished; iii) If a schema was published and is then updated with
compatibility, the new version schema will be automatically
republished on the Central  Server and replace the last version.
This will keep the schemas on the  Central Server up-to-date.

A schema can be unpublished by a Local Server with the following conditions:
i) the user has the ``publish'' role on the Local Server; ii) there is no
document associated with it on the Central Server, and iii) the Local Server
is the last publisher of the schema. The last condition is necessary,
otherwise if the schema is used at multiple Local Servers, every Local Server
can easily stop the publishing which can be against the sharing goal of the
last publisher.

\textbf{Import}

A Local Server can import a shared schema from the Central Server if
the user has the organizer role. When there is a new version of a
schema on the Central Server, the new version schema will be
automatically detected by a Local Server when there is a document
being published from that Local Server.

\textbf{Remove from Central Server}

Users on the Central Server with the organizer role can remove a
schema from the Central Server if no document on Central Server is
using this schema. This can be used to cleanup non-used schemas.

\textbf{Update, or create?}  As a schema  keeps on evolving, the
number of updates on a schema can be many. When it reaches certain
threshold, the latest schema may be very different from the original
schema, the data between the two schemas may be very different, and
the data consistency does not make much sense any more.  In this
case, it may be desirable to create a new schema.  SciPort provides
a functionality to view change history of a schema, and users can
create a new schema from an existing schema in the Schema Editor
tool.

\textbf{An Example of Uniform Schema Management}

A user with organizer privilege on a Local Server L1 creates a
schema S(V1) (Figure \ref{fig:distributedschema}). The user may
later find the schema not accurate, and makes changes to the schema.
Since no document has been created and the schema has never been
shared yet, the user may make arbitrary changes, including
incompatible updates. Once the user has a stable usable version of
the schema, the user begins to author documents based on this
schema, and publishes documents to the Central Server C. Schema
S(V1) will be automatically published to the Central Server. After
some time, the user may need more information for their data or
adjust existing fields, and need to update schema S. Since there are
existing documents using the schema, and the schema was also
published, the user can make only compatible update to schema S(V1).
(If compatible update is not sufficient, the user has to create a
new schema.) Once schema S(V1) is updated as S(V2), it will be
automatically propagated to the Central Server to replace the last
version S(V1). A user with organizer privilege on a Local Server L2
imports schema S(V1) after S(V1) is published on the Central Server,
and documents then are created on L2 on this schema. Later S(V2)
replaces S(V1) on the Central Server, which is detected when a
document of schema S(V1) is published to C. The user at L2 will be
prompted to synchronize the schema, and S(V1) is replaced by S(V2)
on L2.

\subsection{Distributed Multiform Schema Sharing} \label{sec:multiformschema}

Uniform schema sharing provides data compatibility through a single
uniform version of schemas across all servers, and maintains the
ownership of schemas and provides controlled schema evolution. There
can also be cases that multiple sites need to adapt certain schema
to their own needs, and a uniform schema may not be feasible. To
provide flexible schema evolution at each Local Server and support
data compatibility on the Central Server, we provide a multiform
schema sharing approach.

As shown in Figure \ref{fig:publicdistributedschema}, a ``seed'' schema {\em
S} will be first created and made as public owned, and then published onto the
Central Server. Each Local Server will be able to import this schema, and
adjust the schema for its local use ({\em S$_{L1}$}, {\em S$_{L2}$}, etc.)
Schema updates from each site will be conditionally merged on the Central
Server as {\em S$_M$}. The goal of the merging  is to keep the schema version
on the Central Server mostly relaxed, through the following merging
conditions:

\begin{itemize}
  \item If the changes are incremental structural changes, they will be merged. These include
  adding of new fields or new categories;
  \item If the constraints on the Central Server are more permissive
   than the new or updated constraints that the modification suggests,
   then the suggested changes are ignored by the Central Server;
  \item Structural removal changes such as field removal or category removal
  will be ignored and not merged.
\end{itemize}

In this way, each Local Server will maintain its local schema evolution while
the Central Server will maintain a merged schema for shared data
compatibility.

\section{Collaborative Semantically Tagging of Data}\label{sec:tag}

Recently tagging has become a popular method to enable users to add
keywords to Internet resources, thus to improve search and personal
organization \cite{marlow06tag}. In SciPort, data are hierarchically
organized based on a tree based organizational structure. In
practice, it can be very helpful that users can provide additional
classification of data, by assigning tags from a controlled
vocabulary to documents. Each document can be flexibly annotated
with one or more semantic tags, and tags themselves can be shared by
users at both Local Servers and the Central Server.

Semantically tagging adds additional semantics to documents, which
not only provides semantics based query support, but also enhances
semantic interoperability of shared data from multiple distributed
sites.

\subsection{Tagging from Controlled Vocabulary}

Free tagging is used by most Web-based tagging systems, where users
can define arbitrary tags. One issue for free tagging is that since
there is no common vocabulary among these tags, there can be
semantic mismatch between tags.

Instead, SciPort chooses to annotate data using semantic tags coming
from predefined ontology or controlled vocabulary, such as NCI
Enterprise Vocabulary Services (EVS) \cite{ncievs}. By standardizing
tags using such controlled vocabulary, the system can then provide a
controlled  set of semantic tags. Thus data can be categorized into
multiple semantic groups, which makes it possible to express queries
based on common semantics. For instance, when a user authors a
document of a study on breast cancer,  he assigns  a tag
``Stage\_II\_Breast\_Cancer'' (ID: 18077), and another tag
``Cancer\_Risk'' (ID: 7768). A problem arises that expensive lookup
through vocabulary may simply prevent users from using it.

Next we show that with a collaborative tag management system, we can
provide automatic tag lookup in a controlled vocabulary repository
by caching previously retrieved tags in the Central Server with Ajax
technology.

%\begin{figure*}[t] \center
 %\framebox[3.3in][c]{
%\includegraphics[width=3.2in]{collaborativeTags}
%}  \caption{Collaborative Tag Management} \label{collaborativeTags}
%\end{figure*}

%\begin{figure*}[t] \center
 %\framebox[3.3in][c]{
%\includegraphics[width=3.2in]{taglookup}
%} \caption{An Example of Automatic Tag Lookup} \label{taglookup}
%\end{figure*}

\subsection{Collaborative Semantic Tag Management} \label{sec:coltag}

Caching tags is to exploit locality inherent to the subset of the
vocabulary that is used within a group of researchers. Since a
collaborative research consortium often focuses on solving a single
significant problem, the vocabulary is quite smaller than the
standardized vocabulary. For instance, the NCI Thesaurus
\cite{ncithesaurus} is 77MB in size.  In SciPort, we provide a
cached vocabulary repository on the Central Server, thus
previous-retrieved tags from the standardized vocabulary is shared
among all users.   Cached vocabulary on the Central Server makes it
very efficient to search for a tag in the vocabulary: instead of
searching for a tag at a remote large vocabulary all the time,
previous used tags in the tag cache repository can be searched
first.

Figure \ref{collaborativeTags} shows the architecture of
collaborative tag management. At each Local Server, there is a tag
repository that manages all tags on this Local Server; there is a
remote NCI controlled vocabulary database from which users can
dynamically search and retrieve tags. Once a tag is defined on the
Local Server, it will  be automatically cached at the Central Server
tag repository. When a user wants to associate a tag to its data, he
can dynamically search and select the tag, through automatic tag
lookup, as discussed next.

\subsection{Semantic Annotation of Documents with Tags}
By taking advantage of the Ajax technology, we provide automatic tag
lookup while a user wants to add a tag. As the user is typing in a
keyword on a web page to search for a tag, there will be an
automatic tag lookup from three resources: the local tag repository,
the cached/shared tag repository on the Central Server, and the NCI
controlled vocabulary. Implemented through Ajax, the lookup is
performed in the background, and retrieved tags are displayed in the
order of local tags, cached tags, and remote tags.  The lookup will
dynamically load a dropdown list of tags from which the user can
pick up (Figure \ref{taglookup}). By dynamically sending
asynchronous tag queries to tag repositories, users can immediately
select a desired tag to label his data, instead of opening multiple
browser windows to do separate searches.  With this technology, we
are able to support using tags from a controlled vocabulary or
shared repository by providing a convenient interface.

\subsection{Semantically Querying and Browsing Data through Semantic Tags}

Once documents are annotated with semantic tags, it is now possible
for users to semantically browse data by clicking on a semantic tag,
or use tagged fields as additional constraints for specifying
queries.  For example, a user might want to  search all documents
tagged with ``Stage\_II\_Breast\_Cancer'', and a type of ``Breast
Cancer'' can generate a drop down list of semantic tags and the user
can quickly use the right tag to specify queries.  Semantic
annotation can also help to classify data. Since semantic tags
coming from an ontology are hierarchically organized in the
ontology,  it is possible to generate an ontology tree based view of
all documents based on annotated ontology concepts on documents.

%\begin{figure*}[t] \center
%\framebox[4in][c]{
%\includegraphics[width=4in]{sciportfrontpage}
%}
%\caption{A Screenshot of a SciPort Local Server Deployed at University of California, Irvine} \label{sciportfrontpage}
%\end{figure*}

\section{Implementation}

\subsection{Software}

SciPort is built with J2EE and XML, running on Apache Tomcat servers
and Oracle Berkeley DB XML database server (open source) or IBM DB2
XML database. The system is OS neutral and has been tested on
Windows, Linux, and MacOS. It uses standard protocols, including
XML, XSLT, XPath and XQuery, and Web Services. SciPort is a
lightweight application and can be easily deployed and customized
by users.

SciPort is a rich Web-based application, thus it is possible for
users to use it at any place and at any time. SciPort supports major
Web browsers including Internet Explorer, Firefox, Opera and Safari.
Taking advantage of Web 2.0 technologies such as Ajax, SciPort
provides rich application capabilities with smooth user experience.

A salient characteristic of SciPort is that the system is highly
adaptable. Through customizable metadata schemas, hierarchy
organization, and sharing architecture, SciPort can be easily setup
for managing biomedical research data and providing a data sharing
network.

Figure \ref{sciportfrontpage} shows the screenshot of the front page
of a Local Server deployed at University of California, Irvine,
while the Central Server is located at Siemens Corporate Research
located at Princeton, New Jersey.

\subsection{Deployment}

SciPort was initially adopted by the Network for Translational
Research on Optical Imaging (NTROI) for collecting and sharing data
across several institutions (University of California, Irvine,
University of Pennsylvania, Datmouth, Stanford and University of
California, San Francisco. It is again adopted by the second cycle
of Network for Translational Research (Washington University,
University of Texas Health Science Center, Houston, University of
Michigan, and Stanford University).  SciPort is also used for
sharing pathology images and their annotations for a large scale
prostate cancer multi-modality study at University of Pennsylvania,
the State University of New Jersey, Rutgers, and Siemens Corporate
Research.  SciPort was also adopted for supporting Siemens
Healthcare for collecting and sharing large scale biomedical
research data from university and hospital research partners.

\section{Discussion}

The design and development of SciPort has been an iterative process
and driven by numerous discussions with biomedical researchers and
users. During the process, we have learned many lessons.

\textbf{Usability.}  A critical requirement for software tools from
biomedical researchers is the usability of the system. This includes
intuitive user interfaces and workflows for data authoring, sharing
and querying, and the ease of system setup. When the initial version
of SciPort was released, the pilot users complained about multiple
clicks needed to navigate through multiple web pages, and showed
strong desires of simpler interfaces and fast response. Especially,
a single click data publishing is desired, otherwise users gradually
get frustrated to share their data.   The Web based user interfaces
then evolved from static web pages (jumping from one page to
another) based interface to Ajax based interface, and then another
Flex based interface is developed to provide even smoother user
experience. Our conclusion is that smooth user experience of data
sharing tools could much improve the interest for researchers to
share their data.

\textbf{Generalization and Customization.} Although SciPort is
currently a software platform and is not tied to specific
applications, the initial version of SciPort (Version 1.0) was
designed and developed for one single project with static data
forms. Soon we realized that even for a single project, the schemas
were dynamic, and new data forms were occasionally required. And
researchers from other projects were using totally different data
forms. Besides, the data are heterogenous, ranging from structural
data to medical images, to  files, etc. This motivated us to
redesign SciPort as a platform that could provide easy and flexible
customization. This is challenging as schema evolution is very
difficult to support in traditional relational database management
systems based on tables. The emergence of native XML database
technologies makes it possible to support customizable schemas, as
native XML DBMSs have a significant advantage on supporting schema
evolution. Our data models, queries and data management are fully
based on XML.

\textbf{Integration with Other Systems.} In the past, we also worked
on extending SciPort so data managed in SciPort could be integrated
into other infrastructures such as caBIG. We developed a
SciPort-NBIA \cite{nbia} bridge to support such integration.

\section{Related Work}

Computer supported collaborative work has been increasingly used to
support research collaborations. A review of collaborative systems
is presented in \cite{bafoutsou2002281}, and a review of taxonomy of
collaboratory types is discussed \cite{zimmerman07taxonomy}. SciPort
belongs to the Community Data Systems based on this classification.
Lee et al review collaboratory concepts relevant for collaborative
biomedical research \cite{lee09} and analyze the major challenges.
In \cite{myneni10col}, a collaborative information management system
is discussed.  A context-based sharing system is proposed in
\cite{chin04context} to support more data-centric collaboration than
tools oriented ones, and this motivates our metadata oriented
approach for data modeling and sharing in SciPort.

With the increasing collaboration of scientific research,
collaborative cyberinfrastructures have been researched and
developed.  Grid-based systems(such as caBIG{\small \textregistered}
--cancer Biomedical Informatics Grid \cite{cabig}, Biomedical
Informatics Research Network (BIRN) \cite{birn}) provide
infrastructures to integrate existing computing and data resources.
They rely on a top down common data structures. The iPlant
Collaborative (iPC) \cite{pscic}  is a cyberinfrastructure project
recently funded by US NSF. iPlant has a more focus on the human side
of the infrastructure. myGrid \cite{mygrid} is a suite of tools for
e-Science, with a focus on workflows.   A review on
cyberinfrastructure systems for the biological sciences  is
discussed in \cite{stein08}.  Grid based systems are more used on
sharing computing and storage resources, P2P is more used on sharing
data \cite{foster03p2p2grid}.  MIRC \cite{mirc} is an example of P2P
based data system for authoring and sharing radiology  teaching
files.

While Grid based systems are more used on sharing computing and storage
resources, P2P is more used on sharing data \cite{foster03p2p2grid}.  MIRC
\cite{mirc} is a popular pure-P2P based system for authoring and sharing
teaching files.

A publish and subscribe architecture for distributed metadata management is
discussed in \cite{keidl02metadata}, which focuses on the synchronization
problems. In \cite{taylor06reconcile}, an approach of bottom-up collaborative
data sharing is proposed, where each group independently manages and extends
their data, and  the groups compare and reconcile their changes eventually
while tolerating disagreement. Our approach takes an approach in between the
bottom-up and top-down approaches, where each group manages their data, but
also achieves as much agreement on schemas as possible through controlled
schema evolution.

In \cite{rader08tag}, influence on tag choices is analyzed from
del.icio.us. Our approach focuses on semantic tagging from a
controlled vocabulary instead of free tags.  In \cite{pike07},
different approaches for representing scientific knowledge is
discussed.

Extensive work has been done in data integration and schema
integration \cite{halevy06integration,doan05semantic}. In
\cite{beynon97}, a collaborative schema integration system is
discussed for database design. Our system takes a proactive approach
where schema and data consistency is enforced during data authoring
and schema authoring.

\section{Conclusion}

Contemporary biomedical research is moving towards
multi-disciplinary, multi-institutional collaboration. These lead to
strong demand for tools and systems to share biomedical data. This
drives the development of SciPort -- a Web-based data sharing
platform for collaborative biomedical research. To support
meaningful abstraction of data, SciPort provides a generic metadata
model for users to conveniently define their own metadata schemas.
SciPort provides an innovative lightweight hybrid data sharing
architecture which combines the benefits of the centralized approach
and the distributed approach. Investigators are able to flexibly
manage their data and schema sharing, and quickly build data sharing
networks. To enable data consistency for data sharing, SciPort
provides comprehensive collaborative distributed schema management.
Through semantic tagging, SciPort further enhances semantic
interoperability of shared data from distributed sites.

%\section*{Acknowledgement}
%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliography{ijmso}
%\bibliographystyle{unsrt}
%\bibliographystyle{alpha}

\begin{thebibliography}{10}

\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
for collaborative scientific research: a research information
management system', {\it International Journal of Information
Management}, Vol. 30, No. 3, pp.256--264

\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
financial conflicts of interest in biomedical research: a systematic
review', {\it JAMA}, Vol. 289, No. 19, pp.454--65

\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
sciences: progress, visions and challenges', {\it Nature Reviews
Genetics}, Vol. 9, No. 9, pp.678--688.

\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
NIH Statement on Sharing Scientific Research Data,
http://grants.nih.gov/grants/policy/data\_sharing/

\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
genome-wide association studies}{2008}]{nih08policy} Policy for
sharing of data obtained in NIH supported or conducted genome-wide
association studies,
http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html

\bibitem[\protect\citeauthoryear{Network for Translational Research (NTR): Optical Imaging in
Multimodality
Platforms}{http://imaging.cancer.gov/programsandresources/speci\break
alizedinitiatives/ntroi}]{ntr} Network for Translational Research
(NTR): Optical Imaging in Multimodality Platforms,
http://imaging.cancer.gov/programsandresources/specializedinitiatives/ntroi

\bibitem[\protect\citeauthoryear{Piwowar~et~al.}{2008}]{piwowar08culture}
Piwowar, H., Becich, M., Bilofsky, H. and Crowley, R. (2008) `PLoS
medicine', {\it Sept, No. 9, Towards a Data Sharing Culture:
Recommendations for Leadership from Academic Health Centers},
Vol.~5.

\bibitem[\protect\citeauthoryear{Birnholtz et al.}{2003}]{birnholtz03data}
Birnholtz, J.P. and Bietz, M.J. (2003) `Data at work: supporting
sharing in science and engineering', {\it GROUP}, pp.339--348.

\bibitem[\protect\citeauthoryear{Data Sharing \& Intellectual Capital (DSIC) Workspace}
{https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG}]{dsic} Data
Sharing \& Intellectual Capital (DSIC) Workspace,
https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG

\bibitem[\protect\citeauthoryear{Getting Connected with
caBIG}{https://cabig.nci.nih.gov/getting\_connected/}]{cabigconnected}
Getting Connected with caBIG, https://cabig.nci.nih.gov/\break
getting\_connected/

\bibitem[\protect\citeauthoryear{Digital Imaging and Communications in Medicine
(DICOM)}{http://medical.nema.org/}]{dicom} Digital Imaging and
Communications in Medicine (DICOM), http://medical.nema.org/

\bibitem[\protect\citeauthoryear{The Cancer Genome Atlas (TCGA) Data Portal}{http://cancergenome.nih.gov/dataportal}]{tcga}
The Cancer Genome Atlas (TCGA) Data Portal,
http://cancergenome.nih.gov/dataportal

\bibitem[\protect\citeauthoryear{National Biomedical Imaging
Archive}{https://cabig.nci.nih.gov/tools/NCIA}]{nbia} National
Biomedical Imaging Archive, https://cabig.nci.nih.gov/tools/NCIA

\bibitem[\protect\citeauthoryear{caBIG: cancer Biomedical Informatics Grid}{http://caBIG.nci.nih.gov/}]{cabig}
caBIG: cancer Biomedical Informatics Grid, http://caBIG.nci.nih.gov/

\bibitem[\protect\citeauthoryear{Biomedical Informatics Research Network}{
http://www.nbirn.net/}]{birn}
Biomedical Informatics Research Network, http://www.nbirn.net/

\bibitem[\protect\citeauthoryear{Cyberinfrastructure for the Biological Sciences: Plant Science
Cyberinfrastructure Collaborative
(PSCIC)}{http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm}]{pscic}
Cyberinfrastructure for the Biological Sciences: Plant Science
Cyberinfrastructure Collaborative (PSCIC),
http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm

\bibitem[\protect\citeauthoryear{MIRC}{http://mirc.rsna.org}]{mirc}
MIRC, http://mirc.rsna.org

\bibitem[\protect\citeauthoryear{Foster and
Iamnitchi}{2003}]{foster03p2p2grid} Foster, I. and Iamnitchi, A.
(2003) `On death, taxes, and the convergence of peer-to-peer and
grid computing', {\it IPTPS'03}.

\bibitem[\protect\citeauthoryear{Keidl et al.}{2002}]{keidl02metadata}
Keidl, M., Kreutz, A., Kemper, A. and Kossmann, D. (2002) `A publish
{\&} subscribe architecture for distributed metadata management',
{\it ICDE}.

\bibitem[\protect\citeauthoryear{Taylor and Ives}{2006}]{taylor06reconcile}
Taylor, N.E. and Ives, Z.G. (2006) `Reconciling while tolerating
disagreement in collaborative data sharing', {\it SIGMOD}.

\bibitem[\protect\citeauthoryear{Rader and Wash}{2008}]{rader08tag}
Rader, E.J. and Wash, R. (2008) {\it CSCW}, pp.239-248, Influences
on tag choices in del.icio.us.

\bibitem[\protect\citeauthoryear{Halevy et~al.}{2006}]{halevy06integration}
Halevy, A., Rajaraman, A. and Ordille, J. (2006) {\it VLDB, Data
integration: the teenage years},
http://portal.acm.org/citation.cfm?id=1182635.1164130

\bibitem[\protect\citeauthoryear{Doan and Halevy}{2005}]{doan05semantic}
Doan, A. and Halevy, A.Y. (2005) Semantic Integration Research in
the Database Community: A Brief Survey, {\it AI Magazine}, Vol. 26,
No. 1, pp.83--94.

\bibitem[\protect\citeauthoryear{Beynon-Davies et~al.}{1997}]{beynon97}
Beynon-Davies, P., Bonde, L., McPhee, D. and Jones, C.B. (1997) `A
collaborative schema integration system', {\it Comput. Supported
Coop. Work}, Vol. 6, No. 1, Norwell, MA, USA, pp.1--18, issn =
0925-9724.

\bibitem[\protect\citeauthoryear{Wang and Vergara-Niedermayr}{2008}]{wang08com}
Wang, F. and Vergara-Niedermayr, C. (2008) `Collaboratively Sharing
Scientific Data', {\it CollaborateCom}, pp.805--823.

\bibitem[\protect\citeauthoryear{Chin and Lansing}{2004}]{chin04context} Chin Jr., G. and Lansing,
C.S. (2008) `Capturing and Supporting Contexts for Scientific Data
Sharing via the Biological Sciences Collaboratory', {\it CSCW}, ISBN
1-58113-810-5.

\bibitem[\protect\citeauthoryear{W3C XML Query (XQuery)}{http://www.w3.org/XML/Query}]{xquery}
W3C XML Query (XQuery), http://www.w3.org/XML/Query

\bibitem[\protect\citeauthoryear{Wang et al.}{2009}]{wang09security}
Wang, F., Hussels, P. and Liu, P. (2009) `Securely and flexibly
sharing a biomedical data management system', {\it SPIE}.

 \end{thebibliography}
\end{document}

### 2015-11-22 Docs/IJES/journal.tex
including initial version of IJES

--- 2015-10-25 Docs/TODAES/paper.tex
@@
-\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax
+%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{doublecol-new}
+%%%%%%%%%%%%%%%%%%%%%%
 
-\usepackage{listings} % Codes
-%\lstset{
- % language=C,                % choose the language of the code
- % numbers=left,                   % where to put the line-numbers
- % stepnumber=1,                   % the step between two line-numbers.        
- % numbersep=5pt,                  % how far the line-numbers are from the code
- % backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
- % showspaces=false,               % show spaces adding particular underscores
- % showstringspaces=false,         % underline spaces within strings
- % showtabs=false,                 % show tabs within strings adding particular underscores
- % tabsize=2,                      % sets default tabsize to 2 spaces
- % captionpos=b,                   % sets the caption-position to bottom
- % breaklines=true,                % sets automatic line breaking
- % breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
- % title=\lstname,                 % show the filename of files included with \lstinputlisting;
+\usepackage{natbib,stfloats}
+\usepackage{mathrsfs}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{tabularx}
+\usepackage{listings}
+\renewcommand{\lstlistingname}{Algorithm}
+
+\def\newblock{\hskip .11em plus .33em minus .07em}
+
+\theoremstyle{TH}{
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}[lemma]{Theorem}
+\newtheorem{corrolary}[lemma]{Corrolary}
+\newtheorem{conjecture}[lemma]{Conjecture}
+\newtheorem{proposition}[lemma]{Proposition}
+\newtheorem{claim}[lemma]{Claim}
+\newtheorem{stheorem}[lemma]{Wrong Theorem}
+\newtheorem{algorithm}{Algorithm}
+}
+
+\theoremstyle{THrm}{
+\newtheorem{definition}{Definition}[section]
+\newtheorem{question}{Question}[section]
+\newtheorem{remark}{Remark}
+\newtheorem{scheme}{Scheme}
+}
+
+\theoremstyle{THhit}{
+\newtheorem{case}{Case}[section]
+}
+
+\makeatletter
+\def\theequation{\arabic{equation}}
+
+%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
+%Processing,
+%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
+%
+%\def\BottomCatch{%
+%\vskip -10pt
+%\thispagestyle{empty}%
+%\begin{table}[b]%
+%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
+%\\[-12pt]
+%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
+%\end{tabular*}%
+%\vskip -30pt%
+%%%\vskip -35pt%
+%\end{table}%
 %}
+\makeatother
 
-\usepackage{mathtools} % Serve para as equacoes
+%%%%%%%%%%%%%%%%%
+\begin{document}%
+%%%%%%%%%%%%%%%%%
 
-%Montar os Gráficos, cores e divisões.
-\usepackage{color}
-\usepackage{multirow}
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{booktabs}
-\usepackage{tabu,xcolor,colortbl}
-\usepackage{rotating}
-\usepackage{amsmath,array}  
-\usepackage{tabularx} % in the preamble
-\usepackage{graphicx} %Imagens
-\renewcommand{\lstlistingname}{Algorithm}
-%\usepackage{minted}
-%\usemintedstyle{bw}
+\setcounter{page}{1}
 
-\newcolumntype{C}[1]{>{\Centering}m{#1}}
-\renewcommand\tabularxcolumn[1]{C{#1}}
-\usepackage{tabularx,ragged2e,booktabs,caption}
+\LRH{A. Trindade et~al.}
 
-%\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-%\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
+\RRH{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
 
-\usepackage{hyphenat}
-\hyphenation{ESBMC par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }
+\VOL{x}
 
-% Package to generate and customize Algorithm as per ACM style
-\usepackage[ruled]{algorithm2e}
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
+\ISSUE{x}
 
-%\usepackage[skip=\baselineskip]{caption}
-%\captionsetup[lstlisting]{font={small,tt}}
+\PUBYEAR{xxxx}
 
-% Metadata Information
-\acmVolume{9}
-\acmNumber{4}
-\acmArticle{39}
-\acmYear{2015}
-\acmMonth{3}
+\BottomCatch
 
-% Copyright
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
+%\CLline
 
-% DOI
-\doi{0000001.0000001}
+\PUBYEAR{2012}
 
-%ISSN
-\issn{1234-56789}
-
-% Document starts
-\begin{document}
-
-% Page heads
-\markboth{A. Trindade et al.}{Multi-Core Model Checking and Maximum Satisfiability Applied to HW/SW Partitioning}
+\subtitle{}
 
@@
 
-% Title portion
-\author{
-Alessandro Trindade
-\affil{Federal University of Amazonas}
-Hussama Ismail
-\affil{Federal University of Amazonas}
-Edilson Galv\~ao\
-\affil{Federal University of Amazonas}
-Renato Degelo\
-\affil{Federal University of Amazonas}
-Helder Silva
-\affil{Federal University of Amazonas}
-Lucas Cordeiro\affil{Federal University of Amazonas}
-}
+\authorA{Alessandro Trindade, Hussama Ismail}
+\affA{Federal University of Amazonas \\
+E-mail: \{alessandro.b.trindade, hussamaismail\}@gmail.com}
 
-% NOTE! Affiliations placed here should be for the institution where the
-%       BULK of the research was done. If the author has gone to a new
-%       institution, before publication, the (above) affiliation should NOT be changed.
-%       The authors 'current' address may be given in the "Author's addresses:" block (below).
-%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
-%       currently affiliated with NASA.
+\authorB{Edilson Galv\~ao, Renato Degelo}
+\affB{Federal University of Amazonas \\
+E-mail: \{rdegelo, esj.galvao\}@gmail.com}
+
+\authorC{Helder Silva, and Lucas Cordeiro}
+\affC{Federal University of Amazonas \\
+E-mail: prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br}
 
@@
 
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
+\KEYWORD{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}
 
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10010583.10010682.10010684.10010686</concept_id>
-<concept_desc>Hardware~Hardware-software codesign</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010583.10010682.10010712.10010715</concept_id>
-<concept_desc>Hardware~Software tools for EDA</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
-<concept_desc>Software and its engineering~Model checking</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10010940.10010992.10010998.10010999</concept_id>
-<concept_desc>Software and its engineering~Software verification</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
+\REF{to this paper should be made as follows: Rodr\'{\i}guez
+Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
+corporate environmental disclosures on the internet: the case of
+IBEX 35 Spanish companies', {\it International Journal of Metadata,
+Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}
 
-\ccsdesc[500]{Hardware~ Hardware-software codesign}
-\ccsdesc[500]{Hardware~ Software tools for EDA}
-\ccsdesc[500]{Software and its engineering~ Model checking}
-\ccsdesc[500]{Software and its engineering~ Software verification}
+\begin{bio}
+\textcolor{red}{
+Manuel Pedro Rodr\'iguez Bol\'ivar received his PhD in Accounting at
+the University of Granada. He is a Lecturer at the Department of
+Accounting and Finance, University of Granada. His research
+interests include issues related to conceptual frameworks of
+accounting, diffusion of financial information on Internet, Balanced
+Scorecard applications and environmental accounting. He is author of
+a great deal of research studies published at national and
+international journals, conference proceedings as well as book
+chapters, one of which has been edited by Kluwer Academic
+Publishers.\vs{9}}
 
-%
-% End generated code
-%
+\textcolor{red}{\noindent Bel\'en Sen\'es Garc\'ia received her PhD in Accounting at
+the University of Granada. She is a Lecturer at the Department of
+Accounting and Finance, University of Granada. Her research
+interests are related to cultural, institutional and historic
+accounting and in environmental accounting. She has published
+research papers at national and international journals, conference
+proceedings as well as chapters of books.\vs{8}}
 
-%\terms{Design, Algorithms, Performance}
-
-\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}
-
-%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
-%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
-%designed for  wireless sensor network applications.}
-% At a minimum you need to supply the author names, year and a title.
-% IMPORTANT:
-% Full first names whenever they are known, surname last, followed by a period.
-% In the case of two authors, 'and' is placed between them.
-% In the case of three or more authors, the serial comma is used, that is, all author names
-% except the last one but including the penultimate author's name are followed by a comma,
-% and then 'and' is placed before the final author's name.
-% If only first and middle initials are known, then each initial
-% is followed by a period and they are separated by a space.
-% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
-
-\begin{bottomstuff}
-A. Trindade, H. Ismail, R. Degelo, and E. Galv\~ao \\
-Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
-\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ 
-\\
-H. Silva, and L. Cordeiro \\
-Federal University of Amazonas, Brazil\\
-prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br      \\
-\end{bottomstuff}
+\textcolor{red}{\noindent Both authors have published a book about environmental
+accounting edited by the Institute of Accounting and Auditing,
+Ministry of Economic Affairs, in Spain in October 2003.}
+\end{bio}
 
@@
 
-%---------------------------------
 \section{Introduction}
-\label{Introduction}
-%---------------------------------
 
@@
 
-%In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}.
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined.
-This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}.
-Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors.
-Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-The system models are accompanied by algorithms that systematically explore all the states of the system model.
-
 Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
@@
 The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
-
-%Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}.
-In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}.
-However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.
 
@@
 
-% in which its main function is to check the satisfiability of logical formulas based on objective functions
+\subsection{Contributions}
 
-\textbf{Contributions.} The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
+The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
 Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
@@
 
-\textbf{Availability of Data and Tools.
-}Our experiments are based on a set of publicly available benchmarks.
-All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.
+\subsection{Availability of Data and Tools}
+
+Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.
 
@@
 
-%----------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Background}
 \label{background}
-%----------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}.
-%In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages.
-The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit.
-Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
 There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}.
@@
 Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}.
-In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
+In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
 GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$), which are checked for satisfiability by an SMT solver.
@@
 	\centering
-  \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
+	\includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
 	\caption{ESBMC architecture.}
@@
 
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%               framesep=2mm]{matlab}
-%int k;
-%#pragma omp parallel for
-%for (k = 0; k < 10; k++)
-%  a[k] = 2*k;
-%\end{minted}
-%\caption{OpenMP basic Example.}
-%\label{lst:example}
-%\end{listing}
-
 \vspace{2 mm}
-\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
 int k;
@@
 %----------------------------------------------
-
-%SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.
 
@@
 
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%              framesep=2mm]{c++}
-%(Declare-Const K Int) 
-%(Declare-Const W Int)
-%(assert (< K 2)) 
-%(assert (< (- W K) 1))
-%(maximize (+ K W)) 
-%(check-sat)
-%\end{minted}
-%\caption{Example of SMT formula using $\nu$Z.}
-%\label{vZ}
-%\end{listing}
-
 \vspace{2 mm}
@@
 	\centering
-  \includegraphics[scale=0.3]{figures/vzArch.png} 
+  \includegraphics[scale=0.21]{figures/vzArch.png} 
 	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
@@
 and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
-%
-%
-%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
+
 \begin{align}
@@
 \label{hw-sw-partitioning}
-s\left(1-x\right) + c|EX| \leq S_0, 
+s\left(1-x\right) + c|Ex| \leq S_0, 
 \end{align}
@@
 
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%               framesep=2mm]{c++}
-% Initialize Variables 
-% Declare number of nodes and edges
-% Declare hardware cost of each node as array (h)
-% Declare software cost of each node as array (s)
-% Declare communication cost of each edge (c)
-% Declare the initial software cost of (S0)
-% Declare transposed incidence matrix graph G (E)
-% Define the solutions variable (Xi) as Boolean
-% main {
-%  For TipH = 0 to Hmax Do {
-%   populate Xi with nondeterministic/test values
-%   Calculate s(1-x)+c|Ex| and store at variable
-%   Requirement isued by Assume (Variable <= S0)
-%   Calculate Hp cost Based on value tested of Xi
-%   Violation check with Assert(Hp > TipH)
-%  }
-% }
-%\end{minted}
-%\caption{Pseudocode describing sequential ESBMC}
-%\label{Pseudocode-describing-ESBMC}
-%\end{listing}
-
 \vspace{2 mm}
@@
 
-%In the multi-core ESBMC algorithm, the only difference is the fact that the value of $ TipH $ and its range is not declared in the algorithm, %as shown in ESBMC Pseudocode.
-The proposed approach is invoked for each test problem, as follows:
-%$ esbmc-parallel <Filename.c> \; <hminvalue> \; <Hmax> $
-
-%Where $ <Filename.c> $ is the optimization problem described in ANSI-C format, $  <hminvalue> $ is the minimum (zero to HW-SW partitioning %problem) and $ <Hmax> $ is the maximum hardware cost for the specified problem.
-
-%Therefore, the algorithm starts different ESBMC instances using different optimization values, in ascending order, for $ Hmax $ in order to %find a violation.
-If all instances finish and no violation is found, then multi-core ESBMC starts new $ N $ instances.
-When a violation is %found, it reports time and hardware cost.
-If multi-core ESBMC tests all the possibilities for the hardware cost and has not found a violation, %then it reports: $ Violation not found $.
-
 %----------------------------------------------
@@
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
+
 \begin{figure}[h]
 	\centering
-  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
+  \includegraphics[scale=0.77]{figures/esbmc-ss.pdf} 
 	\caption{ESBMC-SS approach.}
@@
 	\centering
-  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
+  \includegraphics[scale=0.77]{figures/esbmc-ps.pdf} 
 	\caption{ESBMC-PS approach.}
@@
 	\centering
-  \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
+  \includegraphics[scale=0.77]{figures/esbmc-pb.pdf} 
 	\caption{ESBMC-PB approach.}
@@
 
-\begin{figure}[ht]
+\begin{figure}[h!]
 	\centering
-  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
+  \includegraphics[scale=0.17]{figures/Fig4.png}
 	\caption{Binary step calculation.}
@@
 
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%               framesep=2mm]{c++}
-%  GetNextStep(){
-%  int largestChunk = -1;
-%  chunk largest;
-%  for each(chunk in chunks){
-%     if(chunk.right - chunk.left > largestChunk){
-%           largestChunk = chunk.right - chunk.left;
-%           largest = chunk;
-%     }
-%   }	
-%   chunks.remove(largest);	
-%   int median = largest.left + floor((largest.right - largest.left) / 2)
-%   if(median > 0){
-%      if(largest.right - largest.left > 1)
-%         chunks.add(new chunk(largest.left, median - 1));	
-%      if(largest.right != largest.left)
-%         chunks.add(new chunk(median + 1, largest.right);
-%    }
-%   return median;
-% }
-%\end{minted}
-%\caption{Steps calculation using intervals.}
-%\label{Steps-Calculation-using-Intervals}
-%\end{listing}
 \vspace {2 mm}
@@
 At the end, the median is returned.
-
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%               framesep=2mm]{c++}
-% step = controller.GetNextStep();
-% int pid = ExecuteStep(step);
-% while(isRunning(pid)){
-%   if(!controller.isNeeded(step))
-%    kill(pid);
-% }
-%\end{minted}
-%\caption{Worker sample.}
-%\label{worker-sample}
-%\end{listing}
 
@@
 Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
-%\begin{listing}[H]
-%\begin{minted}[mathescape,
-%               linenos,
-%               numbersep=7pt,
-%               gobble=0,
-%               frame=lines,
-%               framesep=2mm]{c++}
-%--Initialize Variables
-%  Create vZ context 
-%  Create binary vector (x)
-%  Declare number of nodes, edges and S0
-%  Declare hardware cost of each node as array (h) 
-%  Declare software cost of each node as array (s)
-%  Declare communication cost of each edge (c)
-%  Declare transposed incidence matrix graph G (E)
-%--Arithmetic Expressions
-%  SC = s(1-x)
-%  CMC = c*|EX|
-%  Fobj =  x[i] * h[i]
-%--Assert Constraints
-%  Add constraints (SF + CMC <= S0)
-%  Add constraints to minimize Fobj
-%  Check Model
-%  Print Result
-%\end{minted}
-%\caption{Pseudocode describing ESBMC-$\nu$Z.}
-%\label{vZ-pseudocode}
-%\end{listing}
 
@@
 A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
-
-%----------------------------------------------
-\subsection{Description of Benchmarks}
-\label{Benchmarks-Description}
-%----------------------------------------------
-
-\vspace{1.5 mm}
-\begin{minipage}{\linewidth}
-\centering
-\small
-\sffamily\small
-\tabulinesep=4pt
-\captionof{table}{Description of Benchmarks.} 
-\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{8.9cm}}
-\\
-\toprule[1.5pt]
-\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
-\midrule
-\\
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
-\\
-\hline
-\\
-\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
-\\
-\hline
-\\
-\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
-\\
-\hline
-\\
-\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
-\\
-\hline
-\\
-\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
-\\
-\bottomrule[1.5pt]
-\label{tab:Description-of-Benchmarks} 
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
-The nodes in the graphs correspond to high-level language instructions.
-Software and communication costs are time dimensional, and hardware costs represent the occupied area.
-The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
-The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
-From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
-
-%\begin{table}[h]
-%\centering
-%\caption {Description of Benchmarks.}
-%\small
-%\sffamily\small
-%\tabulinesep=6pt
-
-%\label{Description-of-Benchmarks}
-%\end{table}
-
-%----------------------------------------------
-\subsection{Experimental Results}
-\label{Experimental-Results}
-%----------------------------------------------
-%
-\begin{table*}[h]
-  \centering
-  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
-  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
-\\
- &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
-\cmidrule(r){3-9}
-
-&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
-&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
-&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\
-
-%EXACT Solution
-\bottomrule[1.5pt]
-\rowcolors{1}{}{lightgray}
-
-\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
-& & & & & & & & & \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
-&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
-& & & & & & & & & \\
-
-\bottomrule[1.5pt]
-%ILP
-\multirow{4}{*}{\textbf{\normalsize{ILP}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%GA
-\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
-&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%MultiCore ESBMC
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC Parallel sequential
-\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%ESBMC Parallel Binary
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-\hline
-
-%vZ
-\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
-& & & & & & & & & \\
-&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
-&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
-& & & & & & & & & \\
-
-\bottomrule[1.5pt]
-\end{tabular}
-\label{Experimental-results-of-the-complex-benchmarks}
-\end{table*}
-
-Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}SS, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.
-
-There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
-In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
-
-In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks.
-When ILP produces a result, it provides the optimal solution.
-On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by ESBMC-$\nu$Z.
-On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.
-
-Note further that all multi-core ESBMC implementations produce better results than the sequential one.
-In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase.
-One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $2$.$5$ times slower than ESBMC-$\nu$Z.
-However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools.
-When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
-
-%When ESBMC-$\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$8$ ({\it e.g.}, Clustering).
-
-The only technique that is able to solve all benchmarks is GA; however, its precision is not satisfactory since it produces an error rate between $-37.6$\% and $29.0$\%.
-
-Note that RC$6$ produced timeouts for all implementations of ESBMC; GA did not produce the correct answer, and ILP solves correctly most benchmarks, except for Mars and Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution.
-No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.
-
-The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ---- Bibliography ---- %
-%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section*{Acknowledgement}
+%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.
 
-\bibliographystyle{ACM-Reference-Format-Journals}
-\bibliography{Ref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%\bibliography{ijmso}
+%\bibliographystyle{unsrt}
+%\bibliographystyle{alpha}
+
+\begin{thebibliography}{10}
+
+\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
+Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
+for collaborative scientific research: a research information
+management system', {\it International Journal of Information
+Management}, Vol. 30, No. 3, pp.256--264
+
+\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
+Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
+financial conflicts of interest in biomedical research: a systematic
+review', {\it JAMA}, Vol. 289, No. 19, pp.454--65
+
+\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
+Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
+sciences: progress, visions and challenges', {\it Nature Reviews
+Genetics}, Vol. 9, No. 9, pp.678--688.
+
+\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
+Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
+NIH Statement on Sharing Scientific Research Data,
+http://grants.nih.gov/grants/policy/data\_sharing/
+
+\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
+genome-wide association studies}{2008}]{nih08policy} Policy for
+sharing of data obtained in NIH supported or conducted genome-wide
+association studies,
+http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html
+
+\bibitem[\protect\citeauthoryear{Network for Translational Research (NTR): Optical Imaging in
+Multimodality
+Platforms}{http://imaging.cancer.gov/programsandresources/speci\break
+alizedinitiatives/ntroi}]{ntr} Network for Translational Research
+(NTR): Optical Imaging in Multimodality Platforms,
+http://imaging.cancer.gov/programsandresources/specializedinitiatives/ntroi
+
+\bibitem[\protect\citeauthoryear{Piwowar~et~al.}{2008}]{piwowar08culture}
+Piwowar, H., Becich, M., Bilofsky, H. and Crowley, R. (2008) `PLoS
+medicine', {\it Sept, No. 9, Towards a Data Sharing Culture:
+Recommendations for Leadership from Academic Health Centers},
+Vol.~5.
+
+\bibitem[\protect\citeauthoryear{Birnholtz et al.}{2003}]{birnholtz03data}
+Birnholtz, J.P. and Bietz, M.J. (2003) `Data at work: supporting
+sharing in science and engineering', {\it GROUP}, pp.339--348.
+
+\bibitem[\protect\citeauthoryear{Data Sharing \& Intellectual Capital (DSIC) Workspace}
+{https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG}]{dsic} Data
+Sharing \& Intellectual Capital (DSIC) Workspace,
+https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG
+
+\bibitem[\protect\citeauthoryear{Getting Connected with
+caBIG}{https://cabig.nci.nih.gov/getting\_connected/}]{cabigconnected}
+Getting Connected with caBIG, https://cabig.nci.nih.gov/\break
+getting\_connected/
+
+\bibitem[\protect\citeauthoryear{Digital Imaging and Communications in Medicine
+(DICOM)}{http://medical.nema.org/}]{dicom} Digital Imaging and
+Communications in Medicine (DICOM), http://medical.nema.org/
+
+\bibitem[\protect\citeauthoryear{The Cancer Genome Atlas (TCGA) Data Portal}{http://cancergenome.nih.gov/dataportal}]{tcga}
+The Cancer Genome Atlas (TCGA) Data Portal,
+http://cancergenome.nih.gov/dataportal
+
+\bibitem[\protect\citeauthoryear{National Biomedical Imaging
+Archive}{https://cabig.nci.nih.gov/tools/NCIA}]{nbia} National
+Biomedical Imaging Archive, https://cabig.nci.nih.gov/tools/NCIA
+
+\bibitem[\protect\citeauthoryear{caBIG: cancer Biomedical Informatics Grid}{http://caBIG.nci.nih.gov/}]{cabig}
+caBIG: cancer Biomedical Informatics Grid, http://caBIG.nci.nih.gov/
+
+\bibitem[\protect\citeauthoryear{Biomedical Informatics Research Network}{
+http://www.nbirn.net/}]{birn}
+Biomedical Informatics Research Network, http://www.nbirn.net/
+
+\bibitem[\protect\citeauthoryear{Cyberinfrastructure for the Biological Sciences: Plant Science
+Cyberinfrastructure Collaborative
+(PSCIC)}{http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm}]{pscic}
+Cyberinfrastructure for the Biological Sciences: Plant Science
+Cyberinfrastructure Collaborative (PSCIC),
+http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm
+
+\bibitem[\protect\citeauthoryear{MIRC}{http://mirc.rsna.org}]{mirc}
+MIRC, http://mirc.rsna.org
+
+\bibitem[\protect\citeauthoryear{Foster and
+Iamnitchi}{2003}]{foster03p2p2grid} Foster, I. and Iamnitchi, A.
+(2003) `On death, taxes, and the convergence of peer-to-peer and
+grid computing', {\it IPTPS'03}.
+
+\bibitem[\protect\citeauthoryear{Keidl et al.}{2002}]{keidl02metadata}
+Keidl, M., Kreutz, A., Kemper, A. and Kossmann, D. (2002) `A publish
+{\&} subscribe architecture for distributed metadata management',
+{\it ICDE}.
+
+\bibitem[\protect\citeauthoryear{Taylor and Ives}{2006}]{taylor06reconcile}
+Taylor, N.E. and Ives, Z.G. (2006) `Reconciling while tolerating
+disagreement in collaborative data sharing', {\it SIGMOD}.
+
+\bibitem[\protect\citeauthoryear{Rader and Wash}{2008}]{rader08tag}
+Rader, E.J. and Wash, R. (2008) {\it CSCW}, pp.239-248, Influences
+on tag choices in del.icio.us.
+
+\bibitem[\protect\citeauthoryear{Halevy et~al.}{2006}]{halevy06integration}
+Halevy, A., Rajaraman, A. and Ordille, J. (2006) {\it VLDB, Data
+integration: the teenage years},
+http://portal.acm.org/citation.cfm?id=1182635.1164130
+
+\bibitem[\protect\citeauthoryear{Doan and Halevy}{2005}]{doan05semantic}
+Doan, A. and Halevy, A.Y. (2005) Semantic Integration Research in
+the Database Community: A Brief Survey, {\it AI Magazine}, Vol. 26,
+No. 1, pp.83--94.
+
+\bibitem[\protect\citeauthoryear{Beynon-Davies et~al.}{1997}]{beynon97}
+Beynon-Davies, P., Bonde, L., McPhee, D. and Jones, C.B. (1997) `A
+collaborative schema integration system', {\it Comput. Supported
+Coop. Work}, Vol. 6, No. 1, Norwell, MA, USA, pp.1--18, issn =
+0925-9724.
+
+\bibitem[\protect\citeauthoryear{Wang and Vergara-Niedermayr}{2008}]{wang08com}
+Wang, F. and Vergara-Niedermayr, C. (2008) `Collaboratively Sharing
+Scientific Data', {\it CollaborateCom}, pp.805--823.
+
+\bibitem[\protect\citeauthoryear{Chin and Lansing}{2004}]{chin04context} Chin Jr., G. and Lansing,
+C.S. (2008) `Capturing and Supporting Contexts for Scientific Data
+Sharing via the Biological Sciences Collaboratory', {\it CSCW}, ISBN
+1-58113-810-5.
+
+\bibitem[\protect\citeauthoryear{W3C XML Query (XQuery)}{http://www.w3.org/XML/Query}]{xquery}
+W3C XML Query (XQuery), http://www.w3.org/XML/Query
+
+\bibitem[\protect\citeauthoryear{Wang et al.}{2009}]{wang09security}
+Wang, F., Hussels, P. and Liu, P. (2009) `Securely and flexibly
+sharing a biomedical data management system', {\it SPIE}.
+
+ \end{thebibliography}
 \end{document}

### 2015-11-28 Docs/IJES/journal.tex
adjusting pseudocodes

@@
 
+\vspace{2 mm}
 \begin{equation}
@@
 
-\vspace{3 mm}
+\vspace{2 mm}
 In some cases, the time to find a solution using ILP is impractical.
@@
 \vspace{2 mm}
-\begin{lstlisting}[label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
+\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
 int k;
@@
 
-\vspace{2 mm}
-\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\vspace{2.5 mm}
+\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 (Declare-Const K Int) 
@@
 
+\vspace{-2 mm}
 \begin{align}
@@
 
+\vspace{-3 mm}
 \begin{align}
@@
 Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
-%
-\vspace{1 mm}
+
+\vspace{-2 mm}
 \begin{align}
@@
 \vspace{2 mm}
-\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
 Initialize variables 
@@
 Declare communication cost of each edge (c)
-Declare the initial software cost of ($S_0$)
+Declare the initial sw cost of ($S_0$)
 Declare transposed incidence matrix graph G(E)
-Define the solutions variable ($X_i$) as Boolean
+Define the solutions ($X_i$) as Boolean
 main {
  For TipH = 0 to Hmax Do {
-  Populate $X_i$ with nondeterministic / test values
+  Populate $X_i$ with nondet / test values
   Calculate s(1-x)+c|Ex| and store at variable
-  Requirement isued by Assume (Variable <= $S_0$)
-  Calculate Hp cost Based on value tested of $X_i$
+  Requirement isued by Assume (variable <= $S_0$)
+  Calculate Hp cost Based on value of $X_i$
   Violation check with Assert(Hp > TipH)
@@
 \vspace {2 mm}
-\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 GetNextStep(){
@@
  chunks.remove(largest);	
-  int median = largest.left + floor((largest.right - largest.left) / 2);
+ int median = largest.left + 
+   floor((largest.right - largest.left) / 2);
  if(median > 0){
   if(largest.right - largest.left > 1)
-      chunks.add(new chunk(largest.left, median - 1));	
+   chunks.add(
+     new chunk(largest.left, median - 1)
+   );	
   if(largest.right != largest.left)
-      chunks.add(new chunk(median + 1, largest.right);
+   chunks.add(
+    new chunk(median + 1, largest.right)
+   );
  }
@@
 \vspace {2 mm}
-\begin{lstlisting}[caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
 step = controller.GetNextStep();
@@
 
-The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
-In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
-\textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
-Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
 \vspace {2 mm}
-\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
---Initialize Variables
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+-Initialize Variables
  Create vZ context 
@@
  Declare transposed incidence matrix graph G(E)
---Arithmetic Expressions
+-Arithmetic Expressions
  SC = s(1-x)
@@
  Fobj =  x[i] * h[i]
---Assert Constraints
+-Assert Constraints
  Add constraints (SF + CMC <= $S_0$)
@@
 \end{lstlisting}
+
+The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
+Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
+In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
+\textit{Fobj} should be minimized to obtain the optimal hardware solution.
+To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
+Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
 

### 2015-11-28 Docs/IJES/journal.tex
including experimental evaluation

@@
 \usepackage{tabularx}
+\usepackage{booktabs}
+\usepackage{tabu}
 \usepackage{listings}
+\usepackage[table]{xcolor}
+\usepackage{multirow}
 \renewcommand{\lstlistingname}{Algorithm}
@@
 %----------------------------------------------
+\subsection{Description of Benchmarks}
+\label{Benchmarks-Description}
+%----------------------------------------------
+To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
+The nodes in the graphs correspond to high-level language instructions.
+Software and communication costs are time dimensional, and hardware costs represent the occupied area.
+The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
+The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
+From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
+
+\hspace{-5 mm}
+\begin{minipage}{\linewidth}
+\centering
+\small
+\sffamily\small
+\tabulinesep=4pt
+\captionof{table}{Description of Benchmarks.} 
+\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{4.0 cm}}
+\toprule[1.5pt]
+\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
+\midrule
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\hline
+\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
+\vspace{0.8 mm} Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
+\hline
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph ~\cite{Guthaus2001}\\
+\hline
+\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily \vspace{0.8 mm} Image segmentation algorithm in a medical application\\
+\hline
+\verb|RC6| & \verb|329| & \verb|448| & \rmfamily \vspace{0.8 mm} RC6 cryptography graph algorithm\\
+\hline
+\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily \vspace{0.8 mm} Clustering algorithm based on fuzzy logic\\
+\hline
+\verb|Mars| & \verb|417| & \verb|600| & \rmfamily 
+\vspace{1 mm} MARS cipher from IBM algorithm\\
+\bottomrule[1.5pt]
+\label{tab:Description-of-Benchmarks} 
+\end{tabular}\par
+\bigskip
+\end{minipage}
+
+%----------------------------------------------
+\subsection{Experimental Results}
+\label{Experimental-Results}
+%----------------------------------------------
+
+Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC-SS, ESBMC-PS, ESBMC-PB, ESBMC-$\nu$Z) tools.
+
+There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
+In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
+
+In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks.
+When ILP produces a result, it provides the optimal solution.
+On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by ESBMC-$\nu$Z.
+On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.
+
+Note further that all multi-core ESBMC implementations produce better results than the sequential one.
+In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase.
+One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $2$.$5$ times slower than ESBMC-$\nu$Z.
+However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools.
+When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.
+
+\begin{table*}[ht]
+  \centering
+  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
+  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
+\\
+ &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
+\cmidrule(r){3-9}
+
+&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
+&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
+&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\
+
+\bottomrule[1.5pt]
+\rowcolors{1}{}{lightgray}
+
+\multirow{4}{*}{\textbf{\normalsize{Solution}}}
+& & & & & & & & & \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
+&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
+& & & & & & & & & \\
+
+\bottomrule[1.5pt]
+%ILP
+\multirow{4}{*}{\textbf{\normalsize{ILP}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%GA
+\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
+&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%MultiCore ESBMC
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC Parallel sequential
+\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%ESBMC Parallel Binary
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+\hline
+
+%vZ
+\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
+& & & & & & & & & \\
+&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
+&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
+& & & & & & & & & \\
+
+\bottomrule[1.5pt]
+\end{tabular}
+\label{Experimental-results-of-the-complex-benchmarks}
+\end{table*}
+
+The only technique that is able to solve all benchmarks is GA; however, its precision is not satisfactory since it produces an error rate between $-37.6$\% and $29.0$\%.
+
+Note that RC$6$ produced timeouts for all implementations of ESBMC; GA did not produce the correct answer, and ILP solves correctly most benchmarks, except for Mars and Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution.
+No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.
+
+The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO.
+ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.
+
+%----------------------------------------------
 \section{Related Work}

### 2015-11-28 Docs/IJES/journal.tex
minor changes
including some references

@@
 
-\REF{to this paper should be made as follows: Rodr\'{\i}guez
+\REF{\textcolor{red}{to this paper should be made as follows: Rodr\'{\i}guez
 Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
@@
 IBEX 35 Spanish companies', {\it International Journal of Metadata,
-Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}
+Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}}
 
@@
 $\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
-As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
+As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed fu	nctional programming languages and reports the most useful one subject to some usefulness criterion.
 The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.
@@
 
-%\section*{Acknowledgement}
-%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\bibliography{ijmso}
-%\bibliographystyle{unsrt}
-%\bibliographystyle{alpha}
-
 \begin{thebibliography}{10}
 
-\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
-Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
-for collaborative scientific research: a research information
-management system', {\it International Journal of Information
-Management}, Vol. 30, No. 3, pp.256--264
-
-\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
-Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
-financial conflicts of interest in biomedical research: a systematic
-review', {\it JAMA}, Vol. 289, No. 19, pp.454--65
-
-\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
-Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
-sciences: progress, visions and challenges', {\it Nature Reviews
-Genetics}, Vol. 9, No. 9, pp.678--688.
-
-\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
-Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
-NIH Statement on Sharing Scientific Research Data,
-http://grants.nih.gov/grants/policy/data\_sharing/
-
-\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
-genome-wide association studies}{2008}]{nih08policy} Policy for
-sharing of data obtained in NIH supported or conducted genome-wide
-association studies,
-http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html
+\bibitem[\protect\citeauthoryear{Arato et al.}{2003}]{Arato2003}
+Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it Intl. Symp. on Intelligent Signal Processing}, pp.192--202
+
+\bibitem[\protect\citeauthoryear{Mann et al.}{2007}]{Mann2007}
+Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263
+
+\bibitem[\protect\citeauthoryear{Trindade and Cordeiro}{2015}]{Trindade2015}
+Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems (to appear)}
+
+\bibitem[\protect\citeauthoryear{Trindade et al.}{2016}]{Trindade2016}
+Trindade, A., Ismail, H.
+and Cordeiro, L.
+(2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symp.
+on Computing Systems Engineering (to appear)}
+
+\bibitem[\protect\citeauthoryear{Bjorner et al.}{2015}]{Bjorner2015}
+Bjorner, N., Phan, A.
+and Fleckenstein, L.
+(2015) 'vZ - An Optimizing SMT Solver', {\it Proc.
+of the Intl.
+Conf.
+on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+9035, pp.194--199
+
+\bibitem[\protect\citeauthoryear{Tang et al.}{2010}]{Tang2009}
+Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905
+
+\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
+Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}
+
+\bibitem[\protect\citeauthoryear{Cordeiro et al.}{2012}]{Cordeiro2012}
+Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974
+
+\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
+Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'
+
+\bibitem[\protect\citeauthoryear{Biere et al.}{2009}]{Biere2009}
+Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}
+
+\bibitem[\protect\citeauthoryear{Clarke et al.}{2001}]{Clarke2001}
+Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34
+
+\bibitem[\protect\citeauthoryear{Armando et al.}{2009}]{Armando2009}
+Armando, A., Mantovani, J.
+and Platania, L.
+(2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it Intl.
+Journal on Software Tools for Technology Transfer}, Vol.
+11, No.
+1, pp.69--83
+
+\bibitem[\protect\citeauthoryear{Ganai and Gupta}{2006}]{Ganai2006}
+Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design}, pp.794--801
+
+\bibitem[\protect\citeauthoryear{Ramalho et al.}{2013}]{Ramalho2013}
+Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L.
+and Fischer, B.
+(2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it Intl.
+Conf.
+and Workshops on the Engineering of Computer-Based Systems}, pp.147--156
+
+\bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
+Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340
+
+\bibitem[\protect\citeauthoryear{Brummayer and Biere}{2009}]{Brummayer2009}
+Brummayer, R.
+and Biere, A.
+(2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proc.
+of the Intl.
+Conf.
+on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+5505, pp.174--177
+
+\bibitem[\protect\citeauthoryear{Barrett et al.}{2011}]{Barrett2011}
+Barrett, C., Conway, C., Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A.
+and Tinelli, C.
+(2011) 'CVC4', {\it Proc.
+of the Intl.
+Conf.
+on Computer-Aided Verification}, Vol.
+6806, pp.171--177
+
+\bibitem[\protect\citeauthoryear{Bozzano et al.}{2005}]{Bozzano2005}
+Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S.
+and Sebastiani, R.
+(2005) 'MathSAT: Tight integration of SAT and mathematical decision procedures', {\it Journal of Automated Reasoning}, Vol.
+35, No.
+1-3, pp.265--293
+
+\bibitem[\protect\citeauthoryear{Dutertre}{2014}]{Dutertre2014}
+Dutertre, B. (2014) 'Yices 2.2', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 8559, pp.737--744
+
+\bibitem[\protect\citeauthoryear{Wu et al.}{2014}]{Wu2014}
+Wu M., Wu, W., Tai, N., Zhao, H., Fan, J.
+and Yuan, N.
+(2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proc.
+of the Intl.
+Conf.
+on Software Engineering and Service Science}, pp.921--924
+
+\bibitem[\protect\citeauthoryear{Bjorner and Phan}{2014}]{Bjorner2014}
+Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proc. of the Intl. Symp. on Symbolic Computation in Software Science}, pp.1--10
+
+\bibitem[\protect\citeauthoryear{Paci et al}{2008}]{Federica2008}
+Paci, F., Ferrini, R., Sun, Y.
+and Bertino, E.
+(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proc.
+of the Intl.
+Conf.
+on Service-Oriented Computing}, pp.116--131
+
+\bibitem[\protect\citeauthoryear{Narodytska and Bacchus}{2014}]{NarodytskaN}
+Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proc. of the Conf. on Artificial Intelligence}, pp.2717--2723
 

### 2015-11-28 Docs/IJES/journal.tex
including references

@@
 
-\bibitem[\protect\citeauthoryear{Network for Translational Research (NTR): Optical Imaging in
-Multimodality
-Platforms}{http://imaging.cancer.gov/programsandresources/speci\break
-alizedinitiatives/ntroi}]{ntr} Network for Translational Research
-(NTR): Optical Imaging in Multimodality Platforms,
-http://imaging.cancer.gov/programsandresources/specializedinitiatives/ntroi
-
-\bibitem[\protect\citeauthoryear{Piwowar~et~al.}{2008}]{piwowar08culture}
-Piwowar, H., Becich, M., Bilofsky, H. and Crowley, R. (2008) `PLoS
-medicine', {\it Sept, No. 9, Towards a Data Sharing Culture:
-Recommendations for Leadership from Academic Health Centers},
-Vol.~5.
-
-\bibitem[\protect\citeauthoryear{Birnholtz et al.}{2003}]{birnholtz03data}
-Birnholtz, J.P. and Bietz, M.J. (2003) `Data at work: supporting
-sharing in science and engineering', {\it GROUP}, pp.339--348.
-
-\bibitem[\protect\citeauthoryear{Data Sharing \& Intellectual Capital (DSIC) Workspace}
-{https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG}]{dsic} Data
-Sharing \& Intellectual Capital (DSIC) Workspace,
-https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG
-
-\bibitem[\protect\citeauthoryear{Getting Connected with
-caBIG}{https://cabig.nci.nih.gov/getting\_connected/}]{cabigconnected}
-Getting Connected with caBIG, https://cabig.nci.nih.gov/\break
-getting\_connected/
-
-\bibitem[\protect\citeauthoryear{Digital Imaging and Communications in Medicine
-(DICOM)}{http://medical.nema.org/}]{dicom} Digital Imaging and
-Communications in Medicine (DICOM), http://medical.nema.org/
-
-\bibitem[\protect\citeauthoryear{The Cancer Genome Atlas (TCGA) Data Portal}{http://cancergenome.nih.gov/dataportal}]{tcga}
-The Cancer Genome Atlas (TCGA) Data Portal,
-http://cancergenome.nih.gov/dataportal
-
-\bibitem[\protect\citeauthoryear{National Biomedical Imaging
-Archive}{https://cabig.nci.nih.gov/tools/NCIA}]{nbia} National
-Biomedical Imaging Archive, https://cabig.nci.nih.gov/tools/NCIA
-
-\bibitem[\protect\citeauthoryear{caBIG: cancer Biomedical Informatics Grid}{http://caBIG.nci.nih.gov/}]{cabig}
-caBIG: cancer Biomedical Informatics Grid, http://caBIG.nci.nih.gov/
-
-\bibitem[\protect\citeauthoryear{Biomedical Informatics Research Network}{
-http://www.nbirn.net/}]{birn}
-Biomedical Informatics Research Network, http://www.nbirn.net/
-
-\bibitem[\protect\citeauthoryear{Cyberinfrastructure for the Biological Sciences: Plant Science
-Cyberinfrastructure Collaborative
-(PSCIC)}{http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm}]{pscic}
-Cyberinfrastructure for the Biological Sciences: Plant Science
-Cyberinfrastructure Collaborative (PSCIC),
-http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm
-
-\bibitem[\protect\citeauthoryear{MIRC}{http://mirc.rsna.org}]{mirc}
-MIRC, http://mirc.rsna.org
-
-\bibitem[\protect\citeauthoryear{Foster and
-Iamnitchi}{2003}]{foster03p2p2grid} Foster, I. and Iamnitchi, A.
-(2003) `On death, taxes, and the convergence of peer-to-peer and
-grid computing', {\it IPTPS'03}.
-
-\bibitem[\protect\citeauthoryear{Keidl et al.}{2002}]{keidl02metadata}
-Keidl, M., Kreutz, A., Kemper, A. and Kossmann, D. (2002) `A publish
-{\&} subscribe architecture for distributed metadata management',
-{\it ICDE}.
-
-\bibitem[\protect\citeauthoryear{Taylor and Ives}{2006}]{taylor06reconcile}
-Taylor, N.E. and Ives, Z.G. (2006) `Reconciling while tolerating
-disagreement in collaborative data sharing', {\it SIGMOD}.
-
-\bibitem[\protect\citeauthoryear{Rader and Wash}{2008}]{rader08tag}
-Rader, E.J. and Wash, R. (2008) {\it CSCW}, pp.239-248, Influences
-on tag choices in del.icio.us.
-
-\bibitem[\protect\citeauthoryear{Halevy et~al.}{2006}]{halevy06integration}
-Halevy, A., Rajaraman, A. and Ordille, J. (2006) {\it VLDB, Data
-integration: the teenage years},
-http://portal.acm.org/citation.cfm?id=1182635.1164130
-
-\bibitem[\protect\citeauthoryear{Doan and Halevy}{2005}]{doan05semantic}
-Doan, A. and Halevy, A.Y. (2005) Semantic Integration Research in
-the Database Community: A Brief Survey, {\it AI Magazine}, Vol. 26,
-No. 1, pp.83--94.
-
-\bibitem[\protect\citeauthoryear{Beynon-Davies et~al.}{1997}]{beynon97}
-Beynon-Davies, P., Bonde, L., McPhee, D. and Jones, C.B. (1997) `A
-collaborative schema integration system', {\it Comput. Supported
-Coop. Work}, Vol. 6, No. 1, Norwell, MA, USA, pp.1--18, issn =
-0925-9724.
-
-\bibitem[\protect\citeauthoryear{Wang and Vergara-Niedermayr}{2008}]{wang08com}
-Wang, F. and Vergara-Niedermayr, C. (2008) `Collaboratively Sharing
-Scientific Data', {\it CollaborateCom}, pp.805--823.
-
-\bibitem[\protect\citeauthoryear{Chin and Lansing}{2004}]{chin04context} Chin Jr., G. and Lansing,
-C.S. (2008) `Capturing and Supporting Contexts for Scientific Data
-Sharing via the Biological Sciences Collaboratory', {\it CSCW}, ISBN
-1-58113-810-5.
-
-\bibitem[\protect\citeauthoryear{W3C XML Query (XQuery)}{http://www.w3.org/XML/Query}]{xquery}
-W3C XML Query (XQuery), http://www.w3.org/XML/Query
-
-\bibitem[\protect\citeauthoryear{Wang et al.}{2009}]{wang09security}
-Wang, F., Hussels, P. and Liu, P. (2009) `Securely and flexibly
-sharing a biomedical data management system', {\it SPIE}.
+\bibitem[\protect\citeauthoryear{Barth and Putnam}{1995}]{Barth1995}
+Barth, P. and Putnam, D. (1995) 'Enumeration Algorithm for Linear Pseudo-Boolean Optimization', {\it Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science}
+
+\bibitem[\protect\citeauthoryear{Manquinho and Marques-Silva}{1995}]{Vasco2005}
+Manquinho, V. and Marques-Silva, J. (1995) 'Effective Lower Bounding Techniques for Pseudo-Boolean Optimization', {\it IST/INESC-ID, Technical University of Lisbon, Portugal}
+
+\bibitem[\protect\citeauthoryear{Microsoft Research}{2015}]{Z3API}
+Microsoft Research (2015) 'Z3 API - Source code and documentation', {\it https://z3.codeplex.com/}, Accessed in 18th August 2015
+
+\bibitem[\protect\citeauthoryear{Cormen et al.}{2009}]{Cormem}
+Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292
+
+\bibitem[\protect\citeauthoryear{Dagum and Menon}{1998}]{Dagum1998}
+Dagum, L. and Menon, R. (1998) 'OpenMP: An Industry-Standard API for Shared-Memory Programming', {\it Proc. of the Intl. Conf. on Computational Science Engineering}, pp.46--55
+
+\bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
+MathWorks (2013) 'MATLAB (version R2013a)'
+
+\bibitem[\protect\citeauthoryear{Tranquillo}{2011}]{Tranquillo2011}
+Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}
+
+\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2010}
+Hong, L.
+and Cai, J.
+(2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proc.
+of the Intl.
+Conf.
+on Computer and Automation Engineering}, pp.185--189
+
+\bibitem[\protect\citeauthoryear{Cordeiro and Fischer}{2011}]{Cordeiro2011}
+Cordeiro, L. and Fischer, B. (2011) 'Verifying multi-threaded software using SMT-based context-bounded model checking', {\it Proc. of the Intl. Conf. on Software Engineering}, pp.331--340
+
+\bibitem[\protect\citeauthoryear{Teich}{2012}]{Teich2012}
+Teich, J. (2012) 'Hardware/Software Codesign: The Past, the Present, and Predicting the Future', {\it Proc. of the IEEE, Special Centennial Issue}, Vol. 100, pp.1411--1430
+
+\bibitem[\protect\citeauthoryear{Guthaus et al.}{2011}]{Guthaus2001}
+Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T.
+and Brown, R.
+(2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proc.
+of the annual workshop on workload characterization}, pp.3--14
+
+\bibitem[\protect\citeauthoryear{Arato et al.}{2005}]{Arato2005}
+Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156
+
+\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann2011}
+Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857
+
+\bibitem[\protect\citeauthoryear{Wintersteiger et al.}{2009}]{Wintersteiger2009}
+Wintersteiger, C., Hamadi, Y. and Moura, L. (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 5643, pp.715--720
+
+\bibitem[\protect\citeauthoryear{Qawasmeh et al.}{2014}]{Qawasmeh2014}
+Qawasmeh, A., Malik, A.
+and Chapman, B.
+(2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proc.
+of the Intl.
+Symp.
+on Parallel Distributed processing}, pp.1049--1058
+
+\bibitem[\protect\citeauthoryear{Pavlinovi et al.}{2015}]{Pavlinovic2015}
+Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proc. of the Intl. Conf. on Functional Programming}, pp.412--423
+
+\bibitem[\protect\citeauthoryear{Sebastiani and Trentin}{2015}]{Patrick2015}
+Sebastiani, R. and Trentin, P. (2015) 'OptiMathSAT: A Tool for Optimization Modulo Theories', {\it Proc. of the Intl. Conf. on Computer Aided Verification}, Vol. 9206, pp.447--454
+
+\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann11}
+Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions Software Engineering}, Vol. 9206, pp.845--857
 

### 2015-11-28 Docs/IJES/journal.tex
updating file structure

@@
 
-%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
-%Processing,
-%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
+\JOURNALNAME{\TEN{\it International Journal of Embedded Systems,
+Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}
+}
+
+%
 %
@@
 %}
+
 \makeatother
@@
 
-\vspace{-2 mm}
+\vspace{-5 mm}
 \begin{align}
@@
 At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.
-
-It is possible to inform to ESBMC with which type of values the variables must be tested.
-Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
-Those values that change for each test will generate a possible solution and obey the constraints.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).
-
-A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
-To every test performed, the hardware hint is compared to the feasible solution.
-This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement).
-If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.
-
-The \textit{ASSERT} statement tests the objective function, {\it i.e.}, the hardware cost, and will stop if the hardware cost found is lower than or equal to the optimal solution.
-However, if \textit{ASSERT} returns a \textit{true} condition, {\it i.e.}, the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the \textit{ASSERT} generates a \textit{false} condition.
-When the \textit{false} condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
-That is the point in which the solution is presented (minimum HW cost).
-
-In the ESBMC algorithm, which is shown below, it is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.
 
@@
 
+It is possible to inform to ESBMC with which type of values the variables must be tested.
+Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
+Those values that change for each test will generate a possible solution and obey the constraints.
+If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).
+
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
+To every test performed, the hardware hint is compared to the feasible solution.
+This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement).
+If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.
+
+The \textit{ASSERT} statement tests the objective function, {\it i.e.}, the hardware cost, and will stop if the hardware cost found is lower than or equal to the optimal solution.
+However, if \textit{ASSERT} returns a \textit{true} condition, {\it i.e.}, the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the \textit{ASSERT} generates a \textit{false} condition.
+When the \textit{false} condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
+That is the point in which the solution is presented (minimum HW cost).
+
+In the ESBMC algorithm is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.
+
 %----------------------------------------------
@@
 Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
+
+Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
+From lines $4$ to $9$, the algorithm finds the largest interval.
+Then, from line $10$ the largest interval is removed and the median is calculated in line $11$.
+After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$).
+At the end, the median is returned.
 
@@
 
-Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
-From lines $4$ to $9$, the algorithm finds the largest interval.
-Then, from line $10$ the largest interval is removed and the median is calculated in line $11$.
-After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$).
-At the end, the median is returned.
+Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
+The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$).
+While the step is being executed, the controller checks whether this step is still needed (line $4$).
+If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
 
@@
 
-Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
-The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$).
-While the step is being executed, the controller checks whether this step is still needed (line $4$).
-If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
-
 %----------------------------------------------
@@
 Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
+
+The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
+Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
+In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
+\textit{Fobj} should be minimized to obtain the optimal hardware solution.
+To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
+Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that
+meets the constraints, then the \textit{Fobj} value is provided.
 
@@
 
-The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
-In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
-\textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
-Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.
-
 %----------------------------------------------
@@
 
-\bibitem[\protect\citeauthoryear{Mann et al.}{2007}]{Mann2007}
+\bibitem[\protect\citeauthoryear{Mann \textit{et al.}}{2007}]{Mann2007}
 Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263
@@
 
-\bibitem[\protect\citeauthoryear{Trindade et al.}{2016}]{Trindade2016}
+\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2016}]{Trindade2016}
 Trindade, A., Ismail, H.
@@
 
-\bibitem[\protect\citeauthoryear{Bjorner et al.}{2015}]{Bjorner2015}
+\bibitem[\protect\citeauthoryear{Bjorner \textit{et al.}}{2015}]{Bjorner2015}
 Bjorner, N., Phan, A.
@@
 
-\bibitem[\protect\citeauthoryear{Tang et al.}{2010}]{Tang2009}
+\bibitem[\protect\citeauthoryear{Tang \textit{et al.}}{2010}]{Tang2009}
 Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905
@@
 
-\bibitem[\protect\citeauthoryear{Cordeiro et al.}{2012}]{Cordeiro2012}
+\bibitem[\protect\citeauthoryear{Cordeiro \textit{et al.}}{2012}]{Cordeiro2012}
 Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974
@@
 
-\bibitem[\protect\citeauthoryear{Biere et al.}{2009}]{Biere2009}
+\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
 Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}
 
-\bibitem[\protect\citeauthoryear{Clarke et al.}{2001}]{Clarke2001}
+\bibitem[\protect\citeauthoryear{Clarke \textit{et al.}}{2001}]{Clarke2001}
 Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34
 
-\bibitem[\protect\citeauthoryear{Armando et al.}{2009}]{Armando2009}
+\bibitem[\protect\citeauthoryear{Armando \textit{et al.}}{2009}]{Armando2009}
 Armando, A., Mantovani, J.
@@
 
-\bibitem[\protect\citeauthoryear{Ramalho et al.}{2013}]{Ramalho2013}
+\bibitem[\protect\citeauthoryear{Ramalho \textit{et al.}}{2013}]{Ramalho2013}
 Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L.
@@
 
-\bibitem[\protect\citeauthoryear{Barrett et al.}{2011}]{Barrett2011}
+\bibitem[\protect\citeauthoryear{Barrett \textit{et al.}}{2011}]{Barrett2011}
 Barrett, C., Conway, C., Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A.
@@
 
-\bibitem[\protect\citeauthoryear{Bozzano et al.}{2005}]{Bozzano2005}
+\bibitem[\protect\citeauthoryear{Bozzano \textit{et al.}}{2005}]{Bozzano2005}
 Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S.
@@
 
-\bibitem[\protect\citeauthoryear{Wu et al.}{2014}]{Wu2014}
+\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
 Wu M., Wu, W., Tai, N., Zhao, H., Fan, J.
@@
 
-\bibitem[\protect\citeauthoryear{Cormen et al.}{2009}]{Cormem}
+\bibitem[\protect\citeauthoryear{Cormen \textit{et al.}}{2009}]{Cormem}
 Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292
@@
 
-\bibitem[\protect\citeauthoryear{Guthaus et al.}{2011}]{Guthaus2001}
+\bibitem[\protect\citeauthoryear{Guthaus \textit{et al.}}{2011}]{Guthaus2001}
 Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T.
@@
 
-\bibitem[\protect\citeauthoryear{Arato et al.}{2005}]{Arato2005}
+\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2005}]{Arato2005}
 Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156
 
-\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann2011}
+\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann2011}
 Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857
 
-\bibitem[\protect\citeauthoryear{Wintersteiger et al.}{2009}]{Wintersteiger2009}
+\bibitem[\protect\citeauthoryear{Wintersteiger \textit{et al.}}{2009}]{Wintersteiger2009}
 Wintersteiger, C., Hamadi, Y. and Moura, L. (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 5643, pp.715--720
 
-\bibitem[\protect\citeauthoryear{Qawasmeh et al.}{2014}]{Qawasmeh2014}
+\bibitem[\protect\citeauthoryear{Qawasmeh \textit{et al.}}{2014}]{Qawasmeh2014}
 Qawasmeh, A., Malik, A.
@@
 
-\bibitem[\protect\citeauthoryear{Pavlinovi et al.}{2015}]{Pavlinovic2015}
+\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
 Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proc. of the Intl. Conf. on Functional Programming}, pp.412--423
@@
 
-\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann11}
+\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann11}
 Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions Software Engineering}, Vol. 9206, pp.845--857
@@
 \end{thebibliography}
+
 \end{document}

### 2015-11-30 Docs/IJES/journal.tex
minor changes
modifications in structure to accomplish ijes layout

@@
 \usepackage{graphicx}
-\usepackage{caption}
+\usepackage[labelsep=quad,font=small,justification=justified,singlelinecheck=false,format=plain,labelfont=bf,up,textfont=normal,up]{caption}
 \usepackage{tabularx}
@@
 \usepackage[table]{xcolor}
+\usepackage[tableposition=top]{caption}
 \usepackage{multirow}
-\renewcommand{\lstlistingname}{Algorithm}
+\renewcommand{\lstlistingname}{Figure}
+\renewcommand{\figurename}{Figure}
+
+\makeatletter
+\AtBeginDocument{%
+  \let\c@figure\c@lstlisting
+  \let\thefigure\thelstlisting
+  \let\ftype@lstlisting\ftype@figure % give the floats the same precedence
+}
+\makeatother
 
@@
 \begin{figure}[ht]
+	\caption{ESBMC architecture.}
 	\centering
 	\includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
-	\caption{ESBMC architecture.}
 	\label{ESBMC-Architecture}
@@
 
-\vspace{2 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
+\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=t, caption={OpenMP basic Example.}]
 int k;
@@
 
+\vspace{2 mm}
 In the above example, the {\it for} loop is executed in parallel.
@@
 
-\vspace{2.5 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
 (Declare-Const K Int) 
@@
 
+\vspace{2 mm}
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
@@
 \begin{figure}[ht]
+	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
 	\centering
 	\includegraphics[scale=0.21]{figures/vzArch.png} 
-	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
 	\label{vZ-Architecture}
@@
 
-\vspace{2 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
 Initialize variables 
@@
 
+\vspace{2 mm}
 It is possible to inform to ESBMC with which type of values the variables must be tested.
@@
 \begin{figure}[h]
+	\caption{ESBMC-SS approach.}
 	\centering
 	\includegraphics[scale=0.77]{figures/esbmc-ss.pdf} 	
-	\caption{ESBMC-SS approach.}
 	\label{ESBMC-Multi-core}
@@
 \begin{figure}[h]
+	\caption{ESBMC-PS approach.}
 	\centering
 	\includegraphics[scale=0.77]{figures/esbmc-ps.pdf} 	
-	\caption{ESBMC-PS approach.}
 	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
@@
 \begin{figure}[ht]
+	\caption{ESBMC-PB approach.}
 	\centering
 	\includegraphics[scale=0.77]{figures/esbmc-pb.pdf} 
-	\caption{ESBMC-PB approach.}
 	\label{ESBMC-Binary-Approach}
@@
 \begin{figure}[h!]
+	\caption{Binary step calculation.}
 	\centering
 	\includegraphics[scale=0.17]{figures/Fig4.png}	
-	\caption{Binary step calculation.}
 	\label{Binary-Step-Calculation}
@@
 
-\vspace {2 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
 GetNextStep(){
@@
 
+\vspace {2 mm}
 Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
@@
 
-\vspace {2 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
 step = controller.GetNextStep();
@@
 
-\vspace {2 mm}
-\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
+\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
 -Initialize Variables
@@
 
+\vspace{5 mm}
 \hspace{-5 mm}
@@
 
-\multirow{4}{*}{\textbf{\normalsize{Solution}}}
+\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
 & & & & & & & & & \\
@@
 
+\bibitem[\protect\citeauthoryear{Holzmann}{2012}]{Holzmann2012}
+Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proc. of the Intl. Symp. on Model Checking Software}, Vol. 7385, pp.155--171
+
 \end{thebibliography}

### 2015-11-30 Docs/IJES/journal.tex
including proc to proceedings

@@
 \bibitem[\protect\citeauthoryear{Arato et al.}{2003}]{Arato2003}
-Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it Intl. Symp. on Intelligent Signal Processing}, pp.192--202
+Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202
 
@@
 and Cordeiro, L.
-(2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symp.
-on Computing Systems Engineering (to appear)}
+(2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering (to appear)}
 
@@
 and Fleckenstein, L.
-(2015) 'vZ - An Optimizing SMT Solver', {\it Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+(2015) 'vZ - An Optimizing SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
 9035, pp.194--199
@@
 \bibitem[\protect\citeauthoryear{Tang \textit{et al.}}{2010}]{Tang2009}
-Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905
+Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proceedings of the International Conference on Computer Science Education}, pp.1900--1905
 
@@
 and Platania, L.
-(2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it Intl.
-Journal on Software Tools for Technology Transfer}, Vol.
+(2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it International Journal on Software Tools for Technology Transfer}, Vol.
 11, No.
@@
 \bibitem[\protect\citeauthoryear{Ganai and Gupta}{2006}]{Ganai2006}
-Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design}, pp.794--801
+Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proceedings of the IEEE/ACM International Conference on Computer-Aided Design}, pp.794--801
 
@@
 and Fischer, B.
-(2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it Intl.
-Conf.
-and Workshops on the Engineering of Computer-Based Systems}, pp.147--156
+(2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it International Conference and Workshops on the Engineering of Computer-Based Systems}, pp.147--156
 
 \bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
-Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340
+Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340
 
@@
 and Biere, A.
-(2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proc.
-of the Intl.
-Conf.
-on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+(2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
 5505, pp.174--177
@@
 and Tinelli, C.
-(2011) 'CVC4', {\it Proc.
-of the Intl.
-Conf.
-on Computer-Aided Verification}, Vol.
+(2011) 'CVC4', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol.
 6806, pp.171--177
@@
 \bibitem[\protect\citeauthoryear{Dutertre}{2014}]{Dutertre2014}
-Dutertre, B. (2014) 'Yices 2.2', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 8559, pp.737--744
+Dutertre, B. (2014) 'Yices 2.2', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol. 8559, pp.737--744
 
@@
 and Yuan, N.
-(2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proc.
-of the Intl.
-Conf.
-on Software Engineering and Service Science}, pp.921--924
+(2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proceedings of the International Conference on Software Engineering and Service Science}, pp.921--924
 
 \bibitem[\protect\citeauthoryear{Bjorner and Phan}{2014}]{Bjorner2014}
-Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proc. of the Intl. Symp. on Symbolic Computation in Software Science}, pp.1--10
+Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proceedings of the International Symposium on Symbolic Computation in Software Science}, pp.1--10
 
@@
 and Bertino, E.
-(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proc.
-of the Intl.
-Conf.
-on Service-Oriented Computing}, pp.116--131
+(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proceedings of the International Conference on Service-Oriented Computing}, pp.116--131
 
 \bibitem[\protect\citeauthoryear{Narodytska and Bacchus}{2014}]{NarodytskaN}
-Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proc. of the Conf. on Artificial Intelligence}, pp.2717--2723
+Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proceedings of the Conference on Artificial Intelligence}, pp.2717--2723
 
@@
 \bibitem[\protect\citeauthoryear{Microsoft Research}{2015}]{Z3API}
-Microsoft Research (2015) 'Z3 API - Source code and documentation', {\it https://z3.codeplex.com/}, Accessed in 18th August 2015
+Microsoft Research (2015) 'Z3 API - Source code and documentation' [online] {\it https://z3.codeplex.com/} (Accessed 18 August 2015)
 
@@
 \bibitem[\protect\citeauthoryear{Dagum and Menon}{1998}]{Dagum1998}
-Dagum, L. and Menon, R. (1998) 'OpenMP: An Industry-Standard API for Shared-Memory Programming', {\it Proc. of the Intl. Conf. on Computational Science Engineering}, pp.46--55
+Dagum, L. and Menon, R. (1998) 'OpenMP: An Industry-Standard API for Shared-Memory Programming', {\it Proceedings of the International Conference on Computational Science Engineering}, pp.46--55
 
 \bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
-MathWorks (2013) 'MATLAB (version R2013a)'
+MathWorks Inc. (2013) 'MATLAB (version R2013a)'
 
@@
 and Cai, J.
-(2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proc.
-of the Intl.
-Conf.
-on Computer and Automation Engineering}, pp.185--189
+(2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proceedings of the International Conference on Computer and Automation Engineering}, pp.185--189
 
 \bibitem[\protect\citeauthoryear{Cordeiro and Fischer}{2011}]{Cordeiro2011}
-Cordeiro, L. and Fischer, B. (2011) 'Verifying multi-threaded software using SMT-based context-bounded model checking', {\it Proc. of the Intl. Conf. on Software Engineering}, pp.331--340
+Cordeiro, L.
+and Fischer, B.
+(2011) 'Verifying multi-threaded software using SMT-based context-bounded model checking', {\it Proceedings of the International Conference on Software Engineering}, pp.331--340
 
 \bibitem[\protect\citeauthoryear{Teich}{2012}]{Teich2012}
-Teich, J. (2012) 'Hardware/Software Codesign: The Past, the Present, and Predicting the Future', {\it Proc. of the IEEE, Special Centennial Issue}, Vol. 100, pp.1411--1430
+Teich, J. (2012) 'Hardware/Software Codesign: The Past, the Present, and Predicting the Future', {\it Proceedings of the IEEE, Special Centennial Issue}, Vol. 100, pp.1411--1430
 
@@
 and Brown, R.
-(2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proc.
-of the annual workshop on workload characterization}, pp.3--14
+(2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proceedings of the annual workshop on workload characterization}, pp.3--14
 
@@
 \bibitem[\protect\citeauthoryear{Wintersteiger \textit{et al.}}{2009}]{Wintersteiger2009}
-Wintersteiger, C., Hamadi, Y. and Moura, L. (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 5643, pp.715--720
+Wintersteiger, C., Hamadi, Y.
+and Moura, L.
+(2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol.
+5643, pp.715--720
 
@@
 and Chapman, B.
-(2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proc.
-of the Intl.
-Symp.
-on Parallel Distributed processing}, pp.1049--1058
+(2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proceedings of the International Symposium on Parallel Distributed processing}, pp.1049--1058
 
 \bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
-Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proc. of the Intl. Conf. on Functional Programming}, pp.412--423
+Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proceedings of the International Conference on Functional Programming}, pp.412--423
 
 \bibitem[\protect\citeauthoryear{Sebastiani and Trentin}{2015}]{Patrick2015}
-Sebastiani, R. and Trentin, P. (2015) 'OptiMathSAT: A Tool for Optimization Modulo Theories', {\it Proc. of the Intl. Conf. on Computer Aided Verification}, Vol. 9206, pp.447--454
+Sebastiani, R. and Trentin, P. (2015) 'OptiMathSAT: A Tool for Optimization Modulo Theories', {\it Proceedings of the International Conference on Computer Aided Verification}, Vol. 9206, pp.447--454
 
@@
 \bibitem[\protect\citeauthoryear{Holzmann}{2012}]{Holzmann2012}
-Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proc. of the Intl. Symp. on Model Checking Software}, Vol. 7385, pp.155--171
+Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proceedings of the International Symposium on Model Checking Software}, Vol. 7385, pp.155--171
 

### 2015-11-30 Docs/IJES/journal.tex
Minor changes

@@
 In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
-In~\cite{Trindade2015} and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.
-
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
+In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver~\cite{Wintersteiger2009}.
+
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories~\cite{Bjorner2015}. In particular, 
 $\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
@@
 
-\bibitem[\protect\citeauthoryear{Arato et al.}{2003}]{Arato2003}
+\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2003}]{Arato2003}
 Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202

### 2015-12-01 Docs/IJES/journal.tex
reference problems with IJES text

@@
 Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
-In~\cite{Trindade2015,Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
-The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
+In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
+The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT (~\cite{Bjorner2015}).
 

### 2015-12-02 Docs/IJES/journal.tex
brand new complete version of IJES paper

--- 2015-11-30 Docs/IJES/journal.tex
@@
 
-\authorA{Alessandro Trindade, Hussama Ismail}
-\affA{Federal University of Amazonas \\
-E-mail: \{alessandro.b.trindade, hussamaismail\}@gmail.com}
-
-\authorB{Edilson Galv\~ao, Renato Degelo}
-\affB{Federal University of Amazonas \\
-E-mail: \{rdegelo, esj.galvao\}@gmail.com}
-
-\authorC{Helder Silva, and Lucas Cordeiro}
-\affC{Federal University of Amazonas \\
-E-mail: prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br}
+\authorA{Author A}
+\affA{University A\\
+E-mail: \{nonono\}@nonono.com}
+
+\authorB{Author B}
+\affB{University B\\
+E-mail: \{nonono\}@nonono.com}
+
+%\authorA{Alessandro Trindade, Hussama Ismail}
+%\affA{Federal University of Amazonas \\
+%E-mail: \{alessandro.b.trindade, hussamaismail\}@gmail.com}
+
+%\authorB{Edilson Galv\~ao, Renato Degelo}
+%\affB{Federal University of Amazonas \\
+%E-mail: \{rdegelo, esj.galvao\}@gmail.com}
+
+%\authorC{Helder Silva, and Lucas Cordeiro}
+%\affC{Federal University of Amazonas \\
+%E-mail: prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br}
 
 \begin{abstract}
-We present an alternative approach to solve the hardware and software partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing.
+We present new alternative approaches to solve the hardware and software partitioning problem.
+First we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
 In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
 Each instance checks for a different optimum value until the optimization problem is satisfied.
-We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and also integrate the maximum satisfiability solver $\nu$Z tool into ESBMC.
-We compare all our approaches to another state-of-the-art optimization tool (Matlab).
-Experimental results show that there is no single optimization tool to solve all hardware-software partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve hardware-software partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
+We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
+Other approach integrate the maximum satisfiability solver $\nu$Z tool into ESBMC.
+$\nu$Z provides a portfolio of approaches for solving linear optimization problems over SMT formulas.
+We compare all our approaches to a state-of-the-art optimization tool (MATLAB).
+Experimental results show that there is no single optimization tool to solve all hardware-software partitioning benchmarks.
 \end{abstract}
 
-\KEYWORD{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}
-
-\REF{\textcolor{red}{to this paper should be made as follows: Rodr\'{\i}guez
-Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
-corporate environmental disclosures on the internet: the case of
-IBEX 35 Spanish companies', {\it International Journal of Metadata,
-Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}}
-
+\KEYWORD{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, maximum satisfiability.}
+
+\REF{\textcolor{red}{to this paper should be made as follows: No no no.
+`Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning', {\it International Journal of Embedded Systems}, Vol.
+x, No.
+x, pp.xxx\textendash xxx.}}
+
+%Trindade, A., Ismail, H., Galv\~ao, E., Degelo, R., Silva, H., and Cordeiro, L.%
 \begin{bio}
 \textcolor{red}{
-Manuel Pedro Rodr\'iguez Bol\'ivar received his PhD in Accounting at
-the University of Granada. He is a Lecturer at the Department of
-Accounting and Finance, University of Granada. His research
-interests include issues related to conceptual frameworks of
-accounting, diffusion of financial information on Internet, Balanced
-Scorecard applications and environmental accounting. He is author of
-a great deal of research studies published at national and
-international journals, conference proceedings as well as book
-chapters, one of which has been edited by Kluwer Academic
-Publishers.\vs{9}}
-
-\textcolor{red}{\noindent Bel\'en Sen\'es Garc\'ia received her PhD in Accounting at
-the University of Granada. She is a Lecturer at the Department of
-Accounting and Finance, University of Granada. Her research
-interests are related to cultural, institutional and historic
-accounting and in environmental accounting. She has published
-research papers at national and international journals, conference
-proceedings as well as chapters of books.\vs{8}}
-
-\textcolor{red}{\noindent Both authors have published a book about environmental
-accounting edited by the Institute of Accounting and Auditing,
-Ministry of Economic Affairs, in Spain in October 2003.}
+no no no.\vs{9}}
+
+\textcolor{red}{\noindent No no no.\vs{8}}
+
+\textcolor{red}{\noindent No no no.}
 \end{bio}
@@
 Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
-In~\cite{Trindade2015,Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems.
-The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.
-
-Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
-Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
-All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.
+In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC) as defined in~\cite{Cordeiro2012}, in order to perform HW-SW partitioning in embedded systems.
+In~\cite{Trindade2016} the original ESBMC algorithm was corrected and the right algorithm caused a loss in terms of performance, so a multi-core sequential approach was introduced in order to bring the performance back and turn it similar, in some cases, to conventional optimization tools that are used to perform hardware-software partitioning.
+
+The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification methods, which has been extended and exhauted with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT as defined in ~\cite{Bjorner2015}.
+
+Here, we exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
 
@@
 
-Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}.
-There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}.
+Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}.
+There is no single method available for efficiently solving all optimization problems, according~\cite{Rao2009}.
 The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
@@
 Even with the use of powerful computers, a problem can take hours before an optimal solution is reached.
-If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, according~\cite{Rao2009}, {\it e.g.}, those used in the GA.
 The only drawback is that the found solution may not be the global minimum or maximum.
@@
 This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem~\cite{Clarke2001}.
-
-The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less~\cite{Biere2009}.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, according~\cite{Clarke2001}.
+
+The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}.
 To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.
 
-In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
+In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as shown in~\cite{Cordeiro2012}. 
 In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT.
@@
 
-Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}.
+Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, according~\cite{Ramalho2013}.
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
@@
 The main factor for ESBMC to use only a single-core relies on its back-end ({\it i.e.}, SMT Solver).
-Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}.
+Currently, the SMT solvers supported by ESBMC are: Z3, as shown in~\cite{DeMoura2008}; Boolector, as shown in~\cite{Brummayer2009}; MathSAT, as shown in~\cite{Barrett2011}; CVC4, as shown in~\cite{Bozzano2005}; and Yices, as shown in~\cite{Dutertre2014}.
 Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
@@
 
-The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages~\cite{OpenMP1998}.
+The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages, as defined in~\cite{OpenMP1998}.
 OpenMP supports most processor architectures and operating systems, {\it e.g.}, Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows.
@@
 
-In particular, OpenMP uses the \textit{fork-join} model of parallel execution~\cite{OpenMP1998}.
+In particular, OpenMP uses the \textit{fork-join} model of parallel execution, as shown in~\cite{OpenMP1998}.
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode~\cite{Wu2014}.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode, as shown in~\cite{Wu2014}.
 
@@
 
-In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem~\cite{Bjorner2014}.
-In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes)~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT)~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
-
-In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives~\cite{Bjorner2015}.
+In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as shown in~\cite{Bjorner2014}.
+In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as shown in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+
+In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives, as shown in~\cite{Bjorner2015}.
 In summary, $\nu$Z provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
@@
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
-Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}.
+Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as shown in~\cite{Barth1995} and~\cite{Vasco2005}.
 If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints.
@@
 
-Z3 is available for platforms in C, C$++$, Java, .NET, and Python; it is possible to download Z3 with $\nu$Z from its github repository~\cite{Z3API}.
+Z3 is available for platforms in C, C$++$, Java, .NET, and Python; it is possible to download Z3 with $\nu$Z from its github repository in~\cite{Z3API}.
 In this work, the python API is used to formulate HW-SW partitioning problems using the $\nu$Z tool.
@@
 
-The mathematical modeling of the HW-SW partitioning problem was taken from~\cite{Arato2003,Mann2007}.
+The mathematical modeling of the HW-SW partitioning problem was taken from~\cite{Arato2003} and~\cite{Mann2007}.
 
@@
 Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, where the focus is on bipartitioning ~\cite{Teich2012}.
+That configuration describes a first-generation co-design, where the focus is on bipartitioning, as shown in~\cite{Teich2012}.
 
@@
 \vspace{2 mm}
-\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.
+\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
 
@@
 
-The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}.
+The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
 Both use slack variables in order to be possible to represent constraints and to use commercial tools.
 However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
 
@@
 
-Algorithm~\ref{Pseudocode-describing-ESBMC} shows ESBMC pseudocode with the same constraints and conditions placed on ILP and GA.
+Figure~\ref{Pseudocode-describing-ESBMC} shows ESBMC pseudocode with the same constraints and conditions placed on ILP and GA.
 Two values must be controlled to obtain the results and to perform the optimization.
@@
 
-To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC.
+To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library, according~\cite{Dagum1998}, is used in this present work as a front-end for ESBMC.
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
@@
 
-Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
-
-Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
+Algorithm at Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
+
+Note that algorithm of Figure~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
 From lines $4$ to $9$, the algorithm finds the largest interval.
@@
 \vspace {2 mm}
-Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
+Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
 The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$).
@@
 
-Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}.
+Algorithm of Figure~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions, as seen in~\cite{Bjorner2014}.
 A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the set of constraints.
@@
 The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
-Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.
+Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as shown in~\cite{Mann2007}.
 
@@
 A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11.
-Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
-ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.
-For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}.
-MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.
+Version $2$.$0$.$1$ of Boolector SMT-solver, as shown in~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
+ESBMC-$\nu$Z as a built-in tool to Z3 was also used, as shown in~\cite{Bjorner2014}.
+For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used, as shown in~\cite{TheMathWorks2013}.
+MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software, as shown in~\cite{Tranquillo2011} and is widely used by the engineering community, as shown in~\cite{Hong2010}.
 
@@
 Software and communication costs are time dimensional, and hardware costs represent the occupied area.
-The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}.
+The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}.
 The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
@@
 \midrule
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as shown in~\cite{Guthaus2001}\\
 \hline
 \verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
-\vspace{0.8 mm} Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
-\hline
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph ~\cite{Guthaus2001}\\
+\vspace{0.8 mm} Routine to insert values in Patricia Tree, as shown in ~\cite{Guthaus2001}\\
+\hline
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as shown in~\cite{Guthaus2001}\\
 \hline
@@
 
-Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution~\cite{Mann2007}, to use heuristics to speed up performance time~\cite{Arato2003}, and hybrid ones~\cite{Arato2005}.
+Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution, as shown in~\cite{Mann2007}; to use heuristics to speed up performance time, as shown in~\cite{Arato2003}; and hybrid ones, as shown in~\cite{Arato2005}.
 
@@
 In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
-In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
-In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver~\cite{Wintersteiger2009}.
-
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories~\cite{Bjorner2015}. In particular, 
-$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}.
-As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed fu	nctional programming languages and reports the most useful one subject to some usefulness criterion.
+In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
+In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way but the first had performance issues that were correct by the second, which used only a sequential search to perform multi-core model checking.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver, according~\cite{Wintersteiger2009}.
+
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}. In particular, 
+$\nu$Z tool offers substantial performance improvement in optimization problems, according~\cite{Bjorner2014} and ~\cite{Bjorner2015}.
+As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
 The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.

### 2015-12-03 Docs/IJES/journal.tex
minor changes

@@
 
-\LRH{A. Trindade et~al.}
+%\LRH{A. Trindade et~al.}
 
@@
 \begin{abstract}
-We present new alternative approaches to solve the hardware and software partitioning problem.
-First we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores.
-Each instance checks for a different optimum value until the optimization problem is satisfied.
+We present new alternative approaches to solve the hardware and software (HW-SW) partitioning problem.
+First, we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
+In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores.
+In particular, each instance checks for a different optimum value until the optimization problem is satisfied.
 We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
-Other approach integrate the maximum satisfiability solver $\nu$Z tool into ESBMC.
-$\nu$Z provides a portfolio of approaches for solving linear optimization problems over SMT formulas.
-We compare all our approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all hardware-software partitioning benchmarks.
+Additionally, we integrate the maximum satisfiability solver $\nu$Z tool into ESBMC, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas.
+We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but ESBMC-$\nu$Z outperforms all parallel approaches proposed in this paper.
 \end{abstract}
@@
 Nowadays, with the strong development of embedded systems, the design phase plays an important role.
-At early stages, the design is split into separated flows: hardware and software.
-The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which one in software (SW), must be supported by any well-structured methodology.
+At early stages, the design is split into separated flows: hardware (HW) and software (SW).
+The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware and which one in software, must be supported by any well-structured methodology.
 If there is no methodology support, a number of issues, {\it e.g.}, design flow interruptions, redesigns, and undesired iterations may affect the overall development process, the quality, and the life-cycle of the final system.
 
-Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
+Starting at the $90$'s decade, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
 In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC) as defined in~\cite{Cordeiro2012}, in order to perform HW-SW partitioning in embedded systems.
-In~\cite{Trindade2016} the original ESBMC algorithm was corrected and the right algorithm caused a loss in terms of performance, so a multi-core sequential approach was introduced in order to bring the performance back and turn it similar, in some cases, to conventional optimization tools that are used to perform hardware-software partitioning.
-
-The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification methods, which has been extended and exhauted with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT as defined in ~\cite{Bjorner2015}.
-
-Here, we exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
-Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+In~\cite{Trindade2016}, the original ESBMC algorithm was improved in terms of performance, so a multi-core sequential approach was introduced, in order to speed up the performance and turn it similar, in some cases, to conventional optimization tools, which are used to perform HW-SW partitioning.
+
+The present work thus extends those previous studies since there is a substantial improvement in terms of the SMT-based verification methods.
+In particular, we extend the work of~\cite{Trindade2015} and~\cite{Trindade2016} to exploit a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT as defined in~\cite{Bjorner2015}.
+
+We exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; thus, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according to~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according to~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
 All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
@@
 
-Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.
+Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page \texttt{http://esbmc.org/}.
+
+\subsection{Organization of this Work}
 
@@
 Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}.
-There is no single method available for efficiently solving all optimization problems, according~\cite{Rao2009}.
+There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}.
 The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
@@
 Even with the use of powerful computers, a problem can take hours before an optimal solution is reached.
-If the optimization problem is complex, some heuristics can be used to solve the same problem faster, according~\cite{Rao2009}, {\it e.g.}, those used in the GA.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, according to~\cite{Rao2009}, {\it e.g.}, those used in the GA.
 The only drawback is that the found solution may not be the global minimum or maximum.
@@
 This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, according~\cite{Clarke2001}.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, according to~\cite{Clarke2001}.
 
@@
 
-Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, according~\cite{Ramalho2013}.
+Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, according to~\cite{Ramalho2013}.
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
@@
 
-To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library, according~\cite{Dagum1998}, is used in this present work as a front-end for ESBMC.
+To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library, according to~\cite{Dagum1998}, is used in this present work as a front-end for ESBMC.
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
@@
 In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
-In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way but the first had performance issues that were correct by the second, which used only a sequential search to perform multi-core model checking.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver, according~\cite{Wintersteiger2009}.
-
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}. In particular, 
-$\nu$Z tool offers substantial performance improvement in optimization problems, according~\cite{Bjorner2014} and ~\cite{Bjorner2015}.
+In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver, according to~\cite{Wintersteiger2009}.
+
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
+In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, according to~\cite{Bjorner2014} and~\cite{Bjorner2015}.
 As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
@@
 
-\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2016}]{Trindade2016}
+\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2015}]{Trindade2016}
 Trindade, A., Ismail, H.
 and Cordeiro, L.
-(2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering (to appear)}
+(2015) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering (to appear)}
 

### 2015-12-03 Docs/IJES/journal.tex
add line numbers to the algorithms

@@
 %%%%%%%%%%%%%%%%%
+
+\lstset{language=C,basicstyle=\small}
+\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
+\lstset{tabsize=2}
+\lstset{firstnumber=1}
+\lstset{frame=single}
+\lstset{
+  language={C},
+  morekeywords={assert,uchar}
+}
 
@@
 
-Algorithm at Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
+Algorithm in Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.
 
@@
 Then, from line $10$ the largest interval is removed and the median is calculated in line $11$.
-After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$).
+After that, two new intervals are created, the left side (in line $14$) and the right side (in line $18$).
 At the end, the median is returned.

### 2015-12-03 Docs/IJES/journal.tex
minor changes

@@
 \maketitle
+\clearpage
 
@@
 
+\vspace{-5 mm}
 Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
@@
 
+\vspace{-5 mm}
 As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$.
@@
 
+\vspace{-4 mm}
 Note that there might gaps between steps, which are produced by the customized binary-search.
@@
 
+\vspace{-1.5 mm}
 \begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
@@
 
-\vspace {2 mm}
+\vspace {-1.5 mm}
 Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
@@
 
+\vspace {-2 mm}
 %----------------------------------------------
@@
 %----------------------------------------------
-To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
-The nodes in the graphs correspond to high-level language instructions.
-Software and communication costs are time dimensional, and hardware costs represent the occupied area.
-The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}.
-The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
-From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
-
-\vspace{5 mm}
-\hspace{-5 mm}
+
 \begin{minipage}{\linewidth}
@@
 
+\vspace{-3 mm}
+To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
+The nodes in the graphs correspond to high-level language instructions.
+Software and communication costs are time dimensional, and hardware costs represent the occupied area.
+The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}.
+The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
+From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
+
 %----------------------------------------------
@@
 
+\vspace {-4 mm}
 %----------------------------------------------

### 2015-12-03 Docs/IJES/journal.tex
New Final version: abstract word count problem solved

@@
 First, we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores.
+Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores.
 In particular, each instance checks for a different optimum value until the optimization problem is satisfied.
@@
 We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but ESBMC-$\nu$Z outperforms all parallel approaches proposed in this paper.
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks.
 \end{abstract}

### 2016-08-09 Docs/IJES/revised/journal.tex
revised paper at 8th of August by ABT

--- 2015-12-03 Docs/IJES/journal.tex
@@
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
+Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, and $Aeq$ and $beq$ are matrixes that describe the linear equality constraints
 
@@
 \item{\textbf{maximize(T)}
-this function informs to the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
+this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
 \item{\textbf{minimize(T)}
-this function informs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}
+this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}
 \item{\textbf{Assert-Soft F : weight n}
@@
 
-The inputs of the problem are: a directed simple graph $ G = (V,E) $, called the task graph of the system, is necessary.
-The vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned.
+A directed simple graph $ G = (V,E) $, called the task graph of the system, is given.
+Where the vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned.
 The edges $E$ represent communication between components.
@@
 
-Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
-The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $.
+$P$ is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$.
+The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}.
 The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
@@
 \vspace{2 mm}
-Three different optimization and decision problems can be defined.
-In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints.
+Different optimization (and decision) problems can be defined, \cite{Arato2003}.
+In this paper, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related .
 Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
@@
 \vspace{2 mm}
-\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
+\noindent where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: 1 if the node is realized in hardware and 0 if node is realized in software).
+Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
 
@@
 The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
-Both use slack variables in order to be possible to represent constraints and to use commercial tools.
+Both use slack variables in order to eliminate the modulus operator of Eq.~\ref{hw-sw-partitioning} and to use commercial tools.
 However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
@@
 The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
-$S_0$ must also be defined, as the transposed incidence matrix and the identity matrix, as typically done in MATLAB.
+$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\ref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.
 Here, matrices $A$ and $b$ are generated.
@@
 Declare transposed incidence matrix graph G(E)
-Define the solutions ($X_i$) as Boolean
+Define the solutions ($x_i$) as Boolean
 main {
  For TipH = 0 to Hmax Do {
-  Populate $X_i$ with nondet / test values
-  Calculate s(1-x)+c|Ex| and store at variable
-  Requirement isued by Assume (variable <= $S_0$)
-  Calculate Hp cost Based on value of $X_i$
+  Populate $x_i$ with nondet (the values of test)
+  Calculate s_i(1-x_i)+c|Ex_i| and store at variable
+  Requirement enforced by Assume (variable <= $S_0$)
+  Calculate Hp cost Based on value of $x_i$
   Violation check with Assert(Hp > TipH)
@@
 \vspace{2 mm}
-It is possible to inform to ESBMC with which type of values the variables must be tested.
+It is possible to instruct ESBMC with which type of values the variables must be tested.
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
@@
 
-A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware.
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware (Hmax).
 To every test performed, the hardware hint is compared to the feasible solution.
@@
 
-In the ESBMC algorithm is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.
+In the ESBMC algorithm is not necessary to add slack variables at Eq.~\ref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.
 
@@
 \textit{Fobj} should be minimized to obtain the optimal hardware solution.
-To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
+To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one instructs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized.
 Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that
@@
 
-\bibitem[\protect\citeauthoryear{Paci et al}{2008}]{Federica2008}
+\bibitem[\protect\citeauthoryear{Paci \textit{et al.}}{2008}]{Federica2008}
 Paci, F., Ferrini, R., Sun, Y.

### 2016-08-09 Docs/IJES/journal.tex
What is the meaning of "Aeq" and "beq" in Eq. 1?

@@
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
+Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints
 
@@
 
-\vspace{-5 mm}
 Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.

### 2016-08-09 Docs/IJES/journal.tex
[A-6] In page 5, "Based on ..., (?) is called ..." (please, re-write the sentence).
[A-7] In page 5, "Three different optimization and decision problems", what are these problems? Is the problem addressed among these? why does you focus on that specific problem?

@@
 \vspace{2 mm}
-Different optimization (and decision) problems can be defined, \cite{Arato2003}.
-In this paper, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related .
-Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as
+In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
+In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
+Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as
 

### 2016-08-09 Docs/IJES/journal.tex
[A-8] In eq. 4, what is "E" ? does "x" represent a vector or a single number? what is "s"? what is "c"? (please, explain the variables, parameters, operators, etc. of the eq.).

@@
 \vspace{2 mm}
-\noindent where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: 1 if the node is realized in hardware and 0 if node is realized in software).
+\noindent where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software).
 Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.

### 2016-08-09 Docs/IJES/journal.tex
[A-10] In page 5 (right column), I think that the text "The ESBMC ... (2015)" is unclear and it should be rewritten. Beside, why do you use a "transposed incidence matrix" and "identity matrix"? (maybe is it related to eq. 4??).

@@
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints
+Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints
 
@@
 The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}.
-The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
+The hardware cost of $P$ is given by Eq.~\eqref{hardware-costs}
 
@@
 \noindent
-and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
+and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\eqref{software-communication-costs}
 
@@
 The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
-Both use slack variables in order to eliminate the modulus operator of Eq.~\ref{hw-sw-partitioning} and to use commercial tools.
+Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.
 However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
@@
 The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
-$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\ref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.
+$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.
 Here, matrices $A$ and $b$ are generated.
@@
 
-In the ESBMC algorithm is not necessary to add slack variables at Eq.~\ref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.
+In the ESBMC algorithm is not necessary to add slack variables at Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.
 
@@
 
-The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}.
+The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}.
 Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.

### 2016-08-09 Docs/IJES/journal.tex
[A-13] In page 6 (left column), please, rewrite the last sentence in Section 4.2: "In the ... ? is not ...".

@@
   language={C},
-  morekeywords={assert,uchar}
+  morekeywords={assert,uchar,assume,For,do}
 }
@@
 
+\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}
+
 The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
@@
 Declare number of nodes and edges
-Declare hardware cost of each node as array (h)
-Declare software cost of each node as array (s)
-Declare communication cost of each edge (c)
+Declare the maximum hardware cost ($H_{max}$)
+Declare hardware cost of each node as array ($h$)
+Declare software cost of each node as array ($s$)
+Declare communication cost of each edge ($c$)
 Declare the initial sw cost of ($S_0$)
-Declare transposed incidence matrix graph G(E)
-Define the solutions ($x_i$) as Boolean
+Declare transposed incidence matrix graph $G(E)$
+Define the decision variables ($x_i$) as Boolean
 main {
- For TipH = 0 to Hmax Do {
-  Populate $x_i$ with nondet (the values of test)
-  Calculate s_i(1-x_i)+c|Ex_i| and store at variable
-  Requirement enforced by Assume (variable <= $S_0$)
-  Calculate Hp cost Based on value of $x_i$
-  Violation check with Assert(Hp > TipH)
+ For $TipH=0$ to $H_{max}$ do {
+  Populate $x_i$ with non-deterministic values
+  Calculate $s_i(1-x_i)+c|Ex_i|$ and store in variable
+  Requirement enforced by assume(variable $\leq$ $S_0$)
+  Calculate $H_p$ cost based on value of $x_i$
+  Violation check with assert($Hp > TipH$)
  }
@@
 
-A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware (Hmax).
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware ($H_{max}$).
 To every test performed, the hardware hint is compared to the feasible solution.
@@
 
-In the ESBMC algorithm is not necessary to add slack variables at Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.
+In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.
 

### 2016-08-09 Docs/IJES/journal.tex
updated paper version

@@
 
-\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}
+Remembering that, as defined by formal model, there is a index of each decision variable, indicated by letter "i", which ranges from zero to the number of nodes of the problem to be solved.
+
+%\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}
 
@@
 A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
+The TO was defined based in previous empiric tests, where a bigger TO (5000 seconds, for example) do not caused difference in the results.
 
@@
 &  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
+&  \normalsize{Hp}   &  \normalsize{17}   &  \normalsize{47}   &  \normalsize{40}   &  \normalsize{245}   &  \normalsize{647}    &  \normalsize{8619}   &  -  \\
 &  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
@@
 The idea is to use a heuristic to speed up some phase of an exact solution tool.
-It worth mentioning that the final solution is not necessarily an optimal global solution.
+It is worth mentioning that the final solution is not necessarily an optimal global solution.
 Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.

### 2016-08-09 Docs/IJES/journal.tex
resolving comments for IJES

@@
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
-Those values that change for each test will generate a possible solution and obey the constraints.
-If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).
+\textcolor{blue}{Those values are selected by the SMT Solver during its execution, which is responsible to test once all possible combinations in order to yield a feasible solution.
+If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
 

### 2016-08-10 Docs/IJES/journal.tex
[A-14] In ESBMC-SS, how are the decision variables selected in each instance? Could a solution be evaluated several times in a same iteration or/and in different iterations?

@@
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
-\textcolor{blue}{Those values are selected by the SMT Solver during its execution, which is responsible to test once all possible combinations in order to yield a feasible solution.
+\textcolor{blue}{As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}.
 If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

### 2016-08-10 Docs/IJES/journal.tex
[A-18] In Table 2, why is it showed the error rate for GA? (why is not it showed value Hp?).

@@
 
-\vspace{-5 mm}
 As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$.
@@
 
-\vspace{-4 mm}
 Note that there might gaps between steps, which are produced by the customized binary-search.
@@
 
-\vspace{-1.5 mm}
 \begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
@@
 
-\vspace {-1.5 mm}
 Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances.
@@
 
-\vspace {-2 mm}
 %----------------------------------------------

### 2016-08-10 Docs/IJES/journal.tex
Response: We included an explanation in the paper (at the end of Section 5.1) as follows: “The TO was defined based on previous empirical tests, where a larger TO (e.g., 5000 seconds) did not produce substantial differences in the experimental results.

@@
 A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
-The TO was defined based in previous empiric tests, where a bigger TO (5000 seconds, for example) do not caused difference in the results.
+\textcolor{blue}{The TO was defined based on previous empirical tests, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
 

### 2016-08-10 Docs/IJES/journal.tex
[A-22] In page 9 (right column), "It [is] worth mentioning".
mark implemented comments using the blue color

@@
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints
+\textcolor{blue}{Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints}
 
@@
 \item{\textbf{maximize(T)}
-this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
+\textcolor{blue}{this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}}
 \item{\textbf{minimize(T)}
-this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}
+\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}}
 \item{\textbf{Assert-Soft F : weight n}
@@
 
-A directed simple graph $ G = (V,E) $, called the task graph of the system, is given.
+\textcolor{blue}{A directed simple graph $ G = (V,E) $, called the task graph of the system, is given.
 Where the vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned.
@@
 Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(V_i)$ (or $ s_i $) of software if implemented in software.
-Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).
+Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).}
 
@@
 \vspace{2 mm}
-In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
+\textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
 In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
-Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as
+Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as}
 
@@
 \vspace{2 mm}
-\noindent where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software).
+\noindent \textcolor{blue}{ where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
 Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
@@
 
-The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
-$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.
-Here, matrices $A$ and $b$ are generated.
+\textcolor{blue}{The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
+$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.} Here, matrices $A$ and $b$ are generated.
 At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.
@@
 \vspace{2 mm}
-It is possible to instruct ESBMC with which type of values the variables must be tested.
+\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be tested.
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
-\textcolor{blue}{As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}.
+As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}.
 If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
@@
 
-In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.
+\textcolor{blue}{In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.}
 
@@
 The idea is to use a heuristic to speed up some phase of an exact solution tool.
-It is worth mentioning that the final solution is not necessarily an optimal global solution.
+\textcolor{blue}{It is worth mentioning} that the final solution is not necessarily an optimal global solution.
 Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.

### 2016-08-10 Docs/IJES/journal.tex
update references

@@
 \bibitem[\protect\citeauthoryear{Trindade and Cordeiro}{2015}]{Trindade2015}
-Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems (to appear)}
+Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems}, Vol. 20, No. 1, pp. 1--19
 
@@
 and Cordeiro, L.
-(2015) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering (to appear)}
+(2015) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering}, pp.
+102--105
 

### 2016-08-15 Docs/IJES/journal.tex
revised version of paper

@@
 
-Starting at the $90$'s decade, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
-In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC) as defined in~\cite{Cordeiro2012}, in order to perform HW-SW partitioning in embedded systems.
-In~\cite{Trindade2016}, the original ESBMC algorithm was improved in terms of performance, so a multi-core sequential approach was introduced, in order to speed up the performance and turn it similar, in some cases, to conventional optimization tools, which are used to perform HW-SW partitioning.
-
-The present work thus extends those previous studies since there is a substantial improvement in terms of the SMT-based verification methods.
-In particular, we extend the work of~\cite{Trindade2015} and~\cite{Trindade2016} to exploit a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT as defined in~\cite{Bjorner2015}.
-
-We exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; thus, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+%-----------------related work came to here and was rewriten
+\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem, {\it i.e.}, to find the exact solution of a optimization problem, as shown in~\cite{Mann2007}; to use heuristics to speed up performance time, as shown in~\cite{Arato2003} and~\cite{Arato2005}.
+It is worth mentioning that the using heuristics the final solution is not necessarily an optimal global solution.}
+
+\textcolor{blue}{In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
+In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver, according to~\cite{Wintersteiger2009}.}
+
+\textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
+In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, according to~\cite{Bjorner2014} and~\cite{Bjorner2015}.
+As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
+The authors formulate this alternative single-core approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.}
+
+\textcolor{blue}{At this work, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
 Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according to~\cite{Bjorner2015}.
@@
 All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
-
-\subsection{Contributions}
-
-The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
+To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.}
+
+%-----------------
+%Starting at the $90$'s decade, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
+In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC) as defined in~\cite{Cordeiro2012}, in order to perform HW-SW partitioning in embedded systems.
+In~\cite{Trindade2016}, the original ESBMC algorithm was improved in terms of performance, so a multi-core sequential approach was introduced, in order to speed up the performance and turn it similar, in some cases, to conventional optimization tools, which are used to perform HW-SW partitioning.
+
+%The present work thus extends those previous studies since there is a substantial improvement in terms of the SMT-based verification methods.
+In particular, we extend the work of~\cite{Trindade2015} and~\cite{Trindade2016} to exploit a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization \textcolor{blue}{single-core} tool based on SMT as defined in~\cite{Bjorner2015}.
+
+%We exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; thus, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according to~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according to~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
+
+%The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
+Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
+Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
+Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.
+To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.
+
+%\subsection{Contributions}
+
+%The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
 Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
@@
 
-Remembering that, as defined by formal model, there is a index of each decision variable, indicated by letter "i", which ranges from zero to the number of nodes of the problem to be solved.
+\textcolor{blue}{Remembering that, as defined by formal model, there is a index of each decision variable, indicated by letter "i", which ranges from zero to the number of nodes of the problem to be solved.}
 
@@
 %----------------------------------------------
-\section{Related Work}
-\label{Related-Work}
-%----------------------------------------------
-
-Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution, as shown in~\cite{Mann2007}; to use heuristics to speed up performance time, as shown in~\cite{Arato2003}; and hybrid ones, as shown in~\cite{Arato2005}.
-
-In the first group, the exact solution to the HW-SW partitioning problem is found.
+%\section{Related Work}
+%\label{Related-Work}
+%----------------------------------------------
+
+%Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution, as shown in~\cite{Mann2007}; to use heuristics to speed up performance time, as shown in~\cite{Arato2003}; and hybrid ones, as shown in~\cite{Arato2005}.
+
+%In the first group, the exact solution to the HW-SW partitioning problem is found.
 The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithms.
 The difference is based only on the technique chosen to solve the problem.
-Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution.
+%Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution.
 The difference of this kind of solution to SMT-based verification and maximum satisfiability is based on two facts: all ESBMC implementations guarantee to find the exact solution, but heuristics are faster, when the complexity is greater.
 
-Finally, there are approaches that mixes heuristics with exact solution tools.
+%Finally, there are approaches that mixes heuristics with exact solution tools.
 The idea is to use a heuristic to speed up some phase of an exact solution tool.
@@
 
-In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+%In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
 In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
@@
 
-Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
+%Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
 In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, according to~\cite{Bjorner2014} and~\cite{Bjorner2015}.
@@
 
-The problem addressed in this present paper uses a single objective function for minimization.
+%The problem addressed in this present paper uses a single objective function for minimization.
 In~\cite{Patrick2015}, OptiMathSAT and $\nu$Z are compared for software optimization problems.

### 2016-08-16 Docs/IJES/journal.tex
revised version of the paper

@@
 MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software, as shown in~\cite{Tranquillo2011} and is widely used by the engineering community, as shown in~\cite{Hong2010}.
+
+\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer’s processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
+Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}
 
@@
 
+\textcolor{blue}{Regarding the amount of MO of sequential ESBMC, it has to explore all the states until to find out the answer of HW-SW partitioning, and it starts from an extreme where all the variables are selected as software, and go testing incrementally one by one.
+In the other hand, all the multi-core ESBMCs and SBMC-$\nu$Z, are optimized to reach faster the result, without the need to explore the states as sequential ESBMC does.
+Therefore, when the partitioning problem grows in complexity is natural do reach MO with sequential ESBMC.}
+
 \begin{table*}[ht]
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-Below that, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and notorious.
-ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and its result precise.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
@@
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+\textcolor{blue}{However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+However, it is possible to use free GA and ILP libraries (BSD-Style and MIT licenses) as well.}
+
 Experimental results also pointed to an improvement of ESBMC, when using a parallel approach.
-In particular, all three parallel approaches described in this paper produced expressive results.
-The fastest ESBMC approaches is ESBMC-PB, which produces good results for an intermediate amount of edges and nodes.
+The fastest ESBMC approach is ESBMC-PB, which produces good results for an intermediate amount of edges and nodes.
 Thus, considering that nowadays processors have more and more cores, when modeling the problem, it is possible to consider multi-core model checking as an alternative to solve the HW-SW partitioning problem.

### 2016-08-17 Docs/IJES/journal.tex
[A-26] Is ESBMC-vZ a multi-core proposal? I think that the experimental results are contradictory with regards to title and address of your investigation. In consequence, the contributions and research directions should be clearly express and discussing in the abstract, introduction and conclusions.

@@
 In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver, according to~\cite{Wintersteiger2009}.}
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solving, as described by~\cite{Wintersteiger2009}.}
 
 \textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
-In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, according to~\cite{Bjorner2014} and~\cite{Bjorner2015}.
+In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, as described by~\cite{Bjorner2014} and~\cite{Bjorner2015}.
 As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
@@
 \textcolor{blue}{At this work, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
-Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according to~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according to~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
+Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, as described by~\cite{Bjorner2015}.
+The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, as described in~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
 All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
@@
 Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}.
-There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}.
+There is no single method available for efficiently solving all optimization problems, as described by~\cite{Rao2009}.
 The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
@@
 Even with the use of powerful computers, a problem can take hours before an optimal solution is reached.
-If the optimization problem is complex, some heuristics can be used to solve the same problem faster, according to~\cite{Rao2009}, {\it e.g.}, those used in the GA.
+If the optimization problem is complex, some heuristics can be used to solve the same problem faster, as described by~\cite{Rao2009}, {\it e.g.}, those used in the GA.
 The only drawback is that the found solution may not be the global minimum or maximum.
@@
 This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, according to~\cite{Clarke2001}.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, as described by~\cite{Clarke2001}.
 
@@
 
-Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, according to~\cite{Ramalho2013}.
+Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, as described by~\cite{Ramalho2013}.
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.
@@
 
-To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library, according to~\cite{Dagum1998}, is used in this present work as a front-end for ESBMC.
+To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library, as described in~\cite{Dagum1998}, is used in this present work as a front-end for ESBMC.
 Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and its result precise.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and its result is precise.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.

### 2016-08-17 Docs/IJES/journal.tex
[A-25] What is the reason to obtain MO in ESBMC but not in ESMBC-(SS|PS|PB|vZ)? I think that it should be analyzed.

@@
 
-\textcolor{blue}{Regarding the amount of MO of sequential ESBMC, it has to explore all the states until to find out the answer of HW-SW partitioning, and it starts from an extreme where all the variables are selected as software, and go testing incrementally one by one.
-In the other hand, all the multi-core ESBMCs and SBMC-$\nu$Z, are optimized to reach faster the result, without the need to explore the states as sequential ESBMC does.
-Therefore, when the partitioning problem grows in complexity is natural do reach MO with sequential ESBMC.}
+\textcolor{blue}{Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware.
+In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does.
+As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion.}
 

### 2016-08-17 Docs/IJES/journal.tex
minor changes

@@
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-\textcolor{blue}{However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
-However, it is possible to use free GA and ILP libraries (BSD-Style and MIT licenses) as well.}
+\textcolor{blue}{ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+Similarly, it is also possible to use free GA and ILP libraries (BSD-Style and MIT licenses) for different programing languages.}
 

### 2016-08-18 Docs/IJES/journal.tex
revised version

@@
 In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
-Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as}
+Therefore, the objective function is:}
+
+\vspace{-2 mm}
+\begin{align}
+\label{objective-function}
+minimize\quad h_x 
+\end{align}
+
+\textcolor{blue}{Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as:}
 
@@
 \label{hw-sw-partitioning}
-s\left(1-x\right) + c|Ex| \leq S_0, 
+s\left(1-x\right) + c|Ex| \leq S_0
 \end{align}
 
+\vspace{-2 mm}
+\begin{align}
+\label{hw-sw-partitioning2}
+x \in \{0,1\}^n 
+\end{align}
+
 \vspace{2 mm}
-\noindent \textcolor{blue}{ where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
+\textcolor{blue}{Where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
 Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
@@
 The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
-Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.
-However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
+\textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.} However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
 The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
+\textcolor{blue}{All the parameters of ILP and GA algorithms were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
+Choosing ILP and GA, over other possible optimization techniques, it is due to the fact that these techniques were used in related work, as~\cite{Arato2003} and~\cite{Mann2007}, facilitating the comparison with the techniques that we propose in this paper.}
 
@@
 Each time was measured $3$ times (average taken).
+\textcolor{blue}{Empirical tests done by authors  demonstrated that a higher number of measurements, of each technique, did not produce significant differences in the experimental results (always below of 10\%, and mostly around 3\%).}
+
 Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
@@
 A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
-\textcolor{blue}{The TO was defined based on previous empirical tests, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
+\textcolor{blue}{The TO was defined based on previous empirical tests as well, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
 
@@
 From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
+\textcolor{blue}{The amount and types of benchmarks they were kept of related work to enable comparison with the techniques presented in this work.}
 
@@
 \bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2003}]{Arato2003}
-Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202
-
-\bibitem[\protect\citeauthoryear{Mann \textit{et al.}}{2007}]{Mann2007}
-Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263
-
-\bibitem[\protect\citeauthoryear{Trindade and Cordeiro}{2015}]{Trindade2015}
-Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems}, Vol. 20, No. 1, pp. 1--19
-
-\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2015}]{Trindade2016}
-Trindade, A., Ismail, H.
-and Cordeiro, L.
-(2015) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering}, pp.
-102--105
-
-\bibitem[\protect\citeauthoryear{Bjorner \textit{et al.}}{2015}]{Bjorner2015}
-Bjorner, N., Phan, A.
-and Fleckenstein, L.
-(2015) 'vZ - An Optimizing SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
-9035, pp.194--199
-
-\bibitem[\protect\citeauthoryear{Tang \textit{et al.}}{2010}]{Tang2009}
-Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proceedings of the International Conference on Computer Science Education}, pp.1900--1905
-
-\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
-Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}
-
-\bibitem[\protect\citeauthoryear{Cordeiro \textit{et al.}}{2012}]{Cordeiro2012}
-Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974
-
-\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
-Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'
-
-\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
-Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}
-
-\bibitem[\protect\citeauthoryear{Clarke \textit{et al.}}{2001}]{Clarke2001}
-Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34
+Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202.
+
+\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2005}]{Arato2005}
+Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156.
 
@@
 11, No.
-1, pp.69--83
-
-\bibitem[\protect\citeauthoryear{Ganai and Gupta}{2006}]{Ganai2006}
-Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proceedings of the IEEE/ACM International Conference on Computer-Aided Design}, pp.794--801
-
-\bibitem[\protect\citeauthoryear{Ramalho \textit{et al.}}{2013}]{Ramalho2013}
-Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L.
-and Fischer, B.
-(2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it International Conference and Workshops on the Engineering of Computer-Based Systems}, pp.147--156
-
-\bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
-Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340
-
-\bibitem[\protect\citeauthoryear{Brummayer and Biere}{2009}]{Brummayer2009}
-Brummayer, R.
-and Biere, A.
-(2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
-5505, pp.174--177
+1, pp.69--83.
 
@@
 (2011) 'CVC4', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol.
-6806, pp.171--177
+6806, pp.171--177.
+
+\bibitem[\protect\citeauthoryear{Barth and Putnam}{1995}]{Barth1995}
+Barth, P. and Putnam, D. (1995) 'Enumeration Algorithm for Linear Pseudo-Boolean Optimization', {\it Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science}.
+
+\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
+Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}.
+
+\bibitem[\protect\citeauthoryear{Bjorner and Phan}{2014}]{Bjorner2014}
+Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proceedings of the International Symposium on Symbolic Computation in Software Science}, pp.1--10.
+
+\bibitem[\protect\citeauthoryear{Bjorner \textit{et al.}}{2015}]{Bjorner2015}
+Bjorner, N., Phan, A.
+and Fleckenstein, L.
+(2015) 'vZ - An Optimizing SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+9035, pp.194--199.
 
@@
 35, No.
-1-3, pp.265--293
+1-3, pp.265--293.
+
+\bibitem[\protect\citeauthoryear{Brummayer and Biere}{2009}]{Brummayer2009}
+Brummayer, R.
+and Biere, A.
+(2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, Vol.
+5505, pp.174--177.
+
+\bibitem[\protect\citeauthoryear{Clarke \textit{et al.}}{2001}]{Clarke2001}
+Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34.
+
+\bibitem[\protect\citeauthoryear{Cordeiro and Fischer}{2011}]{Cordeiro2011}
+Cordeiro, L.
+and Fischer, B.
+(2011) 'Verifying multi-threaded software using SMT-based context-bounded model checking', {\it Proceedings of the International Conference on Software Engineering}, pp.331--340.
+
+\bibitem[\protect\citeauthoryear{Cordeiro \textit{et al.}}{2012}]{Cordeiro2012}
+Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974.
+
+\bibitem[\protect\citeauthoryear{Cormen \textit{et al.}}{2009}]{Cormem}
+Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292.
+
+\bibitem[\protect\citeauthoryear{Dagum and Menon}{1998}]{Dagum1998}
+Dagum, L. and Menon, R. (1998) 'OpenMP: An Industry-Standard API for Shared-Memory Programming', {\it Proceedings of the International Conference on Computational Science Engineering}, pp.46--55.
 
 \bibitem[\protect\citeauthoryear{Dutertre}{2014}]{Dutertre2014}
-Dutertre, B. (2014) 'Yices 2.2', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol. 8559, pp.737--744
-
-\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
-Wu M., Wu, W., Tai, N., Zhao, H., Fan, J.
-and Yuan, N.
-(2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proceedings of the International Conference on Software Engineering and Service Science}, pp.921--924
-
-\bibitem[\protect\citeauthoryear{Bjorner and Phan}{2014}]{Bjorner2014}
-Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proceedings of the International Symposium on Symbolic Computation in Software Science}, pp.1--10
+Dutertre, B. (2014) 'Yices 2.2', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol. 8559, pp.737--744.
+
+\bibitem[\protect\citeauthoryear{Ganai and Gupta}{2006}]{Ganai2006}
+Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proceedings of the IEEE/ACM International Conference on Computer-Aided Design}, pp.794--801.
+
+\bibitem[\protect\citeauthoryear{Guthaus \textit{et al.}}{2011}]{Guthaus2001}
+Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T.
+and Brown, R.
+(2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proceedings of the annual workshop on workload characterization}, pp.3--14.
+
+\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann2011}
+Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857.
+
+\bibitem[\protect\citeauthoryear{Holzmann}{2012}]{Holzmann2012}
+Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proceedings of the International Symposium on Model Checking Software}, Vol. 7385, pp.155--171.
+
+\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2010}
+Hong, L.
+and Cai, J.
+(2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proceedings of the International Conference on Computer and Automation Engineering}, pp.185--189.
+
+\bibitem[\protect\citeauthoryear{Mann \textit{et al.}}{2007}]{Mann2007}
+Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263.
+
+\bibitem[\protect\citeauthoryear{Manquinho and Marques-Silva}{1995}]{Vasco2005}
+Manquinho, V. and Marques-Silva, J. (1995) 'Effective Lower Bounding Techniques for Pseudo-Boolean Optimization', {\it IST/INESC-ID, Technical University of Lisbon, Portugal}.
+
+\bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
+MathWorks Inc. (2013) 'MATLAB (version R2013a)'.
+
+\bibitem[\protect\citeauthoryear{Microsoft Research}{2015}]{Z3API}
+Microsoft Research (2015) 'Z3 API - Source code and documentation' [online] {\it https://z3.codeplex.com/} (Accessed 18 August 2015).
+
+\bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
+Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proceedings of the International Conference on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340.
+
+\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
+Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}.
+
+\bibitem[\protect\citeauthoryear{Narodytska and Bacchus}{2014}]{NarodytskaN}
+Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proceedings of the Conference on Artificial Intelligence}, pp.2717--2723.
+
+\bibitem[\protect\citeauthoryear{Qawasmeh \textit{et al.}}{2014}]{Qawasmeh2014}
+Qawasmeh, A., Malik, A.
+and Chapman, B.
+(2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proceedings of the International Symposium on Parallel Distributed processing}, pp.1049--1058.
 
@@
 and Bertino, E.
-(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proceedings of the International Conference on Service-Oriented Computing}, pp.116--131
-
-\bibitem[\protect\citeauthoryear{Narodytska and Bacchus}{2014}]{NarodytskaN}
-Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proceedings of the Conference on Artificial Intelligence}, pp.2717--2723
-
-\bibitem[\protect\citeauthoryear{Barth and Putnam}{1995}]{Barth1995}
-Barth, P. and Putnam, D. (1995) 'Enumeration Algorithm for Linear Pseudo-Boolean Optimization', {\it Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science}
-
-\bibitem[\protect\citeauthoryear{Manquinho and Marques-Silva}{1995}]{Vasco2005}
-Manquinho, V. and Marques-Silva, J. (1995) 'Effective Lower Bounding Techniques for Pseudo-Boolean Optimization', {\it IST/INESC-ID, Technical University of Lisbon, Portugal}
-
-\bibitem[\protect\citeauthoryear{Microsoft Research}{2015}]{Z3API}
-Microsoft Research (2015) 'Z3 API - Source code and documentation' [online] {\it https://z3.codeplex.com/} (Accessed 18 August 2015)
-
-\bibitem[\protect\citeauthoryear{Cormen \textit{et al.}}{2009}]{Cormem}
-Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292
-
-\bibitem[\protect\citeauthoryear{Dagum and Menon}{1998}]{Dagum1998}
-Dagum, L. and Menon, R. (1998) 'OpenMP: An Industry-Standard API for Shared-Memory Programming', {\it Proceedings of the International Conference on Computational Science Engineering}, pp.46--55
-
-\bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
-MathWorks Inc. (2013) 'MATLAB (version R2013a)'
+(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proceedings of the International Conference on Service-Oriented Computing}, pp.116--131.
+
+\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
+Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proceedings of the International Conference on Functional Programming}, pp.412--423.
+
+\bibitem[\protect\citeauthoryear{Ramalho \textit{et al.}}{2013}]{Ramalho2013}
+Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L.
+and Fischer, B.
+(2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it International Conference and Workshops on the Engineering of Computer-Based Systems}, pp.147--156.
+
+\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
+Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'.
+
+\bibitem[\protect\citeauthoryear{Sebastiani and Trentin}{2015}]{Patrick2015}
+Sebastiani, R. and Trentin, P. (2015) 'OptiMathSAT: A Tool for Optimization Modulo Theories', {\it Proceedings of the International Conference on Computer Aided Verification}, Vol. 9206, pp.447--454.
+
+\bibitem[\protect\citeauthoryear{Tang \textit{et al.}}{2010}]{Tang2009}
+Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proceedings of the International Conference on Computer Science Education}, pp.1900--1905.
+
+\bibitem[\protect\citeauthoryear{Teich}{2012}]{Teich2012}
+Teich, J. (2012) 'Hardware/Software Codesign: The Past, the Present, and Predicting the Future', {\it Proceedings of the IEEE, Special Centennial Issue}, Vol. 100, pp.1411--1430.
 
 \bibitem[\protect\citeauthoryear{Tranquillo}{2011}]{Tranquillo2011}
-Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}
-
-\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2010}
-Hong, L.
-and Cai, J.
-(2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proceedings of the International Conference on Computer and Automation Engineering}, pp.185--189
-
-\bibitem[\protect\citeauthoryear{Cordeiro and Fischer}{2011}]{Cordeiro2011}
-Cordeiro, L.
-and Fischer, B.
-(2011) 'Verifying multi-threaded software using SMT-based context-bounded model checking', {\it Proceedings of the International Conference on Software Engineering}, pp.331--340
-
-\bibitem[\protect\citeauthoryear{Teich}{2012}]{Teich2012}
-Teich, J. (2012) 'Hardware/Software Codesign: The Past, the Present, and Predicting the Future', {\it Proceedings of the IEEE, Special Centennial Issue}, Vol. 100, pp.1411--1430
-
-\bibitem[\protect\citeauthoryear{Guthaus \textit{et al.}}{2011}]{Guthaus2001}
-Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T.
-and Brown, R.
-(2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proceedings of the annual workshop on workload characterization}, pp.3--14
-
-\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2005}]{Arato2005}
-Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156
-
-\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann2011}
-Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857
+Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}.
+
+\bibitem[\protect\citeauthoryear{Trindade and Cordeiro}{2015}]{Trindade2015}
+Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems}, Vol. 20, No. 1, pp. 1--19.
+
+\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2015}]{Trindade2016}
+Trindade, A., Ismail, H.
+and Cordeiro, L.
+(2015) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symposium on Computing Systems Engineering}, pp.
+102--105.
 
@@
 (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proceedings of the International Conference on Computer-Aided Verification}, Vol.
-5643, pp.715--720
-
-\bibitem[\protect\citeauthoryear{Qawasmeh \textit{et al.}}{2014}]{Qawasmeh2014}
-Qawasmeh, A., Malik, A.
-and Chapman, B.
-(2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proceedings of the International Symposium on Parallel Distributed processing}, pp.1049--1058
-
-\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
-Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proceedings of the International Conference on Functional Programming}, pp.412--423
-
-\bibitem[\protect\citeauthoryear{Sebastiani and Trentin}{2015}]{Patrick2015}
-Sebastiani, R. and Trentin, P. (2015) 'OptiMathSAT: A Tool for Optimization Modulo Theories', {\it Proceedings of the International Conference on Computer Aided Verification}, Vol. 9206, pp.447--454
-
-\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann11}
-Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions Software Engineering}, Vol. 9206, pp.845--857
-
-\bibitem[\protect\citeauthoryear{Holzmann}{2012}]{Holzmann2012}
-Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proceedings of the International Symposium on Model Checking Software}, Vol. 7385, pp.155--171
+5643, pp.715--720.
+
+\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
+Wu M., Wu, W., Tai, N., Zhao, H., Fan, J.
+and Yuan, N.
+(2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proceedings of the International Conference on Software Engineering and Service Science}, pp.921--924.
 

### 2016-08-19 Docs/IJES/journal.tex
[A-9] The author/s should explain how the constraint are addressed in GA. What is the meaning of "slack variables"?. Also, they should explain how the solutions are represented, what kind of operators (crossover, mutation, parent selection and offspring selection) used, etc. What is the meaning of "Elite" counter that you have modified from 2 to 50? Are 75 generations enough to ensure the convergence of the GA? The author/s should show the objective function. A similar analysis and/or explanation should be performed for ILP. I think that the author/s should give a more detailed explanation of

@@
 The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
-\textcolor{blue}{All the parameters of ILP and GA algorithms were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
-Choosing ILP and GA, over other possible optimization techniques, it is due to the fact that these techniques were used in related work, as~\cite{Arato2003} and~\cite{Mann2007}, facilitating the comparison with the techniques that we propose in this paper.}
+\textcolor{blue}{All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
+In particular, the ILP and GA algorithms were chosen since they were also used in other related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).}
 

### 2016-08-19 Docs/IJES/journal.tex
[B-2] In page 8, column 2: " Each time was measured 3 times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical conﬁdence of 91.7% to ESBMC (sequential, SS, PB and νZ), 95.9% to ESBMC-PS, and 92.0% to ILP and GA. A timeout condition (TO) is reached when the veriﬁcation time is longer than 3600 seconds".  These results are o.k BUT, the problem is 3 times is very short number of times for making an experiment. Generally, people use more than 30 (and use Normal Gaussian on the analysis) or minor 30 (uses T-student). Why the

@@
 A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11.
-Version $2$.$0$.$1$ of Boolector SMT-solver, as shown in~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
-ESBMC-$\nu$Z as a built-in tool to Z3 was also used, as shown in~\cite{Bjorner2014}.
-For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used, as shown in~\cite{TheMathWorks2013}.
-MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software, as shown in~\cite{Tranquillo2011} and is widely used by the engineering community, as shown in~\cite{Hong2010}.
+Version $2$.$0$.$1$ of Boolector SMT-solver, as described in~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC.
+ESBMC-$\nu$Z as a built-in tool to Z3 was also used, as presented in~\cite{Bjorner2014}.
+For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used, as described in~\cite{TheMathWorks2013}.
+MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software, as described in~\cite{Tranquillo2011} and is widely used by the engineering community, as described in~\cite{Hong2010}.
 
@@
 Each time was measured $3$ times (average taken).
-\textcolor{blue}{Empirical tests done by authors  demonstrated that a higher number of measurements, of each technique, did not produce significant differences in the experimental results (always below of 10\%, and mostly around 3\%).}
+\textcolor{blue}{Empirical tests performed by the authors demonstrated that a higher number of measurements, for each technique, did not produce significant differences in the experimental results (which were always below 10\% and mostly around 3\%).}
 

### 2016-08-19 Docs/IJES/journal.tex
[B-3] It was used three programs from Mibench benchmark (CRC3, Dijkstra and Patricia). Why them ? Mibench has 8 programs into 6 categories. Explain the motivation for only these 3 programs. It is possible to add information about more program from Mibench ?

@@
 From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
-\textcolor{blue}{The amount and types of benchmarks they were kept of related work to enable comparison with the techniques presented in this work.}
+\textcolor{blue}{Note that we used the same number (and types) of benchmarks from the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
 

### 2016-08-20 Docs/IJES/journal.tex
replying some comments

@@
 
-Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
-This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.
+\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
+In addition, there is no communication among the workers, but each worker notifies the controller if a violation is found for its TipH value}.
+
+%This approach could potentially lead to great performance improvements, %but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.
 
@@
 The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost.
+Here, variable \textit{SC} refers to the software cost, while \textcolor{blue}{\textit{CMC}} denotes the communication cost.
 In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.

### 2016-08-21 Docs/IJES/journal.tex
fix formulas

@@
 \label{objective-function}
-minimize\quad h_x 
+minimize\quad h_x.
 \end{align}
@@
 \label{hw-sw-partitioning}
-s\left(1-x\right) + c|Ex| \leq S_0
+s\left(1-x\right) + c|Ex| \leq S_0,
 \end{align}
@@
 \label{hw-sw-partitioning2}
-x \in \{0,1\}^n 
+x \in \{0,1\}^n, 
 \end{align}
@@
 \vspace{2 mm}
-\textcolor{blue}{Where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
+\noindent \textcolor{blue}{where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
 Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.

### 2016-08-21 Docs/IJES/journal.tex
[A-15] In ESBMC-PS, how are the decision variables selected by each worker? Could two workers evaluate the same possible solution? Are the "fork" and "join" of the process employed a single time? Do the workers have communication or information interchange? Besides, the author/s said "the processor does not remain idle for a longer period and thus there is almost no optimization", then what is the contribution of this proposal?
minor changes

@@
 \vspace{2 mm}
-\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be tested.
+\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be evaluated.
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
@@
 The previous parallelization is implemented by continuously forking ESBMC instances in a sequential manner until the first violation is found.
-However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some period of time.
+However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some time period.
 
@@
 
-\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
-In addition, there is no communication among the workers, but each worker notifies the controller if a violation is found for its TipH value}.
+\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
+In addition, there is no communication among workers, but each worker notifies the controller if a violation is found for its TipH value}.
 

### 2016-08-22 Docs/IJES/journal.tex
review Section 4.4

@@
 
-\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
-In addition, there is no communication among workers, but each worker notifies the controller if a violation is found for its TipH value}.
+\textcolor{blue}{In contrast to ESBMC-SS, where a new block of threads will be executed only if all threads in the previous execution were concluded, ESBMC-PS aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
+Note that there is no communication among workers, but each worker notifies the controller if a violation is found for its TipH value}.
+
+%Similar to ESBMC-SS, the decision variables are instantiated by the SMT solver to check the verification conditions produced by ESBMC.
+Additionally, each worker is instantiated using a different value for TipH, which checks once for a possible solution.
+There is no communication among workers; however, each worker is responsible for sending a message to the controller if a violation is found for the TipH value during its execution.
+The ESBMC-SS instantiates a block of threads based on the number of available cores in the CPU.
+A new block will be executed only if all threads in the previous execution were concluded.
 

### 2016-08-22 Docs/IJES/journal.tex
[A-17] In ESBMC-vZ, where is "CC" in fig. 12?
revised version of the paper and the reply letter

@@
 \begin{abstract}
-We present new alternative approaches to solve the hardware and software (HW-SW) partitioning problem.
-First, we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores.
-In particular, each instance checks for a different optimum value until the optimization problem is satisfied.
-We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
-Additionally, we integrate the maximum satisfiability solver $\nu$Z tool into ESBMC, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas.
+\textcolor{blue}{Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) is well known by its capability to verify software.
+Its use as optimization tool, to solve hardware and software (HW-SW) partitioning problem, is something new.
+Moreover, its integration with the maximum satisfiability solver $\nu$Z tool, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas, is unprecedented.
+We present new alternative approaches to solve the HW-SW partitioning problem.
+First, we use BMC based on SMT in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
+In other approach, we integrate the maximum satisfiability solver $\nu$Z tool into the BMC tool, making BMC as a specialized solution for optimization in a single-core environment.
+Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores, where each instance checks for a different optimum value until the optimization problem is satisfied.
+We implement five different algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
 We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks.
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based in medium complexity benchmarks, ESBMC integrated with $\nu$Z was faster and precise.}
 \end{abstract}
@@
 Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
-Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, and energy consumption.
-Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption \textcolor{blue}{(the decision is made by user or from project requirement).} Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
 Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
@@
 Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, where the focus is on bipartitioning, as shown in~\cite{Teich2012}.
+That configuration describes a first-generation co-design, \textcolor{blue}{with a simplified HW-SW model,} where the focus is on bipartitioning, as shown in~\cite{Teich2012}.
 
@@
 The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, while \textcolor{blue}{\textit{CMC}} denotes the communication cost.
+Here, variable \textit{SC} refers to the software cost, \textcolor{blue}{while \textit{CMC} denotes the communication cost}.
 In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and its result is precise.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared with GA.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
@@
 In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time.
+\textcolor{blue}{Moreover, it will address specifically more complex types of architectures of HW-SW model, including more than one CPU, and the assumption of just singled-threaded program execution
+will be extended to multiprogramming and multiprocessing (second generation of co-design).}
 
@@
 
+\bibitem[\protect\citeauthoryear{Paci \textit{et al.}}{2008}]{Federica2008}
+Paci, F., Ferrini, R., Sun, Y.
+and Bertino, E.
+(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proceedings of the International Conference on Service-Oriented Computing}, pp.116--131.
+
+\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
+Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proceedings of the International Conference on Functional Programming}, pp.412--423.
+
 \bibitem[\protect\citeauthoryear{Qawasmeh \textit{et al.}}{2014}]{Qawasmeh2014}
@@
 (2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proceedings of the International Symposium on Parallel Distributed processing}, pp.1049--1058.
-
-\bibitem[\protect\citeauthoryear{Paci \textit{et al.}}{2008}]{Federica2008}
-Paci, F., Ferrini, R., Sun, Y.
-and Bertino, E.
-(2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proceedings of the International Conference on Service-Oriented Computing}, pp.116--131.
-
-\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
-Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proceedings of the International Conference on Functional Programming}, pp.412--423.
 

### 2016-08-22 Docs/IJES/journal.tex
revised version

@@
 %-----------------related work came to here and was rewriten
-\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem, {\it i.e.}, to find the exact solution of a optimization problem, as shown in~\cite{Mann2007}; to use heuristics to speed up performance time, as shown in~\cite{Arato2003} and~\cite{Arato2005}.
+\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem, {\it i.e.}, to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
 It is worth mentioning that the using heuristics the final solution is not necessarily an optimal global solution.}
@@
 In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as shown in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as shown in~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solving, as described by~\cite{Wintersteiger2009}.}
-
-\textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as shown in~\cite{Bjorner2015}.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as mentioned in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as presented by~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solving, as described by~\cite{Wintersteiger2009}.}
+
+\textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as presented by~\cite{Bjorner2015}.
 In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, as described by~\cite{Bjorner2014} and~\cite{Bjorner2015}.
@@
 \vspace{2 mm}
+Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
+~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.
+
 In some cases, the time to find a solution using ILP is impractical.
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
+As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing.
+And~\cite{Huong2012} designed a Pareto optimization modified using GA.
+
 Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found.
@@
 Among the recent model checking techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as shown in~\cite{Biere2009}.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}.
 In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, as described by~\cite{Clarke2001}.
@@
 The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.
-
-In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as shown in~\cite{Cordeiro2012}. 
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by}~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.
+
+In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as mentioned in~\cite{Cordeiro2012}. 
 In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT.
@@
 The main factor for ESBMC to use only a single-core relies on its back-end ({\it i.e.}, SMT Solver).
-Currently, the SMT solvers supported by ESBMC are: Z3, as shown in~\cite{DeMoura2008}; Boolector, as shown in~\cite{Brummayer2009}; MathSAT, as shown in~\cite{Barrett2011}; CVC4, as shown in~\cite{Bozzano2005}; and Yices, as shown in~\cite{Dutertre2014}.
+Currently, the SMT solvers supported by ESBMC are: Z3, as \textcolor{blue}{presented by}~\cite{DeMoura2008}; Boolector, as \textcolor{blue}{mentioned in}~\cite{Brummayer2009}; MathSAT, as \textcolor{blue}{presented by}~\cite{Barrett2011}; CVC4, as \textcolor{blue}{presented by}~\cite{Bozzano2005}; and Yices, as \textcolor{blue}{presented by}~\cite{Dutertre2014}.
 Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
@@
 
-In particular, OpenMP uses the \textit{fork-join} model of parallel execution, as shown in~\cite{OpenMP1998}.
+In particular, OpenMP uses the \textit{fork-join} model of parallel execution, as \textcolor{blue}{mentioned} in~\cite{OpenMP1998}.
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode, as shown in~\cite{Wu2014}.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode, as \textcolor{blue}{presented by}~\cite{Wu2014}.
 
@@
 
-In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as shown in~\cite{Bjorner2014}.
-In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as shown in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
-
-In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives, as shown in~\cite{Bjorner2015}.
+In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as \textcolor{blue}{presented by}~\cite{Bjorner2014}.
+In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+
+In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives, as \textcolor{blue}{presented by}~\cite{Bjorner2015}.
 In summary, $\nu$Z provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
@@
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
-Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as shown in~\cite{Barth1995} and~\cite{Vasco2005}.
+Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as \textcolor{blue}{mentioned} in~\cite{Barth1995} and~\cite{Vasco2005}.
 If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints.
@@
 Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, \textcolor{blue}{with a simplified HW-SW model,} where the focus is on bipartitioning, as shown in~\cite{Teich2012}.
+That configuration describes a first-generation co-design, \textcolor{blue}{with a simplified HW-SW model,} where the focus is on bipartitioning, as presented by~\cite{Teich2012}.
 
@@
 \textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.} However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as \textcolor{blue}{mentioned} in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
 \textcolor{blue}{All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
@@
 The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
-Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as shown in~\cite{Mann2007}.
+Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.
 
@@
 
-Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
+Based on \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
 A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.
@@
 \midrule
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as shown in~\cite{Guthaus2001}\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as \textcolor{blue}{presented by}~\cite{Guthaus2001}\\
 \hline
 \verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
-\vspace{0.8 mm} Routine to insert values in Patricia Tree, as shown in ~\cite{Guthaus2001}\\
+\vspace{0.8 mm} Routine to insert values in Patricia Tree, as \textcolor{blue}{presented by} ~\cite{Guthaus2001}\\
 \hline
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as shown in~\cite{Guthaus2001}\\
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as \textcolor{blue}{presented by}~\cite{Guthaus2001}\\
 \hline
@@
 The nodes in the graphs correspond to high-level language instructions.
-Software and communication costs are time dimensional, and hardware costs represent the occupied area.
-The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}.
-The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks.
-From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
-\textcolor{blue}{Note that we used the same number (and types) of benchmarks from the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
+Software and communication costs are time dimensional, i.e., running time of software and the communication time, and hardware costs represent the occupied area.
+The first three benchmarks are extracted from MiBench, as \textcolor{blue}{presented by}~\cite{Guthaus2001}.
+\textcolor{blue}{The fuzzy benchmark was created and presented by}~\cite{Mann2007} and is a significantly large benchmark.
+\textcolor{blue}{And also from ~\cite{Mann2007}, were used RC$6$ and Mars as very complex benchmarks to test the limits of the applicability of each technique.
+Note that we used the same number (and types) of benchmarks from the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
 
@@
 Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC-SS, ESBMC-PS, ESBMC-PB, ESBMC-$\nu$Z) tools.
+\textcolor{blue}{The number of nodes, edges and the initial software cost (S0) are given to each benchmark.
+Hp and Sp represent the results of partitioning process for each technique, i.e., the optimized value of partitioned hardware and software.
+T(s) means the average time taken from the experiments.
+Particularly about GA there is an additional row informing how far from the exact answer is the found solution.}
 
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared with GA.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared with GA).} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
@@
 
-\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2010}
+\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2012}
 Hong, L.
@@
 (2010) 'The application guide of mixed programming between MATLAB and other programming languages', {\it Proceedings of the International Conference on Computer and Automation Engineering}, pp.185--189.
+
+\bibitem[\protect\citeauthoryear{Huong and Binh}{2012}]{Huong2012}
+Huong, P. and Binh, N. (2012) 'An approach to design embedded systems by multi-objective optimization', {\it
+Proceedings of the International Conference on Advanced Technologies for Communications}, pp.165--169.
+
+\bibitem[\protect\citeauthoryear{Jiang\textit{et al.}}{2010}]{Jiang2012}
+Jiang, Y., Zhang, H., Jiao, X., Song, X., Hung, W., Gu, M. and Sun, J. (2012) 'Uncertain model and algorithm for
+hardware/software partitioning', {\it Proceedings of the IEEE Computer Society Annual Symposium on VLSI}, pp.243--248.
 
@@
 Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'.
+
+\bibitem[\protect\citeauthoryear{Sapienza \textit{et al.}}{2013}]{Sapienza2013}
+Sapienza, G., Seceleanu, T. and Crnknovic, I. (2013) 'Partitioning decision process for embedded hardware and
+software deployment', {\it Proceedings of the IEEE 37th Annual Conference and Workshops on Computer Software and
+Applications}, pp.674--680.
 

### 2016-08-23 Docs/IJES/journal.tex
paper review

@@
 First, we use BMC based on SMT in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-In other approach, we integrate the maximum satisfiability solver $\nu$Z tool into the BMC tool, making BMC as a specialized solution for optimization in a single-core environment.
+In another proposed approach, we integrate the maximum satisfiability solver $\nu$Z tool into the BMC tool, making BMC as a specialized solution for optimization in a single-core environment.
 Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores, where each instance checks for a different optimum value until the optimization problem is satisfied.
@@
 We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based in medium complexity benchmarks, ESBMC integrated with $\nu$Z was faster and precise.}
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium complexity benchmarks, ESBMC-$\nu$Z was faster and precise.}
 \end{abstract}
@@
 \textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem, {\it i.e.}, to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
-It is worth mentioning that the using heuristics the final solution is not necessarily an optimal global solution.}
+It is worth mentioning that using heuristics the final solution is not necessarily an optimal global solution.}
 
@@
 The authors formulate this alternative single-core approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.}
+
+\subsection{Contributions}
 
@@
 
-Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page \texttt{http://esbmc.org/}.
+Our experiments are based on a set of publicly available benchmarks.
+\textcolor{blue}{All tools, benchmarks, and results of our evaluation are available on a supplementary web page \texttt{http://esbmc.org} and \texttt{http://esbmc.org/benchmarks}}.
 
@@
 Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
-Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption \textcolor{blue}{(the decision is made by user or from project requirement).} Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption \textcolor{blue}{(the decision is typically made by the engineer or from the project requirement).} Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
 Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
@@
 \textcolor{blue}{All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
-In particular, the ILP and GA algorithms were chosen since they were also used in other related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).}
+In particular, the ILP and GA algorithms were chosen since they were also used in another related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).}
 
@@
 
-\textcolor{blue}{Remembering that, as defined by formal model, there is a index of each decision variable, indicated by letter "i", which ranges from zero to the number of nodes of the problem to be solved.}
+\textcolor{blue}{Note that, as defined by the formal model, there is an index for each decision variable, indicated by letter ``i'', which ranges from $0$ to the number of nodes of the (particular) problem to be solved.}
 
@@
 As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}.
-If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
+If this is achieved, then the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
 
@@
 
-\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer’s processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
+\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
 Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}
@@
 
-Based on \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
+Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
 A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.
@@
 Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC-SS, ESBMC-PS, ESBMC-PB, ESBMC-$\nu$Z) tools.
-\textcolor{blue}{The number of nodes, edges and the initial software cost (S0) are given to each benchmark.
-Hp and Sp represent the results of partitioning process for each technique, i.e., the optimized value of partitioned hardware and software.
+\textcolor{blue}{The number of nodes, edges, and the initial software cost (S0) are given to each benchmark.
+Hp and Sp represent the results of partitioning process for each technique, {\it i.e.}, the optimized value of partitioned hardware and software.
 T(s) means the average time taken from the experiments.
@@
 \textcolor{blue}{Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware.
-In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does.
+In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are (heuristically) optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does.
 As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion.}
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared with GA).} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared to GA).} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
@@
 
-\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2012}
+\bibitem[\protect\citeauthoryear{Hong and Cai}{2010}]{Hong2010}
 Hong, L.

### 2016-08-24 Docs/IJES/journal.tex
revised version

@@
 In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications.
-In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.
+And we conclude and describe future work in Section~\ref{Conclusions}.
 
@@
 \vspace{2 mm}
-Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
-~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.
+\textcolor{blue}{Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
+~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.}
 
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing.
-And~\cite{Huong2012} designed a Pareto optimization modified using GA.
+\textcolor{blue}{As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing.
+And~\cite{Huong2012} designed a Pareto optimization modified using GA.}
 
@@
 
-The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.
+The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
+\textcolor{blue}{although more benchmarks with complexity similar to clustering should be included in future work for a more precise conclusion.
+Note, however, that more than $150$ nodes lead to TO and MO.
+ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.}
 
@@
 In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the search space size.
+
 In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time.
-\textcolor{blue}{Moreover, it will address specifically more complex types of architectures of HW-SW model, including more than one CPU, and the assumption of just singled-threaded program execution
-will be extended to multiprogramming and multiprocessing (second generation of co-design).}
+\textcolor{blue}{And so that the limits of the techniques can be defined more precisely, new benchmarks will be included in future work, with their complexity ranging between 100 and 400 nodes.
+Furthermore, more complex types of architectures of HW-SW model will be addressed, including more than one CPU, and the assumption of just singled-threaded program execution will be extended to multiprogramming and multiprocessing (second generation of co-design).}
 

### 2016-08-25 Docs/IJES/journal.tex
[C-11] The first two paragraphs of related work contains several grammatical mistakes. The conclusion section is full of errors. What does “faster and notorious” and “expressive” mean as execution times.

@@
 
-\textcolor{blue}{At this work, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+\textcolor{blue}{Here, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
 Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, as described by~\cite{Bjorner2015}.

### 2016-08-25 Docs/IJES/journal.tex
revised abstract

@@
 First, we use BMC based on SMT in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-In another proposed approach, we integrate the maximum satisfiability solver $\nu$Z tool into the BMC tool, making BMC as a specialized solution for optimization in a single-core environment.
-Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores, where each instance checks for a different optimum value until the optimization problem is satisfied.
+In another proposed approach, we integrate the $\nu$Z into the BMC, making it as a specialized solution for optimization in a single-core environment.
+Multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores, where each instance checks for a different optimum value until the optimization problem is satisfied.
 We implement five different algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
 We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium complexity benchmarks, ESBMC-$\nu$Z was faster and precise.}
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium complexity benchmarks, ESBMC-$\nu$Z had better performance.}
+
 \end{abstract}

### 2016-08-26 Docs/IJES/journal.tex
review abstract

@@
 \textcolor{blue}{Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) is well known by its capability to verify software.
-Its use as optimization tool, to solve hardware and software (HW-SW) partitioning problem, is something new.
-Moreover, its integration with the maximum satisfiability solver $\nu$Z tool, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas, is unprecedented.
+However, its use as optimization tool, to solve hardware and software (HW-SW) partitioning problem, is something new.
+In particular, its integration with the Maximum Satisfiability solver $\nu$Z tool, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas, is unprecedented.
 We present new alternative approaches to solve the HW-SW partitioning problem.
-First, we use BMC based on SMT in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
-In another proposed approach, we integrate the $\nu$Z into the BMC, making it as a specialized solution for optimization in a single-core environment.
-Multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores, where each instance checks for a different optimum value until the optimization problem is satisfied.
-We implement five different algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC).
-We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium complexity benchmarks, ESBMC-$\nu$Z had better performance.}
+First, we use SMT-based BMC in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem.
+The multi-core SMT-based BMC approaches allow initializing many verification instances based on the number of available processing cores, where each instance checks a different optimum value until the optimization problem is satisfied.
+Additionally, we integrate the $\nu$Z into the BMC, making it as a specialized solution for optimization in a single-core environment.
+We implement all five approaches on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and compare them to a state-of-the-art optimization tool (MATLAB).
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium-size benchmarks, ESBMC-$\nu$Z had better performance.}
 

### 2016-08-26 Docs/IJES/journal.tex
review introduction

@@
 
-Nowadays, with the strong development of embedded systems, the design phase plays an important role.
+Nowadays, with the tight development time of embedded systems, the design phase plays an important role.
 At early stages, the design is split into separated flows: hardware (HW) and software (SW).
 The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware and which one in software, must be supported by any well-structured methodology.
-If there is no methodology support, a number of issues, {\it e.g.}, design flow interruptions, redesigns, and undesired iterations may affect the overall development process, the quality, and the life-cycle of the final system.
+If there is no methodology support, a number of issues, {\it e.g.}, design flow interruptions, redesigns, and undesired iterations might affect the overall development process, the quality, as well as the final system life-cycle.
 
 %-----------------related work came to here and was rewriten
-\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem, {\it i.e.}, to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
+\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem: to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; and to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
 It is worth mentioning that using heuristics the final solution is not necessarily an optimal global solution.}
 
-\textcolor{blue}{In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
-In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software.
+\textcolor{blue}{In terms of SMT-based verification, most related studies are restricted to present the model, its modification to specific programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} use ESBMC for embedded ANSI-C software.
 In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
@@
 \textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as presented by~\cite{Bjorner2015}.
-In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, as described by~\cite{Bjorner2014} and~\cite{Bjorner2015}.
-As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
+In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, as described by~\cite{Bjorner2014}.
+Additionally, as an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
 The authors formulate this alternative single-core approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.}
 
+%---------------------------------
 \subsection{Contributions}
+%---------------------------------
 
 \textcolor{blue}{Here, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
-Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, as described by~\cite{Bjorner2015}.
+Our experimental results are compared to ILP (integer linear programming) and GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, as described by~\cite{Bjorner2015}.
 The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, as described in~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
@@
 In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications.
-And we conclude and describe future work in Section~\ref{Conclusions}.
+We conclude and describe future work in Section~\ref{Conclusions}.
 

### 2016-08-26 Docs/IJES/journal.tex
review Preliminaries

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background}
+\section{Preliminaries}
 \label{background}
@@
 There is no single method available for efficiently solving all optimization problems, as described by~\cite{Rao2009}.
-The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
+The most well-known technique is linear programming, which is a method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables.
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
@@
 \vspace{2 mm}
-\textcolor{blue}{Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
+\textcolor{blue}{Here, we refer to the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
 ~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.}
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-\textcolor{blue}{As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing.
-And~\cite{Huong2012} designed a Pareto optimization modified using GA.}
-
-Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found.
+\textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.}
+
+\textcolor{blue}{Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found, as described by~\cite{Trindade2015} and~\cite{Bjorner2015}}.
 The following sections describe the main features of ESBMC and $\nu$Z tools.

### 2016-08-26 Docs/IJES/journal.tex
review Bounded Model Checking with ESBMC

@@
 
-Among the recent model checking techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}.
-In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, as described by~\cite{Clarke2001}.
+Among recent model checking techniques, there is one that combines model checking with satisﬁability solving.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for specific types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}.
+In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state-space explosion problem, as described by~\cite{Clarke2001}.
 
 The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by}~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.
-
-In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as mentioned in~\cite{Cordeiro2012}. 
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by~\cite{Ganai2006},~\cite{Armando2009},~\cite{Cordeiro2012}}.
+
+In this study, however, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as mentioned in~\cite{Cordeiro2012}. 
 In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT.

### 2016-08-26 Docs/IJES/journal.tex
review 2.2.1 ESBMC Architectur

@@
 
-Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, as described by~\cite{Ramalho2013}.
+Fig.~\ref{ESBMC-Architecture} shows the ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver, as described by~\cite{Cordeiro2012}.
 In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style.

### 2016-08-26 Docs/IJES/journal.tex
review 2.4 Solving Optimization Problems with

@@
 In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as \textcolor{blue}{presented by}~\cite{Bjorner2014}.
-In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; the $\nu$Z main function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
 
@@
 \item{\textbf{minimize(T)}
-\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}}
+\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized; the accepted types are the same as maximize function.}}
 \item{\textbf{Assert-Soft F : weight n}
@@
 The expected result of this optimization problem described in the code below is $2$.
-In fact, the model generated by $\nu$Z shows that $K = 1$ and $W = 1$.
+Indeed, the model generated by $\nu$Z shows that $K = 1$ and $W = 1$.
 
@@
 For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT.
-When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
+When ``soft constrains'' is used in the mode ``lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
 

### 2016-08-26 Docs/IJES/journal.tex
review 3.1 Informal Model (or Assumptions)

@@
 First, there is only one software context, {\it i.e.}, there is just one general-purpose processor, and there is only one hardware context.
-The components of the system must be mapped to either one of these two contexts.
-Second, the software implementation of a component is associated with a software cost, which is the running time of the component.
-Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption \textcolor{blue}{(the decision is typically made by the engineer or from the project requirement).} Fourth, based on the premise that hardware is significantly faster than software, the running time of the components in hardware is considered as zero.
-Finally, if two components are mapped to the same context, then there is no overhead of communication between them; otherwise, there is an overhead.
-The consequence of these assumptions is that scheduling does not need to be addressed in this work.
-Hardware components do not need scheduling, because the running time is assumed to be zero.
-Because there is only one processor, software components do not need to be scheduled as well.
+The system's components must be mapped to either one of these two contexts.
+Second, the software implementation of a component is associated with a software cost, which is the execution time of the component.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption; \textcolor{blue}{the decision is typically made by the engineer or from the project requirement.} Fourth, based on the assumption that hardware is significantly faster than software, the execution time of the components in hardware is considered to be zero.
+Finally, if two components are mapped to the same context, then there is no communication overhead between them; otherwise, there is an overhead.
+The consequence of these assumptions is that scheduling does not need to be addressed in this study.
+Hardware components do not need scheduling, because the execution time is assumed to be zero.
+Since there is only one processor, software components do not need to be scheduled as well.
 Therefore, the focus is only on the partitioning problem.

### 2016-08-26 Docs/IJES/journal.tex
3.2 Formal Model

@@
 The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}.
-The hardware cost of $P$ is given by Eq.~\eqref{hardware-costs}
+The hardware cost of $P$ is given in Eq.~\eqref{hardware-costs}
 
@@
 \noindent
-and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\eqref{software-communication-costs}
+and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given in Eq.~\eqref{software-communication-costs}
 
@@
 \textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
-In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
+In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the objective is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
 Therefore, the objective function is:}

### 2016-08-26 Docs/IJES/journal.tex
review 4.1 Partitioning problem using ILP-based,Genetic Algorithms

@@
 
-As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
+\noindent \textcolor{blue}{As computer hardware architecture moves from single- to multi-core, and more recently to heterogeneous computing as described by~\cite{Mittal2015}, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores}.
 This section describes the verification algorithm using sequential ESBMC, followed by three multi-core model checking algorithms and the integration of the MaxSMT solver $\nu$Z into ESBMC, in order to speed up the HW-SW partitioning verification.
@@
 The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
-\textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools.} However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout.
+\textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and consequently to use commercial tools.} However, GA had improvements from the parameters of related studies to increase the solution accuracy without producing timeout.
 The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as \textcolor{blue}{mentioned} in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
@@
 
+\bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
+Mittal S., Vetter J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Comput. Surv. 47(4):}, pp. 69:1--69:35.
+
 \end{thebibliography}

### 2016-08-26 Docs/IJES/journal.tex
review 4.2 Verification Algorithm using Sequential ESBMC

@@
 
-\textcolor{blue}{Note that, as defined by the formal model, there is an index for each decision variable, indicated by letter ``i'', which ranges from $0$ to the number of nodes of the (particular) problem to be solved.}
+\textcolor{blue}{Note that, as defined by the formal model, there is an index for each decision variable, indicated by the letter \textit{``i''}, which ranges from $0$ to the number of nodes of the (particular) problem to be solved.}
 
@@
 $S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.} Here, matrices $A$ and $b$ are generated.
-At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.
+At that point, the ESBMC algorithm starts to differ from ILP and GA presented in~\cite{Trindade2015}.
 
@@
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
-As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}.
+As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure, as described by~\cite{DeMoura2008,Brummayer2009}.
 If this is achieved, then the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
 
-A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware ($H_{max}$).
-To every test performed, the hardware hint is compared to the feasible solution.
-This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement).
-If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.
+\textcolor{blue}{A loop controls the cost of hardware hint, starting with zero and reaching the maximum value, considering the case where all nodes are partitioned to hardware (which is represented by $H_{max}$)}.
+To every performed test, the hardware hint is compared to the feasible solution.
+This is accomplished by an \textit{ASSERT} statement at the end of the algorithm; a predicate that controls the halt condition (a \textit{true-false} statement).
+If the predicate is \textit{false}, then the optimization is concluded, {\it i.e.}, the solution is found.
 
@@
 However, if \textit{ASSERT} returns a \textit{true} condition, {\it i.e.}, the hardware cost is higher than the optimal solution, then the model-checking algorithm restarts and a new possible solution is generated and tested until the \textit{ASSERT} generates a \textit{false} condition.
-When the \textit{false} condition happens at verification-time, the execution code is aborted and ESBMC presents the counterexample that caused the condition to be broken.
+When the \textit{false} condition occurs, the verification is concluded and ESBMC presents the counterexample that caused the condition to be broken.
 That is the point in which the solution is presented (minimum HW cost).

### 2016-08-26 Docs/IJES/journal.tex
review 4.3 Multi-core ESBMC with OpenMP (ESBMC-SS)

@@
 Typically, ESBMC verification runs are performed only in a single-core.
-If the processor provides $8$ processing cores, only one is used for the verification and the others remain idle.
+If the processor provides $n$ processing cores, only one is used for the verification and the others remain idle.
 Thus, there is a significant unused hardware resource during this process.
@@
 
-ESBMC-SS obtains the problem specification represented by a ANSI-C program.
-The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
+ESBMC-SS obtains the problem specification represented by an ANSI-C program.
+The HW-SW partitioning is violated, when the correct optimum value parameter (represented by $TipH \in \mathbb{N}$) is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores.
 All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}.
 Note that there is no shared-memory (or message-passing) mechanism among threads.
-In particular, different threads are managed by the OpenMP API, which is responsible for the thread life-cycle: start, running, and dead states, using different values as condition.
+In particular, different threads are managed by the OpenMP API, which is responsible for managing the thread life-cycle: start, running, and dead states, using different values as condition.
 After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment.

### 2016-08-26 Docs/IJES/journal.tex
review 4.4 Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)

@@
 
-\textcolor{blue}{In contrast to ESBMC-SS, where a new block of threads will be executed only if all threads in the previous execution were concluded, ESBMC-PS aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
-Note that there is no communication among workers, but each worker notifies the controller if a violation is found for its TipH value}.
+\textcolor{blue}{In contrast to ESBMC-SS, where a new block of threads will be executed only if all threads in the previous execution were concluded, ESBMC-PS aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed, if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
+Note that there is no communication among workers, but each worker notifies the controller if a violation is found for its $TipH$ value.}
 

### 2016-08-26 Docs/IJES/journal.tex
review 4.5 Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)

@@
 Algorithm in Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
-
-Note that algorithm of Figure~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
+Note that the algorithm is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
 From lines $4$ to $9$, the algorithm finds the largest interval.
 Then, from line $10$ the largest interval is removed and the median is calculated in line $11$.
-After that, two new intervals are created, the left side (in line $14$) and the right side (in line $18$).
+After that, two new intervals are created, the left-side (in line $14$) and the right-side (in line $18$).
 At the end, the median is returned.
@@
 The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$).
-While the step is being executed, the controller checks whether this step is still needed (line $4$).
-If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
+While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
 

### 2016-08-26 Docs/IJES/journal.tex
review 4.6 Analysis of the partitioning problem using

@@
 
-Algorithm of Figure~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions, as seen in~\cite{Bjorner2014}.
-A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the set of constraints.
+Algorithm of Figure~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions, as described in~\cite{Bjorner2014}.
+A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the constraints set.
 Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.

### 2016-08-26 Docs/IJES/journal.tex
5 Experimental Evaluation

@@
 The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
-Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.
+Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.
 

### 2016-08-26 Docs/IJES/journal.tex
review 5.1 Experimental Setup

@@
 
-\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
+\textcolor{blue}{Note that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
 Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}
@@
 
-Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
+Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB, and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
 A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.

### 2016-08-26 Docs/IJES/journal.tex
review 5.2 Description of Benchmarks

@@
 
-\vspace{-3 mm}
 To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}.
 The nodes in the graphs correspond to high-level language instructions.
-Software and communication costs are time dimensional, i.e., running time of software and the communication time, and hardware costs represent the occupied area.
+Software and communication costs are time dimensional, {\it i.e.}, software execution time and communication time; and hardware costs represent the occupied area.
 The first three benchmarks are extracted from MiBench, as \textcolor{blue}{presented by}~\cite{Guthaus2001}.
 \textcolor{blue}{The fuzzy benchmark was created and presented by}~\cite{Mann2007} and is a significantly large benchmark.
-\textcolor{blue}{And also from ~\cite{Mann2007}, were used RC$6$ and Mars as very complex benchmarks to test the limits of the applicability of each technique.
-Note that we used the same number (and types) of benchmarks from the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
+\textcolor{blue}{And also from ~\cite{Mann2007}, were used RC$6$ and Mars as very complex benchmarks to test the limits of each technique.
+Note that we used the same number (and types) of benchmarks that were previously used in the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
 

### 2016-08-26 Docs/IJES/journal.tex
review conclusions

@@
 
-There is no single tool for efficiently solving all HW-SW partitioning benchmarks.
+As observed in the experimental evaluation, there is no single tool for efficiently solving all HW-SW partitioning benchmarks.
 In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.
@@
 In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are (heuristically) optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does.
-As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion.}
+As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion problem.}
 
@@
 The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
-\textcolor{blue}{although more benchmarks with complexity similar to clustering should be included in future work for a more precise conclusion.
+\textcolor{blue}{although more benchmarks with similar complexity to clustering should be included in future work for a more precise conclusion.
 Note, however, that more than $150$ nodes lead to TO and MO.

### 2016-08-27 Docs/IJES/journal.tex
improving comment A-16

@@
 Note that the algorithm is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
+\textcolor{blue}{Furthermore, this algorithm is synchronized, which ensures a unique step value for a worker request.}
 From lines $4$ to $9$, the algorithm finds the largest interval.
@@
 While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
+\textcolor{blue}{It is worth mentioning that there is no interchange communication among the workers, but they are responsible to notify the controller if a violation is found.}
 

### 2016-08-27 Docs/IJES/journal.tex
including comments in tex

@@
 \end{lstlisting}
+
+\textcolor{blue}{In general, it is worth mentioning that the complexity for ESBMC-SS, ESBMC-PS, and ESBMC-PB in a sequential time are linear (\textit{i.e.}, O(n)), that is because each algorithm runs all the possible solutions once.
+However, each execution runs an optimization problem, which is solved by the model checker, that is NP-Hard as described by Arato et al.
+(2003).
+Thus, even a parallel time being considered, including possible overheads in OpenMP, the general complexity is simplified by NP-Hard.}
 

### 2016-08-28 Docs/IJES/journal.tex
[C-5] The term TipH and Hmax is used in Figure5 but is not declared. Figure 5 uses “Populate”, but actually it is assignment of decision variables. The pseudocode in Figure 5 is extremely inconsistent. It is very hard to follow what each step of the algorithm is achieving. For the three multi-core version of ESBMC, the author must comment on the complexity of ESBMC-SS, ESBMC-PS, ESBMC-PB. Also, the Open-MP overhead must be described for each version of these algorithms.

@@
 While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
-\textcolor{blue}{It is worth mentioning that there is no interchange communication among the workers, but they are responsible to notify the controller if a violation is found.}
+\textcolor{blue}{Note that there is no interchange communication among workers, but they are responsible for notifying the controller if a given violation is found.}
 
@@
 \end{lstlisting}
+
+%----------------------------------------------
+\subsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
+\label{complexity}
+%----------------------------------------------
+
+\textcolor{blue}{With respect to the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB algorithms, they can all be described in two parts, which include the parallelism and the optimization solving.
+In the first part, the ESBMC-SS, ESBMC-PS, and ESBMC-PB time complexity is considered to be linear ({\it i.e.}, they are denoted by $O(n)$), taking into account a sequential time since each algorithm runs all possible solutions at once.
+However, each execution instance of ESBMC-SS, ESBMC-PS, and ESBMC-PB solves a specific optimization problem that is considered to be NP-Hard, as described by~\cite{Arato2003}.
+Thus, even a parallel execution being implemented, including (possible) overheads due to the use of the OpenMP library, the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB is still NP-Hard.}
 

### 2016-08-28 Docs/IJES/journal.tex
update reply letter

@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
+\subsection{Multi-core ESBMC}
+\label{Multi-core-ESBMC}
+%----------------------------------------------
+
+%----------------------------------------------
+\subsubsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
 \label{Multi-core-ESBMC-with-OpenMP}
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
+\subsubsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
 \label{Multi-core-ESBMC-with-OpenMP-using-workers}
@@
 %----------------------------------------------
-\subsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
+\subsubsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
 \label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
@@
 %----------------------------------------------
-\subsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
+\subsubsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
 \label{complexity}

### 2016-09-06 Docs/IJES/journal.tex
revised version

@@
 
+\textcolor{blue}{There is also the effort to create a hardware-software (HW/SW) co-simulation environment in order to help designers obtain an appropriate HW/SW partitioning that satisfy specified tradeoffs, as described by~\cite{Jan2005} and by~\cite{Hau2009}.}
+
 \textcolor{blue}{In terms of SMT-based verification, most related studies are restricted to present the model, its modification to specific programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-\textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.}
+\textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.
+In the other hand, there is some research done to reduce the complexity of computation in order to improve the performance of some techniques, as described by~\cite{Boucheneb2006}.}
 
@@
 \bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
-Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}.
+Biere, A., Heule, M., Maaren, H. and Walsh, T. (2009) 'Bounded Model Checking', {\it Handbook of Satisfiability}, ISBN 978-1-58603-929-5.
 
@@
 9035, pp.194--199.
+
+\bibitem[\protect\citeauthoryear{Boucheneb and Hadjidj}{2006}]{Boucheneb2006}
+\textcolor{blue}{Boucheneb, H.
+and Hadjidj, R.
+(2006) 'Using inclusion abstraction to construct Atomic State Class Graphs for Time Petri Nets', {\it Int.
+J.
+of Embedded Systems}, Vol.
+2, N.
+1/2, pp.128--139.}
 
@@
 
+\bibitem[\protect\citeauthoryear{Hau and Khalil-Hani}{2009}]{Hau2009}
+\textcolor{blue}{Hau, Y.W.
+and Khalil-Hani, M.
+(2009) 'SystemC-based HW/SW co-simulation platform for system-on-chip (SoC) design space exploration', {\it Int.
+J.
+of Information and Communication Technology}, 2009, Vol.2, N.
+1/2, pp.108--119.}
+
 \bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann2011}
@@
 
+\bibitem[\protect\citeauthoryear{Jan \textit{et al.}}{2005}]{Jan2005}
+\textcolor{blue}{Jan, K.
+Y., Fan, C.
+B., Kuo, A.
+C., Yen, W.
+C., and Lin, Y.
+L.
+(2005) 'A platform based SOC design methodology and its application in image compression', {\it Int.
+J.
+of Embedded Systems}, Vol.1, N.
+1/2, pp.
+23--32.}
+
 \bibitem[\protect\citeauthoryear{Jiang\textit{et al.}}{2010}]{Jiang2012}
@@
 \bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
-MathWorks Inc. (2013) 'MATLAB (version R2013a)'.
+MathWorks Inc. (2013) 'MATLAB (version R2013a)', ISBN 9780982583883.
 
@@
 
+\bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
+\textcolor{blue}{Mittal, S., and Vetter, J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Computing Surveys}, Vol. 47, Issue 4, pp. 69:1--69:35.}
+
 \bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
@@
 \bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
-Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}.
+Muller, M. (2002) 'OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}.
 
@@
 \bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
-Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'.
+Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition', ISBN 978-0-470-18352-6.
 
@@
 \bibitem[\protect\citeauthoryear{Tranquillo}{2011}]{Tranquillo2011}
-Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}.
+Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}, ISBN 9781608457113.
 
@@
 \bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
-Wu M., Wu, W., Tai, N., Zhao, H., Fan, J.
+Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J.
 and Yuan, N.
@@
 
-\bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
-Mittal S., Vetter J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Comput. Surv. 47(4):}, pp. 69:1--69:35.
-
 \end{thebibliography}

### 2016-09-25 Docs/IJES/journal.tex
final version - rev1

@@
 
-%\LRH{A. Trindade et~al.}
+\LRH{A. Trindade et~al.}
 
@@
 
-\PUBYEAR{xxxx}
+\PUBYEAR{2016}
 
@@
 
-\PUBYEAR{2012}
+\PUBYEAR{2016}
 
@@
 
-\authorA{Author A}
-\affA{University A\\
-E-mail: \{nonono\}@nonono.com}
-
-\authorB{Author B}
-\affB{University B\\
-E-mail: \{nonono\}@nonono.com}
-
-%\authorA{Alessandro Trindade, Hussama Ismail}
-%\affA{Federal University of Amazonas \\
-%E-mail: \{alessandro.b.trindade, hussamaismail\}@gmail.com}
-
-%\authorB{Edilson Galv\~ao, Renato Degelo}
-%\affB{Federal University of Amazonas \\
-%E-mail: \{rdegelo, esj.galvao\}@gmail.com}
-
-%\authorC{Helder Silva, and Lucas Cordeiro}
-%\affC{Federal University of Amazonas \\
-%E-mail: prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br}
+\authorA{Alessandro Bezerra Trindade*, Renato de Faria Degelo, Edilson Galv\~ao dos Santos Junior, Hussama Ibrahim Ismail, Helder Cruz da Silva and Lucas Carvalho Cordeiro}
+\affA{Federal University of Amazonas \\
+Av. Rodrigo Ot\'avio, 3000, Campus Universit\'ario, Manaus, Brazil, ZIP 69077-000 \\
+E-mail: alessandro.b.trindade@gmail.com* \\
+E-mail: rdegelo@gmail.com \\
+E-mail: esj.galvao@gmail.com \\
+E-mail: hussamaismail@gmail.com \\
+E-mail: helder@ufam.edu.br \\
+E-mail: lucascordeiro@ufam.edu.br \\
+* Corresponding author}
 
 \begin{abstract}
-\textcolor{blue}{Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) is well known by its capability to verify software.
+Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) is well known by its capability to verify software.
 However, its use as optimization tool, to solve hardware and software (HW-SW) partitioning problem, is something new.
@@
 Additionally, we integrate the $\nu$Z into the BMC, making it as a specialized solution for optimization in a single-core environment.
-We implement all five approaches on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and compare them to a state-of-the-art optimization tool (MATLAB).
-Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium-size benchmarks, ESBMC-$\nu$Z had better performance.}
+We implement all five approaches on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and compare them to a state-of-the-art optimization tool.
+Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but based on medium-size benchmarks, ESBMC-$\nu$Z had better performance.
 
@@
 
-\REF{\textcolor{red}{to this paper should be made as follows: No no no.
-`Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning', {\it International Journal of Embedded Systems}, Vol.
+\REF{to this paper should be made as follows: Trindade, A.B., Degelo, R.F., Santos Junior, E.G., Ismail, H.I., Silva, H.C., and Cordeiro, L.C.
+(2016) `Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning', {\it International Journal of Embedded Systems}, Vol.
 x, No.
-x, pp.xxx\textendash xxx.}}
+x, pp.xxx\textendash xxx.}
 
@@
 \begin{bio}
-\textcolor{red}{
-no no no.\vs{9}}
-
-\textcolor{red}{\noindent No no no.\vs{8}}
-
-\textcolor{red}{\noindent No no no.}
+Alessandro Bezerra Trindade received the B.Sc.
+and M.Sc.
+degrees in electrical engineering from the Federal University of Amazonas (UFAM), in 1995 and 2015, respectively.
+Currently, he is pursuing his PhD in informatics at UFAM.
+\vs{9}
+
+\noindent Renato de Faria Degelo, received his software analysis and development technologist degree in 2011 from Uninorte and is pursuing his M.Sc.
+at UFAM.
+Currently, he is a software engineer at Samsung Institute (SIDIA).\vs{8}
+
+\noindent Edilson Galvão dos Santos Junior, received his computer engineering degree in 2015 from Foundation Center for Analysis, Research and Technological Innovation (FUCAPI) and is pursuing his M.Sc.
+at UFAM.
+Currently, he is a software engineer at SIDIA.\vs{8}
+
+\noindent Hussama Ibrahim Ismail holds a B.Sc.
+degree in computer engineering from FUCAPI in 2013 and a M.Sc.
+degree in Electrical Engineering from UFAM in 2015.
+His current research interests are formal methods and embedded systems.\vs{8}
+
+\noindent Helder Cruz da Silva received the B.Sc.
+degree and the M.Sc.
+from the Federal University of Uberlândia (UFU), in 1998 and 2001, respectively.
+He received the Ph.D.
+degree from University of Minho in 2013.
+Currently, he is an assistant professor at UFAM.\vs{8}
+
+\noindent Lucas Carvalho Cordeiro received the Ph.D.
+degree from the University of Southampton in 2011.
+From 2009 to 2016, he was an adjunct professor at UFAM (he is currently in unpaid leave).
+Since 2016, he is a researcher at the University of Oxford.\vs{8}
+
+%\textcolor{red}{\noindent No no no.\vs{8}}
+
+%\textcolor{red}{\noindent No no no.}
 \end{bio}
@@
 %-----------------related work came to here and was rewriten
-\textcolor{blue}{Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem: to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; and to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
-It is worth mentioning that using heuristics the final solution is not necessarily an optimal global solution.}
-
-\textcolor{blue}{There is also the effort to create a hardware-software (HW/SW) co-simulation environment in order to help designers obtain an appropriate HW/SW partitioning that satisfy specified tradeoffs, as described by~\cite{Jan2005} and by~\cite{Hau2009}.}
-
-\textcolor{blue}{In terms of SMT-based verification, most related studies are restricted to present the model, its modification to specific programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
+Since the first decade of 2000s, two main paths have been tracked to solve the HW-SW partitioning problem: to find the exact solution of a optimization problem, as presented by~\cite{Mann2007}; and to use heuristics to speed up performance time, as presented by~\cite{Arato2003} and~\cite{Arato2005}.
+It is worth mentioning that using heuristics the final solution is not necessarily an optimal global solution.
+
+There is also the effort to create a hardware-software (HW/SW) co-simulation environment in order to help designers obtain an appropriate HW/SW partitioning that satisfy specified tradeoffs, as described by~\cite{Jan2005} and by~\cite{Hau2009}.
+
+In terms of SMT-based verification, most related studies are restricted to present the model, its modification to specific programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness.
 In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs, and~\cite{Cordeiro2012} use ESBMC for embedded ANSI-C software.
 In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way, but the former has performance issues that were improved by the latter, which used only a sequential search to perform multi-core model checking.
-There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as mentioned in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as presented by~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solving, as described by~\cite{Wintersteiger2009}.}
-
-\textcolor{blue}{Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as presented by~\cite{Bjorner2015}.
+There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification, as mentioned in~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism, as presented by~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solving, as described by~\cite{Wintersteiger2009}.
+
+Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories, as presented by~\cite{Bjorner2015}.
 In particular, $\nu$Z tool offers substantial performance improvement in optimization problems, as described by~\cite{Bjorner2014}.
 Additionally, as an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion.
-The authors formulate this alternative single-core approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.}
+The authors formulate this alternative single-core approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program.
 
@@
 
-\textcolor{blue}{Here, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
+Here, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
 Our experimental results are compared to ILP (integer linear programming) and GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, as described by~\cite{Bjorner2015}.
@@
 All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
-To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.}
-
-%-----------------
-%Starting at the $90$'s decade, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}.
-In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC) as defined in~\cite{Cordeiro2012}, in order to perform HW-SW partitioning in embedded systems.
-In~\cite{Trindade2016}, the original ESBMC algorithm was improved in terms of performance, so a multi-core sequential approach was introduced, in order to speed up the performance and turn it similar, in some cases, to conventional optimization tools, which are used to perform HW-SW partitioning.
-
-%The present work thus extends those previous studies since there is a substantial improvement in terms of the SMT-based verification methods.
-In particular, we extend the work of~\cite{Trindade2015} and~\cite{Trindade2016} to exploit a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization \textcolor{blue}{single-core} tool based on SMT as defined in~\cite{Bjorner2015}.
-
-%We exploit the availability of multi-core processors and the tool OpenMP as defined in~\cite{Tang2009}; thus, we apply SMT-based verification methods to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS).
-Experimental results are compared to ILP (integer linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach, according to~\cite{Bjorner2015}.
-The ILP and GA algorithms are implemented with the optimization toolbox of Matlab, according to~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3.
-All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool.
-
-%The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
-Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
-Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.
 To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.
 
-%\subsection{Contributions}
-
-%The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems.
-Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints.
-Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach.
-Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.
-To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.
-
 \subsection{Availability of Data and Tools}
@@
 Our experiments are based on a set of publicly available benchmarks.
-\textcolor{blue}{All tools, benchmarks, and results of our evaluation are available on a supplementary web page \texttt{http://esbmc.org} and \texttt{http://esbmc.org/benchmarks}}.
+All tools, benchmarks, and results of our evaluation are available on a supplementary web page \texttt{http://esbmc.org} and \texttt{http://esbmc.org/benchmarks}.
 
@@
 A particular case of linear programming is ILP, in which the variables can assume just integer values.
-\textcolor{blue}{Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints}
+Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints
 
@@
 \vspace{2 mm}
-\textcolor{blue}{Here, we refer to the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
-~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.}
+Here, we refer to the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time.
+~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.
 
@@
 The only drawback is that the found solution may not be the global minimum or maximum.
-\textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.
-In the other hand, there is some research done to reduce the complexity of computation in order to improve the performance of some techniques, as described by~\cite{Boucheneb2006}.}
-
-\textcolor{blue}{Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found, as described by~\cite{Trindade2015} and~\cite{Bjorner2015}}.
+As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.
+In the other hand, there is some research done to reduce the complexity of computation in order to improve the performance of some techniques, as described by~\cite{Boucheneb2006}.
+
+Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found, as described by~\cite{Trindade2015} and~\cite{Bjorner2015}.
 The following sections describe the main features of ESBMC and $\nu$Z tools.
@@
 Among recent model checking techniques, there is one that combines model checking with satisﬁability solving.
-This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for specific types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}.
+This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for specific types of problems, it offers large performance improvements over previous approaches, as presented by~\cite{Biere2009}.
 In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state-space explosion problem, as described by~\cite{Clarke2001}.
@@
 The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}.
-To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by~\cite{Ganai2006},~\cite{Armando2009},~\cite{Cordeiro2012}}.
+To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as presented by~\cite{Ganai2006},~\cite{Armando2009},~\cite{Cordeiro2012}.
 
@@
 The main factor for ESBMC to use only a single-core relies on its back-end ({\it i.e.}, SMT Solver).
-Currently, the SMT solvers supported by ESBMC are: Z3, as \textcolor{blue}{presented by}~\cite{DeMoura2008}; Boolector, as \textcolor{blue}{mentioned in}~\cite{Brummayer2009}; MathSAT, as \textcolor{blue}{presented by}~\cite{Barrett2011}; CVC4, as \textcolor{blue}{presented by}~\cite{Bozzano2005}; and Yices, as \textcolor{blue}{presented by}~\cite{Dutertre2014}.
+Currently, the SMT solvers supported by ESBMC are: Z3, as presented by~\cite{DeMoura2008}; Boolector, as mentioned in~\cite{Brummayer2009}; MathSAT, as presented by~\cite{Barrett2011}; CVC4, as presented by~\cite{Bozzano2005}; and Yices, as presented by~\cite{Dutertre2014}.
 Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
@@
 
-In particular, OpenMP uses the \textit{fork-join} model of parallel execution, as \textcolor{blue}{mentioned} in~\cite{OpenMP1998}.
+In particular, OpenMP uses the \textit{fork-join} model of parallel execution, as mentioned in~\cite{OpenMP1998}.
 The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads.
-After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode, as \textcolor{blue}{presented by}~\cite{Wu2014}.
+After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode, as presented by~\cite{Wu2014}.
 
@@
 
-In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as \textcolor{blue}{presented by}~\cite{Bjorner2014}.
-In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; the $\nu$Z main function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
-
-In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives, as \textcolor{blue}{presented by}~\cite{Bjorner2015}.
+In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as presented by~\cite{Bjorner2014}.
+In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; the $\nu$Z main function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as mentioned in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.
+
+In $\nu$Z, MaxSAT is responsible for the restrictions, while OptSMT optimizes linear arithmetic objectives, as presented by~\cite{Bjorner2015}.
 In summary, $\nu$Z provides three main functions that extend Z3 for solving optimization problems, which are: \textit{maximize}, \textit{minimize}, and \textit{assert-soft}.
@@
 \item{\textbf{maximize(T)}
-\textcolor{blue}{this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}}
+this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
 \item{\textbf{minimize(T)}
-\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized; the accepted types are the same as maximize function.}}
+this function instructs the solver that a given variable $T$ should be minimized; the accepted types are the same as maximize function.}
 \item{\textbf{Assert-Soft F : weight n}
@@
 Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture.
-Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as \textcolor{blue}{mentioned} in~\cite{Barth1995} and~\cite{Vasco2005}.
+Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as mentioned in~\cite{Barth1995} and~\cite{Vasco2005}.
 If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints.
@@
 Second, the software implementation of a component is associated with a software cost, which is the execution time of the component.
-Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption; \textcolor{blue}{the decision is typically made by the engineer or from the project requirement.} Fourth, based on the assumption that hardware is significantly faster than software, the execution time of the components in hardware is considered to be zero.
+Third, the hardware implementation of a component has a hardware cost, which can be area, heat dissipation, or energy consumption; the decision is typically made by the engineer or from the project requirement.
+Fourth, based on the assumption that hardware is significantly faster than software, the execution time of the components in hardware is considered to be zero.
 Finally, if two components are mapped to the same context, then there is no communication overhead between them; otherwise, there is an overhead.
@@
 Therefore, the focus is only on the partitioning problem.
-That configuration describes a first-generation co-design, \textcolor{blue}{with a simplified HW-SW model,} where the focus is on bipartitioning, as presented by~\cite{Teich2012}.
+That configuration describes a first-generation co-design, with a simplified HW-SW model, where the focus is on bipartitioning, as presented by~\cite{Teich2012}.
 
@@
 
-\textcolor{blue}{A directed simple graph $ G = (V,E) $, called the task graph of the system, is given.
+A directed simple graph $ G = (V,E) $, called the task graph of the system, is given.
 Where the vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned.
@@
 Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(V_i)$ (or $ s_i $) of software if implemented in software.
-Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).}
+Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).
 
@@
 \vspace{2 mm}
-\textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
+In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}.
 In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the objective is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related.
-Therefore, the objective function is:}
+Therefore, the objective function is:
 
@@
 
-\textcolor{blue}{Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as:}
+Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as:
 
@@
 \vspace{2 mm}
-\noindent \textcolor{blue}{where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}.
+\noindent where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software).
 Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
@@
 
-\noindent \textcolor{blue}{As computer hardware architecture moves from single- to multi-core, and more recently to heterogeneous computing as described by~\cite{Mittal2015}, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores}.
+\noindent As computer hardware architecture moves from single- to multi-core, and more recently to heterogeneous computing as described by~\cite{Mittal2015}, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores.
 This section describes the verification algorithm using sequential ESBMC, followed by three multi-core model checking algorithms and the integration of the MaxSMT solver $\nu$Z into ESBMC, in order to speed up the HW-SW partitioning verification.
@@
 The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}.
-\textcolor{blue}{Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and consequently to use commercial tools.} However, GA had improvements from the parameters of related studies to increase the solution accuracy without producing timeout.
-The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as \textcolor{blue}{mentioned} in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
-\textcolor{blue}{All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
-In particular, the ILP and GA algorithms were chosen since they were also used in another related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).}
+Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and consequently to use commercial tools.
+However, GA had improvements from the parameters of related studies to increase the solution accuracy without producing timeout.
+The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as mentioned in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
+All ILP and GA parameters were presented and discussed in~\cite{Trindade2015} and~\cite{Trindade2016}.
+In particular, the ILP and GA algorithms were chosen since they were also used in another related work, as~\cite{Arato2003} and~\cite{Mann2007}, thus facilitating the comparison to the present techniques (that we propose in this paper).
 
@@
 
-\textcolor{blue}{Note that, as defined by the formal model, there is an index for each decision variable, indicated by the letter \textit{``i''}, which ranges from $0$ to the number of nodes of the (particular) problem to be solved.}
+Note that, as defined by the formal model, there is an index for each decision variable, indicated by the letter \textit{``i''}, which ranges from $0$ to the number of nodes of the (particular) problem to be solved.
 
@@
 
-\textcolor{blue}{The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
-$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.} Here, matrices $A$ and $b$ are generated.
+The ESBMC algorithm starts with the declarations of hardware, software, and communication costs.
+$S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.
+Here, matrices $A$ and $b$ are generated.
 At that point, the ESBMC algorithm starts to differ from ILP and GA presented in~\cite{Trindade2015}.
@@
 \vspace{2 mm}
-\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be evaluated.
+It is possible to instruct ESBMC with which type of values the variables must be evaluated.
 Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values.
 As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure, as described by~\cite{DeMoura2008,Brummayer2009}.
-If this is achieved, then the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
-
-\textcolor{blue}{A loop controls the cost of hardware hint, starting with zero and reaching the maximum value, considering the case where all nodes are partitioned to hardware (which is represented by $H_{max}$)}.
+If this is achieved, then the ASSUME directive ensures the compliance of the constraint $A.x \leq b$.
+
+A loop controls the cost of hardware hint, starting with zero and reaching the maximum value, considering the case where all nodes are partitioned to hardware (which is represented by $H_{max}$).
 To every performed test, the hardware hint is compared to the feasible solution.
@@
 
-\textcolor{blue}{In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.}
+In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.
 
@@
 
-\textcolor{blue}{In contrast to ESBMC-SS, where a new block of threads will be executed only if all threads in the previous execution were concluded, ESBMC-PS aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed, if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
-Note that there is no communication among workers, but each worker notifies the controller if a violation is found for its $TipH$ value.}
+In contrast to ESBMC-SS, where a new block of threads will be executed only if all threads in the previous execution were concluded, ESBMC-PS aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed, if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}.
+Note that there is no communication among workers, but each worker notifies the controller if a violation is found for its $TipH$ value.
 
@@
 Note that the algorithm is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
-\textcolor{blue}{Furthermore, this algorithm is synchronized, which ensures a unique step value for a worker request.}
+Furthermore, this algorithm is synchronized, which ensures a unique step value for a worker request.
 From lines $4$ to $9$, the algorithm finds the largest interval.
@@
 While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.
-\textcolor{blue}{Note that there is no interchange communication among workers, but they are responsible for notifying the controller if a given violation is found.}
+Note that there is no interchange communication among workers, but they are responsible for notifying the controller if a given violation is found.
 
@@
 %----------------------------------------------
-\subsubsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
+\subsubsection{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}
 \label{complexity}
@@
 
-\textcolor{blue}{With respect to the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB algorithms, they can all be described in two parts, which include the parallelism and the optimization solving.
+With respect to the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB algorithms, they can all be described in two parts, which include the parallelism and the optimization solving.
 In the first part, the ESBMC-SS, ESBMC-PS, and ESBMC-PB time complexity is considered to be linear ({\it i.e.}, they are denoted by $O(n)$), taking into account a sequential time since each algorithm runs all possible solutions at once.
 However, each execution instance of ESBMC-SS, ESBMC-PS, and ESBMC-PB solves a specific optimization problem that is considered to be NP-Hard, as described by~\cite{Arato2003}.
-Thus, even a parallel execution being implemented, including (possible) overheads due to the use of the OpenMP library, the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB is still NP-Hard.}
+Thus, even a parallel execution being implemented, including (possible) overheads due to the use of the OpenMP library, the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB is still NP-Hard.
 
@@
 The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}.
-Here, variable \textit{SC} refers to the software cost, \textcolor{blue}{while \textit{CMC} denotes the communication cost}.
+Here, variable \textit{SC} refers to the software cost, while \textit{CMC} denotes the communication cost.
 In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values.
@@
 
-\textcolor{blue}{In general, it is worth mentioning that the complexity for ESBMC-SS, ESBMC-PS, and ESBMC-PB in a sequential time are linear (\textit{i.e.}, O(n)), that is because each algorithm runs all the possible solutions once.
+In general, it is worth mentioning that the complexity for ESBMC-SS, ESBMC-PS, and ESBMC-PB in a sequential time are linear (\textit{i.e.}, O(n)), that is because each algorithm runs all the possible solutions once.
 However, each execution runs an optimization problem, which is solved by the model checker, that is NP-Hard as described by Arato et al.
 (2003).
-Thus, even a parallel time being considered, including possible overheads in OpenMP, the general complexity is simplified by NP-Hard.}
+Thus, even a parallel time being considered, including possible overheads in OpenMP, the general complexity is simplified by NP-Hard.
 
@@
 The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation.
-Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.
+Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as presented by~\cite{Mann2007}.
 
@@
 
-\textcolor{blue}{Note that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
-Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}
+Note that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved.
+Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.
 
@@
 Each time was measured $3$ times (average taken).
-\textcolor{blue}{Empirical tests performed by the authors demonstrated that a higher number of measurements, for each technique, did not produce significant differences in the experimental results (which were always below 10\% and mostly around 3\%).}
-
-Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB, and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
+Empirical tests performed by the authors demonstrated that a higher number of measurements, for each technique, did not produce significant differences in the experimental results (which were always below 10\% and mostly around 3\%).
+
+Based on the mean, standard deviation and tolerance interval to each set of time sample, it was obtained a confidence level of $91.7$\% to ESBMC (sequential, SS, PB, and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA.
 A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds.
 A memory-out (MO) occurs when the tool reaches $15$ GB of memory.
-\textcolor{blue}{The TO was defined based on previous empirical tests as well, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
+The TO was defined based on previous empirical tests as well, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.
 
@@
 \midrule
-\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as \textcolor{blue}{presented by}~\cite{Guthaus2001}\\
+\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as presented by~\cite{Guthaus2001}\\
 \hline
 \verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
-\vspace{0.8 mm} Routine to insert values in Patricia Tree, as \textcolor{blue}{presented by} ~\cite{Guthaus2001}\\
+\vspace{0.8 mm} Routine to insert values in Patricia Tree, as presented by ~\cite{Guthaus2001}\\
 \hline
-\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as \textcolor{blue}{presented by}~\cite{Guthaus2001}\\
+\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as presented by~\cite{Guthaus2001}\\
 \hline
@@
 Software and communication costs are time dimensional, {\it i.e.}, software execution time and communication time; and hardware costs represent the occupied area.
-The first three benchmarks are extracted from MiBench, as \textcolor{blue}{presented by}~\cite{Guthaus2001}.
-\textcolor{blue}{The fuzzy benchmark was created and presented by}~\cite{Mann2007} and is a significantly large benchmark.
-\textcolor{blue}{And also from ~\cite{Mann2007}, were used RC$6$ and Mars as very complex benchmarks to test the limits of each technique.
-Note that we used the same number (and types) of benchmarks that were previously used in the literature, in order to enable a fair comparison to other existing techniques presented in this study.}
+The first three benchmarks are extracted from MiBench, as presented by~\cite{Guthaus2001}.
+The fuzzy benchmark was created and presented by~\cite{Mann2007} and is a significantly large benchmark.
+And also from ~\cite{Mann2007}, were used RC$6$ and Mars as very complex benchmarks to test the limits of each technique.
+Note that we used the same number (and types) of benchmarks that were previously used in the literature, in order to enable a fair comparison to other existing techniques presented in this study.
 
@@
 Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC-SS, ESBMC-PS, ESBMC-PB, ESBMC-$\nu$Z) tools.
-\textcolor{blue}{The number of nodes, edges, and the initial software cost (S0) are given to each benchmark.
+The number of nodes, edges, and the initial software cost (S0) are given to each benchmark.
 Hp and Sp represent the results of partitioning process for each technique, {\it i.e.}, the optimized value of partitioned hardware and software.
 T(s) means the average time taken from the experiments.
-Particularly about GA there is an additional row informing how far from the exact answer is the found solution.}
+Particularly about GA there is an additional row informing how far from the exact answer is the found solution.
 
@@
 
-\textcolor{blue}{Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware.
+Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware.
 In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are (heuristically) optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does.
-As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion problem.}
+As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion problem.
 
@@
 The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
-\textcolor{blue}{although more benchmarks with similar complexity to clustering should be included in future work for a more precise conclusion.
+although more benchmarks with similar complexity to clustering should be included in future work for a more precise conclusion.
 Note, however, that more than $150$ nodes lead to TO and MO.
-ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.}
+ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.
 
@@
 Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP.
-\textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4,3 to 7,5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared to GA).} ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
+Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is 4.3 to 7.5 times faster than ILP, faster than any other ESBMC approach (until 462 times faster) and its result is precise (when compared to GA).
+ESBMC-PB is a viable alternative for a number of nodes lower than $150$.
 GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.
@@
 If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler.
-\textcolor{blue}{ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
-Similarly, it is also possible to use free GA and ILP libraries (BSD-Style and MIT licenses) for different programing languages.}
+ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free.
+Similarly, it is also possible to use free GA and ILP libraries (BSD-Style and MIT licenses) for different programing languages.
 
@@
 In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time.
-\textcolor{blue}{And so that the limits of the techniques can be defined more precisely, new benchmarks will be included in future work, with their complexity ranging between 100 and 400 nodes.
-Furthermore, more complex types of architectures of HW-SW model will be addressed, including more than one CPU, and the assumption of just singled-threaded program execution will be extended to multiprogramming and multiprocessing (second generation of co-design).}
+And so that the limits of the techniques can be defined more precisely, new benchmarks will be included in future work, with their complexity ranging between 100 and 400 nodes.
+Furthermore, more complex types of architectures of HW-SW model will be addressed, including more than one CPU, and the assumption of just singled-threaded program execution will be extended to multiprogramming and multiprocessing (second generation of co-design).
 
@@
 \bibitem[\protect\citeauthoryear{Boucheneb and Hadjidj}{2006}]{Boucheneb2006}
-\textcolor{blue}{Boucheneb, H.
-and Hadjidj, R.
-(2006) 'Using inclusion abstraction to construct Atomic State Class Graphs for Time Petri Nets', {\it Int.
-J.
-of Embedded Systems}, Vol.
-2, N.
-1/2, pp.128--139.}
+Boucheneb, H. and Hadjidj, R. (2006) 'Using inclusion abstraction to construct Atomic State Class Graphs for Time Petri Nets', {\it Int. J. of Embedded Systems}, Vol. 2, N. 1/2, pp.128--139.
 
@@
 \bibitem[\protect\citeauthoryear{Hau and Khalil-Hani}{2009}]{Hau2009}
-\textcolor{blue}{Hau, Y.W.
+Hau, Y.W.
 and Khalil-Hani, M.
@@
 of Information and Communication Technology}, 2009, Vol.2, N.
-1/2, pp.108--119.}
+1/2, pp.108--119.
 
@@
 \bibitem[\protect\citeauthoryear{Jan \textit{et al.}}{2005}]{Jan2005}
-\textcolor{blue}{Jan, K.
+Jan, K.
 Y., Fan, C.
@@
 1/2, pp.
-23--32.}
+23--32.
 
@@
 \bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
-\textcolor{blue}{Mittal, S., and Vetter, J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Computing Surveys}, Vol. 47, Issue 4, pp. 69:1--69:35.}
+Mittal, S., and Vetter, J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Computing Surveys}, Vol. 47, Issue 4, pp. 69:1--69:35.
 
